### 2021-06-11 paper/manuscript.tex
Include paper to repository

%% This is file `jasr-template.tex',
%% 
%% Copyright 2019-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references
%%
%% $Id: jasr-template.tex 188 2020-11-16 05:18:23Z rishi $
%%
%% Use the option review to obtain double line spacing
%\documentclass[times,review,preprint,authoryear]{elsarticle}

%% Use the options `twocolumn,final' to obtain the final layout
%% Use longtitle option to break abstract to multiple pages if overfull.
%% For Review pdf (With double line spacing)
%\documentclass[times,twocolumn,review]{elsarticle}
%% For abstracts longer than one page.
%\documentclass[times,twocolumn,review,longtitle]{elsarticle}
%% For Review pdf without preprint line
%\documentclass[times,twocolumn,review,nopreprintline]{elsarticle}
%% Final pdf
\documentclass[times,twocolumn,final,authoryear]{elsarticle}
%%
%\documentclass[times,twocolumn,final,longtitle]{elsarticle}
%%

%%
%% Stylefile to load JASR template
\usepackage{jasr}
\usepackage{framed,multirow}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{latexsym}

%% For line numbers
%\usepackage[switch]{lineno}

% Following three lines are needed for this document.
% If you are not loading colors or url, then these are
% not required.
\usepackage{url}
\usepackage{xcolor}
\usepackage{multirow}
\definecolor{newcolor}{rgb}{.8,.349,.1}

\usepackage[citebordercolor=white]{hyperref}

\journal{Advances in Space Research}

\begin{document}

\verso{Given-name Surname \textit{etal}}

\begin{frontmatter}

\title{Ionospheric Disturbances in Mexican Territory Produced by Objects Entering the Athmosphere from Space \tnoteref{tnote1}}%
%\tnotetext[tnote1]{This is an example for title footnote coding.}

\author[1]{Jorge \snm{Tarango-Yong}\corref{cor1}}
\cortext[cor1]{Tel.: +52-443-476-5525;  \\
  email: jorge.tarango@comunidad.unam.mx
}

\author[1]{Mario \snm{Rodriguez-Martinez}\corref{cor2}}
\cortext[cor2]{email: m.rodriguez@enesmorelia.unam.mx}
%\fntext[fn1]{This is author footnote for second author.}
\author[1]{Raul \snm{Gutierrez}\fnref{fn1}}
%% Third author's email
%\ead{author3@author.com}
%\author[2]{Given-name4 \snm{Surname4}}

\address[1]{Escuela Nacional de Estudios Superiores, UNAM, campus Morelia, Antigua Carretera a P\'atzcuaro No. 8701
Col. Ex Hacienda de San Jos\'e de la Huerta, Morelia, Michoac\'an, 58190, M\'exico}
%\address[2]{}

\received{1 May 2013}
\finalform{10 May 2013}
\accepted{13 May 2013}
\availableonline{15 May 2013}
\communicated{S. Sarkar}

\begin{abstract}
%%%
Please type your abstract here, and the rest of the text, figures,
tables, equations etc. in the main body. Please do not modify LaTeX\ 
commands unless you need to modify them and know how to do it.
%%%%
\end{abstract}

\begin{keyword}
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC 41A05\sep 41A10\sep 65D05\sep 65D17
%% Keywords
\KWD Space Sciences\sep Atmosphere%\sep Keyword3
\end{keyword}

\end{frontmatter}

%% For linenumbers
%\linenumbers

%% main text
\section{Introduction}
\label{sec1}
Please use \verb+elsarticle.cls+ for typesetting your paper. Additionally,
make sure not to remove the package \verb+jasr.sty+ already included in the
preamble:
%\begin{verbatim} 
%  \usepackage{jasr}
%\end{verbatim}

Make sure to have the file \verb+model5-names.bst+ to produce the references in
the correct format.

Any instructions relevant to the \verb+elsarticle.cls+ are
applicable here as well. See the online instruction available at:
\makeatletter
\if@twocolumn
\begin{verbatim}
 https://support.stmdocs.in/wiki/
 index.php?title=Elsarticle.cls
\end{verbatim}
\else
\begin{verbatim}
 https://support.stmdocs.in/wiki/index.php?title=Elsarticle.cls
 \end{verbatim}
\fi
\makeatother

Following commands are defined for this journal which are not in
\verb+elsarticle.cls+. 
\begin{verbatim}
  \received{}
  \finalform{}
  \accepted{}
  \availableonline{}
  \communicated{}
\end{verbatim}

\subsection{Subsection}
This is only a \LaTeX\ template if you need one. 
See the detailed guidelines for manuscript preparation 
and submission at:
\begin{verbatim}
https://ees.elsevier.com/asr
\end{verbatim}

\section{Meteors Database}

We selected a sample of meteors which were observed in mexican territory from the Geostationary Lightning Mapper \citep{GOODMAN:2013}. The sample was selected in such way we chose the most probable obects to be detected by GPS sources in mexican territory:

\begin{itemize}
    \item The objects were detected inside mexican territory.
    \item The objects were detected by both satellites GOES 16 and GOES 17 (stereo)
    \item The detection has been assigned a high confidence ratio.
\end{itemize}

 For the selected sample, shown in , we obtained RINEX data from the TLALOCNet and UNAVCO network databases \citep{Cabral-Cano:2018} to study potential alterations in the ionospehre due to the presence of the passing meteor in the day the meteor was reported. The list of the sample meteors is shown in table \ref{tab:table-meteors}.

\begin{table*}
\centering
\caption{List of meteors passing through Mexico.}
\label{tab:table-meteors}
\begin{tabular}{|r|r|r|r|r|r|}
\hline
ID & Fecha & Start Time (UT)  & Duration (seconds) & Latitud & Longitud \\
\hline
01 & 23-05-2019 & 16:36:18 & $0.197\pm 0.0000$ & $24.30 \pm 0.000$ & $-101.60 \pm 0.849$\\
02 & 18-07-2019 & 14:30:30 & $0.058\pm 0.0000$ & $27.20 \pm 0.000$ & $-103.15 \pm 0.778$\\
03 & 10-08-2019 & 11:18:48 & $0.199\pm 0.0757$ & $21.50 \pm 0.000$ & $-102.50  \pm 0.849$\\
04 & 03-10-2019 & 07:55:33 & $0.106\pm 0.0297$ & $25.65 \pm 0.071$ & $-96.25 \pm   0.778$\\
05 & 09-10-2019 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$\\
06 & 12-10-2019 & 11:12:27 & $0.006\pm 0.0000$ & $28.8 \pm 0.000$ & $-111.3 \pm 0.000$\\
07 & 16-11-2019 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$\\
08 & 17-11-2019 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$\\
09 & 19-11-2019 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm  1.131$\\
10 & 26-11-2019 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$\\
11 & 04-12-2019 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$\\
12 & 15-12-2019 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$\\
13 & 29-12-2019 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$\\
14 & 03-01-2020 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$\\
15 & 06-01-2020 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$\\
16 & 15-01-2020 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$\\
17 & 12-02-2020 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$\\
18 & 03-03-2020 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm 0.636$\\
19 & 31-03-2020 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
20 & 08-04-2020 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$\\
21 & 18-04-2020 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$\\
22 & 20-04-2020 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$\\
23 & 25-04-2020 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$\\
24 & 28-04-2020 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
25 & 08-05-2020 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$\\
26 & 15-07-2020 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$\\
27 & 07-08-2020 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$\\
28 & 13-09-2020 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$\\
29 & 30-09-2020 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
30 & 16-11-2020 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
31 & 17-11-2020 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$\\
32 & 19-12-2020 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$\\
33 & 23-12-2020 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$\\
34 & 29-12-2020 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$\\
35 & 31-03-2021 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$\\\hline
\end{tabular}
\end{table*}

%\begin{table*}
%\centering
%\caption{List of meteors passing through Mexico.}
%\label{tab:table-meteors}
%\begin{tabular}{|l|l|l|l|l|l|}
%\hline
%\multirow{2}{2.5cm}{Date (yyyy-mm-dd)} & \multirow{2}{*}{Time (UT)} & \multirow{2}{*}{Latitude} & %\multirow{2}{*}{Longitude} & \multirow{2}{*}{$\Delta t$ (seconds)}   & \multirow{2}{*}{Location}\\
% & & & &  & \\
%\hline
%2015-07-19 & 07:06:26 & 20.6 & -87.6 & 7.5 & Quintana Roo, Mx. \\
%\hline
%2017-07-31 & 22:01:34 & 24.8 & -118.6 & 1.1 & Pacific Ocean, Near Baja California, Mx. \\
%\hline
%2017-10-01 & 12:43:53 & 36.2 & -111.4 & 0.1 & Arizona, USA \\
%\hline
%2017-11-15 & 03:26:46 & 34.2 & -111.4 & 0.08 & Arizona, USA \\
%\hline
%2019-02-01 & 18:17:10 & 22.5 & -83.8 & 2.3 & La Habana, Cuba \\
%\hline
%2020-02-19 & 2:10 & 19.68 & -101.2 & 3.5 & Michoac\'an, Mx. \\
%\hline
%2020-04-28 & 05:43:17 & 19.9 & -110.2 & 0.8 &  Pacific Ocean, near Colima, Mx. \\
%\hline
%2020-10-17 & 03:14:23 & 26.1 & -100.1 & 0.04 & Nuevo Le\'on, Mx. \\
%\hline 
%2020-11-20 & 2:57:10 & 26.5 & -98.7 & 0.01 & Tamaulipas, Mx.\\
%\hline
%\end{tabular}
%\end{table*}

%Final idea: use GOPI software to get the vTEC data from the day of each event and the previous days.

\section{Ionospheric background}

\section{How to include a figure?}
Change the file name of the figure below with your own 
figure. And remember to change the figure caption too!
\begin{verbatim}
\begin{figure}
  \centering
  \includegraphics[scale=0.5]{fig01}
  \caption{Write the figure caption here.}
  \label{fig:pendulum}
\end{figure}
\end{verbatim}

%\begin{figure}
%\centering
%\includegraphics[scale=0.5]{fig01.pdf}
%\caption{Write the figure caption here.}
%\label{fig:pendulum}
%\end{figure}

\subsection{And a table?}
Just replace the text/values in the template table below 
with your own. You can change the number of 
lines/rows as necessary.

%\begin{table*}
%\centering
%\caption{Title of the table should be at the top}
%\begin{tabular}{|l|l|l|l|}
%\hline
%Column Name1    & Column Name2 & Column Name3 & Column Name4 \\
%\hline
%Parameter Name1 & Value        & Value        & Value        \\
%\hline
%Parameter Name2 & Value        & Value        & Value        \\
%\hline
%Parameter Name3 & Value        & Value        & Value        \\
%\hline
%\end{tabular}
%\end{table*}

\subsection{Equations}
Conventionally, in mathematical equations, variables and
anything that represents a value appear in italics. 
All equations should be numbered for easy referencing. 
The number should appear at the right margin.
\begin{eqnarray}
S'_{\mathrm{pg}} = \frac{S_{\mathrm{pg}} - \mathrm{min}(S_{\mathrm{pG}})}
  {\mathrm{max}(S_{\mathrm{pG}} - \mathrm{min}(S_{\mathrm{pG}}))}
\end{eqnarray}
In mathematical expressions 
in running text "/" should be used
for division (not a horizontal line).

\section{Citations}
%Citations in the text can be made using\\[6pt]
%\verb+\citet{NewmanGirvan2004}+\\[6pt]
%for citation in running text like in 
%\citet{NewmanGirvan2004} or using\\[6pt]
%\verb+\citep{Vehlowetal2013,NewmanGirvan2004}+\\[6pt]
%for citation within parentheses like in 
%\citep{Vehlowetal2013,NewmanGirvan2004}.

%Please use the actual \verb+\cite+ command in the text.
%Also, please double-check the \verb+\citep+ command.

\section{Reference style}
You can include the references in the main text file in \LaTeX
format. Alternately, you can include a separate bibliography
file (refs.bib in this example) and run the following set of 
commands:
\begin{verbatim}
==================

pdflatex myfile.tex

bibtex myfile (no extension in this line!)

pdflatex myfile.tex

pdflatex myfile.tex

==================
\end{verbatim}

\section{A sample entry in the bibliography file}
%{\fontsize{7.5pt}{9.6pt}\selectfont
\begin{verbatim}
==================

@ARTICLE{NewmanGirvan2004,
  author  = {Newman, M. E. J. and Girvan, M.},
  title   = {Finding and evaluating community 
               structure in networks},
  journal = {Phys. Rev. E.},
  volume  = {69},
  number  = {21},
  year    = {2004},
  pages   = {026113}
}

==================
\end{verbatim}
%}

\section{Acknowledgments}

The RINEX data used in this paper were obtained from the Trans-boundary, Land and Atmosphere Long-term Observational and Collaborative Network (TLALOCNet, \citet{Cabral-Cano:2018}), operated by the Servicio de Geodesia Satelital (SGS) at the Instituto de Geofísica-Universidad Nacional Autónoma de México (UNAM) in collaboration with UNAVCO Inc.

We are deeply grateful to all personnel from SGS, SSN and UNAVCO for station installation, maintenance, data acquisition, IT support and data curation and distribution for these networks and in particular to the following individuals and institutions, and those whose hard field work and resourcefulness were central to the success of this project: Bill Douglass, Neal Lord and Bill Unger at UW-Madison, Oscar Diaz-Molina and Luis Salazar-Tlaczani at SGS, John Galetzka, Adam Wallace, Shawn Lawrence, Sean Malloy and Chris Walls at UNAVCO, Jesus Pacheco-Martínez at Universidad Autónoma de Aguascalientes, Bertha Marquez-Azúa and personnel at the Universidad de Guadalajara at campus Guadalajara, Mascota and Ameca, Protección Civil de Jalisco, Universidad de Colima at campus Colima and campus El Naranjo and Centro de Geociencias, Centro de Ciencias de la Atmosfera Instituto de Biología Estacion Chamela at UNAM.
TLALOCNet, SSN-TLALOCNet and other GPS related operations from SGS are supported by CONACyT projects 253760, 256012 and 2017-01-5955, UNAM-PAPIIT projects IN104213, IN111509, IN109315-3, IN104818-3, NSF grant 2025104, NASA-ROSES grant NNX12AQ08G and supplemental support from UNAM-Instituto de Geofísica. UNAVCO's initial support for TLALOCNet (some of its stations now part of the GAGE Facility-NOTA) was performed under EAR-1338091 and is currently supported by NSF and NASA under NSF Cooperative Agreement EAR-1724794.

Also we are grateful with the Direcci\'on General de Asuntos Acad\'emicos (DGAPA) of the Universidad Nacional Aut\'onoma de M\'exico and the Programa de Becas Posdoctorales for funding this project.

%% Bibliography
%% Author year style
\bibliographystyle{model5-names}
\biboptions{authoryear}
\bibliography{bibliography}

\end{document}

%%

### 2021-06-11 Kp-index.py

@@ -83,7 +83,7 @@ x = np.arange(len(Kp))
 bar = plt.bar(x, Kp, width=0.5)
 
 ## Set graph limits
-plt.xlim(0, 24)
+plt.xlim(-0.5, 24)
 plt.ylim(0, 9)
 
 ## Set ticks in both axis

### 2021-06-11 plot_vTEC.py

@@ -88,7 +88,7 @@ for f, g in zip(load_dirs, load_std):
 
 ax = plt.gca()
 ax.set_aspect('equal', adjustable='box')
-plt.legend()
+#plt.legend()
 cbar = plt.colorbar()
 cbar.set_label("vTEC (TECU)")
 

### 2021-06-19 paper/manuscript.tex
Improve vTeC code, insert Kp index graphs and work with paper
- Update Journal
- Insert Kp index graphs
- Normalize colormap in vTEC maps
- Few advances in paper
- Working in make vTEC maps for all events

@@
 \label{sec1}
-Please use \verb+elsarticle.cls+ for typesetting your paper. Additionally,
-make sure not to remove the package \verb+jasr.sty+ already included in the
-preamble:
+%Please use \verb+elsarticle.cls+ for typesetting your paper. Additionally,
+%make sure not to remove the package \verb+jasr.sty+ already included in the
+%preamble:
 %\begin{verbatim} 
@@
 
-Make sure to have the file \verb+model5-names.bst+ to produce the references in
-the correct format.
+%Make sure to have the file \verb+model5-names.bst+ to produce the references in
+%the correct format.
 
-Any instructions relevant to the \verb+elsarticle.cls+ are
-applicable here as well. See the online instruction available at:
-\makeatletter
-\if@twocolumn
-\begin{verbatim}
- https://support.stmdocs.in/wiki/
- index.php?title=Elsarticle.cls
-\end{verbatim}
-\else
-\begin{verbatim}
- https://support.stmdocs.in/wiki/index.php?title=Elsarticle.cls
- \end{verbatim}
-\fi
-\makeatother
+%Any instructions relevant to the \verb+elsarticle.cls+ are
+%applicable here as well. See the online instruction available at:
+%\makeatletter
+%\if@twocolumn
+%\begin{verbatim}
+% https://support.stmdocs.in/wiki/
+% index.php?title=Elsarticle.cls
+%\end{verbatim}
+%\else
+%\begin{verbatim}
+% https://support.stmdocs.in/wiki/index.php?title=Elsarticle.cls
+% \end{verbatim}
+%\fi
+%\makeatother
 
-Following commands are defined for this journal which are not in
-\verb+elsarticle.cls+. 
-\begin{verbatim}
-  \received{}
-  \finalform{}
-  \accepted{}
-  \availableonline{}
-  \communicated{}
-\end{verbatim}
+%Following commands are defined for this journal which are not in
+%\verb+elsarticle.cls+. 
+%\begin{verbatim}
+%  \received{}
+%  \finalform{}
+%  \accepted{}
+%  \availableonline{}
+%  \communicated{}
+%\end{verbatim}
 
-\subsection{Subsection}
-This is only a \LaTeX\ template if you need one. 
-See the detailed guidelines for manuscript preparation 
-and submission at:
-\begin{verbatim}
-https://ees.elsevier.com/asr
-\end{verbatim}
+%\subsection{Subsection}
+%This is only a \LaTeX\ template if you need one. 
+%See the detailed guidelines for manuscript preparation 
+%and submission at:
+%\begin{verbatim}
+%https://ees.elsevier.com/asr
+%\end{verbatim}
 
@@
 We selected a sample of meteors which were observed in mexican territory from the Geostationary Lightning Mapper \citep{GOODMAN:2013}.
-The sample was selected in such way we chose the most probable obects to be detected by GPS sources in mexican territory:
+We used the interactive database available at \url{https://neo-bolide.ndc.nasa.gov/#/} to get the events positions presented in this section.
+The sample was selected in such way we chose the most probable objects to be detected by GPS sources in mexican territory:
 
@@
 
- For the selected sample, shown in , we obtained RINEX data from the TLALOCNet and UNAVCO network databases \citep{Cabral-Cano:2018} to study potential alterations in the ionospehre due to the presence of the passing meteor in the day the meteor was reported.
+ For the selected sample, we obtained RINEX data from the TlalocNet \citep{Cabral-Cano:2018} and UNAVCO network databases to study potential alterations in the ionospehre due to the presence of the passing meteor at the day the meteor was reported.
 The list of the sample meteors is shown in table \ref{tab:table-meteors}.
+The events are in chronological order.
+The reported duration, latitude and longitude correspond to the mean between measurements from satellites GOES-16 and GOES 17; in the same way, the uncertainties correspond to the standard deviation.
+Also their respective positions are available in figure \ref{fig:meteors-map}, where each label correspond to the ID (first column) of table \ref{tab:table-meteors}.
 
@@
   \centering
-\caption{List of meteors passing through Mexico.}
+  \caption{List of meteors passing through Mexico.
+The events are listed in chronological order.
+The listed duration, latitude and longitude correspond to the mean of the measurements of both GOES satellites.
+The uncertainties correspond to the respecting mean deviation.}
 \label{tab:table-meteors}
@@
 \hline
-ID & Fecha & Start Time (UT)  & Duration (seconds) & Latitud & Longitud \\
+ID & Date of event & Start Time (UT)  & Duration (seconds) & Latitude (deg) & Longitude (deg)\\
 \hline
-01 & 23-05-2019 & 16:36:18 & $0.197\pm 0.0000$ & $24.30 \pm 0.000$ & $-101.60 \pm 0.849$\\
-02 & 18-07-2019 & 14:30:30 & $0.058\pm 0.0000$ & $27.20 \pm 0.000$ & $-103.15 \pm 0.778$\\
-03 & 10-08-2019 & 11:18:48 & $0.199\pm 0.0757$ & $21.50 \pm 0.000$ & $-102.50  \pm 0.849$\\
-04 & 03-10-2019 & 07:55:33 & $0.106\pm 0.0297$ & $25.65 \pm 0.071$ & $-96.25 \pm   0.778$\\
-05 & 09-10-2019 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$\\
-06 & 12-10-2019 & 11:12:27 & $0.006\pm 0.0000$ & $28.8 \pm 0.000$ & $-111.3 \pm 0.000$\\
-07 & 16-11-2019 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$\\
-08 & 17-11-2019 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$\\
-09 & 19-11-2019 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm  1.131$\\
-10 & 26-11-2019 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$\\
-11 & 04-12-2019 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$\\
-12 & 15-12-2019 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$\\
-13 & 29-12-2019 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$\\
-14 & 03-01-2020 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$\\
-15 & 06-01-2020 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$\\
-16 & 15-01-2020 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$\\
-17 & 12-02-2020 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$\\
-18 & 03-03-2020 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm 0.636$\\
-19 & 31-03-2020 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
-20 & 08-04-2020 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$\\
-21 & 18-04-2020 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$\\
-22 & 20-04-2020 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$\\
-23 & 25-04-2020 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$\\
-24 & 28-04-2020 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
-25 & 08-05-2020 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$\\
-26 & 15-07-2020 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$\\
-27 & 07-08-2020 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$\\
-28 & 13-09-2020 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$\\
-29 & 30-09-2020 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
-30 & 16-11-2020 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
-31 & 17-11-2020 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$\\
-32 & 19-12-2020 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$\\
-33 & 23-12-2020 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$\\
-34 & 29-12-2020 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$\\
-35 & 31-03-2021 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$\\\hline
+01 & 2019-05-23 & 16:36:18 & $0.197\pm 0.0000$ & $24.30 \pm 0.000$ & $-101.60 \pm 0.849$\\
+02 & 2019-07-18 & 14:30:30 & $0.058\pm 0.0000$ & $27.20 \pm 0.000$ & $-103.15 \pm 0.778$\\
+03 & 2019-08-10 & 11:18:48 & $0.199\pm 0.0757$ & $21.50 \pm 0.000$ & $-102.50  \pm 0.849$\\
+04 & 2019-10-03 & 07:55:33 & $0.106\pm 0.0297$ & $25.65 \pm 0.071$ & $-96.25 \pm   0.778$\\
+05 & 2019-10-09 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$\\
+06 & 2019-10-12 & 11:12:27 & $0.006\pm 0.0000$ & $28.8 \pm 0.000$ & $-111.3 \pm 0.000$\\
+07 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$\\
+08 & 2019-11-17 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$\\
+09 & 2019-11-19 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm  1.131$\\
+10 & 2019-11-26 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$\\
+11 & 2019-12-04 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$\\
+12 & 2019-12-15 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$\\
+13 & 2019-12-29 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$\\
+14 & 2020-01-03 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$\\
+15 & 2020-01-06 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$\\
+16 & 2020-01-15 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$\\
+17 & 2020-02-12 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$\\
+18 & 2020-03-03 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm 0.636$\\
+19 & 2020-03-31 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
+20 & 2020-04-08 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$\\
+21 & 2020-04-18 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$\\
+22 & 2020-04-20 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$\\
+23 & 2020-04-25 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$\\
+24 & 2020-04-28 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
+25 & 2020-05-08 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$\\
+26 & 2020-07-15 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$\\
+27 & 2020-08-07 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$\\
+28 & 2020-09-13 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$\\
+29 & 2020-09-30 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
+30 & 2020-11-16 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
+31 & 2020-11-17 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$\\
+32 & 2020-12-19 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$\\
+33 & 2020-12-23 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$\\
+34 & 2020-12-29 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$\\
+35 & 2021-03-31 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$\\\hline
 \end{tabular}
@@
 
-%\begin{table*}
-%\centering
-%\caption{List of meteors passing through Mexico.}
-%\label{tab:table-meteors}
-%\begin{tabular}{|l|l|l|l|l|l|}
-%\hline
-%\multirow{2}{2.5cm}{Date (yyyy-mm-dd)} & \multirow{2}{*}{Time (UT)} & \multirow{2}{*}{Latitude} & %\multirow{2}{*}{Longitude} & \multirow{2}{*}{$\Delta t$ (seconds)}   & \multirow{2}{*}{Location}\\
-% & & & &  & \\
-%\hline
-%2015-07-19 & 07:06:26 & 20.6 & -87.6 & 7.5 & Quintana Roo, Mx. \\
-%\hline
-%2017-07-31 & 22:01:34 & 24.8 & -118.6 & 1.1 & Pacific Ocean, Near Baja California, Mx. \\
-%\hline
-%2017-10-01 & 12:43:53 & 36.2 & -111.4 & 0.1 & Arizona, USA \\
-%\hline
-%2017-11-15 & 03:26:46 & 34.2 & -111.4 & 0.08 & Arizona, USA \\
-%\hline
-%2019-02-01 & 18:17:10 & 22.5 & -83.8 & 2.3 & La Habana, Cuba \\
-%\hline
-%2020-02-19 & 2:10 & 19.68 & -101.2 & 3.5 & Michoac\'an, Mx. \\
-%\hline
-%2020-04-28 & 05:43:17 & 19.9 & -110.2 & 0.8 &  Pacific Ocean, near Colima, Mx. \\
-%\hline
-%2020-10-17 & 03:14:23 & 26.1 & -100.1 & 0.04 & Nuevo Le\'on, Mx. \\
-%\hline 
-%2020-11-20 & 2:57:10 & 26.5 & -98.7 & 0.01 & Tamaulipas, Mx.\\
-%\hline
-%\end{tabular}
-%\end{table*}
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{../meteors_map}
+  \caption{Positions of events from table \ref{tab:table-meteors}. The label of each point correspond to the ID (first column) of the referred table.}
+  \label{fig:meteors-map}
+\end{figure}
 
@@
 
-\section{Ionospheric background}
+\section{Ionospheric background and vTEC maps}
 
-\section{How to include a figure?}
-Change the file name of the figure below with your own 
-figure. And remember to change the figure caption too!
-\begin{verbatim}
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.5]{fig01}
-  \caption{Write the figure caption here.}
-  \label{fig:pendulum}
-\end{figure}
-\end{verbatim}
+\section{Frecuency Analysis}
+
+\section{Discussion}
+
+%\section{How to include a figure?}
+%Change the file name of the figure below with your own 
+%figure. And remember to change the figure caption too!
+%\begin{verbatim}
+%\begin{figure}
+%  \centering
+%  \includegraphics[scale=0.5]{fig01}
+%  \caption{Write the figure caption here.}
+%  \label{fig:pendulum}
+%\end{figure}
+%\end{verbatim}
 
@@
 
-\subsection{And a table?}
-Just replace the text/values in the template table below 
-with your own. You can change the number of 
-lines/rows as necessary.
+%\subsection{And a table?}
+%Just replace the text/values in the template table below 
+%with your own. You can change the number of 
+%lines/rows as necessary.
 
@@
 
-\subsection{Equations}
-Conventionally, in mathematical equations, variables and
-anything that represents a value appear in italics. 
-All equations should be numbered for easy referencing. 
-The number should appear at the right margin.
-\begin{eqnarray}
-S'_{\mathrm{pg}} = \frac{S_{\mathrm{pg}} - \mathrm{min}(S_{\mathrm{pG}})}
-  {\mathrm{max}(S_{\mathrm{pG}} - \mathrm{min}(S_{\mathrm{pG}}))}
-\end{eqnarray}
-In mathematical expressions 
-in running text "/" should be used
-for division (not a horizontal line).
+%\subsection{Equations}
+%Conventionally, in mathematical equations, variables and
+%anything that represents a value appear in italics. 
+%All equations should be numbered for easy referencing. 
+%The number should appear at the right margin.
+%\begin{eqnarray}
+%S'_{\mathrm{pg}} = \frac{S_{\mathrm{pg}} - \mathrm{min}(S_{\mathrm{pG}})}
+%  {\mathrm{max}(S_{\mathrm{pG}} - \mathrm{min}(S_{\mathrm{pG}}))}
+%\end{eqnarray}
+%In mathematical expressions 
+%in running text "/" should be used
+%for division (not a horizontal line).
 
-\section{Citations}
+%\section{Citations}
 %Citations in the text can be made using\\[6pt]
@@
 
-\section{Reference style}
-You can include the references in the main text file in \LaTeX
-format. Alternately, you can include a separate bibliography
-file (refs.bib in this example) and run the following set of 
-commands:
-\begin{verbatim}
-==================
+%\section{Reference style}
+%You can include the references in the main text file in \LaTeX
+%format. Alternately, you can include a separate bibliography
+%file (refs.bib in this example) and run the following set of 
+%commands:
+%\begin{verbatim}
+%==================
 
-pdflatex myfile.tex
+%pdflatex myfile.tex
 
-bibtex myfile (no extension in this line!)
+%bibtex myfile (no extension in this line!)
 
-pdflatex myfile.tex
+%pdflatex myfile.tex
 
-pdflatex myfile.tex
+%pdflatex myfile.tex
 
-==================
-\end{verbatim}
+%==================
+%\end{verbatim}
 
-\section{A sample entry in the bibliography file}
+%\section{A sample entry in the bibliography file}
 %{\fontsize{7.5pt}{9.6pt}\selectfont
-\begin{verbatim}
-==================
+%\begin{verbatim}
+%==================
 
-@ARTICLE{NewmanGirvan2004,
-  author  = {Newman, M. E. J. and Girvan, M.},
-  title   = {Finding and evaluating community 
-               structure in networks},
-  journal = {Phys. Rev. E.},
-  volume  = {69},
-  number  = {21},
-  year    = {2004},
-  pages   = {026113}
-}
+%@ARTICLE{NewmanGirvan2004,
+%  author  = {Newman, M. E. J. and Girvan, M.},
+%  title   = {Finding and evaluating community 
+%               structure in networks},
+%  journal = {Phys. Rev. E.},
+%  volume  = {69},
+%  number  = {21},
+%  year    = {2004},
+%  pages   = {026113}
+%}
 
-==================
-\end{verbatim}
+%==================
+%\end{verbatim}
 %}

### 2021-06-19 Kp-index.py

@@ -114,4 +114,4 @@ plt.title("Estimated Planetary K Index (3 hours data). Begin {} UTC".format(date
 
 # Save graph
 
-plt.savefig(date+" Kp index.pdf")
+plt.savefig("./Kp index/"+date+" Kp index.pdf")

### 2021-06-19 midpoint.py

@@ -1,0 +1,21 @@
+# This class was taken from https://gist.github.com/bdjackson/2215109d2eaa8c68919c
+# Credit: bdjackson
+
+
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import numpy as np
+
+class MidpointNormalize(mpl.colors.Normalize):
+    """
+    class to help renormalize the color scale
+    """
+    def __init__(self, vmin=None, vmax=None, midpoint=None, clip=False):
+        self.midpoint = midpoint
+        mpl.colors.Normalize.__init__(self, vmin, vmax, clip)
+
+    def __call__(self, value, clip=None):
+        # I'm ignoring masked values and all kinds of edge cases to make a
+        # simple example...
+        x, y = [self.vmin, self.midpoint, self.vmax], [0, 0.5, 1]
+        return np.ma.masked_array(np.interp(value, x, y))

### 2021-06-19 plot_vTEC.py

@@ -15,7 +15,9 @@ import argparse
 from astropy.table import Table
 import glob
 import matplotlib.cm as cm
+import matplotlib.colors as colors
 from scipy.interpolate import interp1d
+from midpoint import MidpointNormalize
 
 
 
@@ -78,11 +80,12 @@ for f, g in zip(load_dirs, load_std):
     cmn_time[mask] = cmn_time[mask] + 24.
     mask2 = cmn_time < max(std_time)
     dTEC = obs_tab["Vtec"][mask2] - mean_TEC_int(cmn_time[mask2])
+    norm = MidpointNormalize(midpoint=0)
     plt.plot(float(s_longitude)-360, float(s_latitude), "r*")
     plt.text(float(s_longitude)-360+0.5, float(s_latitude)-0.5, station.upper(),
 	     bbox=dict(boxstyle='round', pad=0.5, fc='blue', alpha=1))
 
-    plt.scatter(obs_tab["Lon"][mask2]-360, obs_tab["Lat"][mask2], s=1, c=dTEC, cmap="plasma",alpha=0.8)
+    plt.scatter(obs_tab["Lon"][mask2]-360, obs_tab["Lat"][mask2], s=1, c=dTEC, cmap="plasma",alpha=0.8, norm=norm)
 
 # Plot settings
 

### 2021-06-20 plot_vTEC.py
Improve vTEC map code
- Include latitude vs time graph
- Correct bugs
- Improve aestetics
- change cmap pallete
- update journal
- Add Wavelets paper to bibliography

@@ -26,7 +26,7 @@ parser = argparse.ArgumentParser(
 
 
 parser.add_argument('--date', type=str, default='2000-01-01',
-		    help='Choose date. Format: yyyy-mm-dd')
+		       help='Choose date. Format: yyyy-mm-dd')
 
 
 
@@ -38,11 +38,11 @@ directory = "./data/"+date
 
 # set figure style
 sns.set_style("whitegrid") 
-sns.mpl.rc("figure", figsize=(10,6))
+#sns.mpl.rc("figure", figsize=(10,6))
 
-# Read shape file of Mexico map
-sf = shp.Reader("map.shp")
-plot_map(sf)
+# Read shape file of Mexico map (deprecated)
+#sf = shp.Reader("map.shp")
+#plot_map(sf)
 
 
 # Load RINEX capabilities
@@ -52,15 +52,20 @@ std_files = glob.glob(directory+"/*.Std")
 load_dirs = [open(rinex_files[i], "r") for i in range(len(rinex_files))]
 load_std = [Table.read(std_files[i], format="ascii") for i in range(len(std_files))]
 
+# Plot vTEC map
+fig = plt.figure()
+ax = fig.add_subplot(1, 2, 1, adjustable="box", aspect="equal")
+ax1 = fig.add_subplot(1, 2, 2, adjustable="box")
+
 # Load and plot event position
 
 load_meteor_pos = Table.read("meteors_database.tab", format="ascii")
 meteor_mask = load_meteor_pos["Fecha"] == date
-plt.plot(load_meteor_pos["Longitud"][meteor_mask], load_meteor_pos["Latitud"][meteor_mask], "ro")
-plt.annotate(date, (load_meteor_pos["Latitud"][meteor_mask], load_meteor_pos["Longitud"][meteor_mask]),
-	     textcoords="offset points", color="w", xytext=(10, 10), ha="center", bbox=dict(boxstyle="round", pad=0.5, fc="r", alpha=0.7))
+ax.plot(load_meteor_pos["Longitud"][meteor_mask], load_meteor_pos["Latitud"][meteor_mask], "mo")
+ax.annotate("Event", (load_meteor_pos["Longitud"][meteor_mask], load_meteor_pos["Latitud"][meteor_mask]),
[…]

### 2021-07-20 paper/manuscript.tex
Last update: Improvement of vTEC maps, some advances to paper and downloaded more data
- vTEC maps now include data from previos and next day
- vTEC maps now include approximated meteor trajectory (extrapolated from GLM data back in time to be visible)
- Trying to report these advances to paper but with little success

@@
 \usepackage{multirow}
+\usepackage{tablefootnote}
 \definecolor{newcolor}{rgb}{.8,.349,.1}
@@
 %\fntext[fn1]{This is author footnote for second author.}
-\author[1]{Raul \snm{Gutierrez}\fnref{fn1}}
+\author[1]{Raul \snm{Guti\'errez-Zalapa}\fnref{fn1}}
 %% Third author's email
@@
 
-\section{Meteors Database}
+\section{Metodology}
+\subsection{Meteors Database}
 
 We selected a sample of meteors which were observed in mexican territory from the Geostationary Lightning Mapper \citep{GOODMAN:2013}.
-We used the interactive database available at \url{https://neo-bolide.ndc.nasa.gov/#/} to get the events positions presented in this section.
-The sample was selected in such way we chose the most probable objects to be detected by GPS sources in mexican territory:
+Orignally this project was designed to detect ligthning activity in earth's athmosphere, but has been proven that also can detect bolides entering the athmosphere.
+The detection comes from two satellites called GOES-16 and GOES-17 orbiting the earth in geostationary orbits.
+We used the interactive database available at \url{https://neo-bolide.ndc.nasa.gov/#/} to get the events positions presented in this section, as well we obtained data about the bolid trajectory detected and energy released.
+The sample was chosen following the next criteria:%selected in such way we chose the most probable objects to be detected by GPS sources in mexican territory and its surroundings:
 
 \begin{itemize}
-    \item The objects were detected inside mexican territory.
+    \item The objects were detected inside mexican territory and its surroundings.
     \item The objects were detected by both satellites GOES 16 and GOES 17 (stereo)
@@
 \end{itemize}
-
- For the selected sample, we obtained RINEX data from the TlalocNet \citep{Cabral-Cano:2018} and UNAVCO network databases to study potential alterations in the ionospehre due to the presence of the passing meteor at the day the meteor was reported.
-The list of the sample meteors is shown in table \ref{tab:table-meteors}.
-The events are in chronological order.
-The reported duration, latitude and longitude correspond to the mean between measurements from satellites GOES-16 and GOES 17; in the same way, the uncertainties correspond to the standard deviation.
-Also their respective positions are available in figure \ref{fig:meteors-map}, where each label correspond to the ID (first column) of table \ref{tab:table-meteors}.
 
@@
 05 & 2019-10-09 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$\\
-06 & 2019-10-12 & 11:12:27 & $0.006\pm 0.0000$ & $28.8 \pm 0.000$ & $-111.3 \pm 0.000$\\
+06\tablefootnote{This object was only detected by GOES-16 satellite} & 2019-10-12 & 11:12:27 & $0.006\pm 0.0000$ & $28.8 \pm 0.000$ & $-111.3 \pm 0.000$\\
 07 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$\\
@@
 
+\subsection{GPS data}
+
+For the selected sample, we obtained RINEX data from the TlalocNet \citep{Cabral-Cano:2018} and UNAVCO network databases to study potential alterations in the ionospehre due to the presence of the passing meteor at the day the meteor was reported.
+For each event, we downloaded data from stations that surrounds the place where the event was detected (usually 3 to 5 stations.
+)The list of the sample meteors is shown in table \ref{tab:table-meteors}.
+The events are in chronological order.
+The reported duration, latitude and longitude correspond to the mean between measurements from satellites GOES-16 and GOES 17; in the same way, the uncertainties correspond to the standard deviation.
+Also their respective positions are available in figure \ref{fig:meteors-map}, where each label correspond to the ID (first column) of table \ref{tab:table-meteors}.
+
+Using the data provided by TlalocNet and UNAVCO, we procceeded to obtain TEC parameters with the GPS\_GOPI software, available at \url{https://seemala.blogspot.com/}.
+This software takes as input the RINEX data (the navigation file is no strictly neccesary), and the outuput consists in in the vTEC and sTEC measurements for the PRNs of the whole day the event occurred, as well as the averaged TEC as function of time.
+We obtained vTEC maps for the events in table (\ref{tab:table-meteors}) and their respective next and previous day.
+
 %Final idea: use GOPI software to get the vTEC data from the day of each event and the previous days.
@@
 \section{Ionospheric background and vTEC maps}
+
+Ionospheric perturbations also can take place due to space weather and geomagnetic storms.
+So, in order to discard such events we investigated the space weather in the day each event occured.
+In figure (name) we present the geomagnetic \textit{Kp} index for some events.
+We discarded events whose Kp index is equal or grater than 4 in the day of the event or shortly before.
+Also we present in figure (name) the vTEC perturbation maps for the same events in a three day series, centered in the event date.
+The estimated meteor trajectory, obtained from the GLM data is presented in black, continous line, while the linear fit to the GOES-16 and GOES-17 data are presented with the red dashed line, and work as boudary errors.
 

### 2021-07-20 plot_vTEC.py

@@ -26,7 +26,7 @@ parser = argparse.ArgumentParser(
 
 
 parser.add_argument('--date', type=str, default='2000-01-01',
-			   help='Choose date. Format: yyyy-mm-dd')
+			       help='Choose date. Format: yyyy-mm-dd')
 
 
 
@@ -35,6 +35,8 @@ date = cmd_args.date
 
 
 directory = "./data/"+date
+p_directory = directory + "/previous/"
+n_directory = directory+ "/next/"
 
 # set figure style
 sns.set_style("whitegrid") 
@@ -52,52 +54,167 @@ std_files = glob.glob(directory+"/*.Std")
 load_dirs = [open(rinex_files[i], "r") for i in range(len(rinex_files))]
 load_std = [Table.read(std_files[i], format="ascii") for i in range(len(std_files))]
 
+rinex_p = glob.glob(p_directory+"*.Cmn")
+std_p = glob.glob(p_directory+"*.Std")
+rinex_n = glob.glob(n_directory+"*.Cmn")
+std_n = glob.glob(n_directory+"*.Std")
+
+load_dir_p = [open(rinex_p[i], "r") for i in range(len(rinex_p))]
+load_std_p = [Table.read(std_p[i], format="ascii") for i in range(len(std_p))]
+load_dir_n = [open(rinex_n[i], "r") for i in range(len(rinex_n))]
+load_std_n = [Table.read(std_n[i], format="ascii") for i in range(len(std_n))]
+
 # Plot vTEC map
 fig = plt.figure()
-ax = fig.add_subplot(1, 2, 1, adjustable="box", aspect="equal")
-ax1 = fig.add_subplot(1, 2, 2, adjustable="box")
+ax = fig.add_subplot(3, 2, 3, adjustable="box", aspect="equal")
+ax1 = fig.add_subplot(3, 2, 4, adjustable="box")
+axp = fig.add_subplot(3, 2, 1, adjustable="box", aspect="equal")
+axp1 = fig.add_subplot(3, 2, 2, adjustable="box")
+axn = fig.add_subplot(3, 2, 5, adjustable="box", aspect="equal")
+axn1 = fig.add_subplot(3, 2, 6, adjustable="box")
 
-# Load and plot event position
+
[…]

### 2021-08-02 paper/appendix.tex
Include radiated energy during meteor path in journal.org table
- Code to estimate total energy from GLM data
- Estimate total radiated energy following Jenniskens et al. 2018

\appendix
% \appendixpage
% \addappheadtotoc

% This is tha appendix, where we may insert detailed mathematical proccedures or other data which may be useful but also will make the main
% text too large so this should be consulted only in case of neccesity

\section{Estimation of distances to meteors}

The distance between the GOES satellite and the meteor, neccesary to estimate the radiated energy is calculated as follows:

\begin{align}
  R = \left|\vec{r}_{GLM} - \vec{r}_{obj} \right|
\end{align}

where $\vec{r}_{GLM}$ is the vector position of the GLM satellite and $\vec{r}_{obj}$ is the vector position of the meteor.

In cartesian coordinates, the distance $R$ is given by:

\begin{align}
  R &= \left((x_{GLM}-x_{obj})^2 + (y_{GLM}-y_{obj})^2 + (z_{GLM}-z_{obj})^2\right)^{1/2} \label{eq:R}\\
\end{align}

The transformation to spherical coordinates is given by:

\begin{align}
  x = r\cos\phi\cos\theta \label{eq:xtoR}\\
  y = r\sin\phi\cos\theta \label{eq:ytoR}\\
  z = r\sin\theta \label{eq:ztoR}
\end{align}

Where $r$ is measured from the center of the earth, $ -180^\circ < phi <= 180^\circ$ represents the longitude; is positive at east of Greenwich meridian, and negative eastwards. $\-90^\circ <= \theta <= 90^\circ$ represents the latitude and is positive at the north of equator and negative southwards.

Substituting the transform (\ref{eq:xtoR} - \ref{eq:ztoR}) into (\ref{eq:R}), using elemental trigonometry and considering both GLM satellites lie into the equator ($\theta_{GLM}=0$) we get:

\begin{align}
  R^2 &= r_{GLM}^2 + r_{obj}^2 - 2r_{GLM}r_{obj}f(\theta_{obj}, \phi_{obj}, \phi_{GLM}) \label{eq:R2}\\
  \mathrm{where:} & f(\theta_{obj}, \phi_{obj}, \phi_{GLM}) = \cos\theta_{obj}\cos\left(\phi_{GLM}-\phi_{obj}\right)
\end{align}

Since $r_{GLM}$ and $r_{obj}$ are measured from the center of the arth ge find that:

\begin{align}
  r_{GLM} &= r_{earth} + h_{GLM} \label{eq:rg}\\
  r_{obj} &= r_{earth} + h_{obj} \label{eq:ro}
\end{align}

Substituting (\ref{eq:rg}, \ref{eq:ro}) into \ref{eq:R2} and considering that $h_{obj} \ll h_{GLM}$ we get:

\begin{align}
  R^2 = 2r_{earth}^2\left(1-f(\theta_{obj}, \phi_{obj}, \phi_{GLM})\right) +2r_{earth}h_{GLM}\left(1-f(\theta_{obj}, \phi_{obj}, \phi_{GLM})\right) + h_{GLM}^2 - 2h_{GLM}h_{obj}f(\theta_{obj}, \phi_{obj}, \phi_{GLM})
\end{align}

\section{Useful databases}

### 2021-08-02 GLM_energy.py

@@ -1,0 +1,55 @@
+import numpy as np
+from astropy.table import Table
+import glob
+
+# The goal of this program is to estimate the total energy and peak energy
+# from GLM data
+
+# Methodology: sum all the values from the energy column of GLM data and also
+# get the maximum value. Both should be outputs of the program
+
+# Get a list of the paths of al GLM data
+
+dates = ["2019-05-23", "2019-07-18", "2019-08-10", "2019-10-03", "2019-10-09", "2019-11-16", "2019-11-17", "2019-11-19", "2019-11-26", "2019-12-04", "2019-12-15", "2019-12-29", "2020-01-03", "2020-01-06", "2020-01-15", "2020-02-12", "2020-03-03", "2020-03-31", "2020-04-08", "2020-04-18", "2020-04-20", "2020-04-25", "2020-04-28", "2020-05-08", "2020-07-15", "2020-08-07", "2020-09-13","2020-09-30", "2020-11-16", "2020-11-17", "2020-12-19","2020-12-23", "2020-12-29", "2021-03-31"]
+
+G16_dirs = [] 
+G17_dirs = []
+root_folder = "./data/"
+common_folder = "/GLM/"
+for date in dates:
+    g16 = glob.glob(root_folder+date+common_folder+"*16*")
+    g17 = glob.glob(root_folder+date+common_folder+"*17*")
+    G16_dirs.append(g16[0])
+    G17_dirs.append(g17[0])
+# initialize output arrays
+g16_total_energy_array = []
+g17_total_energy_array = []
+
+
+#initialize loop for data adquisition
+
+for g16, g17 in zip(G16_dirs, G17_dirs):
+    data16 = open(g16, "r")
+    data17 = open(g17, "r")
+
+    for i in range(10): # skip unneded data
+        data16.readline()
+        data17.readline()
+
+    # gather the table with meteor info
+    g16data = data16.readlines()
+    g17data = data17.readlines()
+
+    g16table = Table.read(g16data, format="ascii")
+    g17table = Table.read(g17data, format="ascii")
+
+    # estimate peak energy and total energy for each satellite
+    g16_total_energy = np.sum(g16table["energy (joules)"])
+    g16_total_energy_array.append(g16_total_energy)
+    g17_total_energy = np.sum(g17table["energy (joules)"])
+    g17_total_energy_array.append(g17_total_energy)
+
+
[…]

### 2021-08-10 paper/manuscript.tex
Finished filling out GPS stations table with:
- GPS stations names
- Location
- Citations and references

@@
 \usepackage{multirow}
-\usepackage{tablefootnote}
+%\usepackage{tablefootnote}
 \definecolor{newcolor}{rgb}{.8,.349,.1}
@@
 \usepackage[citebordercolor=white]{hyperref}
-
+\usepackage{rotating}
+\usepackage{pdflscape}
+\usepackage{longtable}
 \journal{Advances in Space Research}
@@
 \label{tab:table-meteors}
-\begin{tabular}{|r|r|r|r|r|r|}
+\begin{tabular}{rrrrrr}
 \hline
@@
 05 & 2019-10-09 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$\\
-06\tablefootnote{This object was only detected by GOES-16 satellite} & 2019-10-12 & 11:12:27 & $0.006\pm 0.0000$ & $28.8 \pm 0.000$ & $-111.3 \pm 0.000$\\
-07 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$\\
-08 & 2019-11-17 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$\\
-09 & 2019-11-19 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm  1.131$\\
-10 & 2019-11-26 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$\\
-11 & 2019-12-04 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$\\
-12 & 2019-12-15 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$\\
-13 & 2019-12-29 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$\\
-14 & 2020-01-03 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$\\
-15 & 2020-01-06 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$\\
-16 & 2020-01-15 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$\\
-17 & 2020-02-12 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$\\
-18 & 2020-03-03 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm 0.636$\\
-19 & 2020-03-31 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
-20 & 2020-04-08 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$\\
-21 & 2020-04-18 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$\\
-22 & 2020-04-20 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$\\
-23 & 2020-04-25 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$\\
-24 & 2020-04-28 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
-25 & 2020-05-08 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$\\
-26 & 2020-07-15 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$\\
-27 & 2020-08-07 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$\\
-28 & 2020-09-13 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$\\
-29 & 2020-09-30 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
-30 & 2020-11-16 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
-31 & 2020-11-17 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$\\
-32 & 2020-12-19 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$\\
-33 & 2020-12-23 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$\\
-34 & 2020-12-29 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$\\
-35 & 2021-03-31 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$\\\hline
+06 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$\\
+07 & 2019-11-17 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$\\
+08 & 2019-11-19 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm  1.131$\\
+09 & 2019-11-26 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$\\
+10 & 2019-12-04 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$\\
+11 & 2019-12-15 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$\\
+12 & 2019-12-29 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$\\
+13 & 2020-01-03 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$\\
+14 & 2020-01-06 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$\\
+15 & 2020-01-15 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$\\
+16 & 2020-02-12 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$\\
+17 & 2020-03-03 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm 0.636$\\
+18 & 2020-03-31 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
+19 & 2020-04-08 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$\\
+20 & 2020-04-18 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$\\
+21 & 2020-04-20 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$\\
+22 & 2020-04-25 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$\\
+23 & 2020-04-28 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
+24 & 2020-05-08 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$\\
+25 & 2020-07-15 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$\\
+26 & 2020-08-07 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$\\
+27 & 2020-09-13 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$\\
+28 & 2020-09-30 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
+29 & 2020-11-16 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
+30 & 2020-11-17 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$\\
+31 & 2020-12-19 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$\\
+32 & 2020-12-23 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$\\
+33 & 2020-12-29 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$\\
+34 & 2021-03-31 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$\\\hline
 \end{tabular}
@@
 
-For the selected sample, we obtained RINEX data from the TlalocNet \citep{Cabral-Cano:2018} and UNAVCO network databases to study potential alterations in the ionospehre due to the presence of the passing meteor at the day the meteor was reported.
+This material is based on services provided by the GAGE Facility, operated by UNAVCO, Inc., with support from the National Science Foundation and the National Aeronautics and Space Administration under NSF Cooperative Agreement EAR-1724794.
+
+We got RINEX data from 3 to 7 stations depending of the event location and data availability that surround the event place in all directions as possible.
+A list of the stations where we got RINEX data is available in table  .
+Most of the stations lie in mexican territory, but in some cases we required data from other stations to cover events near the mexican frontier at north or south.
+
+\clearpage
+\onecolumn
+\begin{landscape}
+%\begin{table*}
+%    \centering
+  \begin{longtable}{lllp{4cm}p{10cm}}
+      \caption{List of GPS stations used for this work.}
+      \label{tab:table-stations}
+      \endfirsthead
+      \endhead
+    \hline
+    Station name & Latitude & Longitude & Date of events  & Citation \\\hline
+    BAR1\hyperlink{Hudnut}{${}^1$}\hyperlink{Hudnut2}{${}^5$}& 33.48 & -119.03 & 2019-12-29 2020-01-03 & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - BAR1-Santa Barbara Island One P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5668BHN}.\\
+    BLYT\hyperlink{Hudnut}{${}^1$} & 33.61 & -114.71 & 2019-12-29 2020-01-03 & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2006, SCIGN USGS GPS Network - BLYT-Blythe P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5HT2MKK}.\\
+    CN23 & 17.26 & -88.78 & 2019-11-19 2020-01-15 2020-02-12& UNAVCO Community, 2012, COCONet GPS Network - CN23-BelmopanBZCR2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5Q23XJH}.\\
+    CN25 & 16.23 & -92.13 & 2020-01-15 & UNAVCO Community, 2014, COCONet GPS Network - CN25-ComitandDMEX2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57W69G7}.\\
+    GCFS & 19.31 & -81.18 & 2019-11-19& Watts, Anthony, 2016, COCONet GPS Network - GCFS-G\_CAYMAN\_CYM2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/7ETV-X536}.\\
+    GMPK\hyperlink{Hudnut}{${}^1$} & 33.05 & -114.83 & 2019-12-04 & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - GMPK-Glamis Peak P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/WCHN-H687}.\\
+    GUAT\hyperlink{Garnier}{${}^2$} & 14.59 & -90.52 & 2020-02-12 & DeMets, Charles, Cosenza-Muralles, Beatriz, 2021, Central America 2018 - Guatemala, The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/KH2R-K704}.\\
+    GUAX\hyperlink{Hudnut}{${}^1$} & 28.88 & -118.29 & 2019-10-09 2019-12-15 2019-12-29 2020-01-03 2020-03-31 2020-07-15 2020-09-13 2020-09-30 2020-12-23 & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2001, SCIGN USGS GPS Network - GUAX-Isla Guadalupe P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5GX48T2}.\\
+    IAGX & 29.03 & -113.17 & 2019-12-04 & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network - IAGX-iagxREGNOMmx2018 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/DGWN-A627}.\\
+    INEG & 21.85 & -102.28 & 2020-07-15 2020-08-07 2020-09-30 2020-11-16 2020-11-17 2020-12-19 & No citations were found\\
+    KVTX & 27.55 & -97.89 & 2019-05-23 2019-07-18 2019-08-10 2019-10-03 2019-11-17 2020-04-08 2020-04-18 2020-04-20 2020-05-08 2020-08-07 & UNAVCO Community, 2007, PBO GPS Network - KVTX-KingsvilleTX2006 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J38QH8}.\\
+    MDO1 & 30.68 & -104.02 & 2019-07-18& No citations were found\\
+    MGO5 & 30.68 & -104.02 & 2020-04-20 2020-08-07 & No citations were found\\
+    MGW3 & 29.62 & -89.95 & 2020-04-08 2020-04-20 2020-05-08 & No citations were found\\
+    OXTH & 16.29 & -95.24 & 2020-01-15 2020-02-12 & DeMets, Charles, Cabral-Cano, Enrique, 2008, Oaxaca GPS Network - OXTH-Tehuantepec P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5Q81B5V}.\\
+    OXUM\hyperlink{Graham}{${}^3$} &  &  & 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - OXUM-oxum\_tnet\_mx2001 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J964RP}.\\
+    P001 & 31.95 & -112.80 & 2020-04 25 & UNAVCO Community, 2008, PBO GPS Network - P001-Organ\_PipeAZ2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DR2SGP}.\\
+    P014 & 31.97 & -11.09 & 2019-12-04 2019-12-29 2020-01-03 2020-01-06 2020-04-25 & UNAVCO Community, 2008, PBO GPS Network - P014-Sahuarita\_AZ2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5CMK}.\\
+    P807 & 30.49 & -98.82 & 2019-11-17 2020-01-06 2020-04-20 2020-11-17 & UNAVCO Community, 2012, PBO GPS Network - P807-EcRockStPkTX2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5TQ5ZKM}.\\
+    PLPX & 31.59 & -115.15 & 2019-12-04 & UNAVCO Community, 2011, PBO GPS Network - PLPX-Las\_PintasMX2010 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5K64G3T}.\\
+    PTEX & 32.29 & -116.52 & 2019-12-29 2020-01-03 2020-09-13 2020-12-23 & UNAVCO Community, 2011, PBO GPS Network - PTEX-Testerazo\_MX2011 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XBP}.\\
+    RG06 & 32.63 & -107.86 & 2020-04-25 & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG06-RG06FaywodNM2006 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5668BFR}.\\
+    RG07 & 32.50 & -106.84 & 2020-01-06 & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG07-RG07CrucesNM2006 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5KD1W45}.
+\\
+    SG33 & 31.77 & -106.51 & 2019-11-17 2020-04-18 2020-08-07 & Harder, Steven, Kaip, Galen, Montana, Carlos, 2004, SuomiNet-G GPS Network - SG33-UTEP P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T50863KQ}.\\
+    TGMX  & 20.87 & -86.87 & 2021-03-31 & UNAVCO Community, 2015, COCONet GPS Network - TGMX-PtoMor\_TG\_MX2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5154FB7}.\\
+    TNAM & 20.54 & -103.97 & 2020-03-03 2020-07-15 2020-09-30 2020-11-16 2020-11-17 2020-12-19 & UNAVCO Community, 2014, TLALOCNet - TNAM-TNAM\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5QF8R4R}.\\
+    TNAT & 18.13 & -98.04 & 2020-01-15 & UNAVCO Community, 2014, TLALOCNet - TNAT-TNAT\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5G15Z4S}.\\
+    TNBA & 28.97 & -113.55 & 2019-10-09 2019-11-26 2019-12-15 2019-12-29 2020-01-03& UNAVCO Community, 2015, TLALOCNet - TNBA-TNBA\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57M0688}.\\
+    TNCC & 18.79 & -103.17 & 2020-03-03 & UNAVCO Community, 2015, TLALOCNet - TNCC-TNCC\_TNET\_MX2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T50R9MSK}.\\
+    TNCM & 19.50 & -105.04 & 2020-03-03 2020-04-28 & UNAVCO Community, 2014, TLALOCNet - TNCM-TNCM\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5B856FW}.\\
+    TNCN & 18.55 & -101.97 & 2020-11-16 2020-12-29 & UNAVCO Community, 2016, TLALOCNet - TNCN-TNCN\_TNET\_MX2016 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XQM}.\\
+    TNCU & 28.45 & -106.79 & 2019-05-23 2019-07-18 2019-08-10 2019-11-17 2019-12-15 2020-01-06 2020-03-31 2020-04-18 2020-07-15 2020-08-07 2020-11-17 2020-12-19 & UNAVCO Community, 2014, TLALOCNet - TNCU-CuauhtemocTN2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5V69GV2}.\\
+    TNGF & 19.33 & -99.18 & 2020-11-16 2020-12-29 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2016, TLALOCNet GPS Network - TNGF\_Geofisica-UNAM\_Mexico\_City\_TNET\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T53X851M}.\\
+    TNHM & 29.08 & -110.97 & 2019-10-09 2019-11-26 2019-12-04 2019-12-15 2019-12-29 2020-01-03 2020-03-31 2020-04-18 2020-07-15 2020-08-07 2020-09-13 2020-09-30 2020-12-23 & UNAVCO Community, 2014, TLALOCNet - TNHM-hermosilloTN2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5KP80FV}.\\
+    TNMS & 20.53 & -104.80 & 2019-10-09 2019-11-26 2019-12-15 2020-03-03 2020-07-15 & UNAVCO Community, 2014, TLALOCNet - TNMS-TNMS\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T56H4FQ5}.\\
+    TNNP & 16.12 & -97.14 & 2020-04-28 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, DeMets, Charles, 2016, TLALOCNet - TNNP-tnnp\_tnet\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5N29V96}.\\
+    TNNX & 17.41 & -97.22 & 2020-01-15 2020-02-12 2020-12-29 2021-03-31 & UNAVCO Community, 2014, TLALOCNet - TNNX-TNNX\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T52R3PZ0}.\\
+    TNPP & 31.34 & -113.63 & 2019-12-04 2020-03-31 2020-04-25 & UNAVCO Community, 2015, TLALOCNet - TNPP-TNPP\_TNET\_MX2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5CC0Z0M}.\\
+    TNSJ & 16.17 & -96.49 & 2020-12-29 & UNAVCO Community, 2016, TLALOCNet - TNSJ-tnsj\_tnet\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59S1PF1}.\\
+    TSFX & 30.93 & -114.81 & 2020-09-13 2020-12-23 & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network - TSFX-tsfxREGNOMmx2016 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/AGEA-2G27}.\\
+    UAGU & 21.92 & -102.32 & 2019-05-23 2019-07-18 2019-08-10 2019-10-03 2019-11-17 2019-11-26 2019-12-15 2020-04-18& Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UAGU-uagu\_tnet\_mx2008 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5513WK7}.\\
+    UCOE\hyperlink{Graham}{${}^3$} & 19.81 & -101.69 & 2019-08-10 2020-11-16 2020-11-17 2020-12-19 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UCOE-ucoe\_tnet\_mx2003 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T51834VW}.\\
+    UGEO\hyperlink{Marquez}{${}^4$} & 20.69 & -103.35 & 2019-08-10& Marquez-Azua, Bertha, DeMets, Charles, Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UGEO-ugeo\_tnet\_mx1998 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T58S4N9N}.\\
+    UHSL & 29.57 & -95.65 & 2020-04-08 & Wang, Guoquan, 2014, HoustonNet GPS Network - UHSL-SugarLandUSA2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T55X271S}.\\
+    UHWL & 30.06 & -94.98 & 2020-12-19 & Wang, Guoquan, 2014, HoustonNet GPS Network - UHWL-West Liberty Airport(Deep) P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T53R0R5P}.\\
+    UNPM & 20.86 & -86.86 & 2019-11-19 2020-01-15 2020-02-12 2020-05-08 & UNAVCO Community, 2012, COCONet GPS Network - UNPM-Puerto\_Morelos\_MX\_2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/J1GD-5S40}.\\
+    USMX & 29.82 & -109.68 & 2019-12-29 2020-01-03 2020-01-06 2020-04-25 2020-08-07 2020-09-30& Bennett, Rick, 2004, Northwest Mexico GPS Network - USMX-Universidad de la Sierra P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5W957CQ}.\\
+    UXAL\hyperlink{Graham}{${}^3$} &  &  & 2019-10-03 2020-01-15 2020-02-12 2020-04-08 2020-05-08 2020-12-19 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UXAL-uxal\_tnet\_mx2005 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5D1C}.\\
+    WEPD & 29.69 & -95.23 & 2020-04-20 & Wang, Guoquan, 2014, HoustonNet GPS Network - WEPD-willmselementary P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5NZ85RB}.\\
+    WMOK & 34.74 & -98.78 & 2020-04-20 & UNAVCO Community, 2005, PBO GPS Network - WMOK-WichitaMtnOK2005 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59021Q6}.\\
+    WWMT\hyperlink{Hudnut}{${}^1$} & 33.96 & -116.65 & 2019-12-29 2020-01-03& Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2006, SCIGN USGS GPS Network - WWMT-Whitewater Mountain P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5H993F2}.\\
+    YESX & 28.38 & -108.92 & 2019-11-26 2019-12-15 2020-01-06 2020-04-18 2020-04-28 2020-07-15& Bennett, Rick, 2004, Northwest Mexico GPS Network - YESX-Yecora P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5RJ4GPF}.\\\hline
+    % \end{table*}
+  \end{longtable}
+    \begin{minipage}{0.9\linewidth}
+      \footnotesize
+      Related articles:
+
+      \hypertarget{Hudnut}{${}^1$}\citet{Hudnut:2002},
+      %
+      \hypertarget{Garnier}{${}^2$}\citet{Garnier:2021}, 
+      %
+      \hypertarget{Graham}{${}^3$}\citet{Graham:2016}
+
+      \hypertarget{Marquez}{${}^4$}\href{https://doi.org/10.7283/T58S4N9N}{B.
+Marquez-Azua, E.
+Cabral-Cano, F.
+Correa-Mora and C.
+DeMets, 2004.
+A model for Mexican neotectonics based on Nationwide GPS measurements, 1993-2001, Geofisica Internacional, v.
+43, p.319-330}
+
+      \hypertarget{Hudnut2}{${}^5$}\href{https://doi.org/10.7283/T5668BHN}{Hudnut, K.
+W., Y.
+Bock, J.
+E.
+Galetzka, F.
+H.
+Webb, and W.
+H.
+Young, The Southern California Integrated GPS Network (SCIGN), Proceedings of the International Workshop on Seismotectonics at the Subduction Zone, Y.
+Fujinawa (ed.), NIED, Tsukuba, Japan, pp.
+175-196, 1999}
+
+    \end{minipage}
+  \end{landscape}
+  \clearpage
+  \twocolumn
+%For the selected sample, we obtained RINEX data from the TlalocNet \citep{Cabral-Cano:2018} and UNAVCO network databases to study potential alterations in the ionospehre due to the presence of the passing meteor at the day the meteor was reported.
 For each event, we downloaded data from stations that surrounds the place where the event was detected (usually 3 to 5 stations.
@@
 
-Using the data provided by TlalocNet and UNAVCO, we procceeded to obtain TEC parameters with the GPS\_GOPI software, available at \url{https://seemala.blogspot.com/}.
+%Using the data provided by TlalocNet and UNAVCO, we procceeded to obtain TEC parameters with the GPS\_GOPI software, available at \url{https://seemala.blogspot.com/}.
 This software takes as input the RINEX data (the navigation file is no strictly neccesary), and the outuput consists in in the vTEC and sTEC measurements for the PRNs of the whole day the event occurred, as well as the averaged TEC as function of time.
@@
 \section{Ionospheric background and vTEC maps}
+\label{sec:vTEC maps}
 
-Ionospheric perturbations also can take place due to space weather and geomagnetic storms.
+Iono spheric perturbations also can take place due to space weather and geomagnetic storms.
 So, in order to discard such events we investigated the space weather in the day each event occured.
@@
 %\end{verbatim}
-
 %\begin{figure}

### 2021-08-20 paper/manuscript.tex
Latest updates
- Few advances in paper
- Updated stations database
- Updated meteors database (removed event detected only by GLM-16)
- Updated vTEC maps to have the following improvements
  - Now we can choose the output format of maps between jpg, png and pdf
  - The colormap can be displayed in logarithmic scale
  - A second x axis in right hand graphs now display local time
  - The righthanded graphs now show shade in yellow when there is sunlight and cyan at night

@@
     OXTH & 16.29 & -95.24 & 2020-01-15 2020-02-12 & DeMets, Charles, Cabral-Cano, Enrique, 2008, Oaxaca GPS Network - OXTH-Tehuantepec P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5Q81B5V}.\\
-    OXUM\hyperlink{Graham}{${}^3$} &  &  & 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - OXUM-oxum\_tnet\_mx2001 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J964RP}.\\
+    OXUM\hyperlink{Graham}{${}^3$} & 15.66 & -96.50 & 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - OXUM-oxum\_tnet\_mx2001 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J964RP}.\\
     P001 & 31.95 & -112.80 & 2020-04 25 & UNAVCO Community, 2008, PBO GPS Network - P001-Organ\_PipeAZ2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DR2SGP}.\\
@@
     USMX & 29.82 & -109.68 & 2019-12-29 2020-01-03 2020-01-06 2020-04-25 2020-08-07 2020-09-30& Bennett, Rick, 2004, Northwest Mexico GPS Network - USMX-Universidad de la Sierra P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5W957CQ}.\\
-    UXAL\hyperlink{Graham}{${}^3$} &  &  & 2019-10-03 2020-01-15 2020-02-12 2020-04-08 2020-05-08 2020-12-19 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UXAL-uxal\_tnet\_mx2005 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5D1C}.\\
+    UXAL\hyperlink{Graham}{${}^3$} & 19.52 & -96.92 & 2019-10-03 2020-01-15 2020-02-12 2020-04-08 2020-05-08 2020-12-19 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UXAL-uxal\_tnet\_mx2005 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5D1C}.\\
     WEPD & 29.69 & -95.23 & 2020-04-20 & Wang, Guoquan, 2014, HoustonNet GPS Network - WEPD-willmselementary P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5NZ85RB}.\\

### 2021-08-20 plot_meteors.py

@@ -34,8 +34,8 @@ f = Table.read("meteors_database.tab", format="ascii")
 
 plt.errorbar(f["Longitud"], f["Latitud"], xerr=f["sig_lon"], yerr=f["sig_latitude"], fmt="bo", capsize=3)
 # Offset of labels
-x_off = [10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, -10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10]
-y_off = [10, 10, -10, 10, -10, 10, 10, 10, 10, -10, 10, -10, 10, 10, 10, 10, -10, 10, 10, -10, 10, 10, 10, -10, 10, 10, 10, 10, 10, -10, 10, 10, 10, 10, 10]
+x_off = [10, 10, 10, 10, 10, 10, 10, 10, -10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, -10, -10, 10, 10, 10, 10, 10, 10, 10, 10, -10, 10, -10, 10, 10]
+y_off = [10, 10, -10, 10, -10, 10, 10, 10, 10, -10, -10, -10, 10, 10, 10, -10, -10, 10, 10, 10, 10, 10, 10, 10, -10, 10, 10, 10, 10, 10, 10, 10, 10, 10]
 for i in range(len(f["ID"])):
     plt.annotate(f["ID"][i], (f["Longitud"][i], f["Latitud"][i]), textcoords="offset points", color="w",
     xytext=(x_off[i], y_off[i]), ha="center", bbox=dict(boxstyle="round", pad=0.5, fc="b", alpha=0.7))

### 2021-08-20 plot_stations.py

@@ -5,6 +5,8 @@
 # And the shape file for Mexico from CONABIO
 # http://www.conabio.gob.mx/informacion/metadata/gis/destdv250k_2gw.xml?_xsl=/db/meadata/xsl/fgdc_html.xsl&_indent=no
 
+# The goal of this program was settled to plot event trajectory from GLM data and the stations that were used to get the RINEX data 
+
 import seaborn as sns
 import numpy as np
 import pandas as pd
@@ -14,7 +16,25 @@ from plotfullmap import plot_map
 import argparse
 from astropy.table import Table
 import glob
-import matplotlib.cm as cm
+import argparse
+
+# Load desired date from command line
+
+parser = argparse.ArgumentParser(
+  description=""" Choose a file to work""")
+
+
+parser.add_argument('--date', type=str, default='2000-01-01',
+				 help='Choose date. Format: yyyy-mm-dd')
+
+
+
+cmd_args = parser.parse_args()
+date = cmd_args.date
+
+
+directory = "./data/"+date+"/GLM/"
+
 
 # set figure style
 sns.set_style("whitegrid") 
@@ -28,14 +48,54 @@ plot_map(sf)
 
 stations_pos = Table.read("station_data.tab", format="ascii")
 
+# Develop dictionaries with events positions, their respective stations.
+
[…]

### 2021-08-20 plot_vTEC.py

@@ -28,12 +28,15 @@ parser = argparse.ArgumentParser(
 parser.add_argument('--date', type=str, default='2000-01-01',
 			       help='Choose date. Format: yyyy-mm-dd')
 
+parser.add_argument("--formato", type=str, default="pdf", choices=("pdf", "png", "jpg"), 
+                                help="Choose output format")
 
+parser.add_argument("--log", action="store_true", help="Use logarithmic scale for vTEC")
 
 cmd_args = parser.parse_args()
 date = cmd_args.date
-
-
+formato = cmd_args.formato
+log = cmd_args.log
 directory = "./data/"+date
 p_directory = directory + "/previous/"
 n_directory = directory+ "/next/"
@@ -97,7 +100,7 @@ else: # convert start time from string to float (in hours)
 
 t0_m1 = float(t0_m1_h) + float(t0_m1_m)/60. + float(t0_m1_s)/3600.
 t0_m2 = float(t0_m2_h) + float(t0_m2_m)/60. + float(t0_m2_s)/3600.
-
+#stations = []
 # Load and plot RINEX data
 
 for f, g, fp, gp, fn, gn in zip(load_dirs, load_std, load_dir_p, load_std_p, load_dir_n, load_std_n):
@@ -106,6 +109,7 @@ for f, g, fp, gp, fn, gn in zip(load_dirs, load_std, load_dir_p, load_std_p, loa
     header_n = fn.readline()
     h1, h2 = header.split(",")
     station = h2.split("\\")[-1][0:4]
+#    stations.append(station)
     blank = f.readline()
     blank = fp.readline()
     blank = fn.readline()
@@ -167,15 +171,21 @@ for f, g, fp, gp, fn, gn in zip(load_dirs, load_std, load_dir_p, load_std_p, loa
     dTEC_p = obs_tab_p["Vtec"][mask2_p] - mean_TEC_int_p(cmn_time_p[mask2_p])
     dTEC_n = obs_tab_n["Vtec"][mask2_n] - mean_TEC_int_n(cmn_time_n[mask2_n])
[…]

### 2021-09-02 paper/acknowledgments.tex
Newest changes in scripts, new scripts and advances in paper
- Slight improvements to existing scripts
- Add new script where filters PRNs into a defined time interval around the moment the meteor is fragmented
- Split sections of paper into separated files
    - Advances in methodology section

--- 2021-07-20 paper/manuscript.tex
@@
-%% This is file `jasr-template.tex',
-%% 
-%% Copyright 2019-2020 Elsevier Ltd
-%% 
-%% This file is part of the 'Elsarticle Bundle'.
-%% ---------------------------------------------
-%% 
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%% 
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%% 
-%% Template article for Elsevier's document class `elsarticle'
-%% with harvard style bibliographic references
-%%
-%% $Id: jasr-template.tex 188 2020-11-16 05:18:23Z rishi $
-%%
-%% Use the option review to obtain double line spacing
-%\documentclass[times,review,preprint,authoryear]{elsarticle}
-
-%% Use the options `twocolumn,final' to obtain the final layout
-%% Use longtitle option to break abstract to multiple pages if overfull.
-%% For Review pdf (With double line spacing)
-%\documentclass[times,twocolumn,review]{elsarticle}
-%% For abstracts longer than one page.
-%\documentclass[times,twocolumn,review,longtitle]{elsarticle}
-%% For Review pdf without preprint line
-%\documentclass[times,twocolumn,review,nopreprintline]{elsarticle}
-%% Final pdf
-\documentclass[times,twocolumn,final,authoryear]{elsarticle}
-%%
-%\documentclass[times,twocolumn,final,longtitle]{elsarticle}
-%%
-
-%%
-%% Stylefile to load JASR template
-\usepackage{jasr}
-\usepackage{framed,multirow}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-\usepackage{latexsym}
-
-%% For line numbers
-%\usepackage[switch]{lineno}
-
-% Following three lines are needed for this document.
-% If you are not loading colors or url, then these are
-% not required.
-\usepackage{url}
-\usepackage{xcolor}
-\usepackage{multirow}
-\usepackage{tablefootnote}
-\definecolor{newcolor}{rgb}{.8,.349,.1}
-
-\usepackage[citebordercolor=white]{hyperref}
-
-\journal{Advances in Space Research}
-
-\begin{document}
-
-\verso{Given-name Surname \textit{etal}}
-
-\begin{frontmatter}
-
-\title{Ionospheric Disturbances in Mexican Territory Produced by Objects Entering the Athmosphere from Space \tnoteref{tnote1}}%
-%\tnotetext[tnote1]{This is an example for title footnote coding.}
-
-\author[1]{Jorge \snm{Tarango-Yong}\corref{cor1}}
-\cortext[cor1]{Tel.: +52-443-476-5525;  \\
-  email: jorge.tarango@comunidad.unam.mx
-}
-
-\author[1]{Mario \snm{Rodriguez-Martinez}\corref{cor2}}
-\cortext[cor2]{email: m.rodriguez@enesmorelia.unam.mx}
-%\fntext[fn1]{This is author footnote for second author.}
-\author[1]{Raul \snm{Guti\'errez-Zalapa}\fnref{fn1}}
-%% Third author's email
-%\ead{author3@author.com}
-%\author[2]{Given-name4 \snm{Surname4}}
-
-\address[1]{Escuela Nacional de Estudios Superiores, UNAM, campus Morelia, Antigua Carretera a P\'atzcuaro No. 8701
-Col. Ex Hacienda de San Jos\'e de la Huerta, Morelia, Michoac\'an, 58190, M\'exico}
-%\address[2]{}
-
-\received{1 May 2013}
-\finalform{10 May 2013}
-\accepted{13 May 2013}
-\availableonline{15 May 2013}
-\communicated{S. Sarkar}
-
-\begin{abstract}
-%%%
-Please type your abstract here, and the rest of the text, figures,
-tables, equations etc. in the main body. Please do not modify LaTeX\ 
-commands unless you need to modify them and know how to do it.
-%%%%
-\end{abstract}
-
-\begin{keyword}
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-%\MSC 41A05\sep 41A10\sep 65D05\sep 65D17
-%% Keywords
-\KWD Space Sciences\sep Atmosphere%\sep Keyword3
-\end{keyword}
-
-\end{frontmatter}
-
-%% For linenumbers
-%\linenumbers
-
-%% main text
-\section{Introduction}
-\label{sec1}
-%Please use \verb+elsarticle.cls+ for typesetting your paper. Additionally,
-%make sure not to remove the package \verb+jasr.sty+ already included in the
-%preamble:
-%\begin{verbatim} 
-%  \usepackage{jasr}
-%\end{verbatim}
-
-%Make sure to have the file \verb+model5-names.bst+ to produce the references in
-%the correct format.
-
-%Any instructions relevant to the \verb+elsarticle.cls+ are
-%applicable here as well. See the online instruction available at:
-%\makeatletter
-%\if@twocolumn
-%\begin{verbatim}
-% https://support.stmdocs.in/wiki/
-% index.php?title=Elsarticle.cls
-%\end{verbatim}
-%\else
-%\begin{verbatim}
-% https://support.stmdocs.in/wiki/index.php?title=Elsarticle.cls
-% \end{verbatim}
-%\fi
-%\makeatother
-
-%Following commands are defined for this journal which are not in
-%\verb+elsarticle.cls+. 
-%\begin{verbatim}
-%  \received{}
-%  \finalform{}
-%  \accepted{}
-%  \availableonline{}
-%  \communicated{}
-%\end{verbatim}
-
-%\subsection{Subsection}
-%This is only a \LaTeX\ template if you need one. 
-%See the detailed guidelines for manuscript preparation 
-%and submission at:
-%\begin{verbatim}
-%https://ees.elsevier.com/asr
-%\end{verbatim}
-
-\section{Metodology}
-\subsection{Meteors Database}
-
-We selected a sample of meteors which were observed in mexican territory from the Geostationary Lightning Mapper \citep{GOODMAN:2013}.
-Orignally this project was designed to detect ligthning activity in earth's athmosphere, but has been proven that also can detect bolides entering the athmosphere.
-The detection comes from two satellites called GOES-16 and GOES-17 orbiting the earth in geostationary orbits.
-We used the interactive database available at \url{https://neo-bolide.ndc.nasa.gov/#/} to get the events positions presented in this section, as well we obtained data about the bolid trajectory detected and energy released.
-The sample was chosen following the next criteria:%selected in such way we chose the most probable objects to be detected by GPS sources in mexican territory and its surroundings:
-
-\begin{itemize}
-    \item The objects were detected inside mexican territory and its surroundings.
-    \item The objects were detected by both satellites GOES 16 and GOES 17 (stereo)
-    \item The detection has been assigned a high confidence ratio.
-\end{itemize}
-
-\begin{table*}
-  \centering
-  \caption{List of meteors passing through Mexico.
-The events are listed in chronological order.
-The listed duration, latitude and longitude correspond to the mean of the measurements of both GOES satellites.
-The uncertainties correspond to the respecting mean deviation.}
-\label{tab:table-meteors}
-\begin{tabular}{|r|r|r|r|r|r|}
-\hline
-ID & Date of event & Start Time (UT)  & Duration (seconds) & Latitude (deg) & Longitude (deg)\\
-\hline
-01 & 2019-05-23 & 16:36:18 & $0.197\pm 0.0000$ & $24.30 \pm 0.000$ & $-101.60 \pm 0.849$\\
-02 & 2019-07-18 & 14:30:30 & $0.058\pm 0.0000$ & $27.20 \pm 0.000$ & $-103.15 \pm 0.778$\\
-03 & 2019-08-10 & 11:18:48 & $0.199\pm 0.0757$ & $21.50 \pm 0.000$ & $-102.50  \pm 0.849$\\
-04 & 2019-10-03 & 07:55:33 & $0.106\pm 0.0297$ & $25.65 \pm 0.071$ & $-96.25 \pm   0.778$\\
-05 & 2019-10-09 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$\\
-06\tablefootnote{This object was only detected by GOES-16 satellite} & 2019-10-12 & 11:12:27 & $0.006\pm 0.0000$ & $28.8 \pm 0.000$ & $-111.3 \pm 0.000$\\
-07 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$\\
-08 & 2019-11-17 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$\\
-09 & 2019-11-19 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm  1.131$\\
-10 & 2019-11-26 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$\\
-11 & 2019-12-04 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$\\
-12 & 2019-12-15 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$\\
-13 & 2019-12-29 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$\\
-14 & 2020-01-03 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$\\
-15 & 2020-01-06 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$\\
-16 & 2020-01-15 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$\\
-17 & 2020-02-12 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$\\
-18 & 2020-03-03 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm 0.636$\\
-19 & 2020-03-31 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
-20 & 2020-04-08 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$\\
-21 & 2020-04-18 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$\\
-22 & 2020-04-20 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$\\
-23 & 2020-04-25 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$\\
-24 & 2020-04-28 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
-25 & 2020-05-08 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$\\
-26 & 2020-07-15 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$\\
-27 & 2020-08-07 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$\\
-28 & 2020-09-13 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$\\
-29 & 2020-09-30 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
-30 & 2020-11-16 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
-31 & 2020-11-17 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$\\
-32 & 2020-12-19 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$\\
-33 & 2020-12-23 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$\\
-34 & 2020-12-29 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$\\
-35 & 2021-03-31 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$\\\hline
-\end{tabular}
-\end{table*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{../meteors_map}
-  \caption{Positions of events from table \ref{tab:table-meteors}. The label of each point correspond to the ID (first column) of the referred table.}
-  \label{fig:meteors-map}
-\end{figure}
-
-\subsection{GPS data}
-
-For the selected sample, we obtained RINEX data from the TlalocNet \citep{Cabral-Cano:2018} and UNAVCO network databases to study potential alterations in the ionospehre due to the presence of the passing meteor at the day the meteor was reported.
-For each event, we downloaded data from stations that surrounds the place where the event was detected (usually 3 to 5 stations.
-)The list of the sample meteors is shown in table \ref{tab:table-meteors}.
-The events are in chronological order.
-The reported duration, latitude and longitude correspond to the mean between measurements from satellites GOES-16 and GOES 17; in the same way, the uncertainties correspond to the standard deviation.
-Also their respective positions are available in figure \ref{fig:meteors-map}, where each label correspond to the ID (first column) of table \ref{tab:table-meteors}.
-
-Using the data provided by TlalocNet and UNAVCO, we procceeded to obtain TEC parameters with the GPS\_GOPI software, available at \url{https://seemala.blogspot.com/}.
-This software takes as input the RINEX data (the navigation file is no strictly neccesary), and the outuput consists in in the vTEC and sTEC measurements for the PRNs of the whole day the event occurred, as well as the averaged TEC as function of time.
-We obtained vTEC maps for the events in table (\ref{tab:table-meteors}) and their respective next and previous day.
-
-%Final idea: use GOPI software to get the vTEC data from the day of each event and the previous days.
-
-\section{Ionospheric background and vTEC maps}
-
-Ionospheric perturbations also can take place due to space weather and geomagnetic storms.
-So, in order to discard such events we investigated the space weather in the day each event occured.
-In figure (name) we present the geomagnetic \textit{Kp} index for some events.
-We discarded events whose Kp index is equal or grater than 4 in the day of the event or shortly before.
-Also we present in figure (name) the vTEC perturbation maps for the same events in a three day series, centered in the event date.
-The estimated meteor trajectory, obtained from the GLM data is presented in black, continous line, while the linear fit to the GOES-16 and GOES-17 data are presented with the red dashed line, and work as boudary errors.
-
-\section{Frecuency Analysis}
-
-\section{Discussion}
-
-%\section{How to include a figure?}
-%Change the file name of the figure below with your own 
-%figure. And remember to change the figure caption too!
-%\begin{verbatim}
-%\begin{figure}
-%  \centering
-%  \includegraphics[scale=0.5]{fig01}
-%  \caption{Write the figure caption here.}
-%  \label{fig:pendulum}
-%\end{figure}
-%\end{verbatim}
-
-%\begin{figure}
-%\centering
-%\includegraphics[scale=0.5]{fig01.pdf}
-%\caption{Write the figure caption here.}
-%\label{fig:pendulum}
-%\end{figure}
-
-%\subsection{And a table?}
-%Just replace the text/values in the template table below 
-%with your own. You can change the number of 
-%lines/rows as necessary.
-
-%\begin{table*}
-%\centering
-%\caption{Title of the table should be at the top}
-%\begin{tabular}{|l|l|l|l|}
-%\hline
-%Column Name1    & Column Name2 & Column Name3 & Column Name4 \\
-%\hline
-%Parameter Name1 & Value        & Value        & Value        \\
-%\hline
-%Parameter Name2 & Value        & Value        & Value        \\
-%\hline
-%Parameter Name3 & Value        & Value        & Value        \\
-%\hline
-%\end{tabular}
-%\end{table*}
-
-%\subsection{Equations}
-%Conventionally, in mathematical equations, variables and
-%anything that represents a value appear in italics. 
-%All equations should be numbered for easy referencing. 
-%The number should appear at the right margin.
-%\begin{eqnarray}
-%S'_{\mathrm{pg}} = \frac{S_{\mathrm{pg}} - \mathrm{min}(S_{\mathrm{pG}})}
-%  {\mathrm{max}(S_{\mathrm{pG}} - \mathrm{min}(S_{\mathrm{pG}}))}
-%\end{eqnarray}
-%In mathematical expressions 
-%in running text "/" should be used
-%for division (not a horizontal line).
-
-%\section{Citations}
-%Citations in the text can be made using\\[6pt]
-%\verb+\citet{NewmanGirvan2004}+\\[6pt]
-%for citation in running text like in 
-%\citet{NewmanGirvan2004} or using\\[6pt]
-%\verb+\citep{Vehlowetal2013,NewmanGirvan2004}+\\[6pt]
-%for citation within parentheses like in 
-%\citep{Vehlowetal2013,NewmanGirvan2004}.
-
-%Please use the actual \verb+\cite+ command in the text.
-%Also, please double-check the \verb+\citep+ command.
-
-%\section{Reference style}
-%You can include the references in the main text file in \LaTeX
-%format. Alternately, you can include a separate bibliography
-%file (refs.bib in this example) and run the following set of 
-%commands:
-%\begin{verbatim}
-%==================
-
-%pdflatex myfile.tex
-
-%bibtex myfile (no extension in this line!)
-
-%pdflatex myfile.tex
-
-%pdflatex myfile.tex
-
-%==================
-%\end{verbatim}
-
-%\section{A sample entry in the bibliography file}
-%{\fontsize{7.5pt}{9.6pt}\selectfont
-%\begin{verbatim}
-%==================
-
-%@ARTICLE{NewmanGirvan2004,
-%  author  = {Newman, M. E. J. and Girvan, M.},
-%  title   = {Finding and evaluating community 
-%               structure in networks},
-%  journal = {Phys. Rev. E.},
-%  volume  = {69},
-%  number  = {21},
-%  year    = {2004},
-%  pages   = {026113}
-%}
-
-%==================
-%\end{verbatim}
-%}
-
-\section{Acknowledgments}
-
 The RINEX data used in this paper were obtained from the Trans-boundary, Land and Atmosphere Long-term Observational and Collaborative Network (TLALOCNet, \citet{Cabral-Cano:2018}), operated by the Servicio de Geodesia Satelital (SGS) at the Instituto de Geofísica-Universidad Nacional Autónoma de México (UNAM) in collaboration with UNAVCO Inc.
@@
 Also we are grateful with the Direcci\'on General de Asuntos Acad\'emicos (DGAPA) of the Universidad Nacional Aut\'onoma de M\'exico and the Programa de Becas Posdoctorales for funding this project.
-
-%% Bibliography
-%% Author year style
-\bibliographystyle{model5-names}
-\biboptions{authoryear}
-\bibliography{bibliography}
-
-\end{document}
-
-%%

### 2021-09-02 paper/manuscript.tex
Newest changes in scripts, new scripts and advances in paper
- Slight improvements to existing scripts
- Add new script where filters PRNs into a defined time interval around the moment the meteor is fragmented
- Split sections of paper into separated files
    - Advances in methodology section

--- 2021-07-20 paper/manuscript.tex
@@
 
-\verso{Given-name Surname \textit{etal}}
+\verso{Tarango-Yong \textit{et. al}}
 
@@
 \label{sec1}
+\input{introduction}
 %Please use \verb+elsarticle.cls+ for typesetting your paper. Additionally,
@@
 
-\section{Metodology}
-\subsection{Meteors Database}
+\section{Methodology}
+\label{sec:methodology}
+\input{methodology}
 
-We selected a sample of meteors which were observed in mexican territory from the Geostationary Lightning Mapper \citep{GOODMAN:2013}.
-Orignally this project was designed to detect ligthning activity in earth's athmosphere, but has been proven that also can detect bolides entering the athmosphere.
-The detection comes from two satellites called GOES-16 and GOES-17 orbiting the earth in geostationary orbits.
-We used the interactive database available at \url{https://neo-bolide.ndc.nasa.gov/#/} to get the events positions presented in this section, as well we obtained data about the bolid trajectory detected and energy released.
-The sample was chosen following the next criteria:%selected in such way we chose the most probable objects to be detected by GPS sources in mexican territory and its surroundings:
+\section{Bolides physical parameters}
+\label{sec:bolides}
+\input{meteor-properties}
+\section{Ionospheric background and vTEC maps}
+\label{sec:vTEC maps}
 
-\begin{itemize}
-    \item The objects were detected inside mexican territory and its surroundings.
-    \item The objects were detected by both satellites GOES 16 and GOES 17 (stereo)
-    \item The detection has been assigned a high confidence ratio.
-\end{itemize}
+\input{vTEC-maps}
 
-\begin{table*}
-  \centering
-  \caption{List of meteors passing through Mexico.
-The events are listed in chronological order.
-The listed duration, latitude and longitude correspond to the mean of the measurements of both GOES satellites.
-The uncertainties correspond to the respecting mean deviation.}
-\label{tab:table-meteors}
-\begin{tabular}{|r|r|r|r|r|r|}
-\hline
-ID & Date of event & Start Time (UT)  & Duration (seconds) & Latitude (deg) & Longitude (deg)\\
-\hline
-01 & 2019-05-23 & 16:36:18 & $0.197\pm 0.0000$ & $24.30 \pm 0.000$ & $-101.60 \pm 0.849$\\
-02 & 2019-07-18 & 14:30:30 & $0.058\pm 0.0000$ & $27.20 \pm 0.000$ & $-103.15 \pm 0.778$\\
-03 & 2019-08-10 & 11:18:48 & $0.199\pm 0.0757$ & $21.50 \pm 0.000$ & $-102.50  \pm 0.849$\\
-04 & 2019-10-03 & 07:55:33 & $0.106\pm 0.0297$ & $25.65 \pm 0.071$ & $-96.25 \pm   0.778$\\
-05 & 2019-10-09 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$\\
-06\tablefootnote{This object was only detected by GOES-16 satellite} & 2019-10-12 & 11:12:27 & $0.006\pm 0.0000$ & $28.8 \pm 0.000$ & $-111.3 \pm 0.000$\\
-07 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$\\
-08 & 2019-11-17 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$\\
-09 & 2019-11-19 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm  1.131$\\
-10 & 2019-11-26 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$\\
-11 & 2019-12-04 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$\\
-12 & 2019-12-15 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$\\
-13 & 2019-12-29 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$\\
-14 & 2020-01-03 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$\\
-15 & 2020-01-06 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$\\
-16 & 2020-01-15 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$\\
-17 & 2020-02-12 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$\\
-18 & 2020-03-03 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm 0.636$\\
-19 & 2020-03-31 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
-20 & 2020-04-08 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$\\
-21 & 2020-04-18 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$\\
-22 & 2020-04-20 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$\\
-23 & 2020-04-25 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$\\
-24 & 2020-04-28 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
-25 & 2020-05-08 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$\\
-26 & 2020-07-15 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$\\
-27 & 2020-08-07 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$\\
-28 & 2020-09-13 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$\\
-29 & 2020-09-30 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
-30 & 2020-11-16 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
-31 & 2020-11-17 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$\\
-32 & 2020-12-19 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$\\
-33 & 2020-12-23 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$\\
-34 & 2020-12-29 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$\\
-35 & 2021-03-31 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$\\\hline
-\end{tabular}
-\end{table*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{../meteors_map}
-  \caption{Positions of events from table \ref{tab:table-meteors}. The label of each point correspond to the ID (first column) of the referred table.}
-  \label{fig:meteors-map}
-\end{figure}
-
-\subsection{GPS data}
-
-For the selected sample, we obtained RINEX data from the TlalocNet \citep{Cabral-Cano:2018} and UNAVCO network databases to study potential alterations in the ionospehre due to the presence of the passing meteor at the day the meteor was reported.
-For each event, we downloaded data from stations that surrounds the place where the event was detected (usually 3 to 5 stations.
-)The list of the sample meteors is shown in table \ref{tab:table-meteors}.
-The events are in chronological order.
-The reported duration, latitude and longitude correspond to the mean between measurements from satellites GOES-16 and GOES 17; in the same way, the uncertainties correspond to the standard deviation.
-Also their respective positions are available in figure \ref{fig:meteors-map}, where each label correspond to the ID (first column) of table \ref{tab:table-meteors}.
-
-Using the data provided by TlalocNet and UNAVCO, we procceeded to obtain TEC parameters with the GPS\_GOPI software, available at \url{https://seemala.blogspot.com/}.
-This software takes as input the RINEX data (the navigation file is no strictly neccesary), and the outuput consists in in the vTEC and sTEC measurements for the PRNs of the whole day the event occurred, as well as the averaged TEC as function of time.
-We obtained vTEC maps for the events in table (\ref{tab:table-meteors}) and their respective next and previous day.
-
-%Final idea: use GOPI software to get the vTEC data from the day of each event and the previous days.
-
-\section{Ionospheric background and vTEC maps}
-
-Ionospheric perturbations also can take place due to space weather and geomagnetic storms.
-So, in order to discard such events we investigated the space weather in the day each event occured.
-In figure (name) we present the geomagnetic \textit{Kp} index for some events.
-We discarded events whose Kp index is equal or grater than 4 in the day of the event or shortly before.
-Also we present in figure (name) the vTEC perturbation maps for the same events in a three day series, centered in the event date.
-The estimated meteor trajectory, obtained from the GLM data is presented in black, continous line, while the linear fit to the GOES-16 and GOES-17 data are presented with the red dashed line, and work as boudary errors.
-
-\section{Frecuency Analysis}
+%\section{Frecuency Analysis}
 
 \section{Discussion}
+\label{sec:discission}
 
+\input{discussion}
 %\section{How to include a figure?}
@@
 \section{Acknowledgments}
-
-The RINEX data used in this paper were obtained from the Trans-boundary, Land and Atmosphere Long-term Observational and Collaborative Network (TLALOCNet, \citet{Cabral-Cano:2018}), operated by the Servicio de Geodesia Satelital (SGS) at the Instituto de Geofísica-Universidad Nacional Autónoma de México (UNAM) in collaboration with UNAVCO Inc.
-
-We are deeply grateful to all personnel from SGS, SSN and UNAVCO for station installation, maintenance, data acquisition, IT support and data curation and distribution for these networks and in particular to the following individuals and institutions, and those whose hard field work and resourcefulness were central to the success of this project: Bill Douglass, Neal Lord and Bill Unger at UW-Madison, Oscar Diaz-Molina and Luis Salazar-Tlaczani at SGS, John Galetzka, Adam Wallace, Shawn Lawrence, Sean Malloy and Chris Walls at UNAVCO, Jesus Pacheco-Martínez at Universidad Autónoma de Aguascalientes, Bertha Marquez-Azúa and personnel at the Universidad de Guadalajara at campus Guadalajara, Mascota and Ameca, Protección Civil de Jalisco, Universidad de Colima at campus Colima and campus El Naranjo and Centro de Geociencias, Centro de Ciencias de la Atmosfera Instituto de Biología Estacion Chamela at UNAM.
-TLALOCNet, SSN-TLALOCNet and other GPS related operations from SGS are supported by CONACyT projects 253760, 256012 and 2017-01-5955, UNAM-PAPIIT projects IN104213, IN111509, IN109315-3, IN104818-3, NSF grant 2025104, NASA-ROSES grant NNX12AQ08G and supplemental support from UNAM-Instituto de Geofísica.
-UNAVCO's initial support for TLALOCNet (some of its stations now part of the GAGE Facility-NOTA) was performed under EAR-1338091 and is currently supported by NSF and NASA under NSF Cooperative Agreement EAR-1724794.
-
-Also we are grateful with the Direcci\'on General de Asuntos Acad\'emicos (DGAPA) of the Universidad Nacional Aut\'onoma de M\'exico and the Programa de Becas Posdoctorales for funding this project.
-
+\label{sec:acknowledgments}
+\input{Acknowledgments}
 %% Bibliography

### 2021-09-02 paper/methodology.tex
Newest changes in scripts, new scripts and advances in paper
- Slight improvements to existing scripts
- Add new script where filters PRNs into a defined time interval around the moment the meteor is fragmented
- Split sections of paper into separated files
    - Advances in methodology section

\subsection{Meteors Database}

We selected a sample of meteors which were observed in mexican territory from the Geostationary Lightning Mapper \citep{GOODMAN:2013}. Orignally this project was designed to detect ligthning activity in earth's athmosphere, but has been proven that also can detect bolides entering the athmosphere. The detection comes from two satellites called GOES-16 and GOES-17 orbiting the earth in geostationary orbits. %Figure  shows the area where GOES-16 and GOES-17 detect activity on a lightning flash rate map; in mexican territory clearly both satellites can make detections. %Create a figure where the area coverage of GOES-16 and GOES-17 is shown.
We used the interactive database available at \url{https://neo-bolide.ndc.nasa.gov/#/}. These data are publicly available and easily downloaded from the same website. For each event we can obtain the recorded trajectory of meteors and the corresponding light curve. THe GLM satellites have an umbral magnitude for detection of -14. At this magnitude, a meteor is considered a bolide, and is expected to be at least decimeter-sized (in diameter) to reach such brightness. In the other hand, too bright meteors will saturate the detectors, and thus, lowering the quality of data. The result of this factors implies that the range in size of the objects in our sample varies in diameter between decimeter to meter size. %The sample was chosen following the next criteria:%selected in such way we chose the most probable objects to be detected by GPS sources in mexican territory and its surroundings: 
Each event also has assigned a confidence ratio, from low confidence to high, depending in how bright is the event itself and if the trajectory recorded by GLM ressembles (or not) a straight line. We chose only events whose confidence ratio is high, in oreder to be sure we chose the brightest objects, and thus, in the diameter size of bolides, we favored the meter-sized ones. In table \ref{tab:table-meteors} we list the object we chose to do this work, order in chronological order. The columns of the table, from left to right are and ID to enumerate the meteors in the sample, the date and time each meteor was detected, the duration of the detection, their respective coordinates and the estimated height of the meteor over the ground at the time of the detection. GOES-16 and GOES-17 systematically detect the meteors at slightly different positions and at slightly different times, so we calculated the mean of the duration, latitude and longitude reported by both satellites for each event, and used the standard deviation as the uncertainties.

From table \ref{tab:table-meteors} is also clear that the duration of all the bolides detection last less than a second. This obsevation suggests that the bolides remain undetected by the GLM satellites until they get fragmented due to stagnation presure when they release a huge amount of energy and thus they become detectable.

%From the light curves we can estimate the total radiated energy and then convert it to the total kinetic energy through a relation. With this energy we may estimate physical parameters with the cloud fragmentation model form wheeler et al.

%\begin{itemize}
%    \item The objects were detected inside mexican territory and its surroundings.
%    \item The objects were detected by both satellites GOES 16 and GOES 17 (stereo)
%    \item The detection has been assigned a high confidence ratio.
%\end{itemize}

\begin{table*}
  \centering
  \caption{List of meteors passing through Mexico. The events are listed in chronological order. The listed duration, latitude and longitude correspond to the mean of the measurements of both GOES satellites. The uncertainties correspond to the respecting mean deviation.}
\label{tab:table-meteors}
\begin{tabular}{rrrrrrr}
\hline
ID & Date of event & Start Time (UT)  & Duration (seconds) & Latitude (deg) & Longitude (deg) & Height (km)\\
\hline
01 & 2019-05-23 & 16:36:18 & $0.197\pm 0.0000$ & $24.30 \pm 0.000$ & $-101.60 \pm 0.849$  & 28\\
02 & 2019-07-18 & 14:30:30 & $0.058\pm 0.0000$ & $27.20 \pm 0.000$ & $-103.15 \pm 0.778$  & 72\\
03 & 2019-08-10 & 11:18:48 & $0.199\pm 0.0757$ & $21.50 \pm 0.000$ & $-102.50  \pm 0.849$ & 92\\
04 & 2019-10-03 & 07:55:33 & $0.106\pm 0.0297$ & $25.65 \pm 0.071$ & $-96.25 \pm   0.778$ & 74\\
05 & 2019-10-09 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$ & 32\\
06 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$ & 82\\
07 & 2019-11-17 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$ & 88\\
08 & 2019-11-19 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm  1.131$  & 99\\
09 & 2019-11-26 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$ & 81\\
10 & 2019-12-04 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$ & 77\\
11 & 2019-12-15 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$ & 78\\
12 & 2019-12-29 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$ & 79\\
13 & 2020-01-03 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$ & 74\\
14 & 2020-01-06 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$ & 81\\
15 & 2020-01-15 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$ & 93\\
16 & 2020-02-12 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$ & 90\\
17 & 2020-03-03 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm 0.636$  & 77\\
18 & 2020-03-31 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 61\\
19 & 2020-04-08 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$ & 78\\
20 & 2020-04-18 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$ & 82\\
21 & 2020-04-20 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$ & 88\\
22 & 2020-04-25 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$ & 84\\
23 & 2020-04-28 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 29\\
24 & 2020-05-08 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$ & 81\\
25 & 2020-07-15 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$ & 53\\
26 & 2020-08-07 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$ & 89\\
27 & 2020-09-13 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$ & 85\\
28 & 2020-09-30 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ & 83\\
29 & 2020-11-16 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ & 06\\
30 & 2020-11-17 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$ & 93\\
31 & 2020-12-19 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$ & 98\\
32 & 2020-12-23 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$ & 81\\
33 & 2020-12-29 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$ & 81\\
34 & 2021-03-31 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$  & 24\\\hline
\end{tabular}
\end{table*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{../meteors_map}
  \caption{Positions of events from table \ref{tab:table-meteors}. The label of each point correspond to the ID (first column) of the referred table.}
  \label{fig:meteors-map}
\end{figure}

\subsection{GPS data}

This material is based on services provided by the GAGE Facility, operated by UNAVCO, Inc., with support from the National Science Foundation and the National Aeronautics and Space Administration under NSF Cooperative Agreement EAR-1724794.

We got RINEX data from 3 to 7 stations depending of the event location and data availability that surround the event place in all directions as possible. A list of the stations where we got RINEX data is available in table  . Most of the stations lie in mexican territory, but in some cases we required data from other stations to cover events near the mexican frontier at north or south.

\clearpage
\onecolumn
\begin{landscape}
%\begin{table*}
%    \centering
  \begin{longtable}{lllp{4cm}p{10cm}}
      \caption{List of GPS stations used for this work.}
      \label{tab:table-stations}
      \endfirsthead
      \endhead
    \hline
    Station name & Latitude & Longitude & Date of events  & Citation \\\hline
    BAR1\hyperlink{Hudnut}{${}^1$}\hyperlink{Hudnut2}{${}^5$}& 33.48 & -119.03 & 2019-12-29 2020-01-03 & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - BAR1-Santa Barbara Island One P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5668BHN}.\\
    BLYT\hyperlink{Hudnut}{${}^1$} & 33.61 & -114.71 & 2019-12-29 2020-01-03 & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2006, SCIGN USGS GPS Network - BLYT-Blythe P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5HT2MKK}.\\
    CN23 & 17.26 & -88.78 & 2019-11-19 2020-01-15 2020-02-12& UNAVCO Community, 2012, COCONet GPS Network - CN23-BelmopanBZCR2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5Q23XJH}.\\
    CN25 & 16.23 & -92.13 & 2020-01-15 & UNAVCO Community, 2014, COCONet GPS Network - CN25-ComitandDMEX2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57W69G7}.\\
    GCFS & 19.31 & -81.18 & 2019-11-19& Watts, Anthony, 2016, COCONet GPS Network - GCFS-G\_CAYMAN\_CYM2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/7ETV-X536}.\\
    GMPK\hyperlink{Hudnut}{${}^1$} & 33.05 & -114.83 & 2019-12-04 & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - GMPK-Glamis Peak P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/WCHN-H687}.\\
    GUAT\hyperlink{Garnier}{${}^2$} & 14.59 & -90.52 & 2020-02-12 & DeMets, Charles, Cosenza-Muralles, Beatriz, 2021, Central America 2018 - Guatemala, The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/KH2R-K704}.\\
    GUAX\hyperlink{Hudnut}{${}^1$} & 28.88 & -118.29 & 2019-10-09 2019-12-15 2019-12-29 2020-01-03 2020-03-31 2020-07-15 2020-09-13 2020-09-30 2020-12-23 & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2001, SCIGN USGS GPS Network - GUAX-Isla Guadalupe P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5GX48T2}.\\
    IAGX & 29.03 & -113.17 & 2019-12-04 & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network - IAGX-iagxREGNOMmx2018 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/DGWN-A627}.\\
    INEG & 21.85 & -102.28 & 2020-07-15 2020-08-07 2020-09-30 2020-11-16 2020-11-17 2020-12-19 & No citations were found\\
    KVTX & 27.55 & -97.89 & 2019-05-23 2019-07-18 2019-08-10 2019-10-03 2019-11-17 2020-04-08 2020-04-18 2020-04-20 2020-05-08 2020-08-07 & UNAVCO Community, 2007, PBO GPS Network - KVTX-KingsvilleTX2006 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J38QH8}.\\
    MDO1 & 30.68 & -104.02 & 2019-07-18& No citations were found\\
    MGO5 & 30.68 & -104.02 & 2020-04-20 2020-08-07 & No citations were found\\
    MGW3 & 29.62 & -89.95 & 2020-04-08 2020-04-20 2020-05-08 & No citations were found\\
    OXTH & 16.29 & -95.24 & 2020-01-15 2020-02-12 & DeMets, Charles, Cabral-Cano, Enrique, 2008, Oaxaca GPS Network - OXTH-Tehuantepec P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5Q81B5V}.\\
    OXUM\hyperlink{Graham}{${}^3$} & 15.66 & -96.50 & 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - OXUM-oxum\_tnet\_mx2001 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J964RP}.\\
    P001 & 31.95 & -112.80 & 2020-04 25 & UNAVCO Community, 2008, PBO GPS Network - P001-Organ\_PipeAZ2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DR2SGP}.\\
    P014 & 31.97 & -11.09 & 2019-12-04 2019-12-29 2020-01-03 2020-01-06 2020-04-25 & UNAVCO Community, 2008, PBO GPS Network - P014-Sahuarita\_AZ2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5CMK}.\\
    P807 & 30.49 & -98.82 & 2019-11-17 2020-01-06 2020-04-20 2020-11-17 & UNAVCO Community, 2012, PBO GPS Network - P807-EcRockStPkTX2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5TQ5ZKM}.\\
    PLPX & 31.59 & -115.15 & 2019-12-04 & UNAVCO Community, 2011, PBO GPS Network - PLPX-Las\_PintasMX2010 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5K64G3T}.\\
    PTEX & 32.29 & -116.52 & 2019-12-29 2020-01-03 2020-09-13 2020-12-23 & UNAVCO Community, 2011, PBO GPS Network - PTEX-Testerazo\_MX2011 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XBP}.\\
    RG06 & 32.63 & -107.86 & 2020-04-25 & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG06-RG06FaywodNM2006 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5668BFR}.\\
    RG07 & 32.50 & -106.84 & 2020-01-06 & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG07-RG07CrucesNM2006 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5KD1W45}. \\
    SG33 & 31.77 & -106.51 & 2019-11-17 2020-04-18 2020-08-07 & Harder, Steven, Kaip, Galen, Montana, Carlos, 2004, SuomiNet-G GPS Network - SG33-UTEP P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T50863KQ}.\\
    TGMX  & 20.87 & -86.87 & 2021-03-31 & UNAVCO Community, 2015, COCONet GPS Network - TGMX-PtoMor\_TG\_MX2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5154FB7}.\\
    TNAM & 20.54 & -103.97 & 2020-03-03 2020-07-15 2020-09-30 2020-11-16 2020-11-17 2020-12-19 & UNAVCO Community, 2014, TLALOCNet - TNAM-TNAM\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5QF8R4R}.\\
    TNAT & 18.13 & -98.04 & 2020-01-15 & UNAVCO Community, 2014, TLALOCNet - TNAT-TNAT\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5G15Z4S}.\\
    TNBA & 28.97 & -113.55 & 2019-10-09 2019-11-26 2019-12-15 2019-12-29 2020-01-03& UNAVCO Community, 2015, TLALOCNet - TNBA-TNBA\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57M0688}.\\
    TNCC & 18.79 & -103.17 & 2020-03-03 & UNAVCO Community, 2015, TLALOCNet - TNCC-TNCC\_TNET\_MX2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T50R9MSK}.\\
    TNCM & 19.50 & -105.04 & 2020-03-03 2020-04-28 & UNAVCO Community, 2014, TLALOCNet - TNCM-TNCM\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5B856FW}.\\
    TNCN & 18.55 & -101.97 & 2020-11-16 2020-12-29 & UNAVCO Community, 2016, TLALOCNet - TNCN-TNCN\_TNET\_MX2016 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XQM}.\\
    TNCU & 28.45 & -106.79 & 2019-05-23 2019-07-18 2019-08-10 2019-11-17 2019-12-15 2020-01-06 2020-03-31 2020-04-18 2020-07-15 2020-08-07 2020-11-17 2020-12-19 & UNAVCO Community, 2014, TLALOCNet - TNCU-CuauhtemocTN2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5V69GV2}.\\
    TNGF & 19.33 & -99.18 & 2020-11-16 2020-12-29 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2016, TLALOCNet GPS Network - TNGF\_Geofisica-UNAM\_Mexico\_City\_TNET\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T53X851M}.\\
    TNHM & 29.08 & -110.97 & 2019-10-09 2019-11-26 2019-12-04 2019-12-15 2019-12-29 2020-01-03 2020-03-31 2020-04-18 2020-07-15 2020-08-07 2020-09-13 2020-09-30 2020-12-23 & UNAVCO Community, 2014, TLALOCNet - TNHM-hermosilloTN2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5KP80FV}.\\
    TNMS & 20.53 & -104.80 & 2019-10-09 2019-11-26 2019-12-15 2020-03-03 2020-07-15 & UNAVCO Community, 2014, TLALOCNet - TNMS-TNMS\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T56H4FQ5}.\\
    TNNP & 16.12 & -97.14 & 2020-04-28 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, DeMets, Charles, 2016, TLALOCNet - TNNP-tnnp\_tnet\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5N29V96}.\\
    TNNX & 17.41 & -97.22 & 2020-01-15 2020-02-12 2020-12-29 2021-03-31 & UNAVCO Community, 2014, TLALOCNet - TNNX-TNNX\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T52R3PZ0}.\\
    TNPP & 31.34 & -113.63 & 2019-12-04 2020-03-31 2020-04-25 & UNAVCO Community, 2015, TLALOCNet - TNPP-TNPP\_TNET\_MX2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5CC0Z0M}.\\
    TNSJ & 16.17 & -96.49 & 2020-12-29 & UNAVCO Community, 2016, TLALOCNet - TNSJ-tnsj\_tnet\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59S1PF1}.\\
    TSFX & 30.93 & -114.81 & 2020-09-13 2020-12-23 & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network - TSFX-tsfxREGNOMmx2016 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/AGEA-2G27}.\\
    UAGU & 21.92 & -102.32 & 2019-05-23 2019-07-18 2019-08-10 2019-10-03 2019-11-17 2019-11-26 2019-12-15 2020-04-18& Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UAGU-uagu\_tnet\_mx2008 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5513WK7}.\\
    UCOE\hyperlink{Graham}{${}^3$} & 19.81 & -101.69 & 2019-08-10 2020-11-16 2020-11-17 2020-12-19 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UCOE-ucoe\_tnet\_mx2003 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T51834VW}.\\
    UGEO\hyperlink{Marquez}{${}^4$} & 20.69 & -103.35 & 2019-08-10& Marquez-Azua, Bertha, DeMets, Charles, Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UGEO-ugeo\_tnet\_mx1998 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T58S4N9N}.\\
    UHSL & 29.57 & -95.65 & 2020-04-08 & Wang, Guoquan, 2014, HoustonNet GPS Network - UHSL-SugarLandUSA2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T55X271S}.\\
    UHWL & 30.06 & -94.98 & 2020-12-19 & Wang, Guoquan, 2014, HoustonNet GPS Network - UHWL-West Liberty Airport(Deep) P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T53R0R5P}.\\
    UNPM & 20.86 & -86.86 & 2019-11-19 2020-01-15 2020-02-12 2020-05-08 & UNAVCO Community, 2012, COCONet GPS Network - UNPM-Puerto\_Morelos\_MX\_2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/J1GD-5S40}.\\
    USMX & 29.82 & -109.68 & 2019-12-29 2020-01-03 2020-01-06 2020-04-25 2020-08-07 2020-09-30& Bennett, Rick, 2004, Northwest Mexico GPS Network - USMX-Universidad de la Sierra P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5W957CQ}.\\
    UXAL\hyperlink{Graham}{${}^3$} & 19.52 & -96.92 & 2019-10-03 2020-01-15 2020-02-12 2020-04-08 2020-05-08 2020-12-19 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UXAL-uxal\_tnet\_mx2005 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5D1C}.\\
    WEPD & 29.69 & -95.23 & 2020-04-20 & Wang, Guoquan, 2014, HoustonNet GPS Network - WEPD-willmselementary P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5NZ85RB}.\\
    WMOK & 34.74 & -98.78 & 2020-04-20 & UNAVCO Community, 2005, PBO GPS Network - WMOK-WichitaMtnOK2005 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59021Q6}.\\
    WWMT\hyperlink{Hudnut}{${}^1$} & 33.96 & -116.65 & 2019-12-29 2020-01-03& Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2006, SCIGN USGS GPS Network - WWMT-Whitewater Mountain P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5H993F2}.\\
    YESX & 28.38 & -108.92 & 2019-11-26 2019-12-15 2020-01-06 2020-04-18 2020-04-28 2020-07-15& Bennett, Rick, 2004, Northwest Mexico GPS Network - YESX-Yecora P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5RJ4GPF}.\\\hline
    % \end{table*}
  \end{longtable}
    \begin{minipage}{0.9\linewidth}
      \footnotesize
      Related articles:

      \hypertarget{Hudnut}{${}^1$}\citet{Hudnut:2002},
      %
      \hypertarget{Garnier}{${}^2$}\citet{Garnier:2021}, 
      %
      \hypertarget{Graham}{${}^3$}\citet{Graham:2016}

      \hypertarget{Marquez}{${}^4$}\href{https://doi.org/10.7283/T58S4N9N}{B. Marquez-Azua, E. Cabral-Cano, F. Correa-Mora and C. DeMets, 2004. A model for Mexican neotectonics based on Nationwide GPS measurements, 1993-2001, Geofisica Internacional, v. 43, p.319-330}

      \hypertarget{Hudnut2}{${}^5$}\href{https://doi.org/10.7283/T5668BHN}{Hudnut, K. W., Y. Bock, J. E. Galetzka, F. H. Webb, and W. H. Young, The Southern California Integrated GPS Network (SCIGN), Proceedings of the International Workshop on Seismotectonics at the Subduction Zone, Y. Fujinawa (ed.), NIED, Tsukuba, Japan, pp. 175-196, 1999}

    \end{minipage}
  \end{landscape}
  \clearpage
  \twocolumn
%For the selected sample, we obtained RINEX data from the TlalocNet \citep{Cabral-Cano:2018} and UNAVCO network databases to study potential alterations in the ionospehre due to the presence of the passing meteor at the day the meteor was reported. For each event, we downloaded data from stations that surrounds the place where the event was detected (usually 3 to 5 stations. )The list of the sample meteors is shown in table \ref{tab:table-meteors}. The events are in chronological order. The reported duration, latitude and longitude correspond to the mean between measurements from satellites GOES-16 and GOES 17; in the same way, the uncertainties correspond to the standard deviation. Also their respective positions are available in figure \ref{fig:meteors-map}, where each label correspond to the ID (first column) of table \ref{tab:table-meteors}.

%Using the data provided by TlalocNet and UNAVCO, we procceeded to obtain TEC parameters with the GPS\_GOPI software, available at \url{https://seemala.blogspot.com/}. This software takes as input the RINEX data (the navigation file is no strictly neccesary), and the outuput consists in in the vTEC and sTEC measurements for the PRNs of the whole day the event occurred, as well as the averaged TEC as function of time. We obtained vTEC maps for the events in table (\ref{tab:table-meteors}) and their respective next and previous day.

%Final idea: use GOPI software to get the vTEC data from the day of each event and the previous days.

### 2021-09-02 paper/vTEC-maps.tex
Newest changes in scripts, new scripts and advances in paper
- Slight improvements to existing scripts
- Add new script where filters PRNs into a defined time interval around the moment the meteor is fragmented
- Split sections of paper into separated files
    - Advances in methodology section

Ionospheric perturbations also can take place due to space weather and geomagnetic storms. So, in order to discard such events we investigated the space weather in the day each event occured. In figure (name) we present the geomagnetic \textit{Kp} index for some events. We discarded events whose Kp index is equal or grater than 4 in the day of the event or shortly before. Also we present in figure (name) the vTEC perturbation maps for the same events in a three day series, centered in the event date. The estimated meteor trajectory, obtained from the GLM data is presented in black, continous line, while the linear fit to the GOES-16 and GOES-17 data are presented with the red dashed line, and work as boudary errors.

### 2021-09-02 filtering_vTEC_maps.py

@@ -1,10 +1,3 @@
-# Mexico map plotter
-# The main idea of this program was taken from 
-# https://towardsdatascience.com/mapping-with-matplotlib-pandas-geopandas-and-basemap-in-python-d11b57ab5dac
-# By Ashwani Dhankhar 
-# And the shape file for Mexico from CONABIO
-# http://www.conabio.gob.mx/informacion/metadata/gis/destdv250k_2gw.xml?_xsl=/db/meadata/xsl/fgdc_html.xsl&_indent=no
-
 import seaborn as sns
 import numpy as np
 import pandas as pd
@@ -18,40 +11,41 @@ import matplotlib.cm as cm
 import matplotlib.colors as colors
 from scipy.interpolate import interp1d
 from midpoint import MidpointNormalize
+from matplotlib.ticker import FormatStrFormatter
 
 
+# This is a variant of the plot_vTEC.py script which filters the vTEC data 1 hour before the event
+# and serveral hours after the event (input) and plots the PRNs which satisfy those conditions.
+# We expect to check if any of the chosen stations detected something related to the meteor pass
 
 parser = argparse.ArgumentParser(
     description=""" Choose a file to work""")
 
 
 parser.add_argument('--date', type=str, default='2000-01-01',
-			       help='Choose date. Format: yyyy-mm-dd')
+				 help='Choose date. Format: yyyy-mm-dd')
 
 parser.add_argument("--formato", type=str, default="pdf", choices=("pdf", "png", "jpg"), 
-                                help="Choose output format")
+				  help="Choose output format")
 
 parser.add_argument("--log", action="store_true", help="Use logarithmic scale for vTEC")
 
-parser.add_argument("--substract", action="store_true", help="substract the median of 27 previous days")
+parser.add_argument("--filtertime", type=float, default=1.0, help="Time filtered after the event")
 
+parser.add_argument("--filterbegins", type=float, default=0.2, help="Time filtered before the event")
 cmd_args = parser.parse_args()
[…]

### 2021-09-02 plot_stations.py

@@ -48,6 +48,12 @@ plot_map(sf)
 
 stations_pos = Table.read("station_data.tab", format="ascii")
 
+# Load and plot event position
+load_meteor_pos = Table.read("meteors_database.tab", format="ascii")
+meteor_mask = load_meteor_pos["Fecha"] == date
+plt.plot(load_meteor_pos["Longitud"][meteor_mask], load_meteor_pos["Latitud"][meteor_mask], "mo")
+
+
 # Develop dictionaries with events positions, their respective stations.
 
 dates_stations_dict = {"2019-05-23":("KVTX", "TNCU", "UAGU"), "2019-07-18":("KVTX", "MDO1", "TNCU", "UAGU"), "2019-08-10":("KVTX", "TNCU", "UAGU", "UCOE", "UGEO"), "2019-10-03":("KVTX", "UAGU", "UXAL"), "2019-10-09":("GUAX", "TNBA", "TNHM","TNMS"), "2019-11-17":("GUAX", "TNBA", "PTEX", "TSFX", "TNPP", "P001", "BAR1", "WWMT"), "2019-11-16":("KVTX", "P807", "SG33", "TNCU", "UAGU"), "2019-11-19": ("CN23", "GCFS", "UNPM"), "2019-11-26":("TNBA", "TNHM", "TNMS", "UAGU", "YESX"), "2019-12-04":("GMPK", "IAGX", "P014", "PLPX", "TNHM", "TNPP"), "2019-12-15":("GUAX", "TNBA", "TNCU", "TNHM", "TNMS", "UAGU", "YESX"), "2019-12-29":("BAR1", "BLYT", "GUAX", "P014", "PTEX", "TNBA", "TNHM", "USMX", "WWMT"), "2020-01-03":("BAR1", "BLYT", "GUAX", "P014", "PTEX", "TNBA", "TNHM", "USMX", "WWMT"), "2020-01-06":("P014", "P807", "RG07", "TNCU", "USMX", "YESX"), "2020-01-15":("CN23", "CN25", "OXTH", "TNAT", "TNNX", "UNPM", "UXAL"), "2020-02-12":("CN23", "GUAT", "UNPM", "OXTH", "TNNX", "UXAL"), "2020-03-03":("TNAM", "TNCC", "TNCM", "TNMS"), "2020-03-31":("GUAX", "TNCU", "TNHM", "TNPP"), "2020-04-08":
[…]

### 2021-10-04 paper/introduction.tex
A huge commit:
- Add program to plot Rate of TEC (sTEC or vTEC)
- Improved Program of vTEc maps to plot sTEC maps
- Program to plot Dst index
- Write something in the introduction section
- Improved stations table in methodology section

The Earth's magnetic field represents a final obstacle to the Solar Wind (SW) flux. When descelerated and defected by a non colisional shock wave in the flux direction, generates a cavity known as magnetosphere \citep{Blanco-Cano:2004}. Since the Earth is embedded in this SW flux, is known that under adequated physical conditions (e.g magnetic reconnection) may exist some coupling between the magnetosphere and the Earth's ionosphere \citep{Zolesi:2014, Cnossen:2014}.

The Sun plays an important role in the physical proccesses that occur in the terrestrial magnetosphere-ionosphere system. When the SW interacts with the Earth's magnetosphere, particles may permeate the internal region via magnetic reconnection and penetrate to polar zones and generate boreal or austral auroras thus altering the system \citep{Vazquez:2016, Oka:2011}. By the other hand, the Extreme Ultraviolet Radiation (EUV) and X-rays coming from the Sun may interact with the neutral atmoshere via photoionization \citep{Vlasov:2010}. However, in both cases the final result is that the ionosphere's free electrons population is altered.

Some Ionospheric Perturbations (IP) become relevant due to their spatial and temporal scale in the Space Weather scenario. At intermediate latitudes, the most common in the ionosphere are known as Traveling Ionospheric Disturbances (TIDs). Typically they divide into two groups: a) large scale TIDs, associated with geomagnetic storms with sizes of \SI{\sim 2000}{km}, periods of \SI{\sim 1}{h} and velocities of \SI{\sim 700}{km.s^{-1}}, and b) Medium-scale TIDs, which are not fully associated with geomagnetic storms, present sizes of \SI{\sim 100}{km}, periods from 10 minutes to 1 hour and velocities between \SI{50}{km.s^{-1}} and \SI{1e2}{km.s^{-1}} \citep{Helmboldt:2012}. Diverse methods have benn used to study TIDs, such as incoherent dispersion radars, high frequency Doppler emmisors, data from Global Positioning System (GPS) stations or even radiotelescopes like the VLA or the Mexican Array Radio Telescope (MEXART) \citep{Chilcote:2015, Rodriguez:2014}.

On the other side, the Earth's ionosphere may be affected or modified by other proccesses, particularly there are studies that show how the Vetical Total Electron Content (vTEC) due to shock waves generated for rockets launched to space \citep{Lin:2014}. Similar proccesses modify the Earth's ionosphere due to objects entering the athmosphere from space, such as meteoroids like the one which fell on Chelyabinsk at 2013 \citep{Yang:2014}. Previously, the ionospheric perturbations produced by this object were studied using two independent methods: a) detecting vTEC pertubations using GPS station near the impact location. And b) a wavelets analysis for detection of ...

In 2020 a meteoroid passed in mexican territory through mexican territory, which also was studied \citep{Sergeeva:2020}. The meteoroid was recorded with outdoor cameras in different locations. The trajectory could be estimated, as well as other physical parameters.

In this work we will show a similar analysis for a sample of meteoroids detected in mexican territory by different methods. The first subsample consists in objects detected by the Geostationary Lightning Mapper (GLM) whose sizes are estimated between a few decimeters to meters in diameter \citep{GOODMAN:2013, Jenniskens:2018, Rumpf:2019}. The second subsample will consist in objects detected by ocular witnesses from the American Meteor Society and as comparisson we will include the morelian meteoroid reported in \citet{Sergeeva:2020} and the Chelyabinsk event \citet{Yang:2014}. The paper is arranged in the following way: \S \ref{sec:methodology} describes the samples of meteoroids as well of the properties that can be obtained from direct observations. Also describes the GPS data corresponding to the dates and locations where each object was located. \S \ref{sec:bolides} shows physical parameters of meteoroids obtained from the observed heights and energies. Finally, section \S \ref{sec:vTEC-maps} shows the vTEC maps and scintillation indices obtained from GPS observations.

### 2021-10-04 paper/methodology.tex
A huge commit:
- Add program to plot Rate of TEC (sTEC or vTEC)
- Improved Program of vTEc maps to plot sTEC maps
- Program to plot Dst index
- Write something in the introduction section
- Improved stations table in methodology section

@@
-\subsection{Meteors Database}
-
+\subsection{Meteors Databases}
+\label{ssec:databases}
 We selected a sample of meteors which were observed in mexican territory from the Geostationary Lightning Mapper \citep{GOODMAN:2013}.
@@
   \centering
+  \footnotesize
   \caption{List of meteors passing through Mexico.
@@
 \label{tab:table-meteors}
-\begin{tabular}{rrrrrrr}
+\begin{tabular}{rrrrrrrr}
 \hline
-ID & Date of event & Start Time (UT)  & Duration (seconds) & Latitude (deg) & Longitude (deg) & Height (km)\\
+ID & Date of event & Start Time (UT)  & Duration (seconds) & Latitude (deg) & Longitude (deg) & Height (km) & Maximum Kp index \\
 \hline
-01 & 2019-05-23 & 16:36:18 & $0.197\pm 0.0000$ & $24.30 \pm 0.000$ & $-101.60 \pm 0.849$  & 28\\
-02 & 2019-07-18 & 14:30:30 & $0.058\pm 0.0000$ & $27.20 \pm 0.000$ & $-103.15 \pm 0.778$  & 72\\
-03 & 2019-08-10 & 11:18:48 & $0.199\pm 0.0757$ & $21.50 \pm 0.000$ & $-102.50  \pm 0.849$ & 92\\
-04 & 2019-10-03 & 07:55:33 & $0.106\pm 0.0297$ & $25.65 \pm 0.071$ & $-96.25 \pm   0.778$ & 74\\
-05 & 2019-10-09 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$ & 32\\
-06 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$ & 82\\
-07 & 2019-11-17 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$ & 88\\
-08 & 2019-11-19 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm  1.131$  & 99\\
-09 & 2019-11-26 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$ & 81\\
-10 & 2019-12-04 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$ & 77\\
-11 & 2019-12-15 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$ & 78\\
-12 & 2019-12-29 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$ & 79\\
-13 & 2020-01-03 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$ & 74\\
-14 & 2020-01-06 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$ & 81\\
-15 & 2020-01-15 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$ & 93\\
-16 & 2020-02-12 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$ & 90\\
-17 & 2020-03-03 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm 0.636$  & 77\\
-18 & 2020-03-31 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 61\\
-19 & 2020-04-08 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$ & 78\\
-20 & 2020-04-18 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$ & 82\\
-21 & 2020-04-20 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$ & 88\\
-22 & 2020-04-25 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$ & 84\\
-23 & 2020-04-28 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 29\\
-24 & 2020-05-08 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$ & 81\\
-25 & 2020-07-15 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$ & 53\\
-26 & 2020-08-07 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$ & 89\\
-27 & 2020-09-13 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$ & 85\\
-28 & 2020-09-30 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ & 83\\
-29 & 2020-11-16 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ & 06\\
-30 & 2020-11-17 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$ & 93\\
-31 & 2020-12-19 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$ & 98\\
-32 & 2020-12-23 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$ & 81\\
-33 & 2020-12-29 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$ & 81\\
-34 & 2021-03-31 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$  & 24\\\hline
+GLM-01 & 2019-05-23 & 16:36:18 & $0.197\pm 0.0000$ & $24.30 \pm 0.000$ & $-101.60 \pm 0.849$  & 28 & 2\\
+GLM-02 & 2019-07-18 & 14:30:30 & $0.058\pm 0.0000$ & $27.20 \pm 0.000$ & $-103.15 \pm 0.778$  & 72 & 1\\
+GLM-03 & 2019-08-10 & 11:18:48 & $0.199\pm 0.0757$ & $21.50 \pm 0.000$ & $-102.50  \pm 0.849$ & 92 & 3\\
+GLM-04 & 2019-10-03 & 07:55:33 & $0.106\pm 0.0297$ & $25.65 \pm 0.071$ & $-96.25 \pm   0.778$ & 74 & 2\\
+GLM-05 & 2019-10-09 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$ & 32 & 4\\
+GLM-06 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$ & 82 & 2\\
+GLM-07 & 2019-11-17 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$ & 88 & 3\\
+GLM-08 & 2019-11-19 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm  1.131$  & 99 & 1\\
+GLM-09 & 2019-11-26 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$ & 81 & 2\\
+GLM-10 & 2019-12-04 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$ & 77 & 2\\
+GLM-11 & 2019-12-15 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$ & 78 & 2\\
+GLM-12 & 2019-12-29 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$ & 79 & 1\\
+GLM-13 & 2020-01-03 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$ & 74 & 3\\
+GLM-14 & 2020-01-06 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$ & 81 & 4\\
+GLM-15 & 2020-01-15 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$ & 93 & 2\\
+GLM-16 & 2020-02-12 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$ & 90 & 2\\
+GLM-17 & 2020-03-03 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm 0.636$  & 77 & 2\hyperlink{note2}{${}^2$}\\
+GLM-18 & 2020-03-31 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 61 & 4\\
+GLM-19 & 2020-04-08 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$ & 78 & 3\\
+GLM-20 & 2020-04-18 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$ & 82 & 2\\
+GLM-21 & 2020-04-20 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$ & 88 & 5\\
+GLM-22 & 2020-04-25 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$ & 84 & 3\\
+GLM-23 & 2020-04-28 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 29 & 3\\
+GLM-24 & 2020-05-08 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$ & 81 & 1\\
+GLM-25 & 2020-07-15 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$ & 53 & 2\hyperlink{note}{${}^1$}\\
+GLM-26 & 2020-08-07 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$ & 89 & 2\\
+GLM-27 & 2020-09-13 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$ & 85 & 3\\
+GLM-28 & 2020-09-30 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ & 83 & 4\\
+GLM-29 & 2020-11-16 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ & 06 & 1\\
+GLM-30 & 2020-11-17 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$ & 93 & 1\\
+GLM-31 & 2020-12-19 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$ & 98 & 2\\
+GLM-32 & 2020-12-23 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$ & 81 & 4\\
+GLM-33 & 2020-12-29 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$ & 81 & 3\\
+GLM-34 & 2021-03-31 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$  & 24 & 3\\\hline
 \end{tabular}
+    \begin{minipage}{0.9\linewidth}
+      \footnotesize
+      \hypertarget{note}{${}^1$} Kp index is 4 the previous day of impact
+
+      \hypertarget{note2}{${}^2$}Kp index is 4 two days before the impact 
+    \end{minipage}
+
 \end{table*}
@@
 \subsection{GPS data}
-
+\label{ssec:GPS}
 This material is based on services provided by the GAGE Facility, operated by UNAVCO, Inc., with support from the National Science Foundation and the National Aeronautics and Space Administration under NSF Cooperative Agreement EAR-1724794.
@@
 We got RINEX data from 3 to 7 stations depending of the event location and data availability that surround the event place in all directions as possible.
-A list of the stations where we got RINEX data is available in table  .
+A list of the stations where we got RINEX data is available in table \ref{tab:table-stations}.
 Most of the stations lie in mexican territory, but in some cases we required data from other stations to cover events near the mexican frontier at north or south.
@@
 \onecolumn
+\footnotesize
 \begin{landscape}
@@
 %    \centering
-  \begin{longtable}{lllp{4cm}p{10cm}}
+  \begin{longtable}{llllllp{12cm}}
       \caption{List of GPS stations used for this work.}
@@
     \hline
-    Station name & Latitude & Longitude & Date of events  & Citation \\\hline
-    BAR1\hyperlink{Hudnut}{${}^1$}\hyperlink{Hudnut2}{${}^5$}& 33.48 & -119.03 & 2019-12-29 2020-01-03 & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - BAR1-Santa Barbara Island One P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5668BHN}.\\
-    BLYT\hyperlink{Hudnut}{${}^1$} & 33.61 & -114.71 & 2019-12-29 2020-01-03 & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2006, SCIGN USGS GPS Network - BLYT-Blythe P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5HT2MKK}.\\
-    CN23 & 17.26 & -88.78 & 2019-11-19 2020-01-15 2020-02-12& UNAVCO Community, 2012, COCONet GPS Network - CN23-BelmopanBZCR2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5Q23XJH}.\\
-    CN25 & 16.23 & -92.13 & 2020-01-15 & UNAVCO Community, 2014, COCONet GPS Network - CN25-ComitandDMEX2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57W69G7}.\\
-    GCFS & 19.31 & -81.18 & 2019-11-19& Watts, Anthony, 2016, COCONet GPS Network - GCFS-G\_CAYMAN\_CYM2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/7ETV-X536}.\\
-    GMPK\hyperlink{Hudnut}{${}^1$} & 33.05 & -114.83 & 2019-12-04 & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - GMPK-Glamis Peak P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/WCHN-H687}.\\
-    GUAT\hyperlink{Garnier}{${}^2$} & 14.59 & -90.52 & 2020-02-12 & DeMets, Charles, Cosenza-Muralles, Beatriz, 2021, Central America 2018 - Guatemala, The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/KH2R-K704}.\\
-    GUAX\hyperlink{Hudnut}{${}^1$} & 28.88 & -118.29 & 2019-10-09 2019-12-15 2019-12-29 2020-01-03 2020-03-31 2020-07-15 2020-09-13 2020-09-30 2020-12-23 & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2001, SCIGN USGS GPS Network - GUAX-Isla Guadalupe P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5GX48T2}.\\
-    IAGX & 29.03 & -113.17 & 2019-12-04 & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network - IAGX-iagxREGNOMmx2018 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/DGWN-A627}.\\
-    INEG & 21.85 & -102.28 & 2020-07-15 2020-08-07 2020-09-30 2020-11-16 2020-11-17 2020-12-19 & No citations were found\\
-    KVTX & 27.55 & -97.89 & 2019-05-23 2019-07-18 2019-08-10 2019-10-03 2019-11-17 2020-04-08 2020-04-18 2020-04-20 2020-05-08 2020-08-07 & UNAVCO Community, 2007, PBO GPS Network - KVTX-KingsvilleTX2006 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J38QH8}.\\
-    MDO1 & 30.68 & -104.02 & 2019-07-18& No citations were found\\
-    MGO5 & 30.68 & -104.02 & 2020-04-20 2020-08-07 & No citations were found\\
-    MGW3 & 29.62 & -89.95 & 2020-04-08 2020-04-20 2020-05-08 & No citations were found\\
-    OXTH & 16.29 & -95.24 & 2020-01-15 2020-02-12 & DeMets, Charles, Cabral-Cano, Enrique, 2008, Oaxaca GPS Network - OXTH-Tehuantepec P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5Q81B5V}.\\
-    OXUM\hyperlink{Graham}{${}^3$} & 15.66 & -96.50 & 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - OXUM-oxum\_tnet\_mx2001 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J964RP}.\\
-    P001 & 31.95 & -112.80 & 2020-04 25 & UNAVCO Community, 2008, PBO GPS Network - P001-Organ\_PipeAZ2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DR2SGP}.\\
-    P014 & 31.97 & -11.09 & 2019-12-04 2019-12-29 2020-01-03 2020-01-06 2020-04-25 & UNAVCO Community, 2008, PBO GPS Network - P014-Sahuarita\_AZ2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5CMK}.\\
-    P807 & 30.49 & -98.82 & 2019-11-17 2020-01-06 2020-04-20 2020-11-17 & UNAVCO Community, 2012, PBO GPS Network - P807-EcRockStPkTX2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5TQ5ZKM}.\\
-    PLPX & 31.59 & -115.15 & 2019-12-04 & UNAVCO Community, 2011, PBO GPS Network - PLPX-Las\_PintasMX2010 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5K64G3T}.\\
-    PTEX & 32.29 & -116.52 & 2019-12-29 2020-01-03 2020-09-13 2020-12-23 & UNAVCO Community, 2011, PBO GPS Network - PTEX-Testerazo\_MX2011 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XBP}.\\
-    RG06 & 32.63 & -107.86 & 2020-04-25 & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG06-RG06FaywodNM2006 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5668BFR}.\\
-    RG07 & 32.50 & -106.84 & 2020-01-06 & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG07-RG07CrucesNM2006 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5KD1W45}.
-\\
-    SG33 & 31.77 & -106.51 & 2019-11-17 2020-04-18 2020-08-07 & Harder, Steven, Kaip, Galen, Montana, Carlos, 2004, SuomiNet-G GPS Network - SG33-UTEP P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T50863KQ}.\\
-    TGMX  & 20.87 & -86.87 & 2021-03-31 & UNAVCO Community, 2015, COCONet GPS Network - TGMX-PtoMor\_TG\_MX2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5154FB7}.\\
-    TNAM & 20.54 & -103.97 & 2020-03-03 2020-07-15 2020-09-30 2020-11-16 2020-11-17 2020-12-19 & UNAVCO Community, 2014, TLALOCNet - TNAM-TNAM\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5QF8R4R}.\\
-    TNAT & 18.13 & -98.04 & 2020-01-15 & UNAVCO Community, 2014, TLALOCNet - TNAT-TNAT\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5G15Z4S}.\\
-    TNBA & 28.97 & -113.55 & 2019-10-09 2019-11-26 2019-12-15 2019-12-29 2020-01-03& UNAVCO Community, 2015, TLALOCNet - TNBA-TNBA\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57M0688}.\\
-    TNCC & 18.79 & -103.17 & 2020-03-03 & UNAVCO Community, 2015, TLALOCNet - TNCC-TNCC\_TNET\_MX2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T50R9MSK}.\\
-    TNCM & 19.50 & -105.04 & 2020-03-03 2020-04-28 & UNAVCO Community, 2014, TLALOCNet - TNCM-TNCM\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5B856FW}.\\
-    TNCN & 18.55 & -101.97 & 2020-11-16 2020-12-29 & UNAVCO Community, 2016, TLALOCNet - TNCN-TNCN\_TNET\_MX2016 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XQM}.\\
-    TNCU & 28.45 & -106.79 & 2019-05-23 2019-07-18 2019-08-10 2019-11-17 2019-12-15 2020-01-06 2020-03-31 2020-04-18 2020-07-15 2020-08-07 2020-11-17 2020-12-19 & UNAVCO Community, 2014, TLALOCNet - TNCU-CuauhtemocTN2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5V69GV2}.\\
-    TNGF & 19.33 & -99.18 & 2020-11-16 2020-12-29 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2016, TLALOCNet GPS Network - TNGF\_Geofisica-UNAM\_Mexico\_City\_TNET\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T53X851M}.\\
-    TNHM & 29.08 & -110.97 & 2019-10-09 2019-11-26 2019-12-04 2019-12-15 2019-12-29 2020-01-03 2020-03-31 2020-04-18 2020-07-15 2020-08-07 2020-09-13 2020-09-30 2020-12-23 & UNAVCO Community, 2014, TLALOCNet - TNHM-hermosilloTN2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5KP80FV}.\\
-    TNMS & 20.53 & -104.80 & 2019-10-09 2019-11-26 2019-12-15 2020-03-03 2020-07-15 & UNAVCO Community, 2014, TLALOCNet - TNMS-TNMS\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T56H4FQ5}.\\
-    TNNP & 16.12 & -97.14 & 2020-04-28 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, DeMets, Charles, 2016, TLALOCNet - TNNP-tnnp\_tnet\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5N29V96}.\\
-    TNNX & 17.41 & -97.22 & 2020-01-15 2020-02-12 2020-12-29 2021-03-31 & UNAVCO Community, 2014, TLALOCNet - TNNX-TNNX\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T52R3PZ0}.\\
-    TNPP & 31.34 & -113.63 & 2019-12-04 2020-03-31 2020-04-25 & UNAVCO Community, 2015, TLALOCNet - TNPP-TNPP\_TNET\_MX2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5CC0Z0M}.\\
-    TNSJ & 16.17 & -96.49 & 2020-12-29 & UNAVCO Community, 2016, TLALOCNet - TNSJ-tnsj\_tnet\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59S1PF1}.\\
-    TSFX & 30.93 & -114.81 & 2020-09-13 2020-12-23 & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network - TSFX-tsfxREGNOMmx2016 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/AGEA-2G27}.\\
-    UAGU & 21.92 & -102.32 & 2019-05-23 2019-07-18 2019-08-10 2019-10-03 2019-11-17 2019-11-26 2019-12-15 2020-04-18& Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UAGU-uagu\_tnet\_mx2008 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5513WK7}.\\
-    UCOE\hyperlink{Graham}{${}^3$} & 19.81 & -101.69 & 2019-08-10 2020-11-16 2020-11-17 2020-12-19 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UCOE-ucoe\_tnet\_mx2003 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T51834VW}.\\
-    UGEO\hyperlink{Marquez}{${}^4$} & 20.69 & -103.35 & 2019-08-10& Marquez-Azua, Bertha, DeMets, Charles, Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UGEO-ugeo\_tnet\_mx1998 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T58S4N9N}.\\
-    UHSL & 29.57 & -95.65 & 2020-04-08 & Wang, Guoquan, 2014, HoustonNet GPS Network - UHSL-SugarLandUSA2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T55X271S}.\\
-    UHWL & 30.06 & -94.98 & 2020-12-19 & Wang, Guoquan, 2014, HoustonNet GPS Network - UHWL-West Liberty Airport(Deep) P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T53R0R5P}.\\
-    UNPM & 20.86 & -86.86 & 2019-11-19 2020-01-15 2020-02-12 2020-05-08 & UNAVCO Community, 2012, COCONet GPS Network - UNPM-Puerto\_Morelos\_MX\_2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/J1GD-5S40}.\\
-    USMX & 29.82 & -109.68 & 2019-12-29 2020-01-03 2020-01-06 2020-04-25 2020-08-07 2020-09-30& Bennett, Rick, 2004, Northwest Mexico GPS Network - USMX-Universidad de la Sierra P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5W957CQ}.\\
-    UXAL\hyperlink{Graham}{${}^3$} & 19.52 & -96.92 & 2019-10-03 2020-01-15 2020-02-12 2020-04-08 2020-05-08 2020-12-19 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UXAL-uxal\_tnet\_mx2005 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5D1C}.\\
-    WEPD & 29.69 & -95.23 & 2020-04-20 & Wang, Guoquan, 2014, HoustonNet GPS Network - WEPD-willmselementary P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5NZ85RB}.\\
-    WMOK & 34.74 & -98.78 & 2020-04-20 & UNAVCO Community, 2005, PBO GPS Network - WMOK-WichitaMtnOK2005 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59021Q6}.\\
-    WWMT\hyperlink{Hudnut}{${}^1$} & 33.96 & -116.65 & 2019-12-29 2020-01-03& Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2006, SCIGN USGS GPS Network - WWMT-Whitewater Mountain P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5H993F2}.\\
-    YESX & 28.38 & -108.92 & 2019-11-26 2019-12-15 2020-01-06 2020-04-18 2020-04-28 2020-07-15& Bennett, Rick, 2004, Northwest Mexico GPS Network - YESX-Yecora P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5RJ4GPF}.\\\hline
-    % \end{table*}
+    Station name & Latitude & Longitude & \multicolumn{3}{c}{Events ID}  & Citation \\\hline
+    \multirow{4}{*}{BAR1\hyperlink{Hudnut}{${}^1$}\hyperlink{Hudnut2}{${}^5$}} & \multirow{4}{*}{33.48} & \multirow{4}{*}{-119.03} & \multirow{4}{*}{GLM-07} & \multirow{4}{*}{GLM-12} & \multirow{4}{*}{GLM-13} & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, \\
+    &&&&&& Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - BAR1-Santa \\
+    &&&&&& Barbara Island One P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+    &&&&&& \url{https://doi.org/10.7283/T5668BHN}.\\\hline
+    \multirow{3}{*}{BLYT\hyperlink{Hudnut}{${}^1$}} & \multirow{3}{*}{33.61} & \multirow{3}{*}{-114.71} &  \multirow{3}{*}{GLM-12} & \multirow{3}{*}{GLM-13}  & & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John \\
+    &&&&&& E., Stark, Keith F., 2006, SCIGN USGS GPS Network - BLYT-Blythe P.S., The GAGE Facility operated \\
+    &&&&&&  by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5HT2MKK}.\\\hline
+    \multirow{3}{*}{CN23} & \multirow{3}{*}{17.26} & \multirow{3}{*}{-88.78} &\multirow{3}{*}{GLM-08} & \multirow{3}{*}{GLM-15} & \multirow{3}{*}{GLM-16} & UNAVCO Community, 2012, COCONet GPS Network - CN23-BelmopanBZCR2012 P.S., The GAGE \\
+    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+    &&&&&& \url{https://doi.org/10.7283/T5Q23XJH}.\\\hline
+    \multirow{3}{*}{CN25} & \multirow{3}{*}{16.23} & \multirow{3}{*}{-92.13} & \multirow{3}{*}{GLM-15} & & & UNAVCO Community, 2014, COCONet GPS Network - CN25-ComitandDMEX2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57W69G7}.\\\hline
+    \multirow{3}{*}{GCFS} & \multirow{3}{*}{19.31} & \multirow{3}{*}{-81.18} & \multirow{3}{*}{GLM-08} & & & Watts, Anthony, 2016, COCONet GPS Network - GCFS-G\_CAYMAN\_CYM2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/7ETV-X536}.\\\hline
+    \multirow{4}{*}{GMPK\hyperlink{Hudnut}{${}^1$}} & \multirow{4}{*}{33.05} & \multirow{4}{*}{-114.83} & \multirow{4}{*}{GLM-10} & & & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, \\
+    &&&&&& Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - GMPK-Glamis \\
+    &&&&&& Peak P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+    &&&&&& \url{https://doi.org/10.7283/WCHN-H687}.\\\hline
+    \multirow{3}{*}{GUAT\hyperlink{Garnier}{${}^2$}} & \multirow{3}{*}{14.59} & \multirow{3}{*}{-90.52} & \multirow{3}{*}{GLM-16} & & & DeMets, Charles, Cosenza-Muralles, Beatriz, 2021, Central America 2018 - Guatemala, The GAGE \\
+    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+    &&&&&& \url{https://doi.org/10.7283/KH2R-K704}.\\\hline
+\multirow{4}{*}{GUAX\hyperlink{Hudnut}{${}^1$}} & \multirow{4}{*}{28.88} & \multirow{4}{*}{-118.29} & GLM-05 & GLM-07 & GLM-11 & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John \\
+    &&&GLM-12& GLM-13& GLM-18 & E., Stark, Keith F., 2001, SCIGN USGS GPS Network - GUAX-Isla Guadalupe P.S., The GAGE Facility \\
+    &&& GLM-25 &GLM-27 &GLM-28& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5GX48T2}.\\
+    &&& GLM-32 &       &     &  \\\hline
+    \multirow{3}{*}{IAGX} & \multirow{3}{*}{29.03} & \multirow{3}{*}{-113.17} & \multirow{3}{*}{GLM-10} & & & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network \\
+    &&&&&& - IAGX-iagxREGNOMmx2018 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS  \\
+    &&&&&& Observations Dataset, \url{https://doi.org/10.7283/DGWN-A627}. \\\hline
+    \multirow{2}{*}{INEG} & \multirow{2}{*}{21.85} & \multirow{2}{*}{-102.28} & GLM-25 & GLM-26 & GLM-28  & No citations were found \\
+    &&& GLM-29 & GLM-30 & GLM-31 & \\\hline 
+    \multirow{4}{*}{KVTX} & \multirow{4}{*}{27.55} & \multirow{4}{*}{-97.89} & GLM-01 & GLM-02 & GLM-03  & UNAVCO Community, 2007, PBO GPS Network - KVTX-KingsvilleTX2006 P.S., The GAGE Facility \\
+    &&& GLM-04 & GLM-06 & GLM-19 & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J38QH8}.\\
+    &&& GLM-20 & GLM-21 & GLM-24 & \\
+    &&& GLM-26 &&& \\\hline
+    MDO1 & 30.68 & -104.02 & GLM-02 & & & No citations were found\\\hline
+    MGO5 & 30.68 & -104.02 & GLM-21 &GLM-26 &  & No citations were found\\\hline
+    MGW3 & 29.62 & -89.95 & GLM-19 & GLM-21 & GLM-24 & No citations were found\\\hline
+    \multirow{3}{*}{OXTH} & \multirow{3}{*}{16.29} & \multirow{3}{*}{-95.24} & \multirow{3}{*}{GLM-15} & \multirow{3}{*}{GLM-16} & & DeMets, Charles, Cabral-Cano, Enrique, 2008, Oaxaca GPS Network - OXTH-Tehuantepec P.S., The \\
+    &&&&&& GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+    &&&&&& \url{https://doi.org/10.7283/T5Q81B5V}.\\\hline
+    \multirow{3}{*}{OXUM\hyperlink{Graham}{${}^3$}} & \multirow{3}{*}{15.66} & \multirow{3}{*}{-96.50} & \multirow{3}{*}{GLM-34} & & & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - OXUM-oxum\_tnet\_mx2001 P.S., The \\
+    &&&&&& GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+    &&&&&& \url{https://doi.org/10.7283/T5J964RP}.\\\hline
+    \multirow{2}{*}{P001} & \multirow{2}{*}{31.95} & \multirow{2}{*}{-112.80} & \multirow{2}{*}{GLM-07} & \multirow{2}{*}{GLM-22} & & UNAVCO Community, 2008, PBO GPS Network - P001-Organ\_PipeAZ2007 P.S., The GAGE Facility \\
+    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DR2SGP}.\\\hline
+    \multirow{2}{*}{P014} & \multirow{2}{*}{31.97} & \multirow{2}{*}{-11.09} & GLM-10 & GLM-12 & GLM-13 & UNAVCO Community, 2008, PBO GPS Network - P014-Sahuarita\_AZ2007 P.S., The GAGE Facility \\
+    &&& GLM-14 & GLM-22 & & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5CMK}.\\\hline
+    \multirow{2}{*}{P807} & \multirow{2}{*}{30.49} & \multirow{2}{*}{-98.82} & GLM-06 & GLM-14 & GLM-21 & UNAVCO Community, 2012, PBO GPS Network - P807-EcRockStPkTX2012 P.S., The GAGE Facility \\
+    &&& GLM-30 &&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5TQ5ZKM}.\\\hline
+    \multirow{2}{*}{PLPX} & \multirow{2}{*}{31.59} & \multirow{2}{*}{-115.15} & \multirow{2}{*}{GLM-10} & & & UNAVCO Community, 2011, PBO GPS Network - PLPX-Las\_PintasMX2010 P.S., The GAGE Facility \\
+    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5K64G3T}.\\\hline
+    \multirow{2}{*}{PTEX} & \multirow{2}{*}{32.29} & \multirow{2}{*}{-116.52} & GLM-07 & GLM-12 & GLM-13  & UNAVCO Community, 2011, PBO GPS Network - PTEX-Testerazo\_MX2011 P.S., The GAGE Facility \\
+    &&& GLM-27 & GLM-32 & & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XBP}.\\\hline 
+    \multirow{3}{*}{RG06} & \multirow{3}{*}{32.63} & \multirow{3}{*}{-107.86} & \multirow{3}{*}{GLM-22} & & & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG06-RG06FaywodNM2006 P.S., The GAGE \\
+    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+    &&&&&& \url{https://doi.org/10.7283/T5668BFR}.\\\hline
+    \multirow{3}{*}{RG07} & \multirow{3}{*}{32.50} & \multirow{3}{*}{-106.84} & \multirow{3}{*}{GLM-14} & & & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG07-RG07CrucesNM2006 P.S., The GAGE  \\
+    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+    &&&&&& \url{https://doi.org/10.7283/T5KD1W45}. \\\hline
+    \multirow{3}{*}{SG33} & \multirow{3}{*}{31.77} & \multirow{3}{*}{-106.51} & \multirow{3}{*}{GLM-06} & \multirow{3}{*}{GLM-20} & \multirow{3}{*}{GLM-26} & Harder, Steven, Kaip, Galen, Montana, Carlos, 2004, SuomiNet-G GPS Network - SG33-UTEP P.S., The \\
+    &&&&&& GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset,  \\
+    &&&&&& \url{https://doi.org/10.7283/T50863KQ}. \\\hline
+    \multirow{3}{*}{TGMX}  & \multirow{3}{*}{20.87} & \multirow{3}{*}{-86.87} & \multirow{3}{*}{GLM-34} & & & UNAVCO Community, 2015, COCONet GPS Network - TGMX-PtoMor\_TG\_MX2015 P.S., The GAGE \\
+    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset,  \\
+    &&&&&& \url{https://doi.org/10.7283/T5154FB7}. \\\hline
+    \multirow{2}{*}{TNAM} & \multirow{2}{*}{20.54} & \multirow{2}{*}{-103.97} & GLM-17 & GLM-25 & GLM-28  & UNAVCO Community, 2014, TLALOCNet - TNAM-TNAM\_TNET\_MX2014 P.S., The GAGE Facility \\
+    &&& GLM-29 & GLM-30 & GLM-31 & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5QF8R4R}.\\\hline
+    \multirow{2}{*}{TNAT} & \multirow{2}{*}{18.13} & \multirow{2}{*}{-98.04} & \multirow{2}{*}{GLM-15} & & & UNAVCO Community, 2014, TLALOCNet - TNAT-TNAT\_TNET\_MX2014 P.S., The GAGE Facility \\
+    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5G15Z4S}. \\\hline
+    \multirow{2}{*}{TNBA} & \multirow{2}{*}{28.97} & \multirow{2}{*}{-113.55} & GLM-05 & GLM-07 & GLM-09  & UNAVCO Community, 2015, TLALOCNet - TNBA-TNBA\_TNET\_MX2014 P.S., The GAGE Facility  \\
+    &&& GLM-11 & GLM-12 & GLM-13 & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57M0688}.\\\hline
+    \multirow{2}{*}{TNCC} & \multirow{2}{*}{18.79} & \multirow{2}{*}{-103.17} & \multirow{2}{*}{GLM-17} & & & UNAVCO Community, 2015, TLALOCNet - TNCC-TNCC\_TNET\_MX2015 P.S., The GAGE Facility \\
+    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T50R9MSK}.\\\hline
+    \multirow{2}{*}{TNCM} & \multirow{2}{*}{19.50} & \multirow{2}{*}{-105.04} & \multirow{2}{*}{GLM-17} & \multirow{2}{*}{GLM-23} & & UNAVCO Community, 2014, TLALOCNet - TNCM-TNCM\_TNET\_MX2014 P.S., The GAGE Facility \\
+    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5B856FW}.\\\hline
+    \multirow{2}{*}{TNCN} & \multirow{2}{*}{18.55} & \multirow{2}{*}{-101.97} & \multirow{2}{*}{GLM-29} & \multirow{2}{*}{GLM-33} & & UNAVCO Community, 2016, TLALOCNet - TNCN-TNCN\_TNET\_MX2016 P.S., The GAGE Facility \\
+    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XQM}.\\\hline
+    \multirow{4}{*}{TNCU} & \multirow{4}{*}{28.45} & \multirow{4}{*}{-106.79} & GLM-01 & GLM-02 & GLM-03  & UNAVCO Community, 2014, TLALOCNet - TNCU-CuauhtemocTN2014 P.S., The GAGE Facility \\
+    &&& GLM-06 & GLM-11 & GLM-14 & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5V69GV2}.\\
+    &&& GLM-18 & GLM-20 & GLM-25 & \\
+    &&& GLM-26 & GLM-30 & GLM-31 & \\\hline
+    \multirow{3}{*}{TNGF} & \multirow{3}{*}{19.33} & \multirow{3}{*}{-99.18} & \multirow{3}{*}{GLM-29} & \multirow{3}{*}{GLM-33} & & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2016, TLALOCNet GPS Network - TNGF\_Geofisica-\\
+    &&&&&& UNAM\_Mexico\_City\_TNET\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS \\
+    &&&&&& Observations Dataset, \url{https://doi.org/10.7283/T53X851M}. \\\hline
+    \multirow{5}{*}{TNHM} & \multirow{5}{*}{29.08} & \multirow{5}{*}{-110.97} & GLM-05 & GLM-09 & GLM-10 & UNAVCO Community, 2014, TLALOCNet - TNHM-hermosilloTN2014 P.S., The GAGE Facility \\
+    &&& GLM-11 & GLM-12 & GLM-13 & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5KP80FV}.\\
+    &&& GLM-18 & GLM-20 & GLM-25 & \\
+    &&& GLM-26 & GLM-27 & GLM-28 & \\
+    &&& GLM-32 &        &        & \\\hline
+    \multirow{2}{*}{TNMS} & \multirow{2}{*}{20.53} & \multirow{2}{*}{-104.80} & GLM-05 & GLM-09 & GLM-11  & UNAVCO Community, 2014, TLALOCNet - TNMS-TNMS\_TNET\_MX2014 P.S., The GAGE Facility \\
+    &&& GLM-17 & GLM-25 & & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T56H4FQ5}.\\\hline
+    \multirow{3}{*}{TNNP} & \multirow{3}{*}{16.12} & \multirow{3}{*}{-97.14} & \multirow{3}{*}{GLM-23} & & & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, DeMets, Charles, 2016, TLALOCNet - TNNP-\\
+    &&&&&& tnnp\_tnet\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+    &&&&&& \url{https://doi.org/10.7283/T5N29V96}. \\\hline
+    \multirow{2}{*}{TNNX} & \multirow{2}{*}{17.41} & \multirow{2}{*}{-97.22} & GLM-15 & GLM-16 & GLM-33  & UNAVCO Community, 2014, TLALOCNet - TNNX-TNNX\_TNET\_MX2014 P.S., The GAGE Facility \\
+    &&& GLM-34 &&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T52R3PZ0}.\\\hline
+    \multirow{2}{*}{TNPP} & \multirow{2}{*}{31.34} & \multirow{2}{*}{-113.63} & GLM-07 & GLM-10 & GLM-18 & UNAVCO Community, 2015, TLALOCNet - TNPP-TNPP\_TNET\_MX2015 P.S., The GAGE Facility \\
+    &&& GLM-22 &&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5CC0Z0M}.\\\hline
+    \multirow{2}{*}{TNSJ} & \multirow{2}{*}{16.17} & \multirow{2}{*}{-96.49} & \multirow{2}{*}{GLM-33} & & & UNAVCO Community, 2016, TLALOCNet - TNSJ-tnsj\_tnet\_mx2015 P.S., The GAGE Facility operated by \\
+    &&&&&& UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59S1PF1}.\\\hline
+    \multirow{3}{*}{TSFX} & \multirow{3}{*}{30.93} & \multirow{3}{*}{-114.81} & \multirow{3}{*}{GLM-07} & \multirow{3}{*}{GLM-27} & \multirow{3}{*}{GLM-32} & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network \\
+    &&&&&& - TSFX-tsfxREGNOMmx2016 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS \\
+    &&&&&& Observations Dataset, \url{https://doi.org/10.7283/AGEA-2G27}.\\\hline
+    \multirow{3}{*}{UAGU} & \multirow{3}{*}{21.92} & \multirow{3}{*}{-102.32} & GLM-01 & GLM-02 & GLM-03  & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UAGU-uagu\_tnet\_mx2008 P.S., The \\
+    &&& GLM-04 & GLM-06 & GLM-09 & GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+    &&& GLM-11 & GLM-20 &        & \url{https://doi.org/10.7283/T5513WK7}.\\\hline
+    \multirow{3}{*}{UCOE\hyperlink{Graham}{${}^3$}} & \multirow{3}{*}{19.81} & \multirow{3}{*}{-101.69} & GLM-03 & GLM-06 & GLM-30 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UCOE-ucoe\_tnet\_mx2003 P.S., The \\
+    &&& GLM-31 &&& GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+    &&&&&& \url{https://doi.org/10.7283/T51834VW}. \\\hline
+    \multirow{3}{*}{UGEO\hyperlink{Marquez}{${}^4$}} & \multirow{3}{*}{20.69} & \multirow{3}{*}{-103.35} & \multirow{3}{*}{GLM-03} & & & Marquez-Azua, Bertha, DeMets, Charles, Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, \\
+    &&&&&& TLALOCNet - UGEO-ugeo\_tnet\_mx1998 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS \\
+    &&&&&& Observations Dataset, \url{https://doi.org/10.7283/T58S4N9N}. \\\hline
+    \multirow{2}{*}{UHSL} & \multirow{2}{*}{29.57} & \multirow{2}{*}{-95.65} & \multirow{2}{*}{GLM-19} & & & Wang, Guoquan, 2014, HoustonNet GPS Network - UHSL-SugarLandUSA2014 P.S., The GAGE Facility \\
+    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T55X271S}.\\\hline
+    \multirow{3}{*}{UHWL} & \multirow{3}{*}{30.06} & \multirow{3}{*}{-94.98} & \multirow{3}{*}{GLM-31} & & & Wang, Guoquan, 2014, HoustonNet GPS Network - UHWL-West Liberty Airport(Deep) P.S., The GAGE \\
+    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset,  \\
+    &&&&&& \url{https://doi.org/10.7283/T53R0R5P}. \\\hline
+    \multirow{3}{*}{UNPM} & \multirow{3}{*}{20.86} & \multirow{3}{*}{-86.86} & GLM-08 & GLM-15 & GLM-16  & UNAVCO Community, 2012, COCONet GPS Network - UNPM-Puerto\_Morelos\_MX\_2007 P.S., The \\
+    &&& GLM-24 &&& GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+    &&&&&& \url{https://doi.org/10.7283/J1GD-5S40}.\\\hline
+    \multirow{3}{*}{USMX} & \multirow{3}{*}{29.82} & \multirow{3}{*}{-109.68} & GLM-12 & GLM-13 & GLM-14  & Bennett, Rick, 2004, Northwest Mexico GPS Network - USMX-Universidad de la Sierra P.S., The GAGE \\
+    &&& GLM-22 & GLM-26 & GLM-28 & Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+    &&&&&& \url{https://doi.org/10.7283/T5W957CQ}.\\\hline
+    \multirow{3}{*}{UXAL\hyperlink{Graham}{${}^3$}} & \multirow{3}{*}{19.52} & \multirow{3}{*}{-96.92} & GLM-04 & GLM-15 & GLM-16  & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UXAL-uxal\_tnet\_mx2005 P.S., The \\
+    &&& GLM-19 & GLM-24 & GLM-31 & GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+    &&& GLM-34 &        &        & \url{https://doi.org/10.7283/T5DJ5D1C}.\\\hline
+    \multirow{2}{*}{WEPD} & \multirow{2}{*}{29.69} & \multirow{2}{*}{-95.23} & \multirow{2}{*}{GLM-21} & & & Wang, Guoquan, 2014, HoustonNet GPS Network - WEPD-willmselementary P.S., The GAGE Facility \\
+    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5NZ85RB}. \\\hline
+    \multirow{2}{*}{WMOK} & \multirow{2}{*}{34.74} & \multirow{2}{*}{-98.78} & \multirow{2}{*}{GLM-21} & & & UNAVCO Community, 2005, PBO GPS Network - WMOK-WichitaMtnOK2005 P.S., The GAGE Facility \\
+    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59021Q6}. \\\hline
+    \multirow{4}{*}{WWMT\hyperlink{Hudnut}{${}^1$}} & \multirow{4}{*}{33.96} & \multirow{4}{*}{-116.65} & \multirow{4}{*}{GLM-07} & \multirow{4}{*}{GLM-12} & \multirow{4}{*}{GLM-13} & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John \\
+    &&&&&& E., Stark, Keith F., 2006, SCIGN USGS GPS Network - WWMT-Whitewater Mountain P.S., The GAGE \\
+    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset,  \\
+    &&&&&& \url{https://doi.org/10.7283/T5H993F2}. \\\hline
+    \multirow{2}{*}{YESX} & \multirow{2}{*}{28.38} & \multirow{2}{*}{-108.92} & GLM-09 & GLM-11 & GLM-14  & Bennett, Rick, 2004, Northwest Mexico GPS Network - YESX-Yecora P.S., The GAGE Facility operated \\
+    &&&GLM-20 & GLM-23 & GLM-25 & by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5RJ4GPF}.\\\hline
+
+%    % \end{table*}
   \end{longtable}
@@
 175-196, 1999}
-
     \end{minipage}
@@
   \twocolumn
+
+  The obtained RINEX files are compressed in Hatanaka format, developed at the Geographical Survey Institute by Y.
+Hatanaka \citep{Kumar:2012}.
+From this files we may estimate the Slant Total Electron Content (sTEC) and the Vertical Total Electron Content (vTEC) which may be computed in the following way:
+
+  The Total Electron content along the integrated path of the link $(s_i)$ at the frequency $f_i$ can be inferred from the phase delay $L_i$ of the frequency $f_i$ \citep{Emery:2017}:
+  \begin{align}
+    L_i = s_i - \frac{\SI{40.3082}{m^3.s^{-1}}}{f_i^2}sTEC_i
+  \end{align}
+  Combining two observations at two different frequencies $f_1$ and $f_2$ we may obtain two different phase delays $L_1$ and $L_2$ and derive the TEC along the signal path:
+
+  \begin{align}
+    sTEC = \frac{f_1^2f_2^2\left(L_1-L_2\right)}{\SI{40.3082}{m^3.s^{-1}}\left(f_1^2-f_2^2\right)}
+  \end{align}
+
+  In the other hand, the Vertical Total Electron Content (vTEC) is computed from the sTEC as follows \citep{Kumar:2012}:
+  \begin{align}
+    vTEC = \frac{sTEC-\left[b_R+b_S\right]}{S(\theta_I)}
+  \end{align}
+
+  where $b_R$ and $b_S$ are receiver and satellite biases, respectively.
+$\theta_I$ is the elevation angle in degrees, $S(\theta_I)$ is the obliquity factor with zenith angle $\psi$ at the Ionospheric Pierce Point (IPP):
+
+  \begin{align}
+    S(\theta_i) = \frac{1}{\cos\psi} = \left\lbrace 1-\frac{R_E\cos\theta_I}{R_E+h}\right\rbrace^{-1/2}
+  \end{align}
+
+  Where $R_E$ is the Earth radius in km and $h=\SI{350}{km}$ is the ionospheric shell above the earth's surface.
+
+  Both parameters sTEC and vTEC are computed using a software developed by Gopi K. Seemala, publicly available at \url{https://seemala.blogspot.com/}.
+
 %For the selected sample, we obtained RINEX data from the TlalocNet \citep{Cabral-Cano:2018} and UNAVCO network databases to study potential alterations in the ionospehre due to the presence of the passing meteor at the day the meteor was reported.

### 2021-10-04 Dst_index.py

@@ -1,0 +1,69 @@
+import numpy as np
+from astropy.table import Table
+import argparse 
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+# Script goal: Plot Dst index vs time
+#                                      WDC for Geomagnetism, Kyoto
+#                                Hourly Equatorial Dst Values (REAL-TIME)  
+
+# Read arguments from Terminal and open file
+
+parser = argparse.ArgumentParser(
+    description=""" Choose a file to work""")
+
+
+parser.add_argument('--date', type=str, default='2000-01-01',
+			       help='Choose date. Format: yyyy-mm-dd')
+
+cmd_args = parser.parse_args()
+date = cmd_args.date
+year, month, day = date.split("-")
+datafile = "Dst-index-"+month+"-"+year+".txt"
+directory = "./Dst index/" 
+f = open(directory+datafile, "r")
+
+# Extract information from file
+
+h1 = f.readline()
+print(h1)
+h2 = f.readline()
+print(h2)
+h3 = f.readline()
+print(h3)
+f.readline()
+time_str = f.readline()
+f.readline()
+data = f.readlines()
+
+Tabdata= Table.read(data, format="ascii")
+Dst_index = []
+
+mask = Tabdata["col1"]==int(day)
+maskp = Tabdata["col1"]==int(day) - 1
+# Set the time array for plotting
+
+time = time_str.split()
+for i in range(len(time)):
+    time[i] = int(time[i])
+#time=timep+24
+#time_c = np.array([timep, time])
+#time_c = np.reshape()
+# Set the Dst index array for plotting
+for k in Tabdata.keys()[1:]:
+    Dst_index.append(Tabdata[k][mask][0])
+
+# Plot Dst-index vs time
+
+sns.set_style("whitegrid")
+plt.plot(time, Dst_index)
+plt.xlim(0, 24)
+plt.ylim(-500, 100)
+plt.title("DST (Final)")
+plt.text(0, 85, day+" "+h3.lstrip())
+plt.text(15, 85, h1.lstrip())
+plt.xlabel("Time (UT, hours)")
+plt.ylabel("Dst Index (nT)")
+outfile = datafile.replace(".txt", ".pdf")
+plt.savefig(directory+outfile)

### 2021-10-04 delta_vTEC.py

@@ -1,9 +1,13 @@
-# Mexico map plotter
-# The main idea of this program was taken from 
-# https://towardsdatascience.com/mapping-with-matplotlib-pandas-geopandas-and-basemap-in-python-d11b57ab5dac
-# By Ashwani Dhankhar 
-# And the shape file for Mexico from CONABIO
-# http://www.conabio.gob.mx/informacion/metadata/gis/destdv250k_2gw.xml?_xsl=/db/meadata/xsl/fgdc_html.xsl&_indent=no
+# To check if vTEC is strongly perturbed (as we may expect from a meteor entrance), we may calculate the parameter
+# \delta, defined as:
+
+#             (vTEC_max - <vTEC>)
+#   \delta = ---------------------- (Martinez et al. 2014)
+#                    <vTEC>
+# If \delta >~4 is an indication that the vTEC is strongly disturbed. But since the observed meteors in the GLM sample are small ( <~1m ), we will be less strict with this criteria
+# and set |\delta| >~ 2 and compute this parameter instead of vTEC itself
+
+# For this we will do a variant of the vTEC_maps program since we will compute \delta for each vTEC measurement. <vTEC> will be obtained from the average TEC in ths .Std file.
 
 import seaborn as sns
 import numpy as np
@@ -177,40 +181,33 @@ for f, g, fp, gp, fn, gn in zip(load_dirs, load_std, load_dir_p, load_std_p, loa
                 subs_TEC[i] = np.nan
         subs_TEC_int = interp1d(std_time, subs_TEC) # Maybe substract the mean TEC AND the background TEC is redundant
         if datatype == "vTEC":
-            dTEC =  obs_tab["Vtec"][mask2] - subs_TEC_int(cmn_time[mask2])
-            dTEC_p = obs_tab_p["Vtec"][mask2_p] -subs_TEC_int(cmn_time_p[mask2_p])
[…]

### 2021-10-04 plot_TEC_gradient.py

@@ -5,6 +5,9 @@
 # And the shape file for Mexico from CONABIO
 # http://www.conabio.gob.mx/informacion/metadata/gis/destdv250k_2gw.xml?_xsl=/db/meadata/xsl/fgdc_html.xsl&_indent=no
 
+# This is a clone of the vTEC_maps.py script except in this case we will compute the gradient of TEC instead of substracting the actual TEC from 
+# some backgrond (or not?)
+
 import seaborn as sns
 import numpy as np
 import pandas as pd
@@ -18,7 +21,6 @@ import matplotlib.cm as cm
 import matplotlib.colors as colors
 from scipy.interpolate import interp1d
 from midpoint import MidpointNormalize
-
 
 
 parser = argparse.ArgumentParser(
@@ -53,20 +55,20 @@ sns.set_style("whitegrid")
 # Load RINEX capabilities
 
 rinex_files = glob.glob(directory+"/*.Cmn")
-std_files = glob.glob(directory+"/*.Std")
+#std_files = glob.glob(directory+"/*.Std")
 load_dirs = [open(rinex_files[i], "r") for i in range(len(rinex_files))]
-load_std = [Table.read(std_files[i], format="ascii") for i in range(len(std_files))]
+#load_std = [Table.read(std_files[i], format="ascii") for i in range(len(std_files))]
 
 
 rinex_p = glob.glob(p_directory+"*.Cmn")
-std_p = glob.glob(p_directory+"*.Std")
+#std_p = glob.glob(p_directory+"*.Std")
 rinex_n = glob.glob(n_directory+"*.Cmn")
-std_n = glob.glob(n_directory+"*.Std")
+#std_n = glob.glob(n_directory+"*.Std")
 
 load_dir_p = [open(rinex_p[i], "r") for i in range(len(rinex_p))]
-load_std_p = [Table.read(std_p[i], format="ascii") for i in range(len(std_p))]
+#load_std_p = [Table.read(std_p[i], format="ascii") for i in range(len(std_p))]
 load_dir_n = [open(rinex_n[i], "r") for i in range(len(rinex_n))]
[…]

### 2021-10-19 GLM_energy.py
LACIGE computer update
Update repository into LACIGE computer

@@ -10,7 +10,7 @@ import glob
 
 # Get a list of the paths of al GLM data
 
-dates = ["2019-05-23", "2019-07-18", "2019-08-10", "2019-10-03", "2019-10-09", "2019-11-16", "2019-11-17", "2019-11-19", "2019-11-26", "2019-12-04", "2019-12-15", "2019-12-29", "2020-01-03", "2020-01-06", "2020-01-15", "2020-02-12", "2020-03-03", "2020-03-31", "2020-04-08", "2020-04-18", "2020-04-20", "2020-04-25", "2020-04-28", "2020-05-08", "2020-07-15", "2020-08-07", "2020-09-13","2020-09-30", "2020-11-16", "2020-11-17", "2020-12-19","2020-12-23", "2020-12-29", "2021-03-31"]
+dates = ["2019-02-01", "2019-05-23", "2019-07-18", "2019-08-10", "2019-10-03", "2019-10-09", "2019-11-16", "2019-11-17", "2019-11-19", "2019-11-26", "2019-12-04", "2019-12-15", "2019-12-29", "2020-01-03", "2020-01-06", "2020-01-15", "2020-02-12", "2020-03-03", "2020-03-31", "2020-04-08", "2020-04-18", "2020-04-20", "2020-04-25", "2020-04-28", "2020-05-08", "2020-07-15", "2020-08-07", "2020-09-13","2020-09-30", "2020-11-16", "2020-11-17", "2020-12-19","2020-12-23", "2020-12-29", "2021-03-31"]
 
 G16_dirs = [] 
 G17_dirs = []

### 2021-10-19 Kp-index.py

@@ -18,7 +18,7 @@ parser.add_argument('--datepp', type=str, default='2000-01-01',
 		      help='Choose date. Format: yyyy-mm-dd')
 
 
-parser.add_argument("--ftpfile", type=str, default="Q4", 
+parser.add_argument("--ftpfile", type=str, default="", 
 		    help="choose the file with the corresponding Kp index data")
 
 

### 2021-10-19 ROTI_estimation.py

@@ -1,0 +1,76 @@
+# This program is designed to estimate the standard deviation of
+# the Rate of TEC (ROTI) from 1 Hz RINEX data for every PRN in a
+# *.Cmn file (output of the GPS GOPI software where we get TEC 
+# calculations from Hatanaka files)
+
+import argparse
+import numpy as np
+from astropy.table import Table
+import glob
+
+# Import parameters from command line -----------------------------------------
+
+parser = argparse.ArgumentParser(
+    description=""" Choose a file to work""")
+
+
+parser.add_argument('--date', type=str, default='2000-01-01',
+			       help='Choose date. Format: yyyy-mm-dd')
+
+parser.add_argument("--station", type=str, default="kvtx", 
+                                help="Choose station to work")
+
+
+
+cmd_args = parser.parse_args()
+date = cmd_args.date
+station = cmd_args.station
+
+# Read file to work -----------------------------------------------------------
+
+directory = "./data/"+date+"/high-rate/"
+pathfile = glob.glob(directory+station+"*.Cmn")
+f = open(pathfile[0], "r") #pathfile is an array with one element in this case
+f.readline()
+f.readline()
+f.readline()
+f.readline() # The first 4 lines do not contain useful information
+data = f.readlines()
+Tabdata = Table.read(data, format="ascii")
+time = Tabdata["Time"]
+time_mask = time < 0
+time[time_mask] = time[time_mask] + 24.0 # Fix time values below 0
+
+# Get an array with the available PRNs, set output arrays and loop ----------------
+
+PRNs = np.unique(Tabdata["PRN"])
+N = 60 #The ROTI will be computed on a 60 seconds time interval
+ROTI = []
+outfile = "./data/"+date+"/ROTI-compute_"+station+"_"+date+".tab"
+for p in PRNs:
+    PRN_mask = Tabdata["PRN"] == p # select only the data of the same PRN
+    f_time = np.round(time[PRN_mask]*3600) # time will be measured 
+                                           # in seconds and avoid decimals
+    f_stec = Tabdata["Stec"][PRN_mask] # the ROTI will be computed using sTEC data
+#    t_min, t_max = min(f_time), min(f_time)+N #Define time window where ROTI is 
+                                              #computed
+    ROT = np.gradient(f_stec)/np.gradient(f_time) #Compute ROT for the whole PRN
+    for i in range(N):
[…]

### 2021-10-19 TEC_vs_time.py

@@ -1,0 +1,81 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+from astropy.table import Table
+import argparse
+import glob
+
+# Goal of this program: Obtain TEC vs time plots and analyze them in order to check if we can derive some kind
+# of parameter to quantify the TEC perturbations
+
+# We must recycle a lot of the code lines from plot_vTEC.py
+
+parser = argparse.ArgumentParser(
+    description=""" Choose a file to work""")
+
+
+parser.add_argument('--date', type=str, default='2000-01-01',
+				   help='Choose date. Format: yyyy-mm-dd')
+
+
+
+
+cmd_args = parser.parse_args()
+date = cmd_args.date
+
+
+directory = "./data/"+date
+p_directory = directory + "/previous/"
+n_directory = directory+ "/next/"
+
+# set figure style
+sns.set_style("whitegrid") 
+
+# Load RINEX capabilities
+
+
+std_files = glob.glob(directory+"/*.Std")
+load_std = [Table.read(std_files[i], format="ascii") for i in range(len(std_files))]
+
+
+std_p = glob.glob(p_directory+"*.Std")
+std_n = glob.glob(n_directory+"*.Std")
+
+load_std_p = [Table.read(std_p[i], format="ascii") for i in range(len(std_p))]
+load_std_n = [Table.read(std_n[i], format="ascii") for i in range(len(std_n))]
+
+# Load backgrond median
+
+
+
+# Get the data and plot
+
+fig = plt.figure()
+j=1
+for f, fp, fn in zip(load_std, load_std_p, load_std_n):
+    std_time = f["col1"]
+    std_time_p = fp["col1"]
+    std_time_n = fn["col1"]
+    std_TEC = f["col2"]
+    std_TEC_p = fp["col2"]
+    std_TEC_n = fn["col2"]
+
+    for i in range(len(std_TEC)):
+        if std_TEC[i] == "-":
+            std_TEC[i]=np.nan
+    for i in range(len(std_TEC_p)):
+        if std_TEC_p[i] == "-":
+            std_TEC_p[i]=np.nan
+    for i in range(len(std_TEC_n)):
+        if std_TEC_n[i] == "-":
+            std_TEC_n[i]=np.nan
+
+    avg_TEC = np.array([std_TEC_p, std_TEC, std_TEC_n])
[…]

### 2021-10-19 background-average.py

@@ -1,0 +1,59 @@
+import numpy as np
+from astropy.table import Table
+import glob
+import statistics as stats
+import argparse
+
+# objetivo del programa: Obtener la curva TEC vs tiempo en diferentes fechas previas al evento
+# para una misma estación y obtener ~~un promedio~~ la mediana del comportamiento del TEC y restarlo a los datos
+# Observar si hay alguna fluctución inusual que sería nuestra detección.
+
+
+parser = argparse.ArgumentParser(
+    description=""" Choose a file to work""")
+
+parser.add_argument("--station", type=str,
+                    default="kvtx",
+                    help=" Choose station")
+
+parser.add_argument('--date', type=str, default='2000-01-01',
+                    help='Choose date. Format: yyyy-mm-dd')
+
+
+
+
+cmd_args = parser.parse_args()
+date = cmd_args.date
+station = cmd_args.station
+
+directory = "./data/"+date
+b_data = glob.glob(directory+"/background/"+station+"*.Std")
+
+
+
+Tec_Matrix = []
+
+for b in b_data:
+    Tab = Table.read(b, format="ascii")
+    Tec_Matrix.append(Tab["col2"])
+
+
+
+
+m = len(Tec_Matrix) # Number of RINEX files read
+n = len(Tec_Matrix[0]) # The number of rows in one Std file
+Tec_median = np.zeros(n)
+
+for i in range(0, n):
+    guante = []
+    for j in range(0, m):
+        if Tec_Matrix[j][i]=="-":
+            guante.append(np.nan)
+        else:
+            guante.append(float(Tec_Matrix[j][i]))
+    Tec_median[i] = stats.median(guante)
+
+# Create table with the median curve
+
+out_table = Table([Tab["col1"], Tec_median], names=("Time (UT)", "Mean vTEC"))
+out_table.write(directory+"/"+station+"-mean-TEC.tab", format="ascii", overwrite=True)

### 2021-10-19 delta_vTEC.py

@@ -7,7 +7,7 @@
 # If \delta >~4 is an indication that the vTEC is strongly disturbed. But since the observed meteors in the GLM sample are small ( <~1m ), we will be less strict with this criteria
 # and set |\delta| >~ 2 and compute this parameter instead of vTEC itself
 
-# For this we will do a variant of the vTEC_maps program since we will compute \delta for each vTEC measurement. <vTEC> will be obtained from the average TEC in ths .Std file.
+# For this we will do a variant of the vTEC_maps program since we will compute \delta for each vTEC measurement. <vTEC> will be obtained from the average TEC in the .Std file.
 
 import seaborn as sns
 import numpy as np

### 2021-10-19 energy_factor.py

@@ -1,0 +1,55 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+# The goal of this program is to estime the discrepancy factor between GLM energy estimations
+# and the energy estimations by USG instruments in order to calibrate uncertainties to other
+# events only registered by the GLM. For this we will make a linear fit between GLM and USG
+# energies for events where data is available in both the GLM website and CNEOS fireballs website
+# (Only three events meet this criteria: GLM-00, GLM-23 and GLM-Ven).
+# The slope will be the correction factor and the residuals the uncertainties. 
+
+sns.set_style("whitegrid")
+
+# insert meteor energies
+
+GLM_energies = np.array([1.0763569, 0.065099193, 3.1305469])
+USG_energies = np.array([1.4, 0.076, 6])
+
+GLM_uncertainties = np.array([0.18966796, 0.026813257, 0.28006880])
+weights = 1./(1+GLM_uncertainties)
+
+# Do the fit: p is an array with the fit coefficients, res is the residuals, rank, single values 
+# and rcond are other outputs not used
+p, res, rank, s_values, rcond = np.polyfit(GLM_energies, USG_energies, 1, w=weights, full=True)
+
+# make a linar polynomial with the coefficients
+poly = np.poly1d(p)
+#poly_plus = np.poly1d([p[0]+res[0], p[1]])
+#poly_minus = np.poly1d([p[0]-res[0], p[1]])
+
+# make the plot
+f = plt.figure()
+ax1 = f.add_subplot(1, 2, 1)
+ax2 = f.add_subplot(1, 2, 2)
+ax1.errorbar(GLM_energies, USG_energies, xerr=GLM_uncertainties, fmt="g.", label="data points")
+ax1.plot(GLM_energies, poly(GLM_energies), "k-", label="linear fit")
+#ax1.set_xlabel("Meteor estimated kinetic energy by GLM (kilotons)", fontsize="small")
+ax1.set_ylabel("Meteor estimated kinetic energy by USG sensors (kilotons)", fontsize="small")
+ax1.text(0, 6.5, r"Linear fit: $y={:.3f}x - {:.3f}$".format(p[0], np.abs(p[1])), fontsize="small")
[…]

### 2021-10-19 energy_time.py

@@ -1,0 +1,40 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from astropy.table import Table
+import seaborn as sns
+
+# This program pretends to plot The kinetic energy of the meteors of the sample
+# versus the respecting date.
+
+# Read meteors database table
+
+t = Table.read("meteors_database.tab", format="ascii")
+t2 = Table.read("USG_meteors_database.tab", format="ascii")
+# extract relevant data
+
+ID , date, energy = t["ID"], t["Fecha"], t["Total energy recallibrated (kT)"]
+ID_USG, date_USG, energy_USG = t2["ID"], t2["Fecha"], t2["Energia total (kT)"]
+energy_arr = []
+de = []
+
+for e in energy:
+    a, b = e.split("+/-")
+    energy_arr.append(float(a))
+    de.append(float(b))
+
+
+# Make Boxplot (with whiskers)
+sns.set_style("whitegrid")
+GLM_energy = np.array(energy_arr)
+USG_energy = t2["Energia total (kT)"]
+
+plt.boxplot([GLM_energy, USG_energy], showfliers=False, patch_artist=True, 
+             boxprops=dict(facecolor="red", color="red", alpha=0.5),         
+             whiskerprops=dict(color="red"),
+             capprops=dict(color="red"), 
+             medianprops=dict(color="blue"))
+plt.xticks([1, 2], ["GLM", "USG"])
+plt.xlabel("Meteors sample")
+plt.ylabel("Total energy (kT)")
+plt.title("Meteors energy distribution (outliers removed)")
+plt.savefig("energies_boxplot.pdf")

### 2021-10-19 events_statistics.py

@@ -1,0 +1,32 @@
+import numpy as np
+from astropy.table import Table
+import statistics as stats
+import matplotlib.pyplot as plt
+
+# Code goal: Extract basic statistics of events sample
+
+# Step 1: Read data from table
+
+tab_data = Table.read("meteors_database.tab", format="ascii")
+
+duration = tab_data["dt"]
+s_dur = tab_data["s_dt"]
+lat = tab_data["Latitud"]
+lon = tab_data["Longitud"]
+s_lat = tab_data["sig_latitude"]
+s_lon = tab_data["sig_lon"]
+
+# Step 2: Obtain relevant statistics
+
+## Mean duration
+
+mean_duration = stats.mean(duration)
+mean_s_lat = stats.mean(s_lat)
+mean_s_lon = stats.mean(s_lon)
+
+# Plot data in scatter plots or similar
+plt.scatter(s_lon, s_lat, c="r")
+plt.scatter(mean_s_lon, mean_s_lat, c="b")
+plt.xlabel(r"$\sigma_{lon}$ (deg)")
+plt.ylabel(r"$\sigma_{lat}$ (deg)")
+plt.savefig("events_statistics.pdf")

### 2021-10-19 filtering_vTEC_maps.py

@@ -14,8 +14,8 @@ from midpoint import MidpointNormalize
 from matplotlib.ticker import FormatStrFormatter
 
 
-# This is a variant of the plot_vTEC.py script which filters the vTEC data 1 hour before the event
-# and serveral hours after the event (input) and plots the PRNs which satisfy those conditions.
+# This is a variant of the plot_vTEC.py script which filters the vTEC data several hours before the event
+# and serveral hours after the event (terminal input) and plots the PRNs which satisfy those conditions.
 # We expect to check if any of the chosen stations detected something related to the meteor pass
 
 parser = argparse.ArgumentParser(
@@ -33,16 +33,18 @@ parser.add_argument("--log", action="store_true", help="Use logarithmic scale fo
 parser.add_argument("--filtertime", type=float, default=1.0, help="Time filtered after the event")
 
 parser.add_argument("--filterbegins", type=float, default=0.2, help="Time filtered before the event")
+parser.add_argument("--data", type=str, default="vTEC", choices=("vTEC", "sTEC", "ROTI"), help="Data type to plot")
+
 cmd_args = parser.parse_args()
 date = cmd_args.date
 formato = cmd_args.formato
 log = cmd_args.log
 filtertime = cmd_args.filtertime
 filterbegins=cmd_args.filterbegins
+datatype = cmd_args.data
+
 
 directory = "./data/"+date
-#p_directory = directory + "/previous/" #Previous and next day graphs deprecated
-#n_directory = directory+ "/next/"
 
 # set figure style
 sns.set_style("whitegrid") 
@@ -54,19 +56,10 @@ rinex_files = glob.glob(directory+"/*.Cmn")
 std_files = glob.glob(directory+"/*.Std")
 load_dirs = [open(rinex_files[i], "r") for i in range(len(rinex_files))]
[…]

### 2021-10-19 kp_index_file.py

@@ -1,0 +1,123 @@
+# The goal of this program is to create a file containing the following data
+
+#     Date   | Kp index median | Max Kp index |     Variation       |
+#  ----------+-----------------+--------------+---------------------|
+#  2000-01-01|  Number         | Above 4      |Median - min Kp index|
+#  2000-01-02|  Number         | 4            |  Number             |
+#  2000-01-03|  Number         |  Below 4     |  Number             |
+
+# For use in another program. For this we must recycle some linecodes
+# From our other Kp index program
+
+import glob
+import seaborn as sns
+from astropy.table import Table
+import numpy as np
+import statistics as stats
+
+def yesterday(date):
+    """
+    Enters any date and returns the previos day
+    (is not as easy as you think). Limited to 1990
+    and forward.
+    """
+    year, month, day = date.split("-") # Get year, month and day from date
+    bisiesto = (year =="1992") | (year=="1996") | (year=="2000") | (year=="2004") | (year=="2008") | (year=="2012") | (year=="2016") | (year=="2020") 
+    thirty_day_month = (month == "05") | (month == "07") | (month == "10")| (month == "12")
+    if day == "01":
+        if month == "01": # January 1st case
+            pyear = str(int(year)-1)
+            pmonth = "12"
+            pday = "31"     
+        else:
+            pyear = year
+            pmonth = str(int(month)-1)
+            if int(pmonth) <10:
+                pmonth="0"+pmonth
+            if month == "03": # March 31th case
+                if bisiesto== True:
+                    pday = "29"
+                else:
+                    pday = "28"
+            elif thirty_day_month ==True: # Previous month has 30 days
+                pday = "30"
+            else: # Previous month has 31 days
+                pday = "31"
+    else:
+        pyear = year
+        pmonth = month
[…]

### 2021-10-19 kp_vs_time.py

@@ -1,0 +1,34 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+from astropy.table import Table
+import pandas as pd
+
+# This program pretends to plot the median Kp index of each event date and the two
+# previous days versus date (and use errorbars to estimate variations along these days)
+# Uses swarmplot (if i manage to do this kind of plot i will change the energy boxplot for this)
+
+sns.set_style("whitegrid")
+table = pd.read_csv("Kp_table.csv")
+max_value = table["Max value"]
+#colordict = {0:"green", 1:"green", 2:"green", 3:"green", 4:"yellow", 5:"red", 6:"red", 7:"red", 8:"red" , 9:"red"}
+color_mask_1 = max_value < 4
+color_mask_2 = max_value == 4
+color_mask_3 = max_value > 4
+#ax sns.swarmplot(x="Date", y="Median", data=table)
+x = np.arange(len(table["Date"]))
+y = table["Median"]
+yerr1 = np.array([table["Variation"][color_mask_1], max_value[color_mask_1]-y[color_mask_1]])
+yerr2 = np.array([table["Variation"][color_mask_2], max_value[color_mask_2]-y[color_mask_2]])
+yerr3 = np.array([table["Variation"][color_mask_3], max_value[color_mask_3]-y[color_mask_3]])
+plt.errorbar(x[color_mask_1], y[color_mask_1], fmt="o", yerr=yerr1, c="green")
+plt.errorbar(x[color_mask_2], y[color_mask_2], fmt="o", yerr=yerr2, c="yellow")
+plt.errorbar(x[color_mask_3], y[color_mask_3], fmt="o", yerr=yerr3, c="red")
+xticks = [table["Date"][0], "", "", "", "", table["Date"][25], "", "", table["Date"][40]]
+#xticks[0] = table["Date"][0]
+#xticks[-1] = table["Date"][-1]
+plt.xticks([0, 5, 10, 15, 20, 25, 30, 35, 40], labels=xticks)
+plt.xlabel("Event date")
+plt.ylabel("Kp index median")
+plt.title("")
+plt.savefig("Kp_index_dist.pdf")

### 2021-10-19 plot_meteors.py

@@ -34,10 +34,10 @@ f = Table.read("meteors_database.tab", format="ascii")
 
 plt.errorbar(f["Longitud"], f["Latitud"], xerr=f["sig_lon"], yerr=f["sig_latitude"], fmt="bo", capsize=3)
 # Offset of labels
-x_off = [10, 10, 10, 10, 10, 10, 10, 10, -10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, -10, -10, 10, 10, 10, 10, 10, 10, 10, 10, -10, 10, -10, 10, 10]
-y_off = [10, 10, -10, 10, -10, 10, 10, 10, 10, -10, -10, -10, 10, 10, 10, -10, -10, 10, 10, 10, 10, 10, 10, 10, -10, 10, 10, 10, 10, 10, 10, 10, 10, 10]
+x_off = [10, 10, 10, -10, -10, -10, 10, 10, 10, 10, 10, -10, -10, 10, 10, 10, 10, 10, 10, 10, -10, -10, 10, 10, 10, -10, 10, -10, -10, 10, -10, 10, -10, 10, 10]
+y_off = [10, 10, 10, -10, 10, -10, 10, 10, 10, 10, -10, -10, -10, 10, 10, 10, -10, -10, 10, -10, 10, 10, 10, 10, 10, -10, -10, 10, -10, 10, 10, 10, 10, 10, 10]
 for i in range(len(f["ID"])):
-    plt.annotate(f["ID"][i], (f["Longitud"][i], f["Latitud"][i]), textcoords="offset points", color="w",
+    plt.annotate(f["ID"][i], (f["Longitud"][i], f["Latitud"][i]), textcoords="offset points", color="w", fontsize="small",
     xytext=(x_off[i], y_off[i]), ha="center", bbox=dict(boxstyle="round", pad=0.5, fc="b", alpha=0.7))
 ax = plt.gca()
 ax.set_aspect('equal', adjustable='box')

### 2021-10-19 plot_stations.py

@@ -56,7 +56,7 @@ plt.plot(load_meteor_pos["Longitud"][meteor_mask], load_meteor_pos["Latitud"][me
 
 # Develop dictionaries with events positions, their respective stations.
 
-dates_stations_dict = {"2019-05-23":("KVTX", "TNCU", "UAGU"), "2019-07-18":("KVTX", "MDO1", "TNCU", "UAGU"), "2019-08-10":("KVTX", "TNCU", "UAGU", "UCOE", "UGEO"), "2019-10-03":("KVTX", "UAGU", "UXAL"), "2019-10-09":("GUAX", "TNBA", "TNHM","TNMS"), "2019-11-17":("GUAX", "TNBA", "PTEX", "TSFX", "TNPP", "P001", "BAR1", "WWMT"), "2019-11-16":("KVTX", "P807", "SG33", "TNCU", "UAGU"), "2019-11-19": ("CN23", "GCFS", "UNPM"), "2019-11-26":("TNBA", "TNHM", "TNMS", "UAGU", "YESX"), "2019-12-04":("GMPK", "IAGX", "P014", "PLPX", "TNHM", "TNPP"), "2019-12-15":("GUAX", "TNBA", "TNCU", "TNHM", "TNMS", "UAGU", "YESX"), "2019-12-29":("BAR1", "BLYT", "GUAX", "P014", "PTEX", "TNBA", "TNHM", "USMX", "WWMT"), "2020-01-03":("BAR1", "BLYT", "GUAX", "P014", "PTEX", "TNBA", "TNHM", "USMX", "WWMT"), "2020-01-06":("P014", "P807", "RG07", "TNCU", "USMX", "YESX"), "2020-01-15":("CN23", "CN25", "OXTH", "TNAT", "TNNX", "UNPM", "UXAL"), "2020-02-12":("CN23", "GUAT", "UNPM", "OXTH", "TNNX", "UXAL"), "2020-03-03":("TNAM", "TNCC", "TNCM", "TNMS"), "2020-03-31":("GUAX", "TNCU", "TNHM", "TNPP"), "2020-04-08":("KVTX", "MGW3", "UHSL", "UNPM", "UXAL"), "2020-04-18":("KVTX", "SG33", "TNCU", "TNHM", "UAGU", "YESX"), "2020-04-20":("KVTX", "MGO5", "MGW3", "P807", "WEPD", "WMOK"), "202
[…]

### 2021-10-19 plot_vTEC.py

@@ -156,7 +156,7 @@ for f, g, fp, gp, fn, gn in zip(load_dirs, load_std, load_dir_p, load_std_p, loa
 
     mean_TEC_int = interp1d(std_time, std_TEC)
     mean_TEC_int_p = interp1d(std_time_p, std_TEC_p)
-    mean_TEC_int_n = interp1d(std_time_n, std_TEC_p)
+    mean_TEC_int_n = interp1d(std_time_n, std_TEC_n)
     cmn_time = obs_tab["Time"]
     cmn_time_p = obs_tab_p["Time"]
     cmn_time_n = obs_tab_n["Time"]
@@ -259,26 +259,28 @@ ax1.axvspan(min((t0_m1, t0_m2)), max((t0_m1, t0_m2)), alpha=0.5, color="red")
 newlabel = [0, 5, 10, 15, 20, 25]
 time_zone_dict = {"2019-05-23":-5, "2019-07-18":-5, "2019-08-10":-5, "2019-10-03":-5, "2019-10-09":-7, "2019-11-16":-6, "2019-11-17":-8, "2019-11-19":-7, "2019-11-26":-5, "2019-12-04":-7, "2019-12-15":-7, "2019-12-29":-8, "2020-01-03":-8, "2020-01-06":-7, "2020-01-15":-6, "2020-02-12":-6, "2020-03-03":-6, "2020-03-31":-7, "2020-04-08":-5, "2020-04-18":-6, "2020-04-20":-5, "2020-04-25":-7, "2020-04-28":-6, "2020-05-08":-5, "2020-07-15":-6, "2020-08-07":-6, "2020-09-13":-7, "2020-09-30":-7, "2020-11-16":-6, "2020-11-17":-6, "2020-12-19":-6, "2020-12-23":-7, "2020-12-29":-6, "2021-03-31":-6}
 
-local_time = np.array(newlabel) + time_zone_dict[date]
-for i in range(len(local_time)):
-    if local_time[i] < 0.:
-        local_time[i] = local_time[i] + 24.0
-ax2 = ax1.twiny()
-ax2.set_xticks(newlabel)
-ax2.set_xticklabels(local_time)
-ax2.set_xlim(ax1.get_xlim())
+try:
+    local_time = np.array(newlabel) + time_zone_dict[date]
+    for i in range(len(local_time)):
+        if local_time[i] < 0.:
+            local_time[i] = local_time[i] + 24.0
+    ax2 = ax1.twiny()
[…]

### 2021-10-20 paper/methodology.tex
Adding new table with USG sample

@@
 \label{tab:table-meteors}
-\begin{tabular}{rrrrrrrr}
+\begin{tabular}{rrrrrrrrr}
 \hline
-ID & Date of event & Start Time (UT)  & Duration (seconds) & Latitude (deg) & Longitude (deg) & Height (km) & Maximum Kp index \\
-\hline
-GLM-01 & 2019-05-23 & 16:36:18 & $0.197\pm 0.0000$ & $24.30 \pm 0.000$ & $-101.60 \pm 0.849$  & 28 & 2\\
-GLM-02 & 2019-07-18 & 14:30:30 & $0.058\pm 0.0000$ & $27.20 \pm 0.000$ & $-103.15 \pm 0.778$  & 72 & 1\\
-GLM-03 & 2019-08-10 & 11:18:48 & $0.199\pm 0.0757$ & $21.50 \pm 0.000$ & $-102.50  \pm 0.849$ & 92 & 3\\
-GLM-04 & 2019-10-03 & 07:55:33 & $0.106\pm 0.0297$ & $25.65 \pm 0.071$ & $-96.25 \pm   0.778$ & 74 & 2\\
-GLM-05 & 2019-10-09 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$ & 32 & 4\\
-GLM-06 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$ & 82 & 2\\
-GLM-07 & 2019-11-17 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$ & 88 & 3\\
-GLM-08 & 2019-11-19 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm  1.131$  & 99 & 1\\
-GLM-09 & 2019-11-26 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$ & 81 & 2\\
-GLM-10 & 2019-12-04 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$ & 77 & 2\\
-GLM-11 & 2019-12-15 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$ & 78 & 2\\
-GLM-12 & 2019-12-29 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$ & 79 & 1\\
-GLM-13 & 2020-01-03 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$ & 74 & 3\\
-GLM-14 & 2020-01-06 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$ & 81 & 4\\
-GLM-15 & 2020-01-15 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$ & 93 & 2\\
-GLM-16 & 2020-02-12 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$ & 90 & 2\\
-GLM-17 & 2020-03-03 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm 0.636$  & 77 & 2\hyperlink{note2}{${}^2$}\\
-GLM-18 & 2020-03-31 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 61 & 4\\
-GLM-19 & 2020-04-08 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$ & 78 & 3\\
-GLM-20 & 2020-04-18 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$ & 82 & 2\\
-GLM-21 & 2020-04-20 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$ & 88 & 5\\
-GLM-22 & 2020-04-25 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$ & 84 & 3\\
-GLM-23 & 2020-04-28 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 29 & 3\\
-GLM-24 & 2020-05-08 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$ & 81 & 1\\
-GLM-25 & 2020-07-15 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$ & 53 & 2\hyperlink{note}{${}^1$}\\
-GLM-26 & 2020-08-07 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$ & 89 & 2\\
-GLM-27 & 2020-09-13 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$ & 85 & 3\\
-GLM-28 & 2020-09-30 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ & 83 & 4\\
-GLM-29 & 2020-11-16 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ & 06 & 1\\
-GLM-30 & 2020-11-17 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$ & 93 & 1\\
-GLM-31 & 2020-12-19 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$ & 98 & 2\\
-GLM-32 & 2020-12-23 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$ & 81 & 4\\
-GLM-33 & 2020-12-29 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$ & 81 & 3\\
-GLM-34 & 2021-03-31 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$  & 24 & 3\\\hline
+ID & Date of event  & Start Time (UT)  & Duration (seconds) & Latitude (deg) & Longitude (deg)& Altitude (km)\\\hline
+GLM-00 & 2019-02-01 & 18:17:09 & $2.651\pm 0.4907$ & $22.45 \pm 0.071$ & $-83.50  \pm  0.424$ & 24           \\         
+GLM-01 & 2019-05-23 & 16:36:18 & $0.197\pm 0.0000$ & $24.30 \pm 0.000$ & $-101.60 \pm  0.849$ & 28           \\
+GLM-02 & 2019-07-18 & 14:30:30 & $0.058\pm 0.0000$ & $27.20 \pm 0.000$ & $-103.15 \pm  0.778$ & 72           \\
+GLM-03 & 2019-08-10 & 11:18:48 & $0.199\pm 0.0757$ & $21.50 \pm 0.000$ & $-102.50  \pm 0.849$ & 92           \\
+GLM-04 & 2019-10-03 & 07:55:33 & $0.106\pm 0.0297$ & $25.65 \pm 0.071$ & $-96.25 \pm   0.778$ & 74           \\
+GLM-05 & 2019-10-09 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$ & 32           \\
+GLM-06 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$ & 82           \\
+GLM-07 & 2019-11-17 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$ & 88           \\
+GLM-08 & 2019-11-19 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm   1.131$ & 99           \\
+GLM-09 & 2019-11-26 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$ & 81           \\
+GLM-10 & 2019-12-04 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$ & 77           \\
+GLM-11 & 2019-12-15 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$ & 78           \\
+GLM-12 & 2019-12-29 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$ & 79           \\
+GLM-13 & 2020-01-03 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$ & 74           \\
+GLM-14 & 2020-01-06 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$ & 81           \\
+GLM-15 & 2020-01-15 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$ & 93           \\
+GLM-16 & 2020-02-12 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$ & 90           \\
+GLM-17 & 2020-03-03 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm  0.636$ & 77           \\
+GLM-18 & 2020-03-31 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 61           \\
+GLM-19 & 2020-04-08 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$ & 78           \\
+GLM-20 & 2020-04-18 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$ & 82           \\
+GLM-21 & 2020-04-20 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$ & 88           \\
+GLM-22 & 2020-04-25 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$ & 84           \\
+GLM-23 & 2020-04-28 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 29           \\
+GLM-24 & 2020-05-08 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$ & 81           \\
+GLM-25 & 2020-07-15 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$ & 53           \\
+GLM-26 & 2020-08-07 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$ & 89           \\
+GLM-27 & 2020-09-13 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$ & 85           \\
+GLM-28 & 2020-09-30 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ & 83           \\
+GLM-29 & 2020-11-16 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ &106           \\
+GLM-30 & 2020-11-17 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$ & 93           \\
+GLM-31 & 2020-12-19 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$ & 98           \\
+GLM-32 & 2020-12-23 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$ & 81           \\
+GLM-33 & 2020-12-29 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$ & 81           \\
+GLM-34 & 2021-03-31 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$  & 24           \\
+GLM-Ven& 2019-06-22 & 21:25:45 & $4.873\pm 0.0000$ & $14.9 \pm 0.000$  & $-65.8 \pm 0.000$    & 25           \\ \hline
 \end{tabular}
-    \begin{minipage}{0.9\linewidth}
-      \footnotesize
-      \hypertarget{note}{${}^1$} Kp index is 4 the previous day of impact
-
-      \hypertarget{note2}{${}^2$}Kp index is 4 two days before the impact 
-    \end{minipage}
-
 \end{table*}
@@
 \end{figure}
+
+By the other hand, we got another sample from USG sensors from the Center for Near Earth Object Studies (CNEOS), publicly available at \url{https://cneos.jpl.nasa.gov/fireballs/}.
+As seen in table  , the time span is quite larger, and the released energy is generally larger, as seen in figure  .
+Some elements appear in both samples, since are bright enough to be detected regardless the project involved.
+In USG sample, the total energy of each meteor is obtained directly, but is nt the case for the GLM sample.
+In appendix  we give details about how the total energy is obtained.
+
+\begin{table*}
+    \centering
+  \footnotesize
+  \caption{List of meteors passing through Mexico.
+The events are listed in chronological order.
+The listed duration, latitude and longitude correspond to the mean of the measurements of both GOES satellites.
+The uncertainties correspond to the respecting mean deviation.}
+\label{tab:table-meteors}
+\begin{tabular}{rrrrrrrrrr}
+       &               &                  & \multicolumn{4}{c}{Velocity (km/s)}       &                   &                 &\\\cline{4-7}
+\multicolumn{1}{c}{ID}&\multicolumn{1}{c}{Date of event}&\multicolumn{1}{c}{Start Time (UT)}&\multicolumn{1}{c}{$v$}&\multicolumn{1}{c}{$v_x$}&\multicolumn{1}{c}{$v_y$}&\multicolumn{1}{c}{$v_z$}&\multicolumn{1}{c}{Latitude (deg)}&\multicolumn{1}{c}{Longitude (deg)}&\multicolumn{1}{c}{Altitude (km)}\\\hline
+USG-01 & 1995-08-05    & 17:14:10         &      &         &           &              & 11.6              &  -104.3         &             \\
+USG-02 & 1996-07-12    & 14:04:45         &      &         &           &              & 20.7              &   -93.6         &             \\ 
+USG-03 & 1997-10-09    & 18:47:15         &      &         &           &              & 31.8              &  -106.0         &   37.0      \\
+USG-04 & 2000-01-18    & 08:33:58         &      &         &           &              & 24.3              &   -94.9         &             \\
+USG-05 & 2000-08-25    & 01:12:25         &      &         &           &              & 14.5              &  -106.1         &             \\
+USG-06 & 2005-11-15    & 05:19:07         &      &         &           &              & 26.3              &  -113.4         &   32.4      \\
+USG-07 & 2015-07-19    & 07:06:26         & 17.8 &   9.4   &  13.0     & 7.8          & 20.6              &   -87.6         &   22.0      \\
+USG-08 & 2019-02-01    & 18:17:10         & 16.3 &  -2.4   &  13.6     & 8.7          & 22.5              &   -83.8         &   23.7      \\
+USG-09 & 2019-06-22    & 21:25:48         & 14.9 & -13.4   &   6.0     & 2.5          & 14.9              &   -66.2         &   25.0      \\
+USG-10 & 2020-04-28    & 05:43:17         &      &         &           &              & 20.1              &  -109.4         &             \\\hline  
+  \end{tabular}
+\end{table*}
 

### 2021-11-16 paper/appendix.tex
Emergency Backup

@@
 \section{Estimation of distances to meteors}
-
+\label{app:distance}
 The distance between the GOES satellite and the meteor, neccesary to estimate the radiated energy is calculated as follows:
@@
 \begin{align}
-  R^2 = 2r_{earth}^2\left(1-f(\theta_{obj}, \phi_{obj}, \phi_{GLM})\right) +2r_{earth}h_{GLM}\left(1-f(\theta_{obj}, \phi_{obj}, \phi_{GLM})\right) + h_{GLM}^2 - 2h_{GLM}h_{obj}f(\theta_{obj}, \phi_{obj}, \phi_{GLM})
+  \begin{split}
+    R^2 = 2r_{earth}^2\left(1-f(\theta_{obj}, \phi_{obj}, \phi_{GLM})\right) +2r_{earth}h_{GLM}\\
+    \left(1-f(\theta_{obj}, \phi_{obj}, \phi_{GLM})\right) + h_{GLM}^2 - 2h_{GLM}h_{obj}f(\theta_{obj}, \phi_{obj}, \phi_{GLM})
+    \end{split}
 \end{align}
 
-\section{Useful databases}
+\section{Energy estimation}
+\label{app:energy}
+The total radiant energy emmited is calculated integrating over all the time and all directions.
+The first is obtained simply summing all the light curve points.
+In the other hand, to integrate over all directions, we multiply the GLM event energies by the factor (\SI{1.695e18}{})(\SI{1.018e3}{})$\left(\frac{R}{35780~km}\right)^2$ \citep{Jenniskens:2018}.
+This factor also considers that the GLM only detects light from the OI line.
+Then, we obtain the luminous efficiency $\tau_1$ (i.e the fraction of the total energy converted into radiation) following \citet{Brown:2002}:
+\begin{align}
+  \tau_1 = (0.1212\pm 0.0043)E_0^{0.115\pm 0.075}
+\end{align}
+
+Where $E_0$ is the luminous energy calculated from integrating GLM reported energies (in kilotons).
+Finally the total estimated energy is $E = E_0/\tau_1$.
+We may compare the resulting GLM energies with the energies reported by USG sensors using the events which belong to both samples, and we noticed that the energies obtained with GLM data is systematically lower than the energies reported by the USG sensors.
+In this work we assumed that this discrepancy is due to the GLM sensors does not detect the full meteor paths, just a fraction of the total radiated energy.
+To solve this problem we made a linear fit between the derived energies and the energies reported in the USG sample for the events which appear in both samples, and recallibrate the energies of the rest of the GLM sample.
+The linear fit is shown in figure \ref{fig:lin_fit}.
+We used the linear fit slope as the recallibration factor and the residuals as the error, we neglected the y-intercept term because this term is much larger than the most energies in the GLM sample and strongly affects the recallibrated energy.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{../energy_fit}
+  \caption{Left: Linear fit between energies calculated from GLM data and energies reported by USG sensors.
+Right: Residuals of the fit, used as error in the recallibration factor.
+The three events used for this linear fit are GLM-00 (the cuban meteoroid), GLM-23 and GLM-Ven (Venezolan meteoroid).}
+  \label{fig:lin_fit}
+\end{figure}

### 2021-11-16 paper/methodology.tex
Emergency Backup

--- 2021-09-02 paper/methodology.tex
@@
   \centering
-  \caption{List of meteors passing through Mexico.
+  \footnotesize
+  \caption{List of bolides detected in mexican territory (plus one detected near Venezuela and one detected near Cuba), detected by the Geostationary Lighning mapper.
 The events are listed in chronological order.
@@
 \label{tab:table-meteors}
-\begin{tabular}{rrrrrrr}
+\begin{tabular}{rrrrrrrrrr}
 \hline
-ID & Date of event & Start Time (UT)  & Duration (seconds) & Latitude (deg) & Longitude (deg) & Height (km)\\
-\hline
-01 & 2019-05-23 & 16:36:18 & $0.197\pm 0.0000$ & $24.30 \pm 0.000$ & $-101.60 \pm 0.849$  & 28\\
-02 & 2019-07-18 & 14:30:30 & $0.058\pm 0.0000$ & $27.20 \pm 0.000$ & $-103.15 \pm 0.778$  & 72\\
-03 & 2019-08-10 & 11:18:48 & $0.199\pm 0.0757$ & $21.50 \pm 0.000$ & $-102.50  \pm 0.849$ & 92\\
-04 & 2019-10-03 & 07:55:33 & $0.106\pm 0.0297$ & $25.65 \pm 0.071$ & $-96.25 \pm   0.778$ & 74\\
-05 & 2019-10-09 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$ & 32\\
-06 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$ & 82\\
-07 & 2019-11-17 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$ & 88\\
-08 & 2019-11-19 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm  1.131$  & 99\\
-09 & 2019-11-26 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$ & 81\\
-10 & 2019-12-04 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$ & 77\\
-11 & 2019-12-15 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$ & 78\\
-12 & 2019-12-29 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$ & 79\\
-13 & 2020-01-03 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$ & 74\\
-14 & 2020-01-06 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$ & 81\\
-15 & 2020-01-15 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$ & 93\\
-16 & 2020-02-12 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$ & 90\\
-17 & 2020-03-03 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm 0.636$  & 77\\
-18 & 2020-03-31 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 61\\
-19 & 2020-04-08 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$ & 78\\
-20 & 2020-04-18 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$ & 82\\
-21 & 2020-04-20 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$ & 88\\
-22 & 2020-04-25 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$ & 84\\
-23 & 2020-04-28 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 29\\
-24 & 2020-05-08 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$ & 81\\
-25 & 2020-07-15 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$ & 53\\
-26 & 2020-08-07 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$ & 89\\
-27 & 2020-09-13 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$ & 85\\
-28 & 2020-09-30 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ & 83\\
-29 & 2020-11-16 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ & 06\\
-30 & 2020-11-17 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$ & 93\\
-31 & 2020-12-19 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$ & 98\\
-32 & 2020-12-23 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$ & 81\\
-33 & 2020-12-29 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$ & 81\\
-34 & 2021-03-31 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$  & 24\\\hline
+ID & Date of event  & Start Time (UT)  & Duration (seconds) & Latitude (deg) & Longitude (deg)& Altitude (km) & Energy (kT )\\\hline
+GLM-00 & 2019-02-01 & 18:17:09 & $2.651\pm 0.4907$ & $22.45 \pm 0.071$ & $-83.50  \pm  0.424$ & 24           & 2.0978196 +/- 0.42361329      \\         
+GLM-01 & 2019-05-23 & 16:36:18 & $0.197\pm 0.0000$ & $24.30 \pm 0.000$ & $-101.60 \pm  0.849$ & 28           & 0.011954659 +/- 7.4054404e-3  \\
+GLM-02 & 2019-07-18 & 14:30:30 & $0.058\pm 0.0000$ & $27.20 \pm 0.000$ & $-103.15 \pm  0.778$ & 72           & 5.7827709e-3 +/- 3.9334336e-3 \\
+GLM-03 & 2019-08-10 & 11:18:48 & $0.199\pm 0.0757$ & $21.50 \pm 0.000$ & $-102.50  \pm 0.849$ & 92           & 0.010556123 +/- 6.6488245e-3  \\
+GLM-04 & 2019-10-03 & 07:55:33 & $0.106\pm 0.0297$ & $25.65 \pm 0.071$ & $-96.25 \pm   0.778$ & 74           & 2.9915536e-3 +/- 2.2000998e-3 \\
+GLM-05 & 2019-10-09 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$ & 32           & 0.021837042 +/- 0.012429732   \\
+GLM-06 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$ & 82           & 7.5423706e-3 +/- 4.9626060e-3 \\
+GLM-07 & 2019-11-17 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$ & 88           & 0.022397444 +/- 0.012701445   \\
+GLM-08 & 2019-11-19 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm   1.131$ & 99           & 1.5012507e-3 +/- 1.1909667e-3 \\
+GLM-09 & 2019-11-26 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$ & 81           & 4.9551290e-3 +/- 3.4345742e-3 \\
+GLM-10 & 2019-12-04 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$ & 77           & 0.029149047 +/- 0.015891049   \\
+GLM-11 & 2019-12-15 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$ & 78           & 0.010556123 +/- 6.6488245e-3  \\
+GLM-12 & 2019-12-29 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$ & 79           & 4.2084911e-3 +/- 2.9746446e-3 \\
+GLM-13 & 2020-01-03 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$ & 74           & 0.011607116 +/- 7.2187549e-3  \\
+GLM-14 & 2020-01-06 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$ & 81           & 0.015448801 +/- 9.2392402e-3  \\
+GLM-15 & 2020-01-15 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$ & 93           & 0.012559739 +/- 7.7284725e-3  \\
+GLM-16 & 2020-02-12 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$ & 90           & 8.2107211e-3 +/- 5.3440405e-3 \\
+GLM-17 & 2020-03-03 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm  0.636$ & 77           & 3.4441157e-3 +/- 2.4922397e-3 \\
+GLM-18 & 2020-03-31 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 61           & 7.2469897e-3 +/- 4.7924800e-3 \\
+GLM-19 & 2020-04-08 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$ & 78           & 4.0292119e-3 +/- 2.8626279e-3 \\
+GLM-20 & 2020-04-18 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$ & 82           & 5.8303967e-3 +/- 3.9618242e-3 \\
+GLM-21 & 2020-04-20 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$ & 88           & 0.031378060 +/- 0.016913982   \\
+GLM-22 & 2020-04-25 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$ & 84           & 0.021997346 +/- 0.012507576   \\
+GLM-23 & 2020-04-28 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 29           & 0.12687833 +/- 0.053736010    \\
+GLM-24 & 2020-05-08 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$ & 81           & 0.033207253 +/- 0.017743607   \\
+GLM-25 & 2020-07-15 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$ & 53           & 0.020548979 +/- 0.011800641   \\
+GLM-26 & 2020-08-07 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$ & 89           & 0.014606987 +/- 8.8040841e-3  \\
+GLM-27 & 2020-09-13 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$ & 85           & 0.010995616 +/- 6.8881646e-3  \\
+GLM-28 & 2020-09-30 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ & 83           & 0.014013965 +/- 8.4951275e-3  \\
+GLM-29 & 2020-11-16 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ &106           & 0.052044572 +/- 0.025868548   \\
+GLM-30 & 2020-11-17 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$ & 93           & 0.060624247 +/- 0.029367156   \\
+GLM-31 & 2020-12-19 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$ & 98           & 0.060272985 +/- 0.029225978   \\
+GLM-32 & 2020-12-23 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$ & 81           & 0.012127937 +/- 7.4982028e-3  \\
+GLM-33 & 2020-12-29 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$ & 81           & 0.013161054 +/- 8.0470909e-3  \\
+GLM-34 & 2021-03-31 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$  & 24           & 0.054259119 +/- 0.026782008   \\
+GLM-Ven& 2019-06-22 & 21:25:45 & $4.873\pm 0.0000$ & $14.9 \pm 0.000$  & $-65.8 \pm 0.000$    & 25           & 6.1014359 +/- 0.81239700      \\ \hline
 \end{tabular}
@@
   \includegraphics[width=\linewidth]{../meteors_map}
-  \caption{Positions of events from table \ref{tab:table-meteors}. The label of each point correspond to the ID (first column) of the referred table.}
+  \caption{Positions of events from table \ref{tab:table-meteors} (blue) and table \ref{tab:table-meteors-2}.
+The events GLM-00/USG-08 actually correpond to the same bolide, but there are little discrepancies about the position where the bolide was detecte.
+The same applies for the events GLM-23/USG-10 and GLM-Ven/USG-09, which not appears in the map.}
   \label{fig:meteors-map}
@@
 
+By the other hand, we got another sample of 10 bolidesfrom US Goverment (USG) sensors from the Center for Near Earth Object Studies (CNEOS), publicly available at \url{https://cneos.jpl.nasa.gov/fireballs/}, where we may obtain directly data about bolides position, the date and time each bolide was detected, the energy released at fragmentation, the velocity and the height (the last two not availble for all bolides).
+As seen in table \ref{tab:table-meteors-2}, the time span is quite larger, and the released energy is generally larger.
+Both energy distributions are compared directly in figure \ref{fig:boxplot}.
+Some elements appear in both samples, since are bright enough to be detected regardless the project involved.
+In USG sample, the total energy of each meteor is obtained directly, but is not the case for the GLM sample.
+In appendix \ref{app:distance} and \ref{app:energy} we give details about how this total energy is obtained.
+
+\begin{table*}
+    \centering
+  \footnotesize
+  \caption{List of bolides detected in mexican territory (plus one detected near Venezuela and one detected near Cuba), detected by USG sensors.}
+\label{tab:table-meteors-2}
+\begin{tabular}{rrrrrrrrrrr}
+       &               &                  & \multicolumn{4}{c}{Velocity (km/s)}       &                   &                 &\\\cline{4-7}
+\multicolumn{1}{c}{ID}&\multicolumn{1}{c}{Date of event}&\multicolumn{1}{c}{Start Time (UT)}&\multicolumn{1}{c}{$v$}&\multicolumn{1}{c}{$v_x$}&\multicolumn{1}{c}{$v_y$}&\multicolumn{1}{c}{$v_z$}&\multicolumn{1}{c}{Latitude (deg)}&\multicolumn{1}{c}{Longitude (deg)}&\multicolumn{1}{c}{Altitude (km)} & \multicolumn{1}{c}{Energy (kT)}\\\hline
+USG-01 & 1995-08-05    & 17:14:10         &      &         &           &              & 11.6              &  -104.3         &             &  0.56\\
+USG-02 & 1996-07-12    & 14:04:45         &      &         &           &              & 20.7              &   -93.6         &             &  0.11\\ 
+USG-03 & 1997-10-09    & 18:47:15         &      &         &           &              & 31.8              &  -106.0         &   37.0      &  0.53\\
+USG-04 & 2000-01-18    & 08:33:58         &      &         &           &              & 24.3              &   -94.9         &             &  0.12\\
+USG-05 & 2000-08-25    & 01:12:25         &      &         &           &              & 14.5              &  -106.1         &             &   3.1\\
+USG-06 & 2005-11-15    & 05:19:07         &      &         &           &              & 26.3              &  -113.4         &   32.4      & 0.089\\
+USG-07 & 2015-07-19    & 07:06:26         & 17.8 &   9.4   &  13.0     & 7.8          & 20.6              &   -87.6         &   22.0      & 0.082\\
+USG-08 & 2019-02-01    & 18:17:10         & 16.3 &  -2.4   &  13.6     & 8.7          & 22.5              &   -83.8         &   23.7      &   1.4\\
+USG-09 & 2019-06-22    & 21:25:48         & 14.9 & -13.4   &   6.0     & 2.5          & 14.9              &   -66.2         &   25.0      &   6.0\\
+USG-10 & 2020-04-28    & 05:43:17         &      &         &           &              & 20.1              &  -109.4         &             & 0.076\\\hline  
+  \end{tabular}
+\end{table*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{./figures/energies_boxplot}
+  \caption{Comparison between released energies of bolides detected by the Geostationary Lightning Mapper and USG sensors.}
+  \label{fig:boxplot}
+\end{figure}
+
 \subsection{GPS data}
+\label{ssec:GPS}
+%This material is based on services provided by the GAGE Facility, operated by UNAVCO, Inc., with support from the National Science Foundation and the National Aeronautics and Space Administration under NSF Cooperative Agreement EAR-1724794.
 
-This material is based on services provided by the GAGE Facility, operated by UNAVCO, Inc., with support from the National Science Foundation and the National Aeronautics and Space Administration under NSF Cooperative Agreement EAR-1724794.
-
-We got RINEX data from 3 to 7 stations depending of the event location and data availability that surround the event place in all directions as possible.
-A list of the stations where we got RINEX data is available in table  .
+%We got RINEX data from 3 to 7 stations depending of the event location and data availability that surround the event place in all directions as possible.
+A list of the stations where we got RINEX data is available in table \ref{tab:table-stations}.
 Most of the stations lie in mexican territory, but in some cases we required data from other stations to cover events near the mexican frontier at north or south.
 
-\clearpage
-\onecolumn
-\begin{landscape}
-%\begin{table*}
-%    \centering
-  \begin{longtable}{lllp{4cm}p{10cm}}
-      \caption{List of GPS stations used for this work.}
-      \label{tab:table-stations}
-      \endfirsthead
-      \endhead
-    \hline
-    Station name & Latitude & Longitude & Date of events  & Citation \\\hline
-    BAR1\hyperlink{Hudnut}{${}^1$}\hyperlink{Hudnut2}{${}^5$}& 33.48 & -119.03 & 2019-12-29 2020-01-03 & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - BAR1-Santa Barbara Island One P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5668BHN}.\\
-    BLYT\hyperlink{Hudnut}{${}^1$} & 33.61 & -114.71 & 2019-12-29 2020-01-03 & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2006, SCIGN USGS GPS Network - BLYT-Blythe P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5HT2MKK}.\\
-    CN23 & 17.26 & -88.78 & 2019-11-19 2020-01-15 2020-02-12& UNAVCO Community, 2012, COCONet GPS Network - CN23-BelmopanBZCR2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5Q23XJH}.\\
-    CN25 & 16.23 & -92.13 & 2020-01-15 & UNAVCO Community, 2014, COCONet GPS Network - CN25-ComitandDMEX2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57W69G7}.\\
-    GCFS & 19.31 & -81.18 & 2019-11-19& Watts, Anthony, 2016, COCONet GPS Network - GCFS-G\_CAYMAN\_CYM2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/7ETV-X536}.\\
-    GMPK\hyperlink{Hudnut}{${}^1$} & 33.05 & -114.83 & 2019-12-04 & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - GMPK-Glamis Peak P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/WCHN-H687}.\\
-    GUAT\hyperlink{Garnier}{${}^2$} & 14.59 & -90.52 & 2020-02-12 & DeMets, Charles, Cosenza-Muralles, Beatriz, 2021, Central America 2018 - Guatemala, The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/KH2R-K704}.\\
-    GUAX\hyperlink{Hudnut}{${}^1$} & 28.88 & -118.29 & 2019-10-09 2019-12-15 2019-12-29 2020-01-03 2020-03-31 2020-07-15 2020-09-13 2020-09-30 2020-12-23 & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2001, SCIGN USGS GPS Network - GUAX-Isla Guadalupe P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5GX48T2}.\\
-    IAGX & 29.03 & -113.17 & 2019-12-04 & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network - IAGX-iagxREGNOMmx2018 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/DGWN-A627}.\\
-    INEG & 21.85 & -102.28 & 2020-07-15 2020-08-07 2020-09-30 2020-11-16 2020-11-17 2020-12-19 & No citations were found\\
-    KVTX & 27.55 & -97.89 & 2019-05-23 2019-07-18 2019-08-10 2019-10-03 2019-11-17 2020-04-08 2020-04-18 2020-04-20 2020-05-08 2020-08-07 & UNAVCO Community, 2007, PBO GPS Network - KVTX-KingsvilleTX2006 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J38QH8}.\\
-    MDO1 & 30.68 & -104.02 & 2019-07-18& No citations were found\\
-    MGO5 & 30.68 & -104.02 & 2020-04-20 2020-08-07 & No citations were found\\
-    MGW3 & 29.62 & -89.95 & 2020-04-08 2020-04-20 2020-05-08 & No citations were found\\
-    OXTH & 16.29 & -95.24 & 2020-01-15 2020-02-12 & DeMets, Charles, Cabral-Cano, Enrique, 2008, Oaxaca GPS Network - OXTH-Tehuantepec P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5Q81B5V}.\\
-    OXUM\hyperlink{Graham}{${}^3$} & 15.66 & -96.50 & 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - OXUM-oxum\_tnet\_mx2001 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J964RP}.\\
-    P001 & 31.95 & -112.80 & 2020-04 25 & UNAVCO Community, 2008, PBO GPS Network - P001-Organ\_PipeAZ2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DR2SGP}.\\
-    P014 & 31.97 & -11.09 & 2019-12-04 2019-12-29 2020-01-03 2020-01-06 2020-04-25 & UNAVCO Community, 2008, PBO GPS Network - P014-Sahuarita\_AZ2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5CMK}.\\
-    P807 & 30.49 & -98.82 & 2019-11-17 2020-01-06 2020-04-20 2020-11-17 & UNAVCO Community, 2012, PBO GPS Network - P807-EcRockStPkTX2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5TQ5ZKM}.\\
-    PLPX & 31.59 & -115.15 & 2019-12-04 & UNAVCO Community, 2011, PBO GPS Network - PLPX-Las\_PintasMX2010 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5K64G3T}.\\
-    PTEX & 32.29 & -116.52 & 2019-12-29 2020-01-03 2020-09-13 2020-12-23 & UNAVCO Community, 2011, PBO GPS Network - PTEX-Testerazo\_MX2011 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XBP}.\\
-    RG06 & 32.63 & -107.86 & 2020-04-25 & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG06-RG06FaywodNM2006 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5668BFR}.\\
-    RG07 & 32.50 & -106.84 & 2020-01-06 & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG07-RG07CrucesNM2006 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5KD1W45}.
-\\
-    SG33 & 31.77 & -106.51 & 2019-11-17 2020-04-18 2020-08-07 & Harder, Steven, Kaip, Galen, Montana, Carlos, 2004, SuomiNet-G GPS Network - SG33-UTEP P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T50863KQ}.\\
-    TGMX  & 20.87 & -86.87 & 2021-03-31 & UNAVCO Community, 2015, COCONet GPS Network - TGMX-PtoMor\_TG\_MX2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5154FB7}.\\
-    TNAM & 20.54 & -103.97 & 2020-03-03 2020-07-15 2020-09-30 2020-11-16 2020-11-17 2020-12-19 & UNAVCO Community, 2014, TLALOCNet - TNAM-TNAM\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5QF8R4R}.\\
-    TNAT & 18.13 & -98.04 & 2020-01-15 & UNAVCO Community, 2014, TLALOCNet - TNAT-TNAT\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5G15Z4S}.\\
-    TNBA & 28.97 & -113.55 & 2019-10-09 2019-11-26 2019-12-15 2019-12-29 2020-01-03& UNAVCO Community, 2015, TLALOCNet - TNBA-TNBA\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57M0688}.\\
-    TNCC & 18.79 & -103.17 & 2020-03-03 & UNAVCO Community, 2015, TLALOCNet - TNCC-TNCC\_TNET\_MX2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T50R9MSK}.\\
-    TNCM & 19.50 & -105.04 & 2020-03-03 2020-04-28 & UNAVCO Community, 2014, TLALOCNet - TNCM-TNCM\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5B856FW}.\\
-    TNCN & 18.55 & -101.97 & 2020-11-16 2020-12-29 & UNAVCO Community, 2016, TLALOCNet - TNCN-TNCN\_TNET\_MX2016 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XQM}.\\
-    TNCU & 28.45 & -106.79 & 2019-05-23 2019-07-18 2019-08-10 2019-11-17 2019-12-15 2020-01-06 2020-03-31 2020-04-18 2020-07-15 2020-08-07 2020-11-17 2020-12-19 & UNAVCO Community, 2014, TLALOCNet - TNCU-CuauhtemocTN2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5V69GV2}.\\
-    TNGF & 19.33 & -99.18 & 2020-11-16 2020-12-29 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2016, TLALOCNet GPS Network - TNGF\_Geofisica-UNAM\_Mexico\_City\_TNET\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T53X851M}.\\
-    TNHM & 29.08 & -110.97 & 2019-10-09 2019-11-26 2019-12-04 2019-12-15 2019-12-29 2020-01-03 2020-03-31 2020-04-18 2020-07-15 2020-08-07 2020-09-13 2020-09-30 2020-12-23 & UNAVCO Community, 2014, TLALOCNet - TNHM-hermosilloTN2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5KP80FV}.\\
-    TNMS & 20.53 & -104.80 & 2019-10-09 2019-11-26 2019-12-15 2020-03-03 2020-07-15 & UNAVCO Community, 2014, TLALOCNet - TNMS-TNMS\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T56H4FQ5}.\\
-    TNNP & 16.12 & -97.14 & 2020-04-28 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, DeMets, Charles, 2016, TLALOCNet - TNNP-tnnp\_tnet\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5N29V96}.\\
-    TNNX & 17.41 & -97.22 & 2020-01-15 2020-02-12 2020-12-29 2021-03-31 & UNAVCO Community, 2014, TLALOCNet - TNNX-TNNX\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T52R3PZ0}.\\
-    TNPP & 31.34 & -113.63 & 2019-12-04 2020-03-31 2020-04-25 & UNAVCO Community, 2015, TLALOCNet - TNPP-TNPP\_TNET\_MX2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5CC0Z0M}.\\
-    TNSJ & 16.17 & -96.49 & 2020-12-29 & UNAVCO Community, 2016, TLALOCNet - TNSJ-tnsj\_tnet\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59S1PF1}.\\
-    TSFX & 30.93 & -114.81 & 2020-09-13 2020-12-23 & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network - TSFX-tsfxREGNOMmx2016 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/AGEA-2G27}.\\
-    UAGU & 21.92 & -102.32 & 2019-05-23 2019-07-18 2019-08-10 2019-10-03 2019-11-17 2019-11-26 2019-12-15 2020-04-18& Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UAGU-uagu\_tnet\_mx2008 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5513WK7}.\\
-    UCOE\hyperlink{Graham}{${}^3$} & 19.81 & -101.69 & 2019-08-10 2020-11-16 2020-11-17 2020-12-19 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UCOE-ucoe\_tnet\_mx2003 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T51834VW}.\\
-    UGEO\hyperlink{Marquez}{${}^4$} & 20.69 & -103.35 & 2019-08-10& Marquez-Azua, Bertha, DeMets, Charles, Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UGEO-ugeo\_tnet\_mx1998 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T58S4N9N}.\\
-    UHSL & 29.57 & -95.65 & 2020-04-08 & Wang, Guoquan, 2014, HoustonNet GPS Network - UHSL-SugarLandUSA2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T55X271S}.\\
-    UHWL & 30.06 & -94.98 & 2020-12-19 & Wang, Guoquan, 2014, HoustonNet GPS Network - UHWL-West Liberty Airport(Deep) P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T53R0R5P}.\\
-    UNPM & 20.86 & -86.86 & 2019-11-19 2020-01-15 2020-02-12 2020-05-08 & UNAVCO Community, 2012, COCONet GPS Network - UNPM-Puerto\_Morelos\_MX\_2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/J1GD-5S40}.\\
-    USMX & 29.82 & -109.68 & 2019-12-29 2020-01-03 2020-01-06 2020-04-25 2020-08-07 2020-09-30& Bennett, Rick, 2004, Northwest Mexico GPS Network - USMX-Universidad de la Sierra P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5W957CQ}.\\
-    UXAL\hyperlink{Graham}{${}^3$} & 19.52 & -96.92 & 2019-10-03 2020-01-15 2020-02-12 2020-04-08 2020-05-08 2020-12-19 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UXAL-uxal\_tnet\_mx2005 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5D1C}.\\
-    WEPD & 29.69 & -95.23 & 2020-04-20 & Wang, Guoquan, 2014, HoustonNet GPS Network - WEPD-willmselementary P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5NZ85RB}.\\
-    WMOK & 34.74 & -98.78 & 2020-04-20 & UNAVCO Community, 2005, PBO GPS Network - WMOK-WichitaMtnOK2005 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59021Q6}.\\
-    WWMT\hyperlink{Hudnut}{${}^1$} & 33.96 & -116.65 & 2019-12-29 2020-01-03& Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2006, SCIGN USGS GPS Network - WWMT-Whitewater Mountain P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5H993F2}.\\
-    YESX & 28.38 & -108.92 & 2019-11-26 2019-12-15 2020-01-06 2020-04-18 2020-04-28 2020-07-15& Bennett, Rick, 2004, Northwest Mexico GPS Network - YESX-Yecora P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5RJ4GPF}.\\\hline
-    % \end{table*}
-  \end{longtable}
-    \begin{minipage}{0.9\linewidth}
-      \footnotesize
-      Related articles:
-
-      \hypertarget{Hudnut}{${}^1$}\citet{Hudnut:2002},
+%\clearpage
+%\onecolumn
+%\footnotesize
+%\begin{landscape}
+%%\begin{table*}
+%%    \centering
+%  \begin{longtable}{llllllp{12cm}}
+%      \caption{List of GPS stations used for this work.}
+%      \label{tab:table-stations}
+%      \endfirsthead
+%      \endhead
+%    \hline
+%    Station name & Latitude & Longitude & \multicolumn{3}{c}{Events ID}  & Citation \\\hline
+%    \multirow{4}{*}{BAR1\hyperlink{Hudnut}{${}^1$}\hyperlink{Hudnut2}{${}^5$}} & \multirow{4}{*}{33.48} & \multirow{4}{*}{-119.03} & \multirow{4}{*}{GLM-07} & \multirow{4}{*}{GLM-12} & \multirow{4}{*}{GLM-13} & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, \\
+%    &&&&&& Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - BAR1-Santa \\
+%    &&&&&& Barbara Island One P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+%    &&&&&& \url{https://doi.org/10.7283/T5668BHN}.\\\hline
+%    \multirow{3}{*}{BLYT\hyperlink{Hudnut}{${}^1$}} & \multirow{3}{*}{33.61} & \multirow{3}{*}{-114.71} &  \multirow{3}{*}{GLM-12} & \multirow{3}{*}{GLM-13}  & & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John \\
+%    &&&&&& E., Stark, Keith F., 2006, SCIGN USGS GPS Network - BLYT-Blythe P.S., The GAGE Facility operated \\
+%    &&&&&&  by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5HT2MKK}.\\\hline
+%    \multirow{3}{*}{CN23} & \multirow{3}{*}{17.26} & \multirow{3}{*}{-88.78} &\multirow{3}{*}{GLM-08} & \multirow{3}{*}{GLM-15} & \multirow{3}{*}{GLM-16} & UNAVCO Community, 2012, COCONet GPS Network - CN23-BelmopanBZCR2012 P.S., The GAGE \\
+%    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+%    &&&&&& \url{https://doi.org/10.7283/T5Q23XJH}.\\\hline
+%    \multirow{3}{*}{CN25} & \multirow{3}{*}{16.23} & \multirow{3}{*}{-92.13} & \multirow{3}{*}{GLM-15} & & & UNAVCO Community, 2014, COCONet GPS Network - CN25-ComitandDMEX2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57W69G7}.\\\hline
+%    \multirow{3}{*}{GCFS} & \multirow{3}{*}{19.31} & \multirow{3}{*}{-81.18} & \multirow{3}{*}{GLM-08} & & & Watts, Anthony, 2016, COCONet GPS Network - GCFS-G\_CAYMAN\_CYM2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/7ETV-X536}.\\\hline
+%    \multirow{4}{*}{GMPK\hyperlink{Hudnut}{${}^1$}} & \multirow{4}{*}{33.05} & \multirow{4}{*}{-114.83} & \multirow{4}{*}{GLM-10} & & & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, \\
+%    &&&&&& Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - GMPK-Glamis \\
+%    &&&&&& Peak P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+%    &&&&&& \url{https://doi.org/10.7283/WCHN-H687}.\\\hline
+%    \multirow{3}{*}{GUAT\hyperlink{Garnier}{${}^2$}} & \multirow{3}{*}{14.59} & \multirow{3}{*}{-90.52} & \multirow{3}{*}{GLM-16} & & & DeMets, Charles, Cosenza-Muralles, Beatriz, 2021, Central America 2018 - Guatemala, The GAGE \\
+%    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+%    &&&&&& \url{https://doi.org/10.7283/KH2R-K704}.\\\hline
+%\multirow{4}{*}{GUAX\hyperlink{Hudnut}{${}^1$}} & \multirow{4}{*}{28.88} & \multirow{4}{*}{-118.29} & GLM-05 & GLM-07 & GLM-11 & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John \\
+%    &&&GLM-12& GLM-13& GLM-18 & E., Stark, Keith F., 2001, SCIGN USGS GPS Network - GUAX-Isla Guadalupe P.S., The GAGE Facility \\
+%    &&& GLM-25 &GLM-27 &GLM-28& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5GX48T2}.\\
+%    &&& GLM-32 &       &     &  \\\hline
+%    \multirow{3}{*}{IAGX} & \multirow{3}{*}{29.03} & \multirow{3}{*}{-113.17} & \multirow{3}{*}{GLM-10} & & & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network \\
+%    &&&&&& - IAGX-iagxREGNOMmx2018 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS  \\
+%    &&&&&& Observations Dataset, \url{https://doi.org/10.7283/DGWN-A627}. \\\hline
+%    \multirow{2}{*}{INEG} & \multirow{2}{*}{21.85} & \multirow{2}{*}{-102.28} & GLM-25 & GLM-26 & GLM-28  & No citations were found \\
+%    &&& GLM-29 & GLM-30 & GLM-31 & \\\hline 
+%    \multirow{4}{*}{KVTX} & \multirow{4}{*}{27.55} & \multirow{4}{*}{-97.89} & GLM-01 & GLM-02 & GLM-03  & UNAVCO Community, 2007, PBO GPS Network - KVTX-KingsvilleTX2006 P.S., The GAGE Facility \\
+%    &&& GLM-04 & GLM-06 & GLM-19 & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J38QH8}.\\
+%    &&& GLM-20 & GLM-21 & GLM-24 & \\
+%    &&& GLM-26 &&& \\\hline
+%    MDO1 & 30.68 & -104.02 & GLM-02 & & & No citations were found\\\hline
+%    MGO5 & 30.68 & -104.02 & GLM-21 &GLM-26 &  & No citations were found\\\hline
+%    MGW3 & 29.62 & -89.95 & GLM-19 & GLM-21 & GLM-24 & No citations were found\\\hline
+%    \multirow{3}{*}{OXTH} & \multirow{3}{*}{16.29} & \multirow{3}{*}{-95.24} & \multirow{3}{*}{GLM-15} & \multirow{3}{*}{GLM-16} & & DeMets, Charles, Cabral-Cano, Enrique, 2008, Oaxaca GPS Network - OXTH-Tehuantepec P.S., The \\
+%    &&&&&& GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+%    &&&&&& \url{https://doi.org/10.7283/T5Q81B5V}.\\\hline
+%    \multirow{3}{*}{OXUM\hyperlink{Graham}{${}^3$}} & \multirow{3}{*}{15.66} & \multirow{3}{*}{-96.50} & \multirow{3}{*}{GLM-34} & & & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - OXUM-oxum\_tnet\_mx2001 P.S., The \\
+%    &&&&&& GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+%    &&&&&& \url{https://doi.org/10.7283/T5J964RP}.\\\hline
+%    \multirow{2}{*}{P001} & \multirow{2}{*}{31.95} & \multirow{2}{*}{-112.80} & \multirow{2}{*}{GLM-07} & \multirow{2}{*}{GLM-22} & & UNAVCO Community, 2008, PBO GPS Network - P001-Organ\_PipeAZ2007 P.S., The GAGE Facility \\
+%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DR2SGP}.\\\hline
+%    \multirow{2}{*}{P014} & \multirow{2}{*}{31.97} & \multirow{2}{*}{-11.09} & GLM-10 & GLM-12 & GLM-13 & UNAVCO Community, 2008, PBO GPS Network - P014-Sahuarita\_AZ2007 P.S., The GAGE Facility \\
+%    &&& GLM-14 & GLM-22 & & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5CMK}.\\\hline
+%    \multirow{2}{*}{P807} & \multirow{2}{*}{30.49} & \multirow{2}{*}{-98.82} & GLM-06 & GLM-14 & GLM-21 & UNAVCO Community, 2012, PBO GPS Network - P807-EcRockStPkTX2012 P.S., The GAGE Facility \\
+%    &&& GLM-30 &&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5TQ5ZKM}.\\\hline
+%    \multirow{2}{*}{PLPX} & \multirow{2}{*}{31.59} & \multirow{2}{*}{-115.15} & \multirow{2}{*}{GLM-10} & & & UNAVCO Community, 2011, PBO GPS Network - PLPX-Las\_PintasMX2010 P.S., The GAGE Facility \\
+%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5K64G3T}.\\\hline
+%    \multirow{2}{*}{PTEX} & \multirow{2}{*}{32.29} & \multirow{2}{*}{-116.52} & GLM-07 & GLM-12 & GLM-13  & UNAVCO Community, 2011, PBO GPS Network - PTEX-Testerazo\_MX2011 P.S., The GAGE Facility \\
+%    &&& GLM-27 & GLM-32 & & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XBP}.\\\hline 
+%    \multirow{3}{*}{RG06} & \multirow{3}{*}{32.63} & \multirow{3}{*}{-107.86} & \multirow{3}{*}{GLM-22} & & & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG06-RG06FaywodNM2006 P.S., The GAGE \\
+%    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+%    &&&&&& \url{https://doi.org/10.7283/T5668BFR}.\\\hline
+%    \multirow{3}{*}{RG07} & \multirow{3}{*}{32.50} & \multirow{3}{*}{-106.84} & \multirow{3}{*}{GLM-14} & & & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG07-RG07CrucesNM2006 P.S., The GAGE  \\
+%    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+%    &&&&&& \url{https://doi.org/10.7283/T5KD1W45}. \\\hline
+%    \multirow{3}{*}{SG33} & \multirow{3}{*}{31.77} & \multirow{3}{*}{-106.51} & \multirow{3}{*}{GLM-06} & \multirow{3}{*}{GLM-20} & \multirow{3}{*}{GLM-26} & Harder, Steven, Kaip, Galen, Montana, Carlos, 2004, SuomiNet-G GPS Network - SG33-UTEP P.S., The \\
+%    &&&&&& GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset,  \\
+%    &&&&&& \url{https://doi.org/10.7283/T50863KQ}. \\\hline
+%    \multirow{3}{*}{TGMX}  & \multirow{3}{*}{20.87} & \multirow{3}{*}{-86.87} & \multirow{3}{*}{GLM-34} & & & UNAVCO Community, 2015, COCONet GPS Network - TGMX-PtoMor\_TG\_MX2015 P.S., The GAGE \\
+%    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset,  \\
+%    &&&&&& \url{https://doi.org/10.7283/T5154FB7}. \\\hline
+%    \multirow{2}{*}{TNAM} & \multirow{2}{*}{20.54} & \multirow{2}{*}{-103.97} & GLM-17 & GLM-25 & GLM-28  & UNAVCO Community, 2014, TLALOCNet - TNAM-TNAM\_TNET\_MX2014 P.S., The GAGE Facility \\
+%    &&& GLM-29 & GLM-30 & GLM-31 & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5QF8R4R}.\\\hline
+%    \multirow{2}{*}{TNAT} & \multirow{2}{*}{18.13} & \multirow{2}{*}{-98.04} & \multirow{2}{*}{GLM-15} & & & UNAVCO Community, 2014, TLALOCNet - TNAT-TNAT\_TNET\_MX2014 P.S., The GAGE Facility \\
+%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5G15Z4S}. \\\hline
+%    \multirow{2}{*}{TNBA} & \multirow{2}{*}{28.97} & \multirow{2}{*}{-113.55} & GLM-05 & GLM-07 & GLM-09  & UNAVCO Community, 2015, TLALOCNet - TNBA-TNBA\_TNET\_MX2014 P.S., The GAGE Facility  \\
+%    &&& GLM-11 & GLM-12 & GLM-13 & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57M0688}.\\\hline
+%    \multirow{2}{*}{TNCC} & \multirow{2}{*}{18.79} & \multirow{2}{*}{-103.17} & \multirow{2}{*}{GLM-17} & & & UNAVCO Community, 2015, TLALOCNet - TNCC-TNCC\_TNET\_MX2015 P.S., The GAGE Facility \\
+%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T50R9MSK}.\\\hline
+%    \multirow{2}{*}{TNCM} & \multirow{2}{*}{19.50} & \multirow{2}{*}{-105.04} & \multirow{2}{*}{GLM-17} & \multirow{2}{*}{GLM-23} & & UNAVCO Community, 2014, TLALOCNet - TNCM-TNCM\_TNET\_MX2014 P.S., The GAGE Facility \\
+%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5B856FW}.\\\hline
+%    \multirow{2}{*}{TNCN} & \multirow{2}{*}{18.55} & \multirow{2}{*}{-101.97} & \multirow{2}{*}{GLM-29} & \multirow{2}{*}{GLM-33} & & UNAVCO Community, 2016, TLALOCNet - TNCN-TNCN\_TNET\_MX2016 P.S., The GAGE Facility \\
+%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XQM}.\\\hline
+%    \multirow{4}{*}{TNCU} & \multirow{4}{*}{28.45} & \multirow{4}{*}{-106.79} & GLM-01 & GLM-02 & GLM-03  & UNAVCO Community, 2014, TLALOCNet - TNCU-CuauhtemocTN2014 P.S., The GAGE Facility \\
+%    &&& GLM-06 & GLM-11 & GLM-14 & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5V69GV2}.\\
+%    &&& GLM-18 & GLM-20 & GLM-25 & \\
+%    &&& GLM-26 & GLM-30 & GLM-31 & \\\hline
+%    \multirow{3}{*}{TNGF} & \multirow{3}{*}{19.33} & \multirow{3}{*}{-99.18} & \multirow{3}{*}{GLM-29} & \multirow{3}{*}{GLM-33} & & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2016, TLALOCNet GPS Network - TNGF\_Geofisica-\\
+%    &&&&&& UNAM\_Mexico\_City\_TNET\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS \\
+%    &&&&&& Observations Dataset, \url{https://doi.org/10.7283/T53X851M}. \\\hline
+%    \multirow{5}{*}{TNHM} & \multirow{5}{*}{29.08} & \multirow{5}{*}{-110.97} & GLM-05 & GLM-09 & GLM-10 & UNAVCO Community, 2014, TLALOCNet - TNHM-hermosilloTN2014 P.S., The GAGE Facility \\
+%    &&& GLM-11 & GLM-12 & GLM-13 & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5KP80FV}.\\
+%    &&& GLM-18 & GLM-20 & GLM-25 & \\
+%    &&& GLM-26 & GLM-27 & GLM-28 & \\
+%    &&& GLM-32 &        &        & \\\hline
+%    \multirow{2}{*}{TNMS} & \multirow{2}{*}{20.53} & \multirow{2}{*}{-104.80} & GLM-05 & GLM-09 & GLM-11  & UNAVCO Community, 2014, TLALOCNet - TNMS-TNMS\_TNET\_MX2014 P.S., The GAGE Facility \\
+%    &&& GLM-17 & GLM-25 & & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T56H4FQ5}.\\\hline
+%    \multirow{3}{*}{TNNP} & \multirow{3}{*}{16.12} & \multirow{3}{*}{-97.14} & \multirow{3}{*}{GLM-23} & & & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, DeMets, Charles, 2016, TLALOCNet - TNNP-\\
+%    &&&&&& tnnp\_tnet\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+%    &&&&&& \url{https://doi.org/10.7283/T5N29V96}. \\\hline
+%    \multirow{2}{*}{TNNX} & \multirow{2}{*}{17.41} & \multirow{2}{*}{-97.22} & GLM-15 & GLM-16 & GLM-33  & UNAVCO Community, 2014, TLALOCNet - TNNX-TNNX\_TNET\_MX2014 P.S., The GAGE Facility \\
+%    &&& GLM-34 &&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T52R3PZ0}.\\\hline
+%    \multirow{2}{*}{TNPP} & \multirow{2}{*}{31.34} & \multirow{2}{*}{-113.63} & GLM-07 & GLM-10 & GLM-18 & UNAVCO Community, 2015, TLALOCNet - TNPP-TNPP\_TNET\_MX2015 P.S., The GAGE Facility \\
+%    &&& GLM-22 &&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5CC0Z0M}.\\\hline
+%    \multirow{2}{*}{TNSJ} & \multirow{2}{*}{16.17} & \multirow{2}{*}{-96.49} & \multirow{2}{*}{GLM-33} & & & UNAVCO Community, 2016, TLALOCNet - TNSJ-tnsj\_tnet\_mx2015 P.S., The GAGE Facility operated by \\
+%    &&&&&& UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59S1PF1}.\\\hline
+%    \multirow{3}{*}{TSFX} & \multirow{3}{*}{30.93} & \multirow{3}{*}{-114.81} & \multirow{3}{*}{GLM-07} & \multirow{3}{*}{GLM-27} & \multirow{3}{*}{GLM-32} & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network \\
+%    &&&&&& - TSFX-tsfxREGNOMmx2016 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS \\
+%    &&&&&& Observations Dataset, \url{https://doi.org/10.7283/AGEA-2G27}.\\\hline
+%    \multirow{3}{*}{UAGU} & \multirow{3}{*}{21.92} & \multirow{3}{*}{-102.32} & GLM-01 & GLM-02 & GLM-03  & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UAGU-uagu\_tnet\_mx2008 P.S., The \\
+%    &&& GLM-04 & GLM-06 & GLM-09 & GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+%    &&& GLM-11 & GLM-20 &        & \url{https://doi.org/10.7283/T5513WK7}.\\\hline
+%    \multirow{3}{*}{UCOE\hyperlink{Graham}{${}^3$}} & \multirow{3}{*}{19.81} & \multirow{3}{*}{-101.69} & GLM-03 & GLM-06 & GLM-30 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UCOE-ucoe\_tnet\_mx2003 P.S., The \\
+%    &&& GLM-31 &&& GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+%    &&&&&& \url{https://doi.org/10.7283/T51834VW}. \\\hline
+%    \multirow{3}{*}{UGEO\hyperlink{Marquez}{${}^4$}} & \multirow{3}{*}{20.69} & \multirow{3}{*}{-103.35} & \multirow{3}{*}{GLM-03} & & & Marquez-Azua, Bertha, DeMets, Charles, Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, \\
+%    &&&&&& TLALOCNet - UGEO-ugeo\_tnet\_mx1998 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS \\
+%    &&&&&& Observations Dataset, \url{https://doi.org/10.7283/T58S4N9N}. \\\hline
+%    \multirow{2}{*}{UHSL} & \multirow{2}{*}{29.57} & \multirow{2}{*}{-95.65} & \multirow{2}{*}{GLM-19} & & & Wang, Guoquan, 2014, HoustonNet GPS Network - UHSL-SugarLandUSA2014 P.S., The GAGE Facility \\
+%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T55X271S}.\\\hline
+%    \multirow{3}{*}{UHWL} & \multirow{3}{*}{30.06} & \multirow{3}{*}{-94.98} & \multirow{3}{*}{GLM-31} & & & Wang, Guoquan, 2014, HoustonNet GPS Network - UHWL-West Liberty Airport(Deep) P.S., The GAGE \\
+%    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset,  \\
+%    &&&&&& \url{https://doi.org/10.7283/T53R0R5P}. \\\hline
+%    \multirow{3}{*}{UNPM} & \multirow{3}{*}{20.86} & \multirow{3}{*}{-86.86} & GLM-08 & GLM-15 & GLM-16  & UNAVCO Community, 2012, COCONet GPS Network - UNPM-Puerto\_Morelos\_MX\_2007 P.S., The \\
+%    &&& GLM-24 &&& GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+%    &&&&&& \url{https://doi.org/10.7283/J1GD-5S40}.\\\hline
+%    \multirow{3}{*}{USMX} & \multirow{3}{*}{29.82} & \multirow{3}{*}{-109.68} & GLM-12 & GLM-13 & GLM-14  & Bennett, Rick, 2004, Northwest Mexico GPS Network - USMX-Universidad de la Sierra P.S., The GAGE \\
+%    &&& GLM-22 & GLM-26 & GLM-28 & Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+%    &&&&&& \url{https://doi.org/10.7283/T5W957CQ}.\\\hline
+%    \multirow{3}{*}{UXAL\hyperlink{Graham}{${}^3$}} & \multirow{3}{*}{19.52} & \multirow{3}{*}{-96.92} & GLM-04 & GLM-15 & GLM-16  & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UXAL-uxal\_tnet\_mx2005 P.S., The \\
+%    &&& GLM-19 & GLM-24 & GLM-31 & GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
+%    &&& GLM-34 &        &        & \url{https://doi.org/10.7283/T5DJ5D1C}.\\\hline
+%    \multirow{2}{*}{WEPD} & \multirow{2}{*}{29.69} & \multirow{2}{*}{-95.23} & \multirow{2}{*}{GLM-21} & & & Wang, Guoquan, 2014, HoustonNet GPS Network - WEPD-willmselementary P.S., The GAGE Facility \\
+%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5NZ85RB}. \\\hline
+%    \multirow{2}{*}{WMOK} & \multirow{2}{*}{34.74} & \multirow{2}{*}{-98.78} & \multirow{2}{*}{GLM-21} & & & UNAVCO Community, 2005, PBO GPS Network - WMOK-WichitaMtnOK2005 P.S., The GAGE Facility \\
+%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59021Q6}. \\\hline
+%    \multirow{4}{*}{WWMT\hyperlink{Hudnut}{${}^1$}} & \multirow{4}{*}{33.96} & \multirow{4}{*}{-116.65} & \multirow{4}{*}{GLM-07} & \multirow{4}{*}{GLM-12} & \multirow{4}{*}{GLM-13} & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John \\
+%    &&&&&& E., Stark, Keith F., 2006, SCIGN USGS GPS Network - WWMT-Whitewater Mountain P.S., The GAGE \\
+%    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset,  \\
+%    &&&&&& \url{https://doi.org/10.7283/T5H993F2}. \\\hline
+%    \multirow{2}{*}{YESX} & \multirow{2}{*}{28.38} & \multirow{2}{*}{-108.92} & GLM-09 & GLM-11 & GLM-14  & Bennett, Rick, 2004, Northwest Mexico GPS Network - YESX-Yecora P.S., The GAGE Facility operated \\
+%    &&&GLM-20 & GLM-23 & GLM-25 & by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5RJ4GPF}.\\\hline
 %    
-      \hypertarget{Garnier}{${}^2$}\citet{Garnier:2021}, 
+%%    % \end{table*}
+%  \end{longtable}
+%    \begin{minipage}{0.9\linewidth}
+%      \footnotesize
+%      Related articles:
 %      
-      \hypertarget{Graham}{${}^3$}\citet{Graham:2016}
-
-      \hypertarget{Marquez}{${}^4$}\href{https://doi.org/10.7283/T58S4N9N}{B.
+%      \hypertarget{Hudnut}{${}^1$}\citet{Hudnut:2002},
+%      %
+%      \hypertarget{Garnier}{${}^2$}\citet{Garnier:2021}, 
+%      %
+%      \hypertarget{Graham}{${}^3$}\citet{Graham:2016}
+%      
+%      \hypertarget{Marquez}{${}^4$}\href{https://doi.org/10.7283/T58S4N9N}{B.
 Marquez-Azua, E.
@@
 43, p.319-330}
-
-      \hypertarget{Hudnut2}{${}^5$}\href{https://doi.org/10.7283/T5668BHN}{Hudnut, K.
+%      
+%      \hypertarget{Hudnut2}{${}^5$}\href{https://doi.org/10.7283/T5668BHN}{Hudnut, K.
 W., Y.
@@
 175-196, 1999}
+%    \end{minipage}
+%  \end{landscape}
+%  \clearpage
+%  \twocolumn
 
-    \end{minipage}
-  \end{landscape}
-  \clearpage
-  \twocolumn
+%  The obtained RINEX files are compressed in Hatanaka format, developed at the Geographical Survey Institute by Y.
+Hatanaka \citep{Kumar:2012}.
+From this files we may estimate the Slant Total Electron Content (sTEC) and the Vertical Total Electron Content (vTEC) which may be computed in the following way:
+
+  The Total Electron content along the integrated path of the link $(s_i)$ at the frequency $f_i$ can be inferred from the phase delay $L_i$ of the frequency $f_i$ \citep{Emery:2017}:
+  \begin{align}
+    L_i = s_i - \frac{\SI{40.3082}{m^3.s^{-1}}}{f_i^2}sTEC_i
+  \end{align}
+  Combining two observations at two different frequencies $f_1$ and $f_2$ we may obtain two different phase delays $L_1$ and $L_2$ and derive the TEC along the signal path:
+
+  \begin{align}
+    sTEC = \frac{f_1^2f_2^2\left(L_1-L_2\right)}{\SI{40.3082}{m^3.s^{-1}}\left(f_1^2-f_2^2\right)}
+  \end{align}
+
+  In the other hand, the Vertical Total Electron Content (vTEC) is computed from the sTEC as follows \citep{Kumar:2012}:
+  \begin{align}
+    vTEC = \frac{sTEC-\left[b_R+b_S\right]}{S(\theta_I)}
+  \end{align}
+
+  where $b_R$ and $b_S$ are receiver and satellite biases, respectively.
+$\theta_I$ is the elevation angle in degrees, $S(\theta_I)$ is the obliquity factor with zenith angle $\psi$ at the Ionospheric Pierce Point (IPP):
+
+  \begin{align}
+    S(\theta_i) = \frac{1}{\cos\psi} = \left\lbrace 1-\frac{R_E\cos\theta_I}{R_E+h}\right\rbrace^{-1/2}
+  \end{align}
+
+  Where $R_E$ is the Earth radius in km and $h=\SI{350}{km}$ is the ionospheric shell above the earth's surface.
+
+  Both parameters sTEC and vTEC are computed using a software developed by Gopi K. Seemala, publicly available at \url{https://seemala.blogspot.com/}.
+
 %For the selected sample, we obtained RINEX data from the TlalocNet \citep{Cabral-Cano:2018} and UNAVCO network databases to study potential alterations in the ionospehre due to the presence of the passing meteor at the day the meteor was reported.

### 2021-11-16 paper/vTEC-maps.tex
Emergency Backup

@@
-Ionospheric perturbations also can take place due to space weather and geomagnetic storms.
+In progress ...
+%Ionospheric perturbations also can take place due to space weather and geomagnetic storms.
 So, in order to discard such events we investigated the space weather in the day each event occured.

### 2021-11-16 TEC_detrender.py

@@ -84,33 +84,6 @@ def discontinuity(x):
         else:
             flag = False
     return flag
-
-# **************************** Split discontine PRN *******************************************
-
-def split_PRN(t, TEC):
-    """
-    Split a discontinuos PRN into pieces and return the biggest ones
-    inputs:
-    t, TEC: arrays to be split. t --> time , TEC --> vTEC
-    outputs:
-    output_t, output_TEC --> 2D arrays which contain the fragmented curve
-    """
-
-    index_discontinuity =[]
-    gradient_t = np.gradient(t)
-    for i, dt in enumerate(gradient_t):
-        if dt > 0.01: # 0.01 is like 10 times the regular GPS frequency
-            index_discontinuity.append(i) # collect the indices where time gradient is big enough
-    split_t = np.split(t, index_discontinuity)
-    split_TEC = np.split(TEC, index_discontinuity)
-    output_t = []
-    output_TEC =[]
-    for s, tec in zip(split_t, split_TEC):
-        if len(s) > 20: #if the subarray contain too few elements will be discarded
-            output_t.append(s)
-            output_TEC.append(tec)
-    return output_t, output_TEC
-
 # *************************** Read inputs from command line ***********************************
 
 parser = argparse.ArgumentParser(
@@ -122,7 +95,9 @@ parser.add_argument('--date', type=str, default='2000-01-01',
 
 parser.add_argument("--formato", type=str, default="pdf", choices=("pdf", "png", "jpg"), 
                                 help="Choose output format")
+
 parser.add_argument("--starttime", type=str, default="00:00:00", help="Select the event start time")
+
 parser.add_argument("--filterhigh", type=float, default=30, 
                      help="Filter the upper time interval of the TEC curve (in ninutes)")
 parser.add_argument("--filterlow", type=float, default=10, 
@@ -161,70 +136,52 @@ for p in prn_array:
     selected_TEC = vTEC[PRN_mask]
     time_mask = (selected_time < time_hours + filter_high/60.) & (selected_time > time_hours-filter_low/60.)
 
-# ******************************* Split the signal into fragments *********************************
[…]

### 2021-11-16 plot_meteors.py

@@ -29,16 +29,27 @@ plot_map(sf)
 # Read meteors_database
 
 f = Table.read("meteors_database.tab", format="ascii")
-
+f2 = Table.read("USG_meteors_database.tab", format="ascii")
 # plot positions plus uncertainties in the map
+GLM_mask = f["ID"] == "GLM-Ven" # We will exclude the Venezolan meteor since it will distort the map
+USG_mask = f2["ID"] == "USG-09" # We will exclude the Venezolan meteor since it will distort the map
 
-plt.errorbar(f["Longitud"], f["Latitud"], xerr=f["sig_lon"], yerr=f["sig_latitude"], fmt="bo", capsize=3)
+plt.errorbar(f["Longitud"][~GLM_mask], f["Latitud"][~GLM_mask], xerr=f["sig_lon"][~GLM_mask], yerr=f["sig_latitude"][~GLM_mask], fmt="bo", capsize=3)
+plt.plot(f2["Longitud"][~USG_mask], f2["Latitud"][~USG_mask], "go")
 # Offset of labels
-x_off = [10, 10, 10, -10, -10, -10, 10, 10, 10, 10, 10, -10, -10, 10, 10, 10, 10, 10, 10, 10, -10, -10, 10, 10, 10, -10, 10, -10, -10, 10, -10, 10, -10, 10, 10]
-y_off = [10, 10, 10, -10, 10, -10, 10, 10, 10, 10, -10, -10, -10, 10, 10, 10, -10, -10, 10, -10, 10, 10, 10, 10, 10, -10, -10, 10, -10, 10, 10, 10, 10, 10, 10]
-for i in range(len(f["ID"])):
-    plt.annotate(f["ID"][i], (f["Longitud"][i], f["Latitud"][i]), textcoords="offset points", color="w", fontsize="small",
+x_off = [10, 10, 10, -10, -10, -10, 10, 10, -10, 10, 10, -10, -10, 10, 10, 10, 10, 10, 10, 10, -10, -10, 10, 10, 10, -10, 10, -10, -10, 10, -10, 10, -10, 10, 10]
+y_off = [10, 10, 10, -10, 10, -10, 10, 10, -10, 10, -10, -10, -10, 10, 10, 10, -10, -10, 10, -10, 10, 10, 10, 10, 10, -10, -10, 10, -10, 10, 10, 10, 10, 10, 10]
+
+x2_off = [10, -10, 10, 10, 10, -10, 10, -10, 10]
[…]

### 2021-12-01 paper/methodology.tex
Last commit in linux
- Update methodology section in paper
- Correct issues in TEC detrender

@@
 
-%We got RINEX data from 3 to 7 stations depending of the event location and data availability that surround the event place in all directions as possible.
-A list of the stations where we got RINEX data is available in table \ref{tab:table-stations}.
-Most of the stations lie in mexican territory, but in some cases we required data from other stations to cover events near the mexican frontier at north or south.
+We got RINEX data from 3 to 7 stations depending of the event location and data availability that surround the event place in all directions as possible.
+A list of the stations where we got RINEX data is available in table%\ref{tab:table-stations}
+. Most of the stations lie in mexican territory, but in some cases we required data from other stations to cover events near the mexican frontier at north or south.
 
@@
 
-%  The obtained RINEX files are compressed in Hatanaka format, developed at the Geographical Survey Institute by Y.
+  The obtained RINEX files are compressed in Hatanaka format, developed at the Geographical Survey Institute by Y.
 Hatanaka \citep{Kumar:2012}.
@@
 
-  Both parameters sTEC and vTEC are computed using a software developed by Gopi K. Seemala, publicly available at \url{https://seemala.blogspot.com/}.
+  % Both parameters sTEC and vTEC are computed
+ Using a software developed by Gopi K.
+Seemala, publicly available at \url{https://seemala.blogspot.com/}, we computed the slant TEC (TEC) and vertical TEC (vTEC) for a several number of GPS satellites, each one identified with a PseudoRandom Noise code (PRN).
+For each station, we filtered all the PRN and data that lie in a window of 30 minutes around the time the event was reported.
+Then we estimated the signal trend using a Savitsky-Golay filter and substracting the original signal from the trend.
+
+  \subsection{Wavelet analysis}
 

### 2021-12-22 TEC_detrender.py
update of wavelet program
Now we can measure wavelet coherence spectrum. Need a .gitignore file

@@ -29,18 +29,18 @@ def next_contact_point(x, y, x0, y0):
     # Delta_x and delta_y are the separation between the elements which belong to the ROI and (x0, y0)
     delta_x = x[ROI]-x0
     delta_y = y[ROI]-y0
-    
+
     try:
-        # calculating important angles
+	# calculating important angles
         theta = np.arctan2(delta_y, delta_x)
         cos_alpha = np.sqrt(delta_x**2 + delta_y**2)/(2*R0) 
         delta = np.arcsin(cos_alpha) - theta
-        # Selecting the Next Contact Point (NCP)
+	# Selecting the Next Contact Point (NCP)
         NCP = delta == min(delta) # The next contact point has the smallest angular distance delta
         xf, yf = x0+delta_x[NCP][0], y0+delta_y[NCP][0]
     except ValueError: # this happens because ROI is empty
         xf, yf = x[~ROI & (x>x0)][0], y[~ROI & (x>x0)][0] #The element we will use as next contact point
-                                                          # is the first outside the ROI and greater than x0
+							  # is the first outside the ROI and greater than x0
     return xf, yf
 
 def free_dep_signal(brc_x, brc_y, x, y):
@@ -84,6 +84,33 @@ def discontinuity(x):
         else:
             flag = False
     return flag
+
+# **************************** Split discontine PRN *******************************************
+
+def split_PRN(t, TEC):
+    """
+    Split a discontinuos PRN into pieces and return the biggest ones
+    inputs:
+    t, TEC: arrays to be split. t --> time , TEC --> vTEC
+    outputs:
+    output_t, output_TEC --> 2D arrays which contain the fragmented curve
+    """
+
+    index_discontinuity =[]
+    gradient_t = np.gradient(t)
+    for i, dt in enumerate(gradient_t):
+        if dt > 0.01: # 0.01 is like 10 times the regular GPS frequency
+            index_discontinuity.append(i) # collect the indices where time gradient is big enough
+    split_t = np.split(t, index_discontinuity)
+    split_TEC = np.split(TEC, index_discontinuity)
+    output_t = []
+    output_TEC =[]
+    for s, tec in zip(split_t, split_TEC):
+        if len(s) > 20: #if the subarray contain too few elements will be discarded
+            output_t.append(s)
+            output_TEC.append(tec)
+    return output_t, output_TEC
+
[…]

### 2021-12-22 TEC_grid_maps.py

@@ -1,0 +1,89 @@
+import numpy as np
+from scipy.interpolate import griddata
+import pandas as pd
+import matplotlib.pyplot as plt
+import shapefile as shp
+from plotfullmap import plot_map
+import matplotlib.cm as cm
+import argparse
+
+parser = argparse.ArgumentParser(
+    description=""" Choose a file to work""")
+
+
+parser.add_argument('--date', type=str, default='2000-01-01',
+			       help='Choose date. Format: yyyy-mm-dd')
+
+parser.add_argument("--previous", action="store_true", help="Choose previous days data")
+
+cmd_args = parser.parse_args()
+date = cmd_args.date
+previous = cmd_args.previous
+directory = "./data/"+date
+if previous:
+    directory = "./data/"+date+"/previous"
+df = pd.read_csv(directory+"/detrended_TEC.csv")
+latitude = df["Latitude"]
+longitude = df["Longitude"]
+det_TEC = df["vTEC"]
+
+xmin, ymin = min(longitude), min(latitude)
+xmax, ymax = max(longitude), max(latitude)
+res = 0.2
+Nx, Ny = (xmax-xmin)/res, (ymax-ymin)/res
+grid_x, grid_y = np.mgrid[xmin:xmax:Nx*1j, ymin:ymax:Ny*1j]
+
+fig =plt.figure()
+
+# Read and plot shape file of Mexico map
+sf = shp.Reader("map.shp")
+plot_map(sf)
+
+#Plot GLM trajectories
+
+data_16 = pd.read_csv(directory+"/GLM/GLM-16-data.csv", header=9)
+data_17 = pd.read_csv(directory+"/GLM/GLM-17-data.csv", header=9)
+
+plt.plot(data_16["longitude"], data_16["latitude"], "r.")
+plt.plot(data_17["longitude"], data_17["latitude"], "r.")
+
+
+# Plot event position
+
+event = pd.read_csv("GLM-database.csv")
+mask = event["Fecha"] == date
+event_lat = event["Latitud"][mask]
+event_lon = event["Longitud"][mask]
+event_ID = str(event["ID"][mask])
+#event_lat, event_lon =  22.5, -83.8
+plt.plot(event_lon, event_lat, "m*")
+plt.annotate(event_ID, (event_lon, event_lat), textcoords="offset points", color="w", fontsize="small",
[…]

### 2021-12-22 wavelet_power.py

@@ -1,0 +1,115 @@
+#We used a github repository to analyze the wavelets spectrum base on Torrence & Compo 1998
+# Available at https://github.com/chris-torrence/wavelets
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import argparse
+import sys
+sys.path.insert(0, "../wavelets/wave_python/") 
+from waveletFunctions import wavelet, wave_signif
+import matplotlib.colors as mcolors
+from midpoint import MidpointNormalize
+import glob
+from itertools import combinations
+parser = argparse.ArgumentParser(
+	description=""" Choose a file to work""")
+
+
+parser.add_argument('--date', type=str, default='2000-01-01',
+				   help='Choose date. Format: yyyy-mm-dd')
+
+parser.add_argument("--frequency", type=float, default=15,
+			  help="Sampling time (in seconds)")
+
+
+cmd_args = parser.parse_args()
+date = cmd_args.date
+dt = cmd_args.frequency/3600.
+
+directory ="./data/"+date
+outdir = "./TEC_power_spectrum/"+date
+pdirectory = "./data/"+date+"/previous"
+infile = glob.glob(directory+"/*.csv")[0]
+pinfile = glob.glob(pdirectory+"/*.csv")[0]
+df = pd.read_csv(infile)
+pdf = pd.read_csv(pinfile)
+Date, time, residuals = infile.split("_")
+start_time = float(time)
+stations = np.unique(df["Station"])
+levels = np.linspace(0,1,20)
+norm = MidpointNormalize(midpoint=0)
+for s in stations:
+    station_mask = df["Station"] ==s
+    PRNs = np.unique(df["PRN"][station_mask])
+    prn_pairs = list(combinations(PRNs, 2))
+    previous_PRNs = np.unique(pdf["PRN"][station_mask])
+    previous_PRN_pairs = list(combinations(previous_PRNs, 2))
+    for p,pp in zip(prn_pairs, previous_PRN_pairs):
+        plt.clf()
+        print("station: {}, PRNs: ({}, {})".format(s, p[0], p[1]))
+        prn_mask1 = df["PRN"] ==p[0]
+        prn_mask_p1 = pdf["PRN"] == pp[0]
+        prn_mask2 = df["PRN"] ==p[1]
[…]

### 2021-12-22 paper/arXiv/paper.tex
add .gitignore and add paper vital files
.gitignore will remove certain folder which contains too many files. With this, I found the vital paper files and updated them. Also reorganized files to make three versions of the paper: for elsevier (which I've been working with) and for MDPI (deadline at jan-31 2022) and arXiV.org (without format).

\documentclass[12pt]{article}

\title{Art\'iculo}
\author{Jorge Tarango-Yong}

\begin{document}
\maketitle

Cuerpo del texto aqu\'i
\end{document}

### 2021-12-22 paper/meteor-properties.tex
add .gitignore and add paper vital files
.gitignore will remove certain folder which contains too many files. With this, I found the vital paper files and updated them. Also reorganized files to make three versions of the paper: for elsevier (which I've been working with) and for MDPI (deadline at jan-31 2022) and arXiV.org (without format).

\subsection{Meteoroid masses}

Raul should write this section

### 2021-12-22 paper/methodology.tex
add .gitignore and add paper vital files
.gitignore will remove certain folder which contains too many files. With this, I found the vital paper files and updated them. Also reorganized files to make three versions of the paper: for elsevier (which I've been working with) and for MDPI (deadline at jan-31 2022) and arXiV.org (without format).

@@
 We selected a sample of meteors which were observed in mexican territory from the Geostationary Lightning Mapper \citep{GOODMAN:2013}.
-Orignally this project was designed to detect ligthning activity in earth's athmosphere, but has been proven that also can detect bolides entering the athmosphere.
+Originally this project was designed to detect lightning activity in earth's atmosphere, but has been proven that also can detect bolides entering the atmosphere.
 The detection comes from two satellites called GOES-16 and GOES-17 orbiting the earth in geostationary orbits.
@@
 For each event we can obtain the recorded trajectory of meteors and the corresponding light curve.
-THe GLM satellites have an umbral magnitude for detection of -14.
+The GLM satellites have an umbral magnitude for detection of -14.
 At this magnitude, a meteor is considered a bolide, and is expected to be at least decimeter-sized (in diameter) to reach such brightness.
 In the other hand, too bright meteors will saturate the detectors, and thus, lowering the quality of data.
-The result of this factors implies that the range in size of the objects in our sample varies in diameter between decimeter to meter size.
-%The sample was chosen following the next criteria:%selected in such way we chose the most probable objects to be detected by GPS sources in mexican territory and its surroundings:
-Each event also has assigned a confidence ratio, from low confidence to high, depending in how bright is the event itself and if the trajectory recorded by GLM ressembles (or not) a straight line.
-We chose only events whose confidence ratio is high, in oreder to be sure we chose the brightest objects, and thus, in the diameter size of bolides, we favored the meter-sized ones.
+The result of this factors implies that the range in size of the objects in our sample should vary in diameter between decimeter to meter size.
+Each event also has assigned a confidence ratio, from low confidence to high, depending in how bright is the event itself and if the trajectory recorded by GLM ressembles a straight line.
+We chose only events whose confidence ratio is high, in order to be sure we chose the brightest objects, and thus, in the diameter size of bolides, we favored the meter-sized ones.
 In table \ref{tab:table-meteors} we list the object we chose to do this work, order in chronological order.
-The columns of the table, from left to right are and ID to enumerate the meteors in the sample, the date and time each meteor was detected, the duration of the detection, their respective coordinates and the estimated height of the meteor over the ground at the time of the detection.
+%The columns of the table, from left to right are and ID to enumerate the meteors in the sample, the date and time each meteor was detected, the duration of the detection, their respective coordinates and the estimated height of the meteor over the ground at the time of the detection.
 GOES-16 and GOES-17 systematically detect the meteors at slightly different positions and at slightly different times, so we calculated the mean of the duration, latitude and longitude reported by both satellites for each event, and used the standard deviation as the uncertainties.
+In figure \ref{fig:meteors-map} we show the actual positions at which each bolide was detected.
 
 From table \ref{tab:table-meteors} is also clear that the duration of all the bolides detection last less than a second.
-This obsevation suggests that the bolides remain undetected by the GLM satellites until they get fragmented due to stagnation presure when they release a huge amount of energy and thus they become detectable.
-
-%From the light curves we can estimate the total radiated energy and then convert it to the total kinetic energy through a relation.
-With this energy we may estimate physical parameters with the cloud fragmentation model form wheeler et al.
-
-%\begin{itemize}
-%    \item The objects were detected inside mexican territory and its surroundings.
-%    \item The objects were detected by both satellites GOES 16 and GOES 17 (stereo)
-%    \item The detection has been assigned a high confidence ratio.
-%\end{itemize}
+This observation suggests that the bolides remain undetected by the GLM satellites until they get fragmented due to stagnation pressure when they release a huge amount of energy and thus they become detectable.
 
@@
 \hline
-ID & Date of event  & Start Time (UT)  & Duration (seconds) & Latitude (deg) & Longitude (deg)& Altitude (km) & Energy (kT )\\\hline
+ID & Date of event  & Start Time (UT)  & Duration (seconds) & Latitude (deg) & Longitude (deg)& Altitude (km) & Energy (kT)\\\hline
 GLM-00 & 2019-02-01 & 18:17:09 & $2.651\pm 0.4907$ & $22.45 \pm 0.071$ & $-83.50  \pm  0.424$ & 24           & 2.0978196 +/- 0.42361329      \\         
@@
   \centering
-  \includegraphics[width=\linewidth]{../meteors_map}
+  \includegraphics[width=\linewidth]{../figures/meteors_map}
   \caption{Positions of events from table \ref{tab:table-meteors} (blue) and table \ref{tab:table-meteors-2}.
-The events GLM-00/USG-08 actually correpond to the same bolide, but there are little discrepancies about the position where the bolide was detecte.
+The events GLM-00/USG-08 actually correpond to the same bolide, but there are little discrepancies about the position where the bolide was detected.
 The same applies for the events GLM-23/USG-10 and GLM-Ven/USG-09, which not appears in the map.}
@@
 
-By the other hand, we got another sample of 10 bolidesfrom US Goverment (USG) sensors from the Center for Near Earth Object Studies (CNEOS), publicly available at \url{https://cneos.jpl.nasa.gov/fireballs/}, where we may obtain directly data about bolides position, the date and time each bolide was detected, the energy released at fragmentation, the velocity and the height (the last two not availble for all bolides).
+By the other hand, we got another sample of 10 bolides from US Goverment (USG) sensors from the Center for Near Earth Object Studies (CNEOS), publicly available at \url{https://cneos.jpl.nasa.gov/fireballs/}, where we may obtain directly data about bolides position, the date and time each bolide was detected, the energy released at fragmentation, the velocity and the height (the last two not available for all bolides).
 As seen in table \ref{tab:table-meteors-2}, the time span is quite larger, and the released energy is generally larger.
-Both energy distributions are compared directly in figure \ref{fig:boxplot}.
 Some elements appear in both samples, since are bright enough to be detected regardless the project involved.
-In USG sample, the total energy of each meteor is obtained directly, but is not the case for the GLM sample.
-In appendix \ref{app:distance} and \ref{app:energy} we give details about how this total energy is obtained.
+In USG sample, the total energy of each meteor is already available from the database, but the energy for GLM bolides needs to be estimated.
+To do so, we estimated the distance between GOES satellites and the bolide and then followed \citet{Jenniskens:2018}, but we find some discrepancies in our measurements repect what is already reported for the same bolides in the USG database.
+(see the appendix \ref{app:distance} and \ref{app:energy}) for more details.
+We assumed that such discrepancy is due that GLM detectors underestimate the radiated energy by the bolides since before fragmentation the bolides remain undetectable by GLM sensors, and thus a fraction of the radiated energy is not accounted.
+To solve this, we estimated a correction factor using the bolides that appears in both GLM and USG samples (see figure \ref{fig:lin_fit} in appendix \ref{app:energies}).
+The energy distributions of USG and GLM samples are compared directly in figure \ref{fig:boxplot}.
 
@@
   \centering
-  \includegraphics[width=\linewidth]{./figures/energies_boxplot}
+  \includegraphics[width=\linewidth]{../figures/energies_boxplot}
   \caption{Comparison between released energies of bolides detected by the Geostationary Lightning Mapper and USG sensors.}
@@
 Seemala, publicly available at \url{https://seemala.blogspot.com/}, we computed the slant TEC (TEC) and vertical TEC (vTEC) for a several number of GPS satellites, each one identified with a PseudoRandom Noise code (PRN).
-For each station, we filtered all the PRN and data that lie in a window of 30 minutes around the time the event was reported.
+An example of such TEC calculations is shown in figure \ref{fig:TEC-curve-example}.
+The behavior of the TEC curve is due to many factors, including the earth's rotation, solar activity, etc.
+TID's and wave-like features are not as prominent and are difficult to see.
+So we focused in a time interval close to the moment the bolide was detected, and detrended our time series following \citet{Pradipta:2015} using a Golay-Savitzky filter of order 7.
+An example of the resulting detrending signal is shown in figure .
+The resulting time series are adequate for wavelet analysis.%For each station, we filtered all the PRN and data that lie in a window of 30 minutes around the time the event was reported.
 Then we estimated the signal trend using a Savitsky-Golay filter and substracting the original signal from the trend.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{../figures/abmf173-2019-06-22_page0}
+\label{fig:TEC-curve-example}
+\caption{Example of TEC curve obtained for GPS data for the bolide USG-09 from ABMF station.}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\linewidth]{}
+\end{figure}
 

### 2021-12-22 TEC_series.py

@@ -1,0 +1,52 @@
+import pandas as pd
+import argparse 
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+from statistics import mode
+parser = argparse.ArgumentParser(
+	 description=""" Choose a file to work""")
+
+
+parser.add_argument('--date', type=str, default='2000-01-01',
+				    help='Choose date. Format: yyyy-mm-dd')
+
+
+parser.add_argument("--filterhigh", type=float, default=30, 
+			  help="Filter the upper time interval of the TEC curve (in ninutes)")
+parser.add_argument("--filterlow", type=float, default=10, 
+			  help="Filter the lower time interval of the TEC curve (in ninutes)")
+parser.add_argument("--previous", action="store_true", help="Choose previous day data")
+cmd_args = parser.parse_args()
+date = cmd_args.date
+filter_high = cmd_args.filterhigh
+filter_low = cmd_args.filterlow
+directory = "./data/"+date
+infile = glob.glob(directory+"/*.csv")[0]
+Date, time, residual = infile.split("_")
+outdir = "./TEC_series/"+date
+previous = cmd_args.previous
+if previous:
+    infile = glob.glob(directory+"/previous/*.csv")[0]
+    outdir = "./TEC_series/"+date+"/previous"
+# ****************************** Read data file ************************************************
+
+csv_file = pd.read_csv(infile)
+station_array = np.unique(csv_file["Station"])
+time_hours = float(time)
+
+for s in station_array:
+    s_mask = csv_file["Station"] == s
+    prn_array = np.unique(csv_file["PRN"][s_mask])
+    for p in prn_array:
+        prn_mask = csv_file["PRN"] == p
+        frequency = round(mode(np.gradient(csv_file["Time"]*3600.)))
+        print("Station:{}, PRN:{}, Frequency:{}".format(s, p, frequency))
+        plt.plot(csv_file["Time"][prn_mask & s_mask], csv_file["vTEC"][prn_mask & s_mask])
+        plt.axvline(time_hours, ls="--", c="k")
+        plt.ylim(-0.3, 0.5)
+        plt.xlabel("UT (hours)")
+        plt.ylabel("vTEC (TECU)")
+        plt.title(s.upper()+"-PRN{}".format(p))
+        plt.savefig(outdir+"/{}-TEC_series_PRN_{}.pdf".format(s, p))
+        plt.clf()

### 2021-12-22 h_to_eq.py

@@ -1,0 +1,62 @@
+# This program is aimed to change from horizontal coordinates to equatorial coordinates
+# Horizontal coordinates of events are got from AMS data and equatorial coordinates would give us 
+# the place where the event could be seen at the zenith. If we get an event with two or more
+# witnesses we could find a parallax and thus estimate the altitude
+
+import numpy as np
+from scipy.optimize import fsolve
+import argparse
+
+
+def equations(q, Al, Az, Lat):
+    """
+    Set of equations to solve
+    """
+
+    x, y, z = q
+    k1 = np.sin(Az)*np.cos(Al)
+    k2 = np.cos(Az)*np.cos(Al)*np.sin(Lat) + np.sin(Al)*np.cos(Lat)
+    k3 = -np.cos(Az)*np.cos(Al)*np.cos(Lat) + np.sin(Al)*np.sin(Lat)
+    return (x*z - k1, y*z - k2, 1 - z**2 - k3**2) 
+
+# Input data
+
+parser = argparse.ArgumentParser(description= "Insert local coordinates of events")
+parser.add_argument("--latitude", type=float, help="Local latitude of observer (in degrees)")
+parser.add_argument("--longitude", type=float, help="Local longitude of observer (in degrees)")
+parser.add_argument("--azimuth", type=float, help="Azimuth of the event (in degrees)")
+parser.add_argument("--altitude", type=float, help="Altitude of the event (in degrees)")
+parser.add_argument("--h0", type=float, default=0, help="Initial guess of hour angle (in degrees)")
+parser.add_argument("-d0", type=float, help="Initial guess of declination (in degrees)")
+
+cmd_args = parser.parser_args()
+l_latitude = cmd_args.latitude
+azimuth = cmd_args.azimuth
+altitude = cmd_args.altitude
+h0 = cmd_args.h0
+delta0 = cmd_args.d0
+l_longitude = cmd_args.longitude
+
+# set initial guess
+
+x0 = np.sin(np.radians(h0))
+y0 = np.cos(np.radians(h0))
+z0 = np.cos(np.radians(delta0))
+
+# solve the system
+
+sol = fsolve(equations, (x0, y0, z0), args=(np.radians(altitude), np.radians(azimuth), np.radians(l_latitude)))
+
+# translate solution into (latitude, longitude)
+
[…]

### 2022-02-12 paper/appendix.tex
update of wavelet program
Now we can measure wavelet coherence spectrum. Need a .gitignore file
Up to date paper, journal readme and figures
Up to date:
- journal.org with work desription
- figures of paper
- paper draft for elsevier, MDPI and arXiv formats (I don't know yet in which jornal I will publish)
- Update README
- Updated python codes

@@
 
-Where $r$ is measured from the center of the earth, $ -180^\circ < phi <= 180^\circ$ represents the longitude; is positive at east of Greenwich meridian, and negative eastwards.
+Where $r$ is measured from the center of the earth, $ -180^\circ < \phi <= 180^\circ$ represents the longitude; is positive at east of Greenwich meridian, and negative eastwards.
 $\-90^\circ <= \theta <= 90^\circ$ represents the latitude and is positive at the north of equator and negative southwards.
@@
 
-Since $r_{GLM}$ and $r_{obj}$ are measured from the center of the arth ge find that:
+Since $r_{GLM}$ and $r_{obj}$ are measured from the center of the earth we find that:
 
@@
   \centering
-  \includegraphics[width=\linewidth]{../energy_fit}
+  \includegraphics[width=\linewidth]{../figures/energy_fit}
   \caption{Left: Linear fit between energies calculated from GLM data and energies reported by USG sensors.

### 2022-02-12 paper/arXiv/paper.tex
Up to date paper, journal readme and figures
Up to date:
- journal.org with work desription
- figures of paper
- paper draft for elsevier, MDPI and arXiv formats (I don't know yet in which jornal I will publish)
- Update README
- Updated python codes

@@
 
-\title{Art\'iculo}
-\author{Jorge Tarango-Yong}
+%% Loading LaTeX packages
+
+%% The amssymb package provides various useful mathematical symbols
+\usepackage{amssymb}
+\usepackage{latexsym}
+
+\usepackage{url}
+\usepackage{xcolor}
+\usepackage{multirow}
+\usepackage{hyperref}
+\usepackage{rotating}
+\usepackage{aas_macros}
+\usepackage{pdflscape}
+\usepackage{longtable}
+\usepackage{amssymb,amsmath,amsthm}
+\usepackage{siunitx}
+\usepackage[utf8]{inputenc}
+%\usepackage[spanish]{babel}
+\usepackage{etoolbox}
+\usepackage{fixltx2e}
+\usepackage{natbib}
+\usepackage[top=2.5cm, left=2.5cm, right=2.5cm, bottom=2.5cm]{geometry}
+
+\title{Ionospheric Disturbances in Mexican Territory Produced by Objects Entering the Atmosphere from Space}
+%\author{Jorge Tarango-Yong}
 
@@
 
-Cuerpo del texto aqu\'i
+%% Enter abstract here
+
+\begin{abstract}
+%%%
+Earth's ionosphere may be perturbed by different phenomena, such as %earthquakes, tsunamis or even events caused by humans, like nuclear explosions and rockets launched to space. 
+geomagnetic storms, solar flares with a common origin in our star, the Sun.
+In this work we will study the effects in the ionosphere caused by objects coming from outside the atmosphere (asteroids) inside Mexican territory.
+The Geostationary Lightning Mapper (GLM) started to record the passage of fireballs since 2017 and has recorded over 3000 events in the American continent.
+By the other hand, the Center for Near Earth Object Studies has data of 886 meteors detected around the globe by the United States Government sensors (USG).
+From these databases, we chose a sample of events and collected data and estimated meteor properties such as mass and energy released (if not available).
+Also we collected GPS data from UNAVCO network for the days each event was reported looking for vestiges of the meteors passage.
+With this work, we have observed that the vTEC signal
+ of the ionosphere observed and calculated with GPS data from stations on Earth, is affected by the passage of these objects producing ionospheric perturbations with a permanence of a twice hours in average.
+%%%%
+\end{abstract}
+
+% Begin entering content here
+
+\section{Introduction}
+\label{sec1}
+\input{../introduction}
+
+\section{Observational data}
+\label{sec:methodology}
+\input{../methodology}
+
+\section{Bolides physical parameters}
+\label{sec:bolides}
+\input{../meteor-properties}
+\section{Ionospheric background and wavelet power spectrum}
+\label{sec:vTEC-maps}
+
+\input{../vTEC-maps}
+
+\section{Discussion and conclusions}
+\label{sec:discussion}
+\input{../discussion}
+
+\section{Acknowledgments}
+The author Tarango-Yong thanks to DGAPA-UNAM by the posdoctoral fellowship, as well as the Laboratorio de Ciencias Geoespacilaes (LACIGE) from the Escuela Nacional de Estudios Superiores -- Morelia for the facilities provided to carry out the calculations of this paper.
+In addition, Guti\'errez-Zalapa wishes to thanks the
+Consejo Nacional de Ciencias y Tecnolog\'ia (CONACyT) for the support in carrying out this research, he also wishes to thanks the Posgrado en Ciencias de la Tierra from the Universidad Nacional Aut\'onoma de M\'exico.
+Finally, M.
+Rodr\'iguez-Mart\'inez also is grateful for the DGAPA PAPIIT/PAPIME projects (IN118119/PE103419) to the computing support.
+%\label{sec:acknowledgments}
+%\input{Acknowledgments}
+%% Bibliography
+%% Author year style
+\input{../appendix}  
+\bibliographystyle{mnras}
+%\biboptions{authoryear}
+\bibliography{../bibliography}
+
 \end{document}

### 2022-02-12 paper/discussion.tex
Up to date paper, journal readme and figures
Up to date:
- journal.org with work desription
- figures of paper
- paper draft for elsevier, MDPI and arXiv formats (I don't know yet in which jornal I will publish)
- Update README
- Updated python codes

We collected data for a sample of meteors which were detected around Mexican territory, or with some exceptions, meteoroids that released enough energy to have a good chance to get a vTEC disturbance with nearby GPS stations. We used data from the GLM, where the total energy was estimated from light curves, and USG sensors, where energy data is available. We used the few events which are present in both samples to re-calibrate the energy obtained for the GLM sample since in this few cases the energy estimated with the GLM data is systematically lower than the energy reported by USG sensors. Using the resulting energies, we estimated the bolides mass using a Fragment Cloud Model assuming a certain velocity range.

We have collected GPS data of nearby stations where the event was detected at the date each event occured, and one day before as comparison. We obtained the the vTEC series and we detrended them to remove the effects of Earth rotation and solar activity and make the wave-like features more evident. With these data, we used a wavelet transform using a Morlet wavelet to discover the frequencies at which vTEC perturbations may be produced, how intense these perturbations are and the time interval of these perturbations. If two different stations detect perturbations at the same frequencies that means that a vTEC perturbation was detected with such stations. We have observed that the distribution of wavelet coherent signal show us that the propagation of ionospheric disturbances have a time intervals of occurrence of a two hours from the spectrograms.

### 2022-02-12 paper/introduction.tex
Up to date paper, journal readme and figures
Up to date:
- journal.org with work desription
- figures of paper
- paper draft for elsevier, MDPI and arXiv formats (I don't know yet in which jornal I will publish)
- Update README
- Updated python codes

@@
 The Earth's magnetic field represents a final obstacle to the Solar Wind (SW) flux.
-When descelerated and defected by a non colisional shock wave in the flux direction, generates a cavity known as magnetosphere \citep{Blanco-Cano:2004}.
-Since the Earth is embedded in this SW flux, is known that under adequated physical conditions (e.g magnetic reconnection) may exist some coupling between the magnetosphere and the Earth's ionosphere \citep{Zolesi:2014, Cnossen:2014}.
+When decelerated and defected by a non colisional shock wave in the flux direction, generates a cavity known as magnetosphere \citep{Blanco-Cano:2004}.
+Since the Earth is embedded in this SW flux, is known that under adequate physical conditions (e.g magnetic reconnection) may exist some coupling between the magnetosphere and the Earth's ionosphere \citep{Zolesi:2014, Cnossen:2014}.
 
-The Sun plays an important role in the physical proccesses that occur in the terrestrial magnetosphere-ionosphere system.
+The Sun plays an important role in the physical processes that occur in the terrestrial magnetosphere-ionosphere system.
 When the SW interacts with the Earth's magnetosphere, particles may permeate the internal region via magnetic reconnection and penetrate to polar zones and generate boreal or austral auroras thus altering the system \citep{Vazquez:2016, Oka:2011}.
@@
 
-In this work we will show a similar analysis for a sample of meteoroids detected in mexican territory by different methods.
+In this work we will show a similar analysis for a sample of meteoroids detected in Mexican territory by different methods.
 The first subsample consists in objects detected by the Geostationary Lightning Mapper (GLM) whose sizes are estimated between a few decimeters to meters in diameter \citep{GOODMAN:2013, Jenniskens:2018, Rumpf:2019}.

### 2022-02-12 paper/meteor-properties.tex
Up to date paper, journal readme and figures
Up to date:
- journal.org with work desription
- figures of paper
- paper draft for elsevier, MDPI and arXiv formats (I don't know yet in which jornal I will publish)
- Update README
- Updated python codes

@@
-\subsection{Meteoroid masses}
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{../figures/Energy_vs_Mass-fireballs_en}
+    \caption{Bolides mass derived from Fragment Cloud Model.
+We used three assumptions about the bolide velocity: Minimum velocity $(\sim \SI{15}{km.s^{-1}})$, Medium velocity $(\sim \SI{16}{km.s^{-1}})$ and maximum velocity $(\sim \SI{18}{km.s^{-1}})$.
+This values are based on the available data of USG sample (see table \ref{tab:table-meteors-2})}
+    \label{fig:energy-mass}
+\end{figure}
 
-Raul should write this section
+Once the estimated the bolides energy, we are capable to estimate other bolides parameters, such as the mass.
+For that we used a Fragment Cloud Model \citep{Wheeler:2017}.
+To obtain the bolide mass, we must have previous knowledge of its velocity.
+Based on the few events of the USG sample where we could extract the velocity (see table \ref{tab:table-meteors-2}), we tried three models of bolides mass as a function of its releasing energy: the low velocity model, which assumes a velocity of $\sim \SI{15}{km.s{^-1}}$, medium velocty $v \sim \SI{16}{km.s{^-1}}$ and high velocity $v \sim \SI{18}{km.s{^-1}}$.
+The resultant masses can be seen in figure \ref{fig:energy-mass}.
+For the rest of the sample we need to assume that the bolides velocity is within this range or close enough in order to get a reasonable estimation of its mass.

### 2022-02-12 paper/methodology.tex
Up to date paper, journal readme and figures
Up to date:
- journal.org with work desription
- figures of paper
- paper draft for elsevier, MDPI and arXiv formats (I don't know yet in which jornal I will publish)
- Update README
- Updated python codes

@@
 We assumed that such discrepancy is due that GLM detectors underestimate the radiated energy by the bolides since before fragmentation the bolides remain undetectable by GLM sensors, and thus a fraction of the radiated energy is not accounted.
-To solve this, we estimated a correction factor using the bolides that appears in both GLM and USG samples (see figure \ref{fig:lin_fit} in appendix \ref{app:energies}).
+To solve this, we estimated a correction factor using the bolides that appears in both GLM and USG samples (see figure \ref{fig:lin_fit} in appendix \ref{app:energy}).
 The energy distributions of USG and GLM samples are compared directly in figure \ref{fig:boxplot}.
@@
 TID's and wave-like features are not as prominent and are difficult to see.
-So we focused in a time interval close to the moment the bolide was detected, and detrended our time series following \citet{Pradipta:2015} using a Golay-Savitzky filter of order 7.
-An example of the resulting detrending signal is shown in figure .
+So we focused in a time interval close to the moment the bolide was detected, and detrended our time series following \citet{Pradipta:2015} using a Savitzky-Golay filter of order 7 (future change to this phrase: to do a proper detrending, we should detrend data for a TEC series of a random day when no geomagnetic storm or unusual events happened, callibrate the Savitsky-Golay filter for using a proper order and use it for our data).
+An example of the resulting detrending signal is shown in figure \ref{fig:detrending-example}.
 The resulting time series are adequate for wavelet analysis.%For each station, we filtered all the PRN and data that lie in a window of 30 minutes around the time the event was reported.
@@
 \begin{figure}
-\includegraphics[width=\linewidth]{../figures/abmf173-2019-06-22_page0}
+\includegraphics[width=\linewidth]{../figures/cn05173-2019-06-22_page0}
 \label{fig:TEC-curve-example}
-\caption{Example of TEC curve obtained for GPS data for the bolide USG-09 from ABMF station.}
+\caption{Example of TEC curve obtained for GPS data for the bolide USG-09 from CN05 station.}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=\linewidth]{}
+\begin{tabular}{cc}
+\includegraphics[width=0.45\linewidth]{../figures/cn05-6-190}&
+\includegraphics[width=0.45\linewidth]{../figures/cn05-TEC_series_PRN_6}
+\end{tabular}
+\label{fig:detrending-example}
+\caption{Example of detrending process with USG-09 event.
+Left: Undetrended TEC series for station CN05 with PRN 6 (blue) versus Golay-Savitsky fit of order 7 (red dashed curve).
+Right: detrended curve resulting from substracting the Golay-Savitsky fit from the original signal.}
 \end{figure}
@@
 \subsection{Wavelet analysis}
+
+Wavelet analysis is a powerful tool for analyzing variations of power within a time series \citep{Torrence:1998}.
+For this task we used a Morlet wavelet $\Psi_0(\eta) = \pi^{-1/4}\exp(i\omega_0\eta)\exp(-\eta^2/2)$, where $\omega_0$ is a non-dimensional frequency, usually set to be 6 to satisfy the admissibity condition \citep{Farge:1992} and $\eta$ is a non-dimensional "time parameter".
+
+With this, the wavelet transform is given by:
+
+\begin{align}
+W_n(s) = \sum_{k=0}^{N-1}\hat{x}_k\hat{\Psi}^*\left(s\omega_k\right)\exp(i\omega_k n\delta t)
+\end{align}
+
+Where the $*$ indicates the complex conjugate, $k=0, 1, \ldots, N-1$ is the frequency index, s is the scale, $\delta t$ is the time spacing between data, $\omega_k$ is the angular frequency defined as:
+
+\begin{align}
+  \omega_k = \left\lbrace
+  \begin{array}{ccc}
+    \frac{2\pi k}{N\delta t} & : & k\leq \frac{N}{2} \\
+    -\frac{2\pi k}{N\delta t} & : & k > \frac{N}{2} 
+  \end{array}
+  \right.
+\end{align}
+And $\hat{\Psi}^*\left(s\omega_k\right)$ is the normalized wavelet function:
+
+\begin{align}
+  \hat{\Psi}^*\left(s\omega_k\right) = \left( \frac{2\pi s}{\delta t}\right)^{1/2} \hat{\Psi}_0\left(s\omega_k\right)
+\end{align}
+
+Since $\Psi(\eta)$ is a complex function, is expected that $W_n(s)$ is also complex.
+The transform can be divided into real and imaginary part.
+From the amplitude $|W_n(s)|$, from which we can obtain the power spectrum $|W_n(s)|^2$.
+
+If two stations show similar power spectrums, we can be confident enough to compute the wavelet coherence of both time series, defined as \citep{Yang:2011}:
+
+\begin{align}
+  R^2_{1,2}=\frac{|W_{12}|^2}{\left(|W_1|^2|W_2|^2\right)}
+\end{align}
+
+where the $W_{12}= W_1W^*_2$ is the cross wavelet spectrum, $W_i$ is the wavelet transform of the time series and $W^*_i$ is the complex conjugate of $W_i$.
+Regions with high coherence indicate the precence of a TID with frequency $1/T$, where $T$ is the period of the region with high frequency.
 

### 2022-02-12 paper/vTEC-maps.tex
Up to date paper, journal readme and figures
Up to date:
- journal.org with work desription
- figures of paper
- paper draft for elsevier, MDPI and arXiv formats (I don't know yet in which jornal I will publish)
- Update README
- Updated python codes

--- 2021-09-02 paper/vTEC-maps.tex
@@
-Ionospheric perturbations also can take place due to space weather and geomagnetic storms.
-So, in order to discard such events we investigated the space weather in the day each event occured.
-In figure (name) we present the geomagnetic \textit{Kp} index for some events.
-We discarded events whose Kp index is equal or grater than 4 in the day of the event or shortly before.
-Also we present in figure (name) the vTEC perturbation maps for the same events in a three day series, centered in the event date.
-The estimated meteor trajectory, obtained from the GLM data is presented in black, continous line, while the linear fit to the GOES-16 and GOES-17 data are presented with the red dashed line, and work as boudary errors.
+For each TEC series like figure \ref{fig:detrending-example} we computed $|W_n(s)|^2$ to find any wave-like features in any of the TEC series, where $s$ is the wavelet scale (somehow is the analogous to the wavelength).
+The presence of this features allow us to trace the TEC perturbations produced by the meteor.
+Examples are shown in figure \ref{fig:power-spectrums}.
+Due to the fact we are working with finite time series, edge effects become important at the beginning or the end of the time series, and when the wavelet scale is similar or greater than the time series length.
+The limit when these errors become important is called Cone of Influence (COI), the COI is shown as a white dashed line in figure \ref{fig:power-spectrums}.
+At a closer look of this spectra is clear that in some cases the wavelet spectra in the previous day is more intense than the event day.
+This happens because no TEC perturbations was really detected, but instead noise appears as wavelets.
+This is an indicator that the TEC perturbances either propagate to other location or it is too faint to be detectable.
+
+\begin{figure*}
+  \begin{tabular}{cc}
+  \includegraphics[width=0.5\linewidth]{../figures/cn05-PRN2-contour}  & \includegraphics[width=0.5\linewidth]{../figures/cn27-PRN2-contour}\\
+  \includegraphics[width=0.5\linewidth]{../figures/crlr-PRN2-contour}  & \includegraphics[width=0.5\linewidth]{../figures/crse-PRN2-contour}
+  \end{tabular}
+  \label{fig:power-spectrums}
+  \caption{Examples of power spectrums for event USG-09, PRN 2.
+Top left: Station CN05.
+Top Right: Station CN27.
+Bottom left: station CRLR.
+Bottom right: station CRSE.
+In each figure the left panel corresponds to the event day and the right panel corresponds to the previous day of the event.
+The white dashed lines correspond to the Cone of Influence, where all the wavelet spectrum below is subject to error.}
+\end{figure*}

### 2022-02-12 TEC_detrender.py

@@ -119,30 +119,23 @@ parser = argparse.ArgumentParser(
 
 parser.add_argument('--date', type=str, default='2000-01-01',
 				 help='Choose date. Format: yyyy-mm-dd')
-
-#parser.add_argument("--formato", type=str, default="pdf", choices=("pdf", "png", "jpg"), 
-#                                help="Choose output format")
 parser.add_argument("--starttime", type=str, default="00:00:00", help="Select the event start time")
-#parser.add_argument("--filterhigh", type=float, default=30, 
-#		       help="Filter the upper time interval of the TEC curve (in ninutes)")
-#parser.add_argument("--filterlow", type=float, default=10, 
-#		       help="Filter the lower time interval of the TEC curve (in ninutes)")
 parser.add_argument("--previous", action="store_true", help="Choose previous day data")
+parser.add_argument("--sets", type=str, help="Choose between sets of stations")
 
 cmd_args = parser.parse_args()
 date = cmd_args.date
-#formato = cmd_args.formato
 start_time = cmd_args.starttime
-#filter_high = cmd_args.filterhigh
-#filter_low = cmd_args.filterlow
 previous = cmd_args.previous
-filter_low = np.array([-10, -15, -20, -25, -30, -35, -40, -45, -50, -55, -60])
-filter_high = np.array([30, 40, 50, 60, 70, 80, 90, 100, 110, 120, 130])
+filter_low = np.array([-15, -35, -60])
+filter_high = np.array([40, 80, 130])
+stations_set = cmd_args.sets
+set_folder = "/set"+stations_set
 # ****************************** Read data file ************************************************
 
-directory = "./data/"+date
+directory = "./data/"+date+set_folder
 if previous:
-    directory = "./data/"+date+"/previous"
+    directory = "./data/"+date+set_folder+"/previous"
 files = glob.glob(directory+"/*.Cmn")
 
 # ******************************* Set final output lists ******************************************
@@ -155,92 +148,92 @@ final_lon = []
 final_vTEC = []
 window_size = []
 
-for fl, fh in zip(filter_low, filter_high): # Now the window size is variable
-    ws = fh-fl
-    
+# Use the longest window size to keep most frequencies inside COI
+#for fl, fh in zip(filter_low, filter_high): # Now the window size is variable
+fh = 130
+fl = -60
+ws = fh-fl
+for File in files:
+    f = open(File, "r")
+    for i in range(4):
+        f.readline()
 
-    for File in files:
[…]

### 2022-02-12 TEC_series.py

@@ -5,42 +5,50 @@ import matplotlib.pyplot as plt
 import glob
 from statistics import mode
 parser = argparse.ArgumentParser(
-	 description=""" Choose a file to work""")
+	   description=""" Choose a file to work""")
 
 
 parser.add_argument('--date', type=str, default='2000-01-01',
-				    help='Choose date. Format: yyyy-mm-dd')
+				      help='Choose date. Format: yyyy-mm-dd')
 
 
-parser.add_argument("--filterhigh", type=float, default=30, 
-			  help="Filter the upper time interval of the TEC curve (in ninutes)")
-parser.add_argument("--filterlow", type=float, default=10, 
-			  help="Filter the lower time interval of the TEC curve (in ninutes)")
+#parser.add_argument("--filterhigh", type=float, default=30, 
+#			    help="Filter the upper time interval of the TEC curve (in minutes)")
+#parser.add_argument("--filterlow", type=float, default=10, 
+#			    help="Filter the lower time interval of the TEC curve (in minutes)")
 parser.add_argument("--previous", action="store_true", help="Choose previous day data")
+parser.add_argument("--sets", type=str, help="Choose between sets of stations")
 cmd_args = parser.parse_args()
 date = cmd_args.date
-filter_high = cmd_args.filterhigh
-filter_low = cmd_args.filterlow
-directory = "./data/"+date
+#filter_high = cmd_args.filterhigh
+#filter_low = cmd_args.filterlow
+previous = cmd_args.previous
+stations_set = cmd_args.sets
+set_folder = "/set"+stations_set
+directory = "./data/"+date+set_folder
+outdir = "./TEC_series/"+date+set_folder
 infile = glob.glob(directory+"/*.csv")[0]
 Date, time, residual = infile.split("_")
-outdir = "./TEC_series/"+date
-previous = cmd_args.previous
 if previous:
     infile = glob.glob(directory+"/previous/*.csv")[0]
-    outdir = "./TEC_series/"+date+"/previous"
+    outdir = "./TEC_series/"+date+set_folder+"/previous"
 # ****************************** Read data file ************************************************
 
 csv_file = pd.read_csv(infile)
 station_array = np.unique(csv_file["Station"])
 time_hours = float(time)
+fh = 130
+fl = -60
+ws = fh-fl
 
+#for ws in window_size:
+#    win_mask = csv_file["WSize"] == ws
[…]

### 2022-02-12 wavelet_power.py

@@ -11,105 +11,111 @@ import matplotlib.colors as mcolors
 from midpoint import MidpointNormalize
 import glob
 from itertools import combinations
+from scipy.interpolate import interp1d
+
 parser = argparse.ArgumentParser(
-	description=""" Choose a file to work""")
+	  description=""" Choose a file to work""")
 
 
 parser.add_argument('--date', type=str, default='2000-01-01',
-				   help='Choose date. Format: yyyy-mm-dd')
+				     help='Choose date. Format: yyyy-mm-dd')
 
 parser.add_argument("--frequency", type=float, default=15,
-			  help="Sampling time (in seconds)")
+			    help="Sampling time (in seconds)")
 
-
+parser.add_argument("--sets", type=str, help="Choose between sets of stations")
 cmd_args = parser.parse_args()
 date = cmd_args.date
 dt = cmd_args.frequency/3600.
-
-directory ="./data/"+date
-outdir = "./TEC_power_spectrum/"+date
-pdirectory = "./data/"+date+"/previous"
+stations_set = cmd_args.sets
+set_folder = "/set"+stations_set
+directory ="./data/"+date+set_folder
+outdir = "./TEC_power_spectrum/"+date+set_folder
+pdirectory = "./data/"+date+set_folder+"/previous"
 infile = glob.glob(directory+"/*.csv")[0]
 pinfile = glob.glob(pdirectory+"/*.csv")[0]
 df = pd.read_csv(infile)
 pdf = pd.read_csv(pinfile)
-Date, time, residuals = infile.split("_")
+Date, time, residuals = infile.split("_") 
 start_time = float(time)
 stations = np.unique(df["Station"])
+#window_size = np.unique(df["WSize"])
 levels = np.linspace(0,1,20)
 norm = MidpointNormalize(midpoint=0)
-for s in stations:
-    station_mask = df["Station"] ==s
-    PRNs = np.unique(df["PRN"][station_mask])
-    prn_pairs = list(combinations(PRNs, 2))
-    previous_PRNs = np.unique(pdf["PRN"][station_mask])
-    previous_PRN_pairs = list(combinations(previous_PRNs, 2))
-    for p,pp in zip(prn_pairs, previous_PRN_pairs):
-        plt.clf()
-        print("station: {}, PRNs: ({}, {})".format(s, p[0], p[1]))
[…]

### 2022-02-12 wavelet_power2.py

@@ -1,0 +1,94 @@
+#We used a github repository to analyze the wavelets spectrum base on Torrence & Compo 1998
+# Available at https://github.com/chris-torrence/wavelets
+# This is a clone of wavelet_power.py with the exception we will get the wavelet spectrum for a single station and a single PRN
+# (No coherence spectrum) with a contour of the 95% confidence interval
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import argparse
+import sys
+sys.path.insert(0, "../wavelets/wave_python/") 
+from waveletFunctions import wavelet, wave_signif
+import matplotlib.colors as mcolors
+from midpoint import MidpointNormalize
+import glob
+from itertools import combinations
+from scipy.interpolate import interp1d
+
+parser = argparse.ArgumentParser(
+	  description=""" Choose a file to work""")
+
+
+parser.add_argument('--date', type=str, default='2000-01-01',
+				     help='Choose date. Format: yyyy-mm-dd')
+
+parser.add_argument("--frequency", type=float, default=15,
+			    help="Sampling time (in seconds)")
+
+parser.add_argument("--sets", type=str, help="Choose between sets of stations")
+parser.add_argument("--station", type=str, help="Choose station")
+parser.add_argument("--PRN", type=int, help="Choose PRN")
+cmd_args = parser.parse_args()
+date = cmd_args.date
+dt = cmd_args.frequency/3600.
+stations_set = cmd_args.sets
+set_folder = "/set"+stations_set
+station = cmd_args.station
+PRN = cmd_args.PRN
+directory ="./data/"+date+set_folder
+outdir = "./paper/figures"
+pdirectory = "./data/"+date+set_folder+"/previous"
+infile = glob.glob(directory+"/*.csv")[0]
+pinfile = glob.glob(pdirectory+"/*.csv")[0]
+df = pd.read_csv(infile)
+pdf = pd.read_csv(pinfile)
+Date, time, residuals = infile.split("_") 
+start_time = float(time)
+levels = 20
+norm = MidpointNormalize(midpoint=0)
+
+fh = 130
+fl = -60
+ws = fh-fl
+
[…]

### 2022-11-29 paper/appendix.tex
Update ELSEVIER paper (which compiles) to overleaf at 28-November-2022

--- 2021-08-02 paper/appendix.tex
@@
 
-% This is tha appendix, where we may insert detailed mathematical proccedures or other data which may be useful but also will make the main
-% text too large so this should be consulted only in case of neccesity
+% This is the appendix, where we may insert detailed mathematical procedures or other data which may be useful but also will make the main
+% text too large so this should be consulted only in case of necessity
+\section{Bolide velocity components}
+\label{app:velocity}
+The USG database from JPL is a great source of information about the brightest bolides that have entered the atmosphere since 1988.
+However, the velocity components $(v_x, v_y, v_z)$ are displayed in a geocentric Earth-fixed reference frame explained as follows:
 
-\section{Estimation of distances to meteors}
+$v_x$ lies in the Earth's equatorial plane, parallel to the equator and points towards the prime meridian, $v_z$ is parallel to the earth's rotational axis and points towards the north celestial pole and $v_y$ completes the right-handed reference system.
+Figure  shows graphically these velocity components.
 
-The distance between the GOES satellite and the meteor, neccesary to estimate the radiated energy is calculated as follows:
+In the other hand, it might be useful and more intuitive to describe the velocity components in terms of the local reference system composed by $(v_{lon}, v_{lat}, v_h)$, where $v_{lon}$ is the velocity component parallel to the equatorial plane, positive towards east, $v_{lat}$ is parallel to the polar plane, positive to north, and $v_h$ is the radial component pointing towards the center of Earth.
+Figure \ref{fig:ref_velocity} sketches both reference systems simultaneously.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{../figures/meteor_velocity_references.pdf}
+    \caption{Velocity components of bolide.
+The geocentric Earth fixed reference system is sketched in black and the local spherical reference system in blue.
+The components parallel to the equatorial plane are not shown since are perpendicular to the plane of the page.}
+    \label{fig:ref_velocity}
+\end{figure}
+
+The transformation between both reference systems in the north-west hemisphere is given as follows:
 
 \begin{align}
-  R = \left|\vec{r}_{GLM} - \vec{r}_{obj} \right|
+v_{lon} &= v_x \label{eq:vlon}\\
+v_{lat} &= v_z\cos{L} - v_y\sin{L} \label{eq:vlat}\\
+v_h     &= v_y\cos{L} + v_z\sin{L} \label{eq:vh}
 \end{align}
 
-where $\vec{r}_{GLM}$ is the vector position of the GLM satellite and $\vec{r}_{obj}$ is the vector position of the meteor.
-
-In cartesian coordinates, the distance $R$ is given by:
+Where $L$ is the bolide latitude.
+With this information, we can estimate the velocity tangential to the Earth's surface as $v_{tan} = \left((v_{lon})^2 + (v_{lat})^2\right)^{1/2}$ and finally the trajectory angle respect to the normal as $\tan\theta = \frac{v_{tan}}{v_h}$.
+Using equations (\ref{eq:vlon}) to (\ref{eq:vh}) we obtain the following:
 
 \begin{align}
-  R &= \left((x_{GLM}-x_{obj})^2 + (y_{GLM}-y_{obj})^2 + (z_{GLM}-z_{obj})^2\right)^{1/2} \label{eq:R}\\
+    v_{tan} &= \left((v_x)^2 + (v_z\cos{L}-v_y\sin{L})^2\right)^{1/2} \\
+    \tan\theta &= \frac{\left((v_x)^2 + (v_z\cos{L}-v_y\sin{L})^2\right)^{1/2}}{v_y\cos{L} + v_z\sin{L}}  \label{eq:meteor-angle}
 \end{align}
 
-The transformation to spherical coordinates is given by:
+Substituting the corresponding data from table \ref{tab:Meteor-parameters} into equation (\ref{eq:meteor-angle}) we find that that the trajectory angle of the meteor respect to the normal is $\theta \approx 64.4^{\circ}$
+
+\section{Detrending test signal}
+\label{app:test-signal}
+Figure \ref{fig:test-signal} shows the form of this test time series, described mathematically as follows \citep{Boris:2020}:
+ \begin{align}
+     I_R(t) &= A\cdot \exp\left[-0.5\left(\frac{t-t_m}{d_t}\right)^2\right]\cdot \sum^{i}_{n}\sin\left(\omega_i t\right) \label{eq:ref-signal}\\
+     Trend(t) &= B\cdot \left|t - t_0\right|^3 \label{eq:trend}
+ \end{align}
+
+ \begin{figure*}
+     \centering
+     \includegraphics[width=\linewidth]{../figures/test_signal}
+     \caption{Initial setup for testing detrending method. a) Reference signal given by equation (\ref{eq:ref-signal}). b) Superposition between a) and the trend given by (\ref{eq:trend})}.
+     \label{fig:test-signal}
+ \end{figure*}
+
+ Where equation (\ref{eq:ref-signal}) is the signal we want to detrend and equation (\ref{eq:trend}) is the trend we want to remove.
+$A$ is the amplitude of the signal, set as $\SI{0.2}{TECU}$, $t_m$ is a parameter which determines the position of the envelope maximum, set as $\SI{250}{min}$, which is the half of the array length, $d_t$ is the half width of the envelope, set as $\SI{50}{min}$ and $\omega_i$ are the frequencies of three harmonics with periods of $\SI{20}{min}$, $\SI{40}{min}$ and $\SI{60}{min}$.
+In the other hand, $B$ is the amplitude of the trend, set as $\SI{3.84e-6}{TECU.min^{-1}}$ and $t_0=\SI{250}{min}$ determines position of the minimum of the trend.
+
+ For the detrending we used a Savitsky-Golay filter of order 3, this is lowest order filter which at the same time avoids too much oscillations and allows to the fit (and its derivative) to be smooth.
+The other remaining parameter is the window size, i.e.
+the number of convolution coefficients neccesary for the regression, which must be an odd integer, greater than the order of the polynomial order and lower than the array size.
+Then, we estimated the detrended signal using all possible values for the window size and estimated the residuals as follows:
 
  \begin{align}
-  x = r\cos\phi\cos\theta \label{eq:xtoR}\\
-  y = r\sin\phi\cos\theta \label{eq:ytoR}\\
-  z = r\sin\theta \label{eq:ztoR}
+     residuals = \sum_{i}^N \left(d_i - s_i\right)^2
  \end{align}
+ Where $N$ is the array size, $d_i$ is the value of the detrended signal at the time $t_i$ and $s_i$ is the reference signal at the same time.
+In figure  we show the behavior of residuals as a function of the window size relative to the array size.
+We noted that the residuals behavior is almost insensitive to the window size when its size is lower than than 60\% of the array size, when the errors start to grow exponentially, but going to more detail, we found that using a window size of about $1/4$ of the array length, such errors are minimal.
+The detrended test curve is shown in figure \ref{fig:detrended-test}, compared with the original signal, as well as the substraction of both curves.
+In an ideal situation it should be zero for all times, but even in this case the amplitude of the envelope is about the tenth part of the amplitude of the envelope of the signal.
 
-Where $r$ is measured from the center of the earth, $ -180^\circ < phi <= 180^\circ$ represents the longitude; is positive at east of Greenwich meridian, and negative eastwards.
-$\-90^\circ <= \theta <= 90^\circ$ represents the latitude and is positive at the north of equator and negative southwards.
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{../figures/IRvsDetrended}
+\label{fig:detrended-test}
+\caption{Left: Original test signal (blue continuous curve) compared with the result of detrending the superposition of the test signal with the test trend (figure \ref{fig:test-signal}b), which is the orange dashed curve.
+Right: Substraction of both curves of left side.
+The amplitude of the envelope of this residuals qualitatively is about tenth percent of the amplitude of the original signal.}
+\end{figure*}
 
-Substituting the transform (\ref{eq:xtoR} - \ref{eq:ztoR}) into (\ref{eq:R}), using elemental trigonometry and considering both GLM satellites lie into the equator ($\theta_{GLM}=0$) we get:
+\section{Coordinates transformation}
+\label{app:azimuth}
+
+In order to change coordinates form geocentric to local coordinates for the bolide position, we may assume the flat earth approximation since the GPS stations we used in our work are located near the place the bolide was detected, and the apparent curvature of Earth at the bolide height is almost zero.
+With this in mind, in figure \ref{fig:flat_earth_aproximation} we show the flat Earth approximation in order to transform the geocentric coordinates of the bolide (latitude and longitude) to their corresponding local coordinates azimuth and elevation.
+With the aid of this image, we derive the following equations:
 
 \begin{align}
-  R^2 &= r_{GLM}^2 + r_{obj}^2 - 2r_{GLM}r_{obj}f(\theta_{obj}, \phi_{obj}, \phi_{GLM}) \label{eq:R2}\\
-  \mathrm{where:} & f(\theta_{obj}, \phi_{obj}, \phi_{GLM}) = \cos\theta_{obj}\cos\left(\phi_{GLM}-\phi_{obj}\right)
+    \tan{Az} &= \frac{\Delta \lambda}{\Delta L} \\
+    \tan{Ele} &= \frac{h}{r}
 \end{align}
+Where $r = R_E\left((\Delta L)^2 + (\delta\lambda)^2\right)^{1/2}$ and $(\delta L, \delta\lambda)$ are the separation in latitude and longitude of the bolide from the GPS station, respectively.
+Azimuth is measured from the north counterclockwise and elevation is measured from the Earth's horizon to zenith, in such way azimuth goes from $0^\circ$ to $360^\circ$ and elevation from $0^\circ$ to $90^\circ$.
 
-Since $r_{GLM}$ and $r_{obj}$ are measured from the center of the arth ge find that:
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{../figures/coord_transform_drawing.pdf}
+    \caption{Sketch of flat Earth approximation for transforming the fireball position from geocentric coordinates to local coordinates.
+From this picture we can derive equations () to () to estimate the local azimuth and elevation of the bolide at the GPS station position.
+$\vec{R}$ is the vector pointing to the bolide position with origin in the GPS station.
+$r$ is the projection of $\vec{R}$ in the Earth's plane.
+$L_s$ and $L_B$ are the latitudes of the station and the bolide, respectively, while $\lambda_s$ and $\lambda_B$ their longitudes, $h$ is the bolide height and $R_E$ the radius of Earth.}
+    \label{fig:flat_earth_aproximation}
+\end{figure}
+%To do such transformation we do the following process \citep{Kroger:1996}:
 
-\begin{align}
-  r_{GLM} &= r_{earth} + h_{GLM} \label{eq:rg}\\
-  r_{obj} &= r_{earth} + h_{obj} \label{eq:ro}
-\end{align}
+%The transformation from celestial coordinates to local coordinates are given by:
 
-Substituting (\ref{eq:rg}, \ref{eq:ro}) into \ref{eq:R2} and considering that $h_{obj} \ll h_{GLM}$ we get:
+%\begin{align}
+%    \sin(E) = \sin{\delta}\sin{L} + \cos{L}\cos{H}\cos\delta \label{eq:elevation}\\
+%    \cos{A} = \frac{\sin{\delta}-\sin{E}\sin{L}}{\cos{E}\cos{L}} \label{eq:cos-A}
+%\end{align}
+%Where $E$ is the elevation of the object, $\delta$ is the declination, $H$ is the hour angle, $A = Az$ when $\sin{H} <0$, otherwise $Az = 360-A$ where $Az$ is the Azimuth.
+Finally $L$ is the latitude of the observer (i.e, the GPS station).
+%If there were an observer located in the same coordinates than the fragmentation of the bolide took place, then this hypothetical observer should have seen the bolide at zenith.
+The celestial coordinates of the bolide at this location are zero hour angle and declination equal to object reported latitude.
+The hour angle is relative to the time and place the object is being observed, and we need the hour angle of the object from the place is observed (the GPS station).
+To do this we need estimate the hour angle of the object from the station perspective, and the hour angle from the "zenith perspective":
+%\begin{align}
+%    H = LST_s - RA\label{eq:LST}\\
+%    0 = LST_z - RA \label{eq:z-LST}
+%\end{align}
+%Where $LST_s$ is the Local Sidereal Time from the station perspective, and $LST_z$ is the same but from the "zenith perspective", and $RA$ is the right ascension, which is the same in both perspectives.
+We can also write the Local sidereal time in terms of the Greenwich local time as follows:%If we sum the last equations we find that:
+%\begin{align}
+%    LST = GST + Lon_{obs} -RA \label{eq:LST-GST}
+%\end{align}
 
-\begin{align}
-  R^2 = 2r_{earth}^2\left(1-f(\theta_{obj}, \phi_{obj}, \phi_{GLM})\right) +2r_{earth}h_{GLM}\left(1-f(\theta_{obj}, \phi_{obj}, \phi_{GLM})\right) + h_{GLM}^2 - 2h_{GLM}h_{obj}f(\theta_{obj}, \phi_{obj}, \phi_{GLM})
-\end{align}
+%Where $GST$ is the Greenwich Local time and $Lon_obs$ is the observer longitude. Substituting (\ref{eq:LST-GST}) into (\ref{eq:LST}) and (\ref{eq:z-LST}) and sum the resulting equations we find that:
 
-\section{Useful databases}
+%\begin{align}
+%    H = Lon_s - Lon_z \label{eq:H-lon}
+%\end{align}
+
+%Where $Lon_s$ is the station longitude and $Lon_z$ is the longitude of the bolide.
+Substituting \ref{eq:H-lon} into (\ref{eq:elevation}) and (\ref{eq:cos-A}) we can find the Azimuth and elevation in terms of the local latitude and longitude and the object's reported latitude and longitude:
+
+%\begin{align}
+%    \sin(E) = \sin{\delta}\sin{L} + \cos{L}\cos(Lon_s - Lon_z) \label{eq:elevation_f}\\
+%    \cos{A} = \frac{\sin{\delta}-\sin{E}\sin{L}}{\cos{E}\cos{L}} \label{eq:cos-A_f}
+%\end{align}
+
+%Examples of bolides trajectories against satellites trajectories are found in figures \ref{fig:boav-trajectory} - \ref{fig:ttsf-trajectory} for stations BOAV, CN00, CN04, CN05, KOUR and TTSF:
+
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=\linewidth]{../figures/azimuth-elevation-map-boav-polar}
+%    \caption{Satellites trajectory from BOAV station perspective in colors in polar coordinates, where the azimuth is represented in the polar axis and the elevation in the radial axis, being the zenith at the center of the graph and the horizon at the edge.
+The estimated meteor trajectory is shown in a black dashed line and GLM data as magenta dots.
+Practically for all stations, the satellite with PRN 13 is the closest to the bolide trajectory.
+The dashed curves represent the propagation radius of TIDs after 1 hour (red) and two hours (blue) in the azimuth-elevation space assuming TIDs propagate at \SI{362}{km.s^{-1}}, the same as the reported high frequency TIDs from Chelyabinsk meteor \citep{Yang:2014}.}
+%    \label{fig:boav-trajectory}
+%\end{figure}
+
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=\linewidth]{../figures/azimuth-elevation-map-cn00-polar}
+%    \caption{Same as figure \ref{fig:boav-trajectory} but using station CN00.}
+%    \label{fig:cn00-trajectory}
+%\end{figure}\begin{figure}
+%    \centering
+%    \includegraphics[width=\linewidth]{../figures/azimuth-elevation-map-cn04-polar}
+%    \caption{Same as figure \ref{fig:boav-trajectory} but using station CN04.}
+%    \label{fig:cn04-trajectory}
+%\end{figure}\begin{figure}
+%    \centering
+%    \includegraphics[width=\linewidth]{../figures/azimuth-elevation-map-cn05-polar}
+%    \caption{Same as figure \ref{fig:boav-trajectory} but using station CN05.}
+%    \label{fig:cn05-trajectory}
+%\end{figure}
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=\linewidth]{../figures/azimuth-elevation-map-kour-polar}
+%    \caption{Same as figure \ref{fig:boav-trajectory} but using station KOUR.}
+%    \label{fig:kour-trajectory}
+%\end{figure}
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=\linewidth]{../figures/azimuth-elevation-map-ttsf-polar}
+%    \caption{Same as figure \ref{fig:boav-trajectory} but using station TTSF.}
+%    \label{fig:ttsf-trajectory}
+%\end{figure}
+
+\section{UNAVCO Acknowledgements and stations list}
+
+In table  we will enlist the stations from we collected data for our work.
+This material is based on services provided by the GAGE Facility, operated by UNAVCO, Inc., with support from the National Science Foundation and the National Aeronautics and Space Administration under NSF Cooperative Agreement EAR-1724794, we are deeply grateful with all the people that was involved and whose work we are citing here.
+
+\clearpage
+\onecolumn
+\footnotesize
+\begin{landscape}
+\begin{table*}
+    \centering
+       \caption{List of GPS stations used for this work.}
+      \label{tab:table-stations}
+    \begin{tabular}{lllp{8cm}}
+
+    %  \endfirsthead
+    %  \endhead
+    \toprule
+    Station name & Latitude (deg) & Longitude (deg) & Citation \\
+    AIRS & 16.74 & -62.21 & \url{https://doi.org/10.7283/T53B5XGJ}\\
+    BARA & 18.21 & -71.09 & None available                       \\
+    BOAV & 2.85  & -60.70 & None available \\
+    CN00 & 17.67 & -61.79 & \url{https://doi.org/10.7283/T5FN14GQ} \\
+    CN04 & 14.02 & -60.97 &  \url{https://doi.org/10.7283/T5BP0124} \\
+    CN05 & 18.56 & -68.35 & \url{https://doi.org/10.7283/T5VQ30ZH} \\
+    CN19 & 12.61 & -70.04 & \url{https://doi.org/10.7283/T5HD7SZB}\\
+    CN27 & 19.67 & -69.93 & \url{https://doi.org/10.7283/T5JD4V2P} \\
+    CN40 & 12.18 & -68.96 & \url{https://doi.org/10.7283/T5BV7DWT} \\
+    CRLR & 18.41 & -68.93 & \url{https://doi.org/10.7283/T5FN14JM} \\
+    CRSE & 18.76 & -69.04 & None available \\
+    GERD & 16.80 & -62.19 & \url{https://doi.org/10.7283/T5TT4PBT} \\
+    GRE1 & 12.22 & -61.64 & \url{https://doi.org/10.7283/T5BC3WZ5} \\
+    JME2 & 18.23 & -72.54 &  \url{https://doi.org/10.7283/T5KW5D38}\\
+    KOUG & 5.10  & -52.64 & None available \\
+    KOUR & 5.25  & -52.81 & None available \\
+    LVEG & 19.22 & -70.53 & \url{https://doi.org/10.7283/T5CZ35GC}\\
+    NWBL & 16.82 & -62.20 & \url{https://doi.org/10.7283/T5ZK5F13} \\
+    OLVN & 16.75 & -62.23 & \url{https://doi.org/10.7283/T5Q23XMD} \\
+    RCHY & 16.70 & -62.15 & \url{https://doi.org/10.7283/T5707ZSJ} \\
+    RDAZ & 18.45 & -70.72 & None available \\
+    RDF2 & 19.45 & -70.68 & None available \\
+    RDHI & 18.60 & -68.72 & None available \\
+    RDLT & 19.31 & -69.55 & \url{https://doi.org/10.7283/T5J101GT} \\
+    RDMA & 19.54 & -71.08 & \url{https://doi.org/10.7283/T50863NM} \\
+    RDMC & 19.85 & -71.64 & None available \\
+    RDMS & 18.98 & -69.04 & \url{https://doi.org/10.7283/T5DV1HPQ} \\
+    RDNE & 18.50 & -71.42 & None available \\
+    RDON & 16.93 & -62.35 & \url{https://doi.org/10.7283/T5W37TFB} \\
+    RDSD & 18.46 & -69.91 & \url{https://doi.org/10.7283/T5CZ3594} \\
+    RDSF & 19.29 & -70.25 & None available \\
+    RDSJ & 18.82 & -71.23 & \url{https://doi.org/10.7283/T59W0CTW} \\
+    SPED & 18.46 & -69.31 & \url{https://doi.org/10.7283/T5HQ3X75} \\
+    SROD & 19.48 & -71.34 & \url{https://doi.org/10.7283/T5862DSD} \\
+    TGDR & 18.21 & -71.10 & \url{https://doi.org/10.7283/T5222S3R} \\
+    TRNT & 16.76 & -62.16 & \url{https://doi.org/10.7283/T5K935W2} \\
+    TTSF & 10.28 & -61.47 & \url{https://doi.org/10.7283/T5JQ0ZCJ} \\
+    TTUW & 10.64 & -61.40 & \url{https://doi.org/10.7283/T5TQ5ZTR} \\
+    \bottomrule
+\end{tabular}     
+\end{table*}
+  \end{landscape}
+  \clearpage
+  \twocolumn

### 2022-11-29 paper/discussion.tex
Update ELSEVIER paper (which compiles) to overleaf at 28-November-2022

@@
-We collected data for a sample of meteors which were detected around Mexican territory, or with some exceptions, meteoroids that released enough energy to have a good chance to get a vTEC disturbance with nearby GPS stations.
-We used data from the GLM, where the total energy was estimated from light curves, and USG sensors, where energy data is available.
-We used the few events which are present in both samples to re-calibrate the energy obtained for the GLM sample since in this few cases the energy estimated with the GLM data is systematically lower than the energy reported by USG sensors.
-Using the resulting energies, we estimated the bolides mass using a Fragment Cloud Model assuming a certain velocity range.
-
-We have collected GPS data of nearby stations where the event was detected at the date each event occured, and one day before as comparison.
-We obtained the the vTEC series and we detrended them to remove the effects of Earth rotation and solar activity and make the wave-like features more evident.
-With these data, we used a wavelet transform using a Morlet wavelet to discover the frequencies at which vTEC perturbations may be produced, how intense these perturbations are and the time interval of these perturbations.
-If two different stations detect perturbations at the same frequencies that means that a vTEC perturbation was detected with such stations.
-We have observed that the distribution of wavelet coherent signal show us that the propagation of ionospheric disturbances have a time intervals of occurrence of a two hours from the spectrograms.
+We collected data for a sample of GPS station from UNAVCO network around the Caribbean bolide was detected in the same day and next day.
+We used data from the GLM, where the total energy was estimated from light curves, and USG sensors, where energy data is available to spot the bolide position and estimate the trajectory at the fragmentation instant.
+For GPS data, we adapted the method from \citet{Pradipta:2015} for detrending all the resultant TEC curves to remove the effects of Earth rotation and solar activity and make the wave-like features more evident.
+In order to discriminate which stations made a detection from the ones who didn't, we compared the detrended time series with a Morlet wavelet.
+We discarded other sources of GWs such like slow solar wind reached by fast wind, fluctuations in solar X-rays, coronal mass ejections and solar terminator effects.
+We found TIDs features in sTEC series from stations CN04, CN40, GRE1, TTSF, TTUW, BOAV, KOUG and KOUR stations with at least one satellite.

### 2022-11-29 paper/introduction.tex
Update ELSEVIER paper (which compiles) to overleaf at 28-November-2022

@@
-The Earth's magnetic field represents a final obstacle to the Solar Wind (SW) flux.
-When decelerated and defected by a non colisional shock wave in the flux direction, generates a cavity known as magnetosphere \citep{Blanco-Cano:2004}.
-Since the Earth is embedded in this SW flux, is known that under adequate physical conditions (e.g magnetic reconnection) may exist some coupling between the magnetosphere and the Earth's ionosphere \citep{Zolesi:2014, Cnossen:2014}.
+Bolides impact the Earth every day, from the smallest ($d<\SI{0.5}{m}$), which are destroyed when entering the atmosphere to the biggest and most rare events, where an asteroid with a diameter $d>\SI{100}{m}$ is almost unaffected by the atmosphere and is technically unable to slow them down.
+If their diameter is greater than \SI{1}{km} the impact can be considered a global catastrophe \citep{Dudorov:2020}.
+Some famous modern cases are the Tunguska event 1n 1908 \citep{Wheeler:2019} and the Chelyabinsk event \citep{Yang:2014} in 2013.
 
-The Sun plays an important role in the physical processes that occur in the terrestrial magnetosphere-ionosphere system.
-When the SW interacts with the Earth's magnetosphere, particles may permeate the internal region via magnetic reconnection and penetrate to polar zones and generate boreal or austral auroras thus altering the system \citep{Vazquez:2016, Oka:2011}.
-By the other hand, the Extreme Ultraviolet Radiation (EUV) and X-rays coming from the Sun may interact with the neutral atmoshere via photoionization \citep{Vlasov:2010}.
-However, in both cases the final result is that the ionosphere's free electrons population is altered.
+Such events have been recently recorded in certain databases, such as the Center for Near Earth Objects Studies (CNEOS), Jet Propulsion Laboratory (JPL) and the Geostationary Lightning Mapper (GLM), publicly available at \url{https://cneos.jpl.nasa.gov/fireballs/} and \url{https://neo-bolide.ndc.nasa.gov/#/}, respectively.
 
-Some Ionospheric Perturbations (IP) become relevant due to their spatial and temporal scale in the Space Weather scenario.
-At intermediate latitudes, the most common in the ionosphere are known as Traveling Ionospheric Disturbances (TIDs).
-Typically they divide into two groups: a) large scale TIDs, associated with geomagnetic storms with sizes of \SI{\sim 2000}{km}, periods of \SI{\sim 1}{h} and velocities of \SI{\sim 700}{km.s^{-1}}, and b) Medium-scale TIDs, which are not fully associated with geomagnetic storms, present sizes of \SI{\sim 100}{km}, periods from 10 minutes to 1 hour and velocities between \SI{50}{km.s^{-1}} and \SI{1e2}{km.s^{-1}} \citep{Helmboldt:2012}.
-Diverse methods have benn used to study TIDs, such as incoherent dispersion radars, high frequency Doppler emmisors, data from Global Positioning System (GPS) stations or even radiotelescopes like the VLA or the Mexican Array Radio Telescope (MEXART) \citep{Chilcote:2015, Rodriguez:2014}.
-
-On the other side, the Earth's ionosphere may be affected or modified by other proccesses, particularly there are studies that show how the Vetical Total Electron Content (vTEC) due to shock waves generated for rockets launched to space \citep{Lin:2014}.
-Similar proccesses modify the Earth's ionosphere due to objects entering the athmosphere from space, such as meteoroids like the one which fell on Chelyabinsk at 2013 \citep{Yang:2014}.
-Previously, the ionospheric perturbations produced by this object were studied using two independent methods: a) detecting vTEC pertubations using GPS station near the impact location.
-And b) a wavelets analysis for detection of ...
-
-In 2020 a meteoroid passed in mexican territory through mexican territory, which also was studied \citep{Sergeeva:2020}.
-The meteoroid was recorded with outdoor cameras in different locations.
-The trajectory could be estimated, as well as other physical parameters.
-
-In this work we will show a similar analysis for a sample of meteoroids detected in Mexican territory by different methods.
-The first subsample consists in objects detected by the Geostationary Lightning Mapper (GLM) whose sizes are estimated between a few decimeters to meters in diameter \citep{GOODMAN:2013, Jenniskens:2018, Rumpf:2019}.
-The second subsample will consist in objects detected by ocular witnesses from the American Meteor Society and as comparisson we will include the morelian meteoroid reported in \citet{Sergeeva:2020} and the Chelyabinsk event \citet{Yang:2014}.
-The paper is arranged in the following way: \S \ref{sec:methodology} describes the samples of meteoroids as well of the properties that can be obtained from direct observations.
-Also describes the GPS data corresponding to the dates and locations where each object was located.
-\S \ref{sec:bolides} shows physical parameters of meteoroids obtained from the observed heights and energies.
-Finally, section \S \ref{sec:vTEC-maps} shows the vTEC maps and scintillation indices obtained from GPS observations.
+We picked our interest in one certain event, that we nicknamed ``the Caribbean Meteoroid'', because this meteoroid is the most energetic which appear in both databases and thus is an interesting case for studying the potential Traveling Ionospheric Disturbances (TIDs) that could be produced.
+To do so, we collected RINEX data from nearby GPS stations from the UNAVCO network (also publicly available) and developed a method to detrend the resultant TEC series and estimate the TIDs propagation speed ...
+(The introduction also needs to be polished after getting the main results)

### 2022-11-29 paper/meteor-properties.tex
Update ELSEVIER paper (which compiles) to overleaf at 28-November-2022

@@
-\begin{figure}
+\begin{table}
     \centering
-    \includegraphics[width=\linewidth]{../figures/Energy_vs_Mass-fireballs_en}
-    \caption{Bolides mass derived from Fragment Cloud Model.
-We used three assumptions about the bolide velocity: Minimum velocity $(\sim \SI{15}{km.s^{-1}})$, Medium velocity $(\sim \SI{16}{km.s^{-1}})$ and maximum velocity $(\sim \SI{18}{km.s^{-1}})$.
-This values are based on the available data of USG sample (see table \ref{tab:table-meteors-2})}
-    \label{fig:energy-mass}
-\end{figure}
+     \caption{Caribbean meteor possible physical properties obtained with  algorithm  , assuming a density of \SI{3000}{kg.m^{-3}}}
+    \begin{tabular}{lr}\toprule
+       Initial Velocity  &  \SI{19.9}{km.s^{-1}}\\
+        Initial mass & \SI{340}{kg} \\
+        Entry angle (deg) & 64 \\
+        \bottomrule
+    \end{tabular}
+    \label{tab:meteor-properties}
+\end{table}
 
-Once the estimated the bolides energy, we are capable to estimate other bolides parameters, such as the mass.
+Using the estimation of the meteor energy and velocity from table \ref{tab:Meteor-parameters}, the trajectory angle estimated in appendix \ref{app:velocity} from the velocity components of $64.4^\circ$ and assuming the meteor has a density of \SI{3000}{kg.m^-3}, consistent with the composition of \textit{condrites} (we must assure or edit this last statement), we estimated the initial velocity, initial mass and entry angle using (add citation and more text and once got the references) ...%we are capable to estimate other bolides parameters, such as the mass.
 For that we used a Fragment Cloud Model \citep{Wheeler:2017}.

### 2022-11-29 paper/methodology.tex
Update ELSEVIER paper (which compiles) to overleaf at 28-November-2022

--- 2021-12-01 paper/methodology.tex
@@
-\subsection{Meteors Databases}
+\subsection{Meteor location and trajectory}
 \label{ssec:databases}
-We selected a sample of meteors which were observed in mexican territory from the Geostationary Lightning Mapper \citep{GOODMAN:2013}.
-Orignally this project was designed to detect ligthning activity in earth's athmosphere, but has been proven that also can detect bolides entering the athmosphere.
-The detection comes from two satellites called GOES-16 and GOES-17 orbiting the earth in geostationary orbits.
-%Figure  shows the area where GOES-16 and GOES-17 detect activity on a lightning flash rate map; in mexican territory clearly both satellites can make detections.
-%Create a figure where the area coverage of GOES-16 and GOES-17 is shown.
-We used the interactive database available at \url{https://neo-bolide.ndc.nasa.gov/#/}.
-These data are publicly available and easily downloaded from the same website.
-For each event we can obtain the recorded trajectory of meteors and the corresponding light curve.
-THe GLM satellites have an umbral magnitude for detection of -14.
-At this magnitude, a meteor is considered a bolide, and is expected to be at least decimeter-sized (in diameter) to reach such brightness.
-In the other hand, too bright meteors will saturate the detectors, and thus, lowering the quality of data.
-The result of this factors implies that the range in size of the objects in our sample varies in diameter between decimeter to meter size.
-%The sample was chosen following the next criteria:%selected in such way we chose the most probable objects to be detected by GPS sources in mexican territory and its surroundings:
-Each event also has assigned a confidence ratio, from low confidence to high, depending in how bright is the event itself and if the trajectory recorded by GLM ressembles (or not) a straight line.
-We chose only events whose confidence ratio is high, in oreder to be sure we chose the brightest objects, and thus, in the diameter size of bolides, we favored the meter-sized ones.
-In table \ref{tab:table-meteors} we list the object we chose to do this work, order in chronological order.
-The columns of the table, from left to right are and ID to enumerate the meteors in the sample, the date and time each meteor was detected, the duration of the detection, their respective coordinates and the estimated height of the meteor over the ground at the time of the detection.
-GOES-16 and GOES-17 systematically detect the meteors at slightly different positions and at slightly different times, so we calculated the mean of the duration, latitude and longitude reported by both satellites for each event, and used the standard deviation as the uncertainties.
 
-From table \ref{tab:table-meteors} is also clear that the duration of all the bolides detection last less than a second.
-This obsevation suggests that the bolides remain undetected by the GLM satellites until they get fragmented due to stagnation presure when they release a huge amount of energy and thus they become detectable.
+Data of the Caribbean meteoroid is available from the Geostationary Lightning Mapper (GLM) \citep{GOODMAN:2013} and the Center for Near Earth Object Studies (CNEOS) of the Jet Propultion Laboratory (JPL) of the NASA.
+We used the interactive database of both projects, available at \url{https://neo-bolide.ndc.nasa.gov/#/} and \url{https://cneos.jpl.nasa.gov/fireballs/}.
+From these databases, we found basic physical parameters such as event coordinates, altitude, total velocity asn its componentes, total radiated energy and calculated impact energy.
+These data are shown in table \ref{tab:Meteor-parameters}.
 
-%From the light curves we can estimate the total radiated energy and then convert it to the total kinetic energy through a relation.
-With this energy we may estimate physical parameters with the cloud fragmentation model form wheeler et al.
+\begin{table*}[t]
+    \centering
+    \caption{List of meteor basic parameters. Source: \url{https://cneos.jpl.nasa.gov/fireballs/}}
+    \begin{tabular}{cc|c}
+     \toprule
+    Event date  (yyyy-mm-dd)&   & 2019-06-22 \\\hline
+    Time (UT) & &21:25:48\\\hline
+    Latitude (deg) & & 14.9\\\hline
+    Longitude (deg) & & -66.2\\\hline
+    Altitude (km) & &25.0\\\hline
+    Velocity (km/s) & & 14.9\\\hline
+    Duration (seconds)& & 4.873 \\\hline
+    \multirow{3}{*}{Velocity components (km/s)}&$v_x$ & -13.4 \\\cline{2-3}
+     & $v_y$& 6.0\\\cline{2-3}
+     & $v_z$ & 2.5\\\hline
+    Total radiated energy (J) & &\SI{294.7e10}{}\\\hline
+    Calculated Total Impact energy (kt)&  & 6 \\
+    \bottomrule
+    \end{tabular}
+    \label{tab:Meteor-parameters}
+\end{table*}
 
-%\begin{itemize}
-%    \item The objects were detected inside mexican territory and its surroundings.
-%    \item The objects were detected by both satellites GOES 16 and GOES 17 (stereo)
-%    \item The detection has been assigned a high confidence ratio.
-%\end{itemize}
+Row 7 shows the velocity components of the bolide.
+$v_x$ is the velocity in the equatorial plane, positive towards the prime meridian, $v_z$ is directed towards the celestial north pole and $v_y$ completes the right-handed coordinate system, see figure \ref{fig:ref_velocity} in appendix \ref{app:velocity}.
 
-\begin{table*}
-  \centering
-  \footnotesize
-  \caption{List of bolides detected in mexican territory (plus one detected near Venezuela and one detected near Cuba), detected by the Geostationary Lighning mapper.
-The events are listed in chronological order.
-The listed duration, latitude and longitude correspond to the mean of the measurements of both GOES satellites.
-The uncertainties correspond to the respecting mean deviation.}
-\label{tab:table-meteors}
-\begin{tabular}{rrrrrrrrrr}
-\hline
-ID & Date of event  & Start Time (UT)  & Duration (seconds) & Latitude (deg) & Longitude (deg)& Altitude (km) & Energy (kT )\\\hline
-GLM-00 & 2019-02-01 & 18:17:09 & $2.651\pm 0.4907$ & $22.45 \pm 0.071$ & $-83.50  \pm  0.424$ & 24           & 2.0978196 +/- 0.42361329      \\         
-GLM-01 & 2019-05-23 & 16:36:18 & $0.197\pm 0.0000$ & $24.30 \pm 0.000$ & $-101.60 \pm  0.849$ & 28           & 0.011954659 +/- 7.4054404e-3  \\
-GLM-02 & 2019-07-18 & 14:30:30 & $0.058\pm 0.0000$ & $27.20 \pm 0.000$ & $-103.15 \pm  0.778$ & 72           & 5.7827709e-3 +/- 3.9334336e-3 \\
-GLM-03 & 2019-08-10 & 11:18:48 & $0.199\pm 0.0757$ & $21.50 \pm 0.000$ & $-102.50  \pm 0.849$ & 92           & 0.010556123 +/- 6.6488245e-3  \\
-GLM-04 & 2019-10-03 & 07:55:33 & $0.106\pm 0.0297$ & $25.65 \pm 0.071$ & $-96.25 \pm   0.778$ & 74           & 2.9915536e-3 +/- 2.2000998e-3 \\
-GLM-05 & 2019-10-09 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$ & 32           & 0.021837042 +/- 0.012429732   \\
-GLM-06 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$ & 82           & 7.5423706e-3 +/- 4.9626060e-3 \\
-GLM-07 & 2019-11-17 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$ & 88           & 0.022397444 +/- 0.012701445   \\
-GLM-08 & 2019-11-19 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm   1.131$ & 99           & 1.5012507e-3 +/- 1.1909667e-3 \\
-GLM-09 & 2019-11-26 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$ & 81           & 4.9551290e-3 +/- 3.4345742e-3 \\
-GLM-10 & 2019-12-04 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$ & 77           & 0.029149047 +/- 0.015891049   \\
-GLM-11 & 2019-12-15 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$ & 78           & 0.010556123 +/- 6.6488245e-3  \\
-GLM-12 & 2019-12-29 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$ & 79           & 4.2084911e-3 +/- 2.9746446e-3 \\
-GLM-13 & 2020-01-03 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$ & 74           & 0.011607116 +/- 7.2187549e-3  \\
-GLM-14 & 2020-01-06 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$ & 81           & 0.015448801 +/- 9.2392402e-3  \\
-GLM-15 & 2020-01-15 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$ & 93           & 0.012559739 +/- 7.7284725e-3  \\
-GLM-16 & 2020-02-12 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$ & 90           & 8.2107211e-3 +/- 5.3440405e-3 \\
-GLM-17 & 2020-03-03 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm  0.636$ & 77           & 3.4441157e-3 +/- 2.4922397e-3 \\
-GLM-18 & 2020-03-31 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 61           & 7.2469897e-3 +/- 4.7924800e-3 \\
-GLM-19 & 2020-04-08 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$ & 78           & 4.0292119e-3 +/- 2.8626279e-3 \\
-GLM-20 & 2020-04-18 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$ & 82           & 5.8303967e-3 +/- 3.9618242e-3 \\
-GLM-21 & 2020-04-20 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$ & 88           & 0.031378060 +/- 0.016913982   \\
-GLM-22 & 2020-04-25 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$ & 84           & 0.021997346 +/- 0.012507576   \\
-GLM-23 & 2020-04-28 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$ & 29           & 0.12687833 +/- 0.053736010    \\
-GLM-24 & 2020-05-08 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$ & 81           & 0.033207253 +/- 0.017743607   \\
-GLM-25 & 2020-07-15 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$ & 53           & 0.020548979 +/- 0.011800641   \\
-GLM-26 & 2020-08-07 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$ & 89           & 0.014606987 +/- 8.8040841e-3  \\
-GLM-27 & 2020-09-13 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$ & 85           & 0.010995616 +/- 6.8881646e-3  \\
-GLM-28 & 2020-09-30 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ & 83           & 0.014013965 +/- 8.4951275e-3  \\
-GLM-29 & 2020-11-16 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$ &106           & 0.052044572 +/- 0.025868548   \\
-GLM-30 & 2020-11-17 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$ & 93           & 0.060624247 +/- 0.029367156   \\
-GLM-31 & 2020-12-19 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$ & 98           & 0.060272985 +/- 0.029225978   \\
-GLM-32 & 2020-12-23 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$ & 81           & 0.012127937 +/- 7.4982028e-3  \\
-GLM-33 & 2020-12-29 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$ & 81           & 0.013161054 +/- 8.0470909e-3  \\
-GLM-34 & 2021-03-31 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$  & 24           & 0.054259119 +/- 0.026782008   \\
-GLM-Ven& 2019-06-22 & 21:25:45 & $4.873\pm 0.0000$ & $14.9 \pm 0.000$  & $-65.8 \pm 0.000$    & 25           & 6.1014359 +/- 0.81239700      \\ \hline
-\end{tabular}
-\end{table*}
+From GLM data we know that the bolide was visible for 4.873 seconds. The trajectory using the data is shown in figure  \ref{fig:bolide-trajectory}, among with the GLM records.
 
@@
     \centering
-  \includegraphics[width=\linewidth]{../meteors_map}
-  \caption{Positions of events from table \ref{tab:table-meteors} (blue) and table \ref{tab:table-meteors-2}.
-The events GLM-00/USG-08 actually correpond to the same bolide, but there are little discrepancies about the position where the bolide was detecte.
-The same applies for the events GLM-23/USG-10 and GLM-Ven/USG-09, which not appears in the map.}
-  \label{fig:meteors-map}
+    \includegraphics[width=\linewidth]{../figures/bolide-trajectory}
+    \caption{In orange continuous line, the Caribbean bolide estimated trajectory using velocity components from table \ref{tab:Meteor-parameters}. In blue dots, GLM position records.}
+    \label{fig:bolide-trajectory}
 \end{figure}
 
-By the other hand, we got another sample of 10 bolidesfrom US Goverment (USG) sensors from the Center for Near Earth Object Studies (CNEOS), publicly available at \url{https://cneos.jpl.nasa.gov/fireballs/}, where we may obtain directly data about bolides position, the date and time each bolide was detected, the energy released at fragmentation, the velocity and the height (the last two not availble for all bolides).
-As seen in table \ref{tab:table-meteors-2}, the time span is quite larger, and the released energy is generally larger.
-Both energy distributions are compared directly in figure \ref{fig:boxplot}.
-Some elements appear in both samples, since are bright enough to be detected regardless the project involved.
-In USG sample, the total energy of each meteor is obtained directly, but is not the case for the GLM sample.
-In appendix \ref{app:distance} and \ref{app:energy} we give details about how this total energy is obtained.
+  \section{RINEX data}
+  \label{sec:GPS-data}
+  We collected RINEX data for event from 38 stations that surrounded the impact coordinates for the day of the event.
+Since the event ocurred near 24:00 UT, we also obtained GPS data for the next day in case of there would be TIDs detected several hours after the fragmentation.
+We obtained TEC curves using the GOPI software and detrended the resulting time series for each receiver-satellite line of sight.
+%The spatial distribution of stations is shown in figure \ref{fig:stations_map}, and
+  Table \ref{tab:table-stations} shows the stations names, coordinates and proper citations.
 
-\begin{table*}
-    \centering
-  \footnotesize
-  \caption{List of bolides detected in mexican territory (plus one detected near Venezuela and one detected near Cuba), detected by USG sensors.}
-\label{tab:table-meteors-2}
-\begin{tabular}{rrrrrrrrrrr}
-       &               &                  & \multicolumn{4}{c}{Velocity (km/s)}       &                   &                 &\\\cline{4-7}
-\multicolumn{1}{c}{ID}&\multicolumn{1}{c}{Date of event}&\multicolumn{1}{c}{Start Time (UT)}&\multicolumn{1}{c}{$v$}&\multicolumn{1}{c}{$v_x$}&\multicolumn{1}{c}{$v_y$}&\multicolumn{1}{c}{$v_z$}&\multicolumn{1}{c}{Latitude (deg)}&\multicolumn{1}{c}{Longitude (deg)}&\multicolumn{1}{c}{Altitude (km)} & \multicolumn{1}{c}{Energy (kT)}\\\hline
-USG-01 & 1995-08-05    & 17:14:10         &      &         &           &              & 11.6              &  -104.3         &             &  0.56\\
-USG-02 & 1996-07-12    & 14:04:45         &      &         &           &              & 20.7              &   -93.6         &             &  0.11\\ 
-USG-03 & 1997-10-09    & 18:47:15         &      &         &           &              & 31.8              &  -106.0         &   37.0      &  0.53\\
-USG-04 & 2000-01-18    & 08:33:58         &      &         &           &              & 24.3              &   -94.9         &             &  0.12\\
-USG-05 & 2000-08-25    & 01:12:25         &      &         &           &              & 14.5              &  -106.1         &             &   3.1\\
-USG-06 & 2005-11-15    & 05:19:07         &      &         &           &              & 26.3              &  -113.4         &   32.4      & 0.089\\
-USG-07 & 2015-07-19    & 07:06:26         & 17.8 &   9.4   &  13.0     & 7.8          & 20.6              &   -87.6         &   22.0      & 0.082\\
-USG-08 & 2019-02-01    & 18:17:10         & 16.3 &  -2.4   &  13.6     & 8.7          & 22.5              &   -83.8         &   23.7      &   1.4\\
-USG-09 & 2019-06-22    & 21:25:48         & 14.9 & -13.4   &   6.0     & 2.5          & 14.9              &   -66.2         &   25.0      &   6.0\\
-USG-10 & 2020-04-28    & 05:43:17         &      &         &           &              & 20.1              &  -109.4         &             & 0.076\\\hline  
-  \end{tabular}
-\end{table*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{./figures/energies_boxplot}
-  \caption{Comparison between released energies of bolides detected by the Geostationary Lightning Mapper and USG sensors.}
-  \label{fig:boxplot}
-\end{figure}
-
-\subsection{GPS data}
-\label{ssec:GPS}
-%This material is based on services provided by the GAGE Facility, operated by UNAVCO, Inc., with support from the National Science Foundation and the National Aeronautics and Space Administration under NSF Cooperative Agreement EAR-1724794.
-
-We got RINEX data from 3 to 7 stations depending of the event location and data availability that surround the event place in all directions as possible.
-A list of the stations where we got RINEX data is available in table%\ref{tab:table-stations}
-. Most of the stations lie in mexican territory, but in some cases we required data from other stations to cover events near the mexican frontier at north or south.
-
-%\clearpage
-%\onecolumn
-%\footnotesize
-%\begin{landscape}
-%%\begin{table*}
-%%    \centering
-%  \begin{longtable}{llllllp{12cm}}
-%      \caption{List of GPS stations used for this work.}
-%      \label{tab:table-stations}
-%      \endfirsthead
-%      \endhead
-%    \hline
-%    Station name & Latitude & Longitude & \multicolumn{3}{c}{Events ID}  & Citation \\\hline
-%    \multirow{4}{*}{BAR1\hyperlink{Hudnut}{${}^1$}\hyperlink{Hudnut2}{${}^5$}} & \multirow{4}{*}{33.48} & \multirow{4}{*}{-119.03} & \multirow{4}{*}{GLM-07} & \multirow{4}{*}{GLM-12} & \multirow{4}{*}{GLM-13} & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, \\
-%    &&&&&& Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - BAR1-Santa \\
-%    &&&&&& Barbara Island One P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
-%    &&&&&& \url{https://doi.org/10.7283/T5668BHN}.\\\hline
-%    \multirow{3}{*}{BLYT\hyperlink{Hudnut}{${}^1$}} & \multirow{3}{*}{33.61} & \multirow{3}{*}{-114.71} &  \multirow{3}{*}{GLM-12} & \multirow{3}{*}{GLM-13}  & & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John \\
-%    &&&&&& E., Stark, Keith F., 2006, SCIGN USGS GPS Network - BLYT-Blythe P.S., The GAGE Facility operated \\
-%    &&&&&&  by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5HT2MKK}.\\\hline
-%    \multirow{3}{*}{CN23} & \multirow{3}{*}{17.26} & \multirow{3}{*}{-88.78} &\multirow{3}{*}{GLM-08} & \multirow{3}{*}{GLM-15} & \multirow{3}{*}{GLM-16} & UNAVCO Community, 2012, COCONet GPS Network - CN23-BelmopanBZCR2012 P.S., The GAGE \\
-%    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
-%    &&&&&& \url{https://doi.org/10.7283/T5Q23XJH}.\\\hline
-%    \multirow{3}{*}{CN25} & \multirow{3}{*}{16.23} & \multirow{3}{*}{-92.13} & \multirow{3}{*}{GLM-15} & & & UNAVCO Community, 2014, COCONet GPS Network - CN25-ComitandDMEX2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57W69G7}.\\\hline
-%    \multirow{3}{*}{GCFS} & \multirow{3}{*}{19.31} & \multirow{3}{*}{-81.18} & \multirow{3}{*}{GLM-08} & & & Watts, Anthony, 2016, COCONet GPS Network - GCFS-G\_CAYMAN\_CYM2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/7ETV-X536}.\\\hline
-%    \multirow{4}{*}{GMPK\hyperlink{Hudnut}{${}^1$}} & \multirow{4}{*}{33.05} & \multirow{4}{*}{-114.83} & \multirow{4}{*}{GLM-10} & & & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, \\
-%    &&&&&& Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - GMPK-Glamis \\
-%    &&&&&& Peak P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
-%    &&&&&& \url{https://doi.org/10.7283/WCHN-H687}.\\\hline
-%    \multirow{3}{*}{GUAT\hyperlink{Garnier}{${}^2$}} & \multirow{3}{*}{14.59} & \multirow{3}{*}{-90.52} & \multirow{3}{*}{GLM-16} & & & DeMets, Charles, Cosenza-Muralles, Beatriz, 2021, Central America 2018 - Guatemala, The GAGE \\
-%    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
-%    &&&&&& \url{https://doi.org/10.7283/KH2R-K704}.\\\hline
-%\multirow{4}{*}{GUAX\hyperlink{Hudnut}{${}^1$}} & \multirow{4}{*}{28.88} & \multirow{4}{*}{-118.29} & GLM-05 & GLM-07 & GLM-11 & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John \\
-%    &&&GLM-12& GLM-13& GLM-18 & E., Stark, Keith F., 2001, SCIGN USGS GPS Network - GUAX-Isla Guadalupe P.S., The GAGE Facility \\
-%    &&& GLM-25 &GLM-27 &GLM-28& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5GX48T2}.\\
-%    &&& GLM-32 &       &     &  \\\hline
-%    \multirow{3}{*}{IAGX} & \multirow{3}{*}{29.03} & \multirow{3}{*}{-113.17} & \multirow{3}{*}{GLM-10} & & & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network \\
-%    &&&&&& - IAGX-iagxREGNOMmx2018 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS  \\
-%    &&&&&& Observations Dataset, \url{https://doi.org/10.7283/DGWN-A627}. \\\hline
-%    \multirow{2}{*}{INEG} & \multirow{2}{*}{21.85} & \multirow{2}{*}{-102.28} & GLM-25 & GLM-26 & GLM-28  & No citations were found \\
-%    &&& GLM-29 & GLM-30 & GLM-31 & \\\hline 
-%    \multirow{4}{*}{KVTX} & \multirow{4}{*}{27.55} & \multirow{4}{*}{-97.89} & GLM-01 & GLM-02 & GLM-03  & UNAVCO Community, 2007, PBO GPS Network - KVTX-KingsvilleTX2006 P.S., The GAGE Facility \\
-%    &&& GLM-04 & GLM-06 & GLM-19 & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J38QH8}.\\
-%    &&& GLM-20 & GLM-21 & GLM-24 & \\
-%    &&& GLM-26 &&& \\\hline
-%    MDO1 & 30.68 & -104.02 & GLM-02 & & & No citations were found\\\hline
-%    MGO5 & 30.68 & -104.02 & GLM-21 &GLM-26 &  & No citations were found\\\hline
-%    MGW3 & 29.62 & -89.95 & GLM-19 & GLM-21 & GLM-24 & No citations were found\\\hline
-%    \multirow{3}{*}{OXTH} & \multirow{3}{*}{16.29} & \multirow{3}{*}{-95.24} & \multirow{3}{*}{GLM-15} & \multirow{3}{*}{GLM-16} & & DeMets, Charles, Cabral-Cano, Enrique, 2008, Oaxaca GPS Network - OXTH-Tehuantepec P.S., The \\
-%    &&&&&& GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
-%    &&&&&& \url{https://doi.org/10.7283/T5Q81B5V}.\\\hline
-%    \multirow{3}{*}{OXUM\hyperlink{Graham}{${}^3$}} & \multirow{3}{*}{15.66} & \multirow{3}{*}{-96.50} & \multirow{3}{*}{GLM-34} & & & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - OXUM-oxum\_tnet\_mx2001 P.S., The \\
-%    &&&&&& GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
-%    &&&&&& \url{https://doi.org/10.7283/T5J964RP}.\\\hline
-%    \multirow{2}{*}{P001} & \multirow{2}{*}{31.95} & \multirow{2}{*}{-112.80} & \multirow{2}{*}{GLM-07} & \multirow{2}{*}{GLM-22} & & UNAVCO Community, 2008, PBO GPS Network - P001-Organ\_PipeAZ2007 P.S., The GAGE Facility \\
-%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DR2SGP}.\\\hline
-%    \multirow{2}{*}{P014} & \multirow{2}{*}{31.97} & \multirow{2}{*}{-11.09} & GLM-10 & GLM-12 & GLM-13 & UNAVCO Community, 2008, PBO GPS Network - P014-Sahuarita\_AZ2007 P.S., The GAGE Facility \\
-%    &&& GLM-14 & GLM-22 & & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5CMK}.\\\hline
-%    \multirow{2}{*}{P807} & \multirow{2}{*}{30.49} & \multirow{2}{*}{-98.82} & GLM-06 & GLM-14 & GLM-21 & UNAVCO Community, 2012, PBO GPS Network - P807-EcRockStPkTX2012 P.S., The GAGE Facility \\
-%    &&& GLM-30 &&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5TQ5ZKM}.\\\hline
-%    \multirow{2}{*}{PLPX} & \multirow{2}{*}{31.59} & \multirow{2}{*}{-115.15} & \multirow{2}{*}{GLM-10} & & & UNAVCO Community, 2011, PBO GPS Network - PLPX-Las\_PintasMX2010 P.S., The GAGE Facility \\
-%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5K64G3T}.\\\hline
-%    \multirow{2}{*}{PTEX} & \multirow{2}{*}{32.29} & \multirow{2}{*}{-116.52} & GLM-07 & GLM-12 & GLM-13  & UNAVCO Community, 2011, PBO GPS Network - PTEX-Testerazo\_MX2011 P.S., The GAGE Facility \\
-%    &&& GLM-27 & GLM-32 & & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XBP}.\\\hline 
-%    \multirow{3}{*}{RG06} & \multirow{3}{*}{32.63} & \multirow{3}{*}{-107.86} & \multirow{3}{*}{GLM-22} & & & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG06-RG06FaywodNM2006 P.S., The GAGE \\
-%    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
-%    &&&&&& \url{https://doi.org/10.7283/T5668BFR}.\\\hline
-%    \multirow{3}{*}{RG07} & \multirow{3}{*}{32.50} & \multirow{3}{*}{-106.84} & \multirow{3}{*}{GLM-14} & & & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG07-RG07CrucesNM2006 P.S., The GAGE  \\
-%    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
-%    &&&&&& \url{https://doi.org/10.7283/T5KD1W45}. \\\hline
-%    \multirow{3}{*}{SG33} & \multirow{3}{*}{31.77} & \multirow{3}{*}{-106.51} & \multirow{3}{*}{GLM-06} & \multirow{3}{*}{GLM-20} & \multirow{3}{*}{GLM-26} & Harder, Steven, Kaip, Galen, Montana, Carlos, 2004, SuomiNet-G GPS Network - SG33-UTEP P.S., The \\
-%    &&&&&& GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset,  \\
-%    &&&&&& \url{https://doi.org/10.7283/T50863KQ}. \\\hline
-%    \multirow{3}{*}{TGMX}  & \multirow{3}{*}{20.87} & \multirow{3}{*}{-86.87} & \multirow{3}{*}{GLM-34} & & & UNAVCO Community, 2015, COCONet GPS Network - TGMX-PtoMor\_TG\_MX2015 P.S., The GAGE \\
-%    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset,  \\
-%    &&&&&& \url{https://doi.org/10.7283/T5154FB7}. \\\hline
-%    \multirow{2}{*}{TNAM} & \multirow{2}{*}{20.54} & \multirow{2}{*}{-103.97} & GLM-17 & GLM-25 & GLM-28  & UNAVCO Community, 2014, TLALOCNet - TNAM-TNAM\_TNET\_MX2014 P.S., The GAGE Facility \\
-%    &&& GLM-29 & GLM-30 & GLM-31 & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5QF8R4R}.\\\hline
-%    \multirow{2}{*}{TNAT} & \multirow{2}{*}{18.13} & \multirow{2}{*}{-98.04} & \multirow{2}{*}{GLM-15} & & & UNAVCO Community, 2014, TLALOCNet - TNAT-TNAT\_TNET\_MX2014 P.S., The GAGE Facility \\
-%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5G15Z4S}. \\\hline
-%    \multirow{2}{*}{TNBA} & \multirow{2}{*}{28.97} & \multirow{2}{*}{-113.55} & GLM-05 & GLM-07 & GLM-09  & UNAVCO Community, 2015, TLALOCNet - TNBA-TNBA\_TNET\_MX2014 P.S., The GAGE Facility  \\
-%    &&& GLM-11 & GLM-12 & GLM-13 & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57M0688}.\\\hline
-%    \multirow{2}{*}{TNCC} & \multirow{2}{*}{18.79} & \multirow{2}{*}{-103.17} & \multirow{2}{*}{GLM-17} & & & UNAVCO Community, 2015, TLALOCNet - TNCC-TNCC\_TNET\_MX2015 P.S., The GAGE Facility \\
-%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T50R9MSK}.\\\hline
-%    \multirow{2}{*}{TNCM} & \multirow{2}{*}{19.50} & \multirow{2}{*}{-105.04} & \multirow{2}{*}{GLM-17} & \multirow{2}{*}{GLM-23} & & UNAVCO Community, 2014, TLALOCNet - TNCM-TNCM\_TNET\_MX2014 P.S., The GAGE Facility \\
-%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5B856FW}.\\\hline
-%    \multirow{2}{*}{TNCN} & \multirow{2}{*}{18.55} & \multirow{2}{*}{-101.97} & \multirow{2}{*}{GLM-29} & \multirow{2}{*}{GLM-33} & & UNAVCO Community, 2016, TLALOCNet - TNCN-TNCN\_TNET\_MX2016 P.S., The GAGE Facility \\
-%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XQM}.\\\hline
-%    \multirow{4}{*}{TNCU} & \multirow{4}{*}{28.45} & \multirow{4}{*}{-106.79} & GLM-01 & GLM-02 & GLM-03  & UNAVCO Community, 2014, TLALOCNet - TNCU-CuauhtemocTN2014 P.S., The GAGE Facility \\
-%    &&& GLM-06 & GLM-11 & GLM-14 & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5V69GV2}.\\
-%    &&& GLM-18 & GLM-20 & GLM-25 & \\
-%    &&& GLM-26 & GLM-30 & GLM-31 & \\\hline
-%    \multirow{3}{*}{TNGF} & \multirow{3}{*}{19.33} & \multirow{3}{*}{-99.18} & \multirow{3}{*}{GLM-29} & \multirow{3}{*}{GLM-33} & & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2016, TLALOCNet GPS Network - TNGF\_Geofisica-\\
-%    &&&&&& UNAM\_Mexico\_City\_TNET\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS \\
-%    &&&&&& Observations Dataset, \url{https://doi.org/10.7283/T53X851M}. \\\hline
-%    \multirow{5}{*}{TNHM} & \multirow{5}{*}{29.08} & \multirow{5}{*}{-110.97} & GLM-05 & GLM-09 & GLM-10 & UNAVCO Community, 2014, TLALOCNet - TNHM-hermosilloTN2014 P.S., The GAGE Facility \\
-%    &&& GLM-11 & GLM-12 & GLM-13 & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5KP80FV}.\\
-%    &&& GLM-18 & GLM-20 & GLM-25 & \\
-%    &&& GLM-26 & GLM-27 & GLM-28 & \\
-%    &&& GLM-32 &        &        & \\\hline
-%    \multirow{2}{*}{TNMS} & \multirow{2}{*}{20.53} & \multirow{2}{*}{-104.80} & GLM-05 & GLM-09 & GLM-11  & UNAVCO Community, 2014, TLALOCNet - TNMS-TNMS\_TNET\_MX2014 P.S., The GAGE Facility \\
-%    &&& GLM-17 & GLM-25 & & operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T56H4FQ5}.\\\hline
-%    \multirow{3}{*}{TNNP} & \multirow{3}{*}{16.12} & \multirow{3}{*}{-97.14} & \multirow{3}{*}{GLM-23} & & & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, DeMets, Charles, 2016, TLALOCNet - TNNP-\\
-%    &&&&&& tnnp\_tnet\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
-%    &&&&&& \url{https://doi.org/10.7283/T5N29V96}. \\\hline
-%    \multirow{2}{*}{TNNX} & \multirow{2}{*}{17.41} & \multirow{2}{*}{-97.22} & GLM-15 & GLM-16 & GLM-33  & UNAVCO Community, 2014, TLALOCNet - TNNX-TNNX\_TNET\_MX2014 P.S., The GAGE Facility \\
-%    &&& GLM-34 &&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T52R3PZ0}.\\\hline
-%    \multirow{2}{*}{TNPP} & \multirow{2}{*}{31.34} & \multirow{2}{*}{-113.63} & GLM-07 & GLM-10 & GLM-18 & UNAVCO Community, 2015, TLALOCNet - TNPP-TNPP\_TNET\_MX2015 P.S., The GAGE Facility \\
-%    &&& GLM-22 &&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5CC0Z0M}.\\\hline
-%    \multirow{2}{*}{TNSJ} & \multirow{2}{*}{16.17} & \multirow{2}{*}{-96.49} & \multirow{2}{*}{GLM-33} & & & UNAVCO Community, 2016, TLALOCNet - TNSJ-tnsj\_tnet\_mx2015 P.S., The GAGE Facility operated by \\
-%    &&&&&& UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59S1PF1}.\\\hline
-%    \multirow{3}{*}{TSFX} & \multirow{3}{*}{30.93} & \multirow{3}{*}{-114.81} & \multirow{3}{*}{GLM-07} & \multirow{3}{*}{GLM-27} & \multirow{3}{*}{GLM-32} & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network \\
-%    &&&&&& - TSFX-tsfxREGNOMmx2016 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS \\
-%    &&&&&& Observations Dataset, \url{https://doi.org/10.7283/AGEA-2G27}.\\\hline
-%    \multirow{3}{*}{UAGU} & \multirow{3}{*}{21.92} & \multirow{3}{*}{-102.32} & GLM-01 & GLM-02 & GLM-03  & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UAGU-uagu\_tnet\_mx2008 P.S., The \\
-%    &&& GLM-04 & GLM-06 & GLM-09 & GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
-%    &&& GLM-11 & GLM-20 &        & \url{https://doi.org/10.7283/T5513WK7}.\\\hline
-%    \multirow{3}{*}{UCOE\hyperlink{Graham}{${}^3$}} & \multirow{3}{*}{19.81} & \multirow{3}{*}{-101.69} & GLM-03 & GLM-06 & GLM-30 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UCOE-ucoe\_tnet\_mx2003 P.S., The \\
-%    &&& GLM-31 &&& GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
-%    &&&&&& \url{https://doi.org/10.7283/T51834VW}. \\\hline
-%    \multirow{3}{*}{UGEO\hyperlink{Marquez}{${}^4$}} & \multirow{3}{*}{20.69} & \multirow{3}{*}{-103.35} & \multirow{3}{*}{GLM-03} & & & Marquez-Azua, Bertha, DeMets, Charles, Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, \\
-%    &&&&&& TLALOCNet - UGEO-ugeo\_tnet\_mx1998 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS \\
-%    &&&&&& Observations Dataset, \url{https://doi.org/10.7283/T58S4N9N}. \\\hline
-%    \multirow{2}{*}{UHSL} & \multirow{2}{*}{29.57} & \multirow{2}{*}{-95.65} & \multirow{2}{*}{GLM-19} & & & Wang, Guoquan, 2014, HoustonNet GPS Network - UHSL-SugarLandUSA2014 P.S., The GAGE Facility \\
-%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T55X271S}.\\\hline
-%    \multirow{3}{*}{UHWL} & \multirow{3}{*}{30.06} & \multirow{3}{*}{-94.98} & \multirow{3}{*}{GLM-31} & & & Wang, Guoquan, 2014, HoustonNet GPS Network - UHWL-West Liberty Airport(Deep) P.S., The GAGE \\
-%    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset,  \\
-%    &&&&&& \url{https://doi.org/10.7283/T53R0R5P}. \\\hline
-%    \multirow{3}{*}{UNPM} & \multirow{3}{*}{20.86} & \multirow{3}{*}{-86.86} & GLM-08 & GLM-15 & GLM-16  & UNAVCO Community, 2012, COCONet GPS Network - UNPM-Puerto\_Morelos\_MX\_2007 P.S., The \\
-%    &&& GLM-24 &&& GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
-%    &&&&&& \url{https://doi.org/10.7283/J1GD-5S40}.\\\hline
-%    \multirow{3}{*}{USMX} & \multirow{3}{*}{29.82} & \multirow{3}{*}{-109.68} & GLM-12 & GLM-13 & GLM-14  & Bennett, Rick, 2004, Northwest Mexico GPS Network - USMX-Universidad de la Sierra P.S., The GAGE \\
-%    &&& GLM-22 & GLM-26 & GLM-28 & Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
-%    &&&&&& \url{https://doi.org/10.7283/T5W957CQ}.\\\hline
-%    \multirow{3}{*}{UXAL\hyperlink{Graham}{${}^3$}} & \multirow{3}{*}{19.52} & \multirow{3}{*}{-96.92} & GLM-04 & GLM-15 & GLM-16  & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UXAL-uxal\_tnet\_mx2005 P.S., The \\
-%    &&& GLM-19 & GLM-24 & GLM-31 & GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \\
-%    &&& GLM-34 &        &        & \url{https://doi.org/10.7283/T5DJ5D1C}.\\\hline
-%    \multirow{2}{*}{WEPD} & \multirow{2}{*}{29.69} & \multirow{2}{*}{-95.23} & \multirow{2}{*}{GLM-21} & & & Wang, Guoquan, 2014, HoustonNet GPS Network - WEPD-willmselementary P.S., The GAGE Facility \\
-%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5NZ85RB}. \\\hline
-%    \multirow{2}{*}{WMOK} & \multirow{2}{*}{34.74} & \multirow{2}{*}{-98.78} & \multirow{2}{*}{GLM-21} & & & UNAVCO Community, 2005, PBO GPS Network - WMOK-WichitaMtnOK2005 P.S., The GAGE Facility \\
-%    &&&&&& operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59021Q6}. \\\hline
-%    \multirow{4}{*}{WWMT\hyperlink{Hudnut}{${}^1$}} & \multirow{4}{*}{33.96} & \multirow{4}{*}{-116.65} & \multirow{4}{*}{GLM-07} & \multirow{4}{*}{GLM-12} & \multirow{4}{*}{GLM-13} & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John \\
-%    &&&&&& E., Stark, Keith F., 2006, SCIGN USGS GPS Network - WWMT-Whitewater Mountain P.S., The GAGE \\
-%    &&&&&& Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset,  \\
-%    &&&&&& \url{https://doi.org/10.7283/T5H993F2}. \\\hline
-%    \multirow{2}{*}{YESX} & \multirow{2}{*}{28.38} & \multirow{2}{*}{-108.92} & GLM-09 & GLM-11 & GLM-14  & Bennett, Rick, 2004, Northwest Mexico GPS Network - YESX-Yecora P.S., The GAGE Facility operated \\
-%    &&&GLM-20 & GLM-23 & GLM-25 & by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5RJ4GPF}.\\\hline
-%    
-%%    % \end{table*}
-%  \end{longtable}
-%    \begin{minipage}{0.9\linewidth}
-%      \footnotesize
-%      Related articles:
-%      
-%      \hypertarget{Hudnut}{${}^1$}\citet{Hudnut:2002},
-%      %
-%      \hypertarget{Garnier}{${}^2$}\citet{Garnier:2021}, 
-%      %
-%      \hypertarget{Graham}{${}^3$}\citet{Graham:2016}
-%      
-%      \hypertarget{Marquez}{${}^4$}\href{https://doi.org/10.7283/T58S4N9N}{B.
-Marquez-Azua, E.
-Cabral-Cano, F.
-Correa-Mora and C.
-DeMets, 2004.
-A model for Mexican neotectonics based on Nationwide GPS measurements, 1993-2001, Geofisica Internacional, v.
-43, p.319-330}
-%      
-%      \hypertarget{Hudnut2}{${}^5$}\href{https://doi.org/10.7283/T5668BHN}{Hudnut, K.
-W., Y.
-Bock, J.
-E.
-Galetzka, F.
-H.
-Webb, and W.
-H.
-Young, The Southern California Integrated GPS Network (SCIGN), Proceedings of the International Workshop on Seismotectonics at the Subduction Zone, Y.
-Fujinawa (ed.), NIED, Tsukuba, Japan, pp.
-175-196, 1999}
-%    \end{minipage}
-%  \end{landscape}
-%  \clearpage
-%  \twocolumn
+%  \begin{figure}
+%      \centering
+%      \includegraphics[width=\linewidth]{./figures/caribbean_stations_map}
+%      \caption{UNAVCO GPS stations map.
+The red star shows the positions where the bolide fragmented.
+The blue arrow shows the direction the bolide was moving in such instant.
+The green dots represent the positions of the stations we got GPS data.}
+%      \label{fig:stations_map}
+%  \end{figure}
 
@@
   The Total Electron content along the integrated path of the link $(s_i)$ at the frequency $f_i$ can be inferred from the phase delay $L_i$ of the frequency $f_i$ \citep{Emery:2017}:
+
   \begin{align}
@@
 
-  In the other hand, the Vertical Total Electron Content (vTEC) is computed from the sTEC as follows \citep{Kumar:2012}:
+  In the other hand, the vertical Total Electron Content (vTEC) is computed from the sTEC as follows \citep{Kumar:2012}.
+In figure \ref{fig:TEC-sketch} we illustrate the satellite-receiver path and how the vTEC and sTEC are related.
+
   \begin{align}
@@
   \begin{align}
-    S(\theta_i) = \frac{1}{\cos\psi} = \left\lbrace 1-\frac{R_E\cos\theta_I}{R_E+h}\right\rbrace^{-1/2}
+    S(\theta_I) = \frac{1}{\cos\psi} = \left\lbrace 1-\frac{R_E\cos\theta_I}{R_E+h}\right\rbrace^{-1/2}
   \end{align}
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{../figures/TEC_drawing.pdf}
+    \caption{Schematic figure of TEC calculations in the ionosphere.
+The GPS satellite is located at an elevation of $\theta_I$ from the position of the receiver.
+The Ionospheric Pierce Point (IPP) is located at a height of $h=\SI{350}{km}$ above the Earth's surface.
+$\psi$ is the zenital angle.
+sTEC is measured along the satellite-receiver path and vTEC is measured in the radial direction sharing the same IPP as the satellite-receiver path.}
+    \label{fig:TEC-sketch}
+\end{figure}
+
   % Both parameters sTEC and vTEC are computed
  Using a software developed by Gopi K.
-Seemala, publicly available at \url{https://seemala.blogspot.com/}, we computed the slant TEC (TEC) and vertical TEC (vTEC) for a several number of GPS satellites, each one identified with a PseudoRandom Noise code (PRN).
-For each station, we filtered all the PRN and data that lie in a window of 30 minutes around the time the event was reported.
-Then we estimated the signal trend using a Savitsky-Golay filter and substracting the original signal from the trend.
+Seemala, publicly available at \url{https://seemala.blogspot.com/}, we computed the slant TEC (sTEC) and vertical TEC (vTEC) for a several number of GPS satellites, each one identified with a PseudoRandom Noise code (PRN).
+An example of such TEC calculations is shown in figure \ref{fig:TEC-curve-example}.
+The behavior of the TEC curve is due to many factors, including the earth's rotation, solar activity, etc.
+TID's and wave-like features are not as prominent and are difficult to see.
+Since our sample is quite large, detrending process must be automatized in some degree, and it is critical to do this process adequately to have a correct interpretation of data \citep{Boris:2020}.
 
-  \subsection{Wavelet analysis}
+ \subsection{Detrending process}
 
-%For the selected sample, we obtained RINEX data from the TlalocNet \citep{Cabral-Cano:2018} and UNAVCO network databases to study potential alterations in the ionospehre due to the presence of the passing meteor at the day the meteor was reported.
-For each event, we downloaded data from stations that surrounds the place where the event was detected (usually 3 to 5 stations.
-)The list of the sample meteors is shown in table \ref{tab:table-meteors}.
-The events are in chronological order.
-The reported duration, latitude and longitude correspond to the mean between measurements from satellites GOES-16 and GOES 17; in the same way, the uncertainties correspond to the standard deviation.
-Also their respective positions are available in figure \ref{fig:meteors-map}, where each label correspond to the ID (first column) of table \ref{tab:table-meteors}.
+ For detrending our data we used a method developed for detecting plasma bubbles in the equatorial region \citep{Pradipta:2015}, but proved to be effective for detecting Acoustic Gravity Waves (AGWs) and Traveling Ionospheric Disturbances (TIDs).
+ With this method we are able to infer the trend from our TEC data using a Savitsky-Golay filter.
+However, the results of this filtering are sensitive to the parameters we use for such filtering, thus altering significantly the quality of the detrended signal.
+ The TEC time series are assumed to be an additive combination of a signal and a trend \citep{Boris:2020}.
+Thus we tested the method of \citet{Pradipta:2015} over the sum of a known signal and a known trend and find the parameters of the Savitsky-Golay filter that recover in the best way the original signal.
+We used a test signal with the purpose to find out the most appropriate parameters for the filter and we show its functional form in appendix \ref{app:test-signal}.
 
-%Using the data provided by TlalocNet and UNAVCO, we procceeded to obtain TEC parameters with the GPS\_GOPI software, available at \url{https://seemala.blogspot.com/}.
-This software takes as input the RINEX data (the navigation file is no strictly neccesary), and the outuput consists in in the vTEC and sTEC measurements for the PRNs of the whole day the event occurred, as well as the averaged TEC as function of time.
-We obtained vTEC maps for the events in table (\ref{tab:table-meteors}) and their respective next and previous day.
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../figures/BOAV-vTEC-curves}
+\label{fig:TEC-curve-example}
+\caption{Example of vTEC curves obtained for GPS data from BOAV station.}
+\end{figure}
 
-%Final idea: use GOPI software to get the vTEC data from the day of each event and the previous days.
+On the other side, not necessarily all satellites could have detected ionospheric perturbations produced by TIDs, most of then should have detected other non related phenomena.
+To check which satellites have the best probabilities of detecting TIDs we compared in an azimuth-elevation map the satellites trajectory against the bolide trajectory.
+To do so we converted the bolide coordinates.
+The procedure is shown in \ref{app:azimuth}.
+
+From Chelyabinsk event \citep{Yang:2014} we learned that high frequency TIDs (1.0 - 2.5 mHz) may travel at speed of $\sim 362 \pm 23~\mathrm{m~s^{-1}}$.
+Using this upper bound (since this event being less energetic, we can expect that similar TIDs in this case would travel at lower speed), we estimated the sphere where the TIDs should have propagated after a certain time interval.
+These propagation circles are shown in our azimuth-elevation maps.
+
+From these figures that are representative of the trajectories observed for all stations we can see that the bolide is observed at an elevation of about 80 degrees and that the satellite that consistently was closest to the bolide trajectory is PRN 13, but after a few hours, PRN 2, PRN 17 and PRN 19 could intercept TIDs as they propagate from the bolide.
+
+\subsection{Morlet Wavelet}
+\label{ssec:Morlet}
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{../figures/morlet.pdf}
+    \caption{Example of Morlet wavelet.
+Since this is a complex function, we show in blue continous curve the real part and in green dashed curve the imaginary part.
+The Morlet wavelet consist in a sinosoid function with a determined frequency and damped to the left and right by a gaussian.}
+    \label{fig:Morlet_wavelet}
+\end{figure}
+
+From our time series, we must distinguish some features that should appear if any TIDs has been detected.
+The TIDs are wave-like features constrained in a limited amount of time.
+A function that fits this description is the Morlet wavelet, which is given by \citep{Torrence:1998}:
+
+\begin{align}
+    \Psi_0(\eta) = \pi^{-1/4}\exp(i\omega_0\eta)\exp(-\eta^2/2)
+\end{align}
+
+Where $\omega_0$ is a non-dimensional frequency, usually set to be 6 to satisfy the admissibity condition \citep{Farge:1992} and $\eta$ is a non-dimensional "time parameter".
+The real and imaginary part of the Morlet wavelet is shown in figure \ref{fig:Morlet_wavelet}.
+
+\subsection{TIDs velocity estimation}
+
+%In figure \ref{fig:fragmentation-scheme} we analyze the scenario where TIDs are generated when the bolide is fragmented due to stagnation pressure.
+At this moment, a large amount of energy is released in the form of a shock wave that propagates isotropically.
+When the shock wave reaches back the ionosphere, the perturbed gas becomes detectable to our GPS sensors, if the perturbed area lies in the satellite-receiver Line Of Sight (LOS).
+In this case we should expect that TIDs appear in out time series in a certain time interval after the fragmentation occurred (the time needed for the shock wave reaching the ionosphere).
+
+In figure \ref{fig:TID-scheme-2} we sketch the scenario where TIDs may be generated.
+This model explains that when the bolide enters the atmosphere perturbs the gas in its path.
+The bolide passes through the ionosphere before fragmentation then the TIDs generated should have been detected before fragmentation, too.
+The delay time in this case depends now in the bolide velocity as it penetrates the atmosphere.
+%\begin{figure}
+%    \centering
+%\includegraphics[width=\linewidth]{figures/ionosphere_drawing.pdf}
+%    \caption{Scheme of TIDs generation: here the bolide is fragmented due to stagnation pressure at height $h_B$.
+The fragmentation releases energy isotropically and eventually the blast reaches the ionosphere.
+The area of the perturbed ionosphere can or cannot be at the satellite-receiver Line of Sight (LOS).}
+%    \label{fig:fragmentation-scheme}
+%\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{../figures/ionosphere_drawing2.pdf}
+       \caption{TIDs generation sketch. When the bolide passes through the atmosphere perturbs the gas in its way. The resulting TIDs can be detected before the bolide fragmentation.}
+    \label{fig:TID-scheme-2}
+\end{figure}

### 2022-11-29 paper/sTEC-time_series.tex
Update journal.org and jupyter notebooks

Ionospheric perturbations also can take place due to space weather and geomagnetic storms. So, in order to discard such events we investigated the space weather in the day each event occurred. We investigated the solar wind conditions in the event day and the previous 7 days, the x-ray flux %the planetary K index (Kp index) at the event day and the previous two days 
and the Dst index at the event date.

%\subsection{Planetary K index}

 %In figure \ref{fig:Kp-index} we show the Kp index for the day of the Caribbean bolide event. We discarded events whose Kp index is equal or grater than 4 at the day and time the meteor passage occured. These data were obtained from the NOAA/Space Weather Prediction Center. We found that the Kp index is lower than 4 for the event date and adjacent days, so we can safely assume that geomagnetic storms are not a treat for our detection of TIDs.

%\begin{figure}
%\centering
%\includegraphics[width=\linewidth]{./figures/2019-06-22 Kp index}
%\caption{Planetary K index for 2019-06-22 and two previous days (NOAA/Space Weather Prediction Center). Only Moderate K index warnings were issued.}
%\label{fig:Kp-index}
%\end{figure}

\subsection{Dst Index}

We obtained measurements of Dst Index from WDC for Geomagnetism, Kyoto DST index service (\url{https://wdc.kugi.kyoto-u.ac.jp/dstdir/}), and is shown in figure \ref{fig:Dst_index}. We see that  Dst index remains practically constant around zero, which confirms that there were not geomagnetic storms that could prevent us from detecting TIDs in our GPS data.

\subsection{Solar wind}

Another source of ``space weather noise'' that we should discard is unusual solar wind behavior or even coronal mass ejections. We collected data from the Deep Space Climate Observatory (DSCOVR) of solar wind speed, temperature, density, dynamic pressure and solar magnetic field, in order to monitor the solar wind behavior in the day of the event and the previous 6 or 7 days.% In figure \ref{fig:wind_temp} we can see in the event day and the prior week solar wind temperature remained between $\sim \SI{1e4}{}$ and $\sim \SI{1e5}{K}$. %Solar magnetic field in the range of $\sim -6$ to $\sim \SI{6}{nT}$, while total magnetic field did not go over \SI{10}{nT}. 
%Neither for temperature or magnetic field detected sudden changes of magnitude.

We were concerned of shock waves produced by rapid wind reaching slow wind, which also may produce TIDs and thus contaminating our GPS data, and may not be distinguishable from TIDs produced by the meteor passage. To check the presence of such shock waves, we estimate the relative velocity of solar wind of one day respect the previous one. The results are shown in figure \ref{fig:solar-relative-speed}, where we see that this velocity is almost constant and gives no chance for a fast stream reaching a slow one producing a shock wave.

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{../figures/caribbean-Dst-index.pdf}
    \caption{Dst index for 2019 June 22th. Data obtained from WDC for Geomagnetism, Kyoto DST index service.}
    \label{fig:Dst_index}
\end{figure*}

%\begin{figure}
%    \centering
%    \includegraphics[width=\linewidth]{figures/solar-wind-temperature-all.pdf}
%    \caption{Solar wind temperature in logarithmic scale from 2019-06-16 to event date. Each curve represent one day data.}
%    \label{fig:wind_temp}
%\end{figure}

%\begin{figure*}
%    \centering
%    \includegraphics[width=\linewidth]{figures/solar-magnetic-field-all.pdf}
%    \caption{Solar magnetic field components (colors) and total magnetic field (black) for the event date and the prior week. Each curve represent one day data.}
%    \label{fig:solar_mag_field}
%\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{../figures/solar_speed_all_wcs.pdf}
    \caption{Relative speed of solar wind at the event day and previous week respect the previous day, normalized with speed of sound. Each curve represents one day data.}
    \label{fig:solar-relative-speed}
\end{figure*}

\subsection{X-rays flux}

X rays are a clear source of ionization, they are generated mainly in the corona due to magnetospheric activity. A sudden increase of the flux or sudden variations may be a source of GW or giving appearance of GW. We investigated the X ray flux from the Sun at the event date and the previous week and collected data from the NOAA Space Prediction Center. %We show the results in figures \ref{fig:X-rays-1} to . 
X-rays flux remained constant in the time range we collected data.

%\begin{figure}
%    \centering
%    \includegraphics[width=\linewidth]{figures/20190618_xray.jpg}
%    \caption{X-ray flux obtained from NOAA Space Prediction Center, starting at Jun 16 00:00 hrs UT and ending at Jun 19 24:00 hrs UT. Color curves represent data from GOES satellites and the wavelength range: purple for GOES 14 in the range from 0.5 to \SI{4.0}{\AA}, yellow for GOES 14 in the range from 1.0 to \SI{8.0}{\AA}, blue for GOES 15 in the range from 0.5 to \SI{4.0}{\AA} and red for GOES 15 in the range from 0.5 to \SI{4.0}{\AA}. In all cases the X-ray flux remains constant.}
%    \label{fig:X-rays-1}
%\end{figure}

%\begin{figure}
%    \centering
%    \includegraphics[width=\linewidth]{figures/20190621_xray.jpg}
%    \caption{Same as figure \ref{fig:X-rays-1} but data starts at Jun 19 00:00 hrs and ends at Jun 21 24:00 hrs.}
%    \label{fig:X-rays-2}
%\end{figure}

%\begin{figure}
%    \centering
%    \includegraphics[width=\linewidth]{figures/20190622_xray.jpg}
%    \caption{Same as figures \ref{fig:X-rays-1} and \ref{fig:X-rays-2} but data starts at Jun 20 00:00 hrs and ends at Jun 22 24:00 hrs, which includes the event date.}
%    \label{fig:X-rays-3}
%\end{figure}

\subsection{dTEC and W index}

Finally we wanted to check the effects of solar cycle variations. The critical frequencies of reflection $f_c$ is proportional to the number of sunspots in the Sun, thus affecting our TEC measurements. Seasonal variations may be important too, since solar flux varies as the Earth revolves around the Sun. To measure these effects, we computed dTEC, defined as:

\begin{align}
    dTEC = \log_{10}\frac{TEC}{medTEC}
\end{align}

Where $TEC$ is the average TEC measurements of a certain day, while $medTEC$ is the median TEC of the 27 previous days, corresponding to the solar rotation period. dTEC was computed for the event day with each station. The W index reveals TEC behavior and the ionospheric perturbation level. In table \ref{tab:W-index} we show the W index levels, the corresponding dTEC and how perturbed is the ionosphere. %In this case and nearby stations, we noted that meteor fragmentation occurred briefly before local sunset, so solar terminator effects must be accomplished.

\begin{table}
    \centering
    \caption{W index values with their corresponding dTEC values and a brief description of the ionospheric state when thos index is obtained.}
    \begin{tabular}{lcr}\toprule
    dTEC & W index   & Ionospheric state     \\
    \hline
    $dTEC = 0$ & 0   & Reference quiet state \\
    $0<|dTEC|<0.046$ & $\pm 1$ & Quiet state \\
    $0.046<|dTEC|<0.155$ & $\pm 2$ & Weak perturbation \\
    $0.155<|dTEC|<0.301$ & $\pm 3$ & Moderated storm   \\
    $|dTEC|> 0.301$  & $\pm 4$ & Intense storm         \\\bottomrule
    \end{tabular}
    \label{tab:W-index}
\end{table}

We estimated the dTEC and the corresponding W index for all the GPS stations from we collected data. An example is shown in figure \ref{fig:dtec-boav}. In this figure we see how dTEC changes in time on the meteor date. The moment the meteor fragmented is shown with a black dashed line. The W index values are shown as the colored background.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../figures/dTEC_Windex_boav.pdf}
    \caption{dTEC and W index for station BOAV. dTEC is shown as the continuous blue curve. The corresponding W index ranges are shown as the colored backgrounds, from quiet state in blue to strong storm $(|W|=4)$ in red. The meteor fragmentation time is shown in vertical dashed line, and  as additional information the local sunrise and sunset in dashed blue lines.}
    \label{fig:dtec-boav}
\end{figure}

In this example and most of the stations we noted that the W index stands in negative values from -2 to -3 and normalizes to 1 after the 10 hrs. To understand the origin of this behavior we also included the local sunrise and sunset, and we found out that W index is quite negative at night, and normalizes after sunrise (local night occurs from 21-23 hrs of previous day to $\sim \SI{10}{hrs}$, check table \ref{tab:table-stations} for accurate information). Also found out that meteor fragmentation occurred a few hours before sunset, depending on the station. The high fluctuations in the dTEC may be attributable to the fact that at nighttime the logarithm is more susceptible to small variations since TEC is closer to zero. Fluctuations normalize after sunrise.

\subsection{Solar terminator}

If a meteoroid passage and explosion occurs at sunrise or sunset, the passage of the solar terminator should be taken into account since is one of the GW sources and cause some disturbances in the ionosphere \citep{Somsikov:2011}. In figure \ref{fig:solar_terminator} we see that meteor fragmentation occurred outside the solar terminator, but some GPS stations (KOUG and KOUR) are located very close to (sunset comes about 20 minutes after the fragmentation). In order to distinguish between the effects of the meteor and the solar terminator we detrended GPS data for the mentioned stations at dates prior of the meteor fall, those dates are close enough to guarantee that the sunset occurs almost at the same time. With this we can isolate the effects of the solar terminator and analyze its effects to check how they affect into our time series. Some results are shown in figure \ref{fig:solar_terminator_time_series} for station KOUG, PRNs 2 and 12. In these cases we see that the solar terminator does perturb the ionosphere, and its effects can bypass the detrending process, since they consist in wave-like variations of TEC. But these perturbations most of the time are weaker and distinguishable from the perturbations produced by the meteor passage, so we can safely assume that they don't affect in our detections. Even more, comparing time series from previous days we can help us to discriminate between time series with detected TID from others where only noise is recorded since some patterns in the time series can be detected. Time series too similar with the previous days can be classified as non detections.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../figures/BOAV-KOUG-KOUR-sunset.pdf}
    \caption{Solar terminator position for the most southern stations: BOAV (yellow shadow), KOUG and KOUR (gray shadow). The corresponding sunset times are labeled in the corresponding terminator line, and the sunset time difference between KOUG and KOUR stations is just 2 minutes. Sunset time in stations KOUR and KOUG occured 20 minutes later than meteor fragmentation.}
    \label{fig:solar_terminator}
\end{figure}

\begin{figure*}
    \centering
    \begin{tabular}{ccc}
    \includegraphics[width=0.3\linewidth]{../figures/KOUG_2019-06-19_PRN2.pdf} & \includegraphics[width=0.3\linewidth]{../figures/KOUG_2019-06-20_PRN2.pdf}& \includegraphics[width=0.3\linewidth]{../figures/koug-sTEC_series_PRN_2.pdf} \\
\includegraphics[width=0.3\linewidth]{../figures/KOUG_2019-06-19_PRN12.pdf} & \includegraphics[width=0.3\linewidth]{../figures/KOUG_2019-06-20_PRN12.pdf} & \includegraphics[width=0.3 \linewidth]{../figures/koug-sTEC_series_PRN_12.pdf}
    \end{tabular}
    \caption{Detrended sTEC time series for station KOUG for the days 2019-06-19, 2019-06-20 and 2019-06-22 (three days before meteor fall, two days and the meteor fall date, from left to right). The satellite receiver LOS with PRN 2 is in top, and the LOS with PRN 12 is in bottom.}
    \label{fig:solar_terminator_time_series}
\end{figure*}

\subsection{sTEC time series}

We detrended the RINEX data we obtained for all stations and analyzed separately each satellite-receiver time series in order to find by visual inspection wave-like features. We must be careful when making conclusions about the presence of TIDs produced by the bolide in the cases when the sunset and the fragmentation occurred in a short period of time. We separated those time series where we detected the presence of such features (see \S \ref{ssec:Morlet}), from all the others, which could be too noisy, too few data, etc. A significant sample of about 10\% of all the time series we have are shown in figures \ref{fig:sTEC-series}-\ref{fig:sTEC-series3}.

\begin{figure*}
    \centering
    \begin{tabular}{cc}
    \includegraphics[width=0.45\linewidth]{../figures/cn04-sTEC_series_PRN_6-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/cn04-sTEC_series_PRN_6.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/cn40-sTEC_series_PRN_12-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/cn40-sTEC_series_PRN_12.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/ttsf-sTEC_series_PRN_2-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/ttsf-sTEC_series_PRN_2.pdf}\\
%    \includegraphics[width=0.3\linewidth]{}  \includegraphics[width=0.3\linewidth]{}\\
    \end{tabular}
    \caption{sTEC time series for stations where TIDs are likely to be detected. In the left panels we show the time series for the previous day of meteor fall, and in the right panels the time series for the meteor fall date.}
    \label{fig:sTEC-series}
\end{figure*}

\begin{figure*}
    \centering
    \begin{tabular}{cc}
    \includegraphics[width=0.45\linewidth]{../figures/ttuw-sTEC_series_PRN_2-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/ttuw-sTEC_series_PRN_2.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/boav-sTEC_series_PRN_2-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/boav-sTEC_series_PRN_2.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/boav-sTEC_series_PRN_12-previous.pdf}  \includegraphics[width=0.45\linewidth]{../figures/boav-sTEC_series_PRN_12.pdf}\\
    \end{tabular}
    \caption{Continuation of figure \ref{fig:sTEC-series}}
    \label{fig:sTEC-series2}
\end{figure*}

\begin{figure*}
    \centering
    \begin{tabular}{cc}
    \includegraphics[width=0.45\linewidth]{../figures/koug-sTEC_series_PRN_2-previous.pdf} & \includegraphics[width=0.45\linewidth]{../figures/koug-sTEC_series_PRN_2.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/koug-sTEC_series_PRN_12-previous.pdf} & \includegraphics[width=0.45\linewidth]{../figures/koug-sTEC_series_PRN_12.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/gre1-sTEC_series_PRN_2-previous.pdf} & \includegraphics[width=0.45\linewidth]{../figures/gre1-sTEC_series_PRN_2.pdf}
    \end{tabular}
    \caption{Continuation of figures \ref{fig:sTEC-series} and \ref{fig:sTEC-series2}.}
    \label{fig:sTEC-series3}
\end{figure*}

In order to check which stations actually observed the TIDs generated by the bolide fragmentation, we proceeded to learn which stations were located near the bolide trajectory at the event time or the next few hours. Stations located far of the bolide trajectory are more likely to have detected other phenomena not related with the bolide passage. Since we are using sTEC measurements, we want to have a picture of the line of sight we are considering in our sTEC measurements. To do such task we will compare the bolide trajectory with all of the satellites in local coordinates (azimuth and elevation) to see if at least one was close enough to the bolide trajectory and its elevation. Such diagrams are shown in figures  for the same stations of figures \ref{fig:sTEC-series} - \ref{fig:sTEC-series3}. Ideally if the satellite trajectory intersects the meteor trajectory in our TEC series we see the TEC variations in the line of sight where the meteor passed. But is also possible that a slightly distant satellite detected some TIDs that propagated away from the source.

\begin{figure*}
    \begin{tabular}{cc}
      \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-boav-polar-hlght.pdf}   & \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-cn04-polar-hlght.pdf} \\
            \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-cn40-polar-hlght.pdf}   & \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-gre1-polar-hlght.pdf} \\
     \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-koug-polar-hlght.pdf}   & \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-ttsf-polar-hlght.pdf} \\
    \end{tabular}
    \label{fig:azimuth-elevations-maps-1}
    \caption{Azimuth-Elevation maps for GPS stations which presumably detected TIDs. In colored curves we show the satellites trajectories with their respective label. The black dots are the meteor trajectory using the GLM data and the magenta dashed curve represent the meteor trajectory using the velocity parameters from table \ref{tab:Meteor-parameters}.}
\end{figure*}

\begin{figure*}
    \centering
    \begin{tabular}{cc}
    \includegraphics[width=0.45\linewidth]{../figures/boav_satellites_positions_terminator_21-25-48.pdf} & \includegraphics[width=0.45\linewidth]{../figures/cn04_satellites_positions_terminator_21-25-48.pdf}\\
    \includegraphics[width=0.45\linewidth]{../figures/cn40_satellites_positions_terminator_21-25-48.pdf} & \includegraphics[width=0.45\linewidth]{../figures/gre1_satellites_positions_terminator_21-25-48.pdf} \\
    \includegraphics[width=0.45\linewidth]{../figures/koug_satellites_positions_terminator_21-25-48.pdf} & \includegraphics[width=0.45\linewidth]{../figures/ttsf_satellites_positions_terminator_21-25-48.pdf}
    \end{tabular}
    \caption{Position of IPP in the satellite-receiver LoS for the same GPS stations as figure \ref{fig:azimuth-elevations-maps-1}. The GLM data are shown in magenta dots, the fragmentation position in a red star and the estimated trajectory from 1 hour before fragmentation to a few seconds after fragmentation is shown in green dashed line. The position of the GPS station is shown with a blue triangle. The solar terminator appears in BOAV and KOUG stations as a blue shadow.}
    \label{fig:satellites-and-terminator}
\end{figure*}

% The mathematical proccedure to change the GLM data and the estimated trajectory, using the parameters from table \ref{tab:Meteor-parameters}. 
%\subsection{Wavelet power spectrum}

%For each TEC series like figure \ref{fig:detrending-example} we computed $|W_n(s)|^2$ to find any wave-like features in any of the TEC series, where $s$ is the wavelet scale (somehow is the analogous to the wavelength). The presence of this features allow us to trace the TEC perturbations produced by the meteor. Examples are shown in figure \ref{fig:power-spectrums}. Due to the fact we are working with finite time series, edge effects become important at the beginning or the end of the time series, and when the wavelet scale is similar or greater than the time series length. The limit when these errors become important is called Cone of Influence (COI), the COI is shown as a white dashed line in figure \ref{fig:power-spectrums}. At a closer look of this spectra is clear that in some cases the wavelet spectra in the previous day is more intense than the event day. This happens because no TEC perturbations was really detected, but instead noise appears as wavelets. This is an indicator that the TEC perturbances either propagate to other location or it is too faint to be detectable.

%\begin{figure*}
%  \begin{tabular}{cc}
%  \includegraphics[width=0.5\linewidth]{./figures/cn05-PRN2-contour}  & %\includegraphics[width=0.5\linewidth]{./figures/cn27-PRN2-contour}\\
%  \includegraphics[width=0.5\linewidth]{./figures/crlr-PRN2-contour}  & %\includegraphics[width=0.5\linewidth]{./figures/crse-PRN2-contour}
%  \end{tabular}
%  \label{fig:power-spectrums}
%  \caption{Examples of power spectrums for event USG-09, PRN 2. Top left: Station CN05. Top Right: Station CN27. Bottom left: station CRLR. Bottom right: station CRSE. In each figure the left panel corresponds to the event day and the right panel corresponds to the previous day of the event. The white dashed lines correspond to the Cone of Influence, where all the wavelet spectrum below is subject to error.}
%\end{figure*}

### 2022-12-03 Dst_index.py
Update .gitignore with output files
Update python scripts, modify output of azimuth elevation maps to png
because pdfs were too heavy. Update jupyter notebooks

@@ -21,7 +21,7 @@ cmd_args = parser.parse_args()
 date = cmd_args.date
 year, month, day = date.split("-")
 datafile = "Dst-index-"+month+"-"+year+".txt"
-directory = "./Dst index/" 
+directory = "./Dst_index/" 
 f = open(directory+datafile, "r")
 
 # Extract information from file
@@ -41,7 +41,7 @@ Tabdata= Table.read(data, format="ascii")
 Dst_index = []
 
 mask = Tabdata["col1"]==int(day)
-maskp = Tabdata["col1"]==int(day) - 1
+#maskp = Tabdata["col1"]==int(day) - 1
 # Set the time array for plotting
 
 time = time_str.split()
@@ -65,5 +65,7 @@ plt.text(0, 85, day+" "+h3.lstrip())
 plt.text(15, 85, h1.lstrip())
 plt.xlabel("Time (UT, hours)")
 plt.ylabel("Dst Index (nT)")
+plt.gcf().set_size_inches(10, 3)
+plt.tight_layout()
 outfile = datafile.replace(".txt", ".pdf")
 plt.savefig(directory+outfile)

### 2022-12-03 TEC_detrender.py

@@ -23,24 +23,24 @@ def next_contact_point(x, y, x0, y0):
     output:
     (xf, yf): coordinates of the next contact point
     """
-    # Define region of interest
+	# Define region of interest
     R0 = 1 # Radius of the barrell roll. Unitary radius works pretty well
     ROI = (x > x0) & (x < x0 + 2*R0)
-    # Delta_x and delta_y are the separation between the elements which belong to the ROI and (x0, y0)
+	# Delta_x and delta_y are the separation between the elements which belong to the ROI and (x0, y0)
     delta_x = x[ROI]-x0
     delta_y = y[ROI]-y0
 
     try:
-	  # calculating important angles
+	      # calculating important angles
         theta = np.arctan2(delta_y, delta_x)
         cos_alpha = np.sqrt(delta_x**2 + delta_y**2)/(2*R0) 
         delta = np.arcsin(cos_alpha) - theta
-	  # Selecting the Next Contact Point (NCP)
+	      # Selecting the Next Contact Point (NCP)
         NCP = delta == min(delta) # The next contact point has the smallest angular distance delta
         xf, yf = x0+delta_x[NCP][0], y0+delta_y[NCP][0]
     except ValueError: # this happens because ROI is empty
         xf, yf = x[~ROI & (x>x0)][0], y[~ROI & (x>x0)][0] #The element we will use as next contact point
-							    # is the first outside the ROI and greater than x0
+								# is the first outside the ROI and greater than x0
     return xf, yf
 
 def free_dep_signal(brc_x, brc_y, x, y):
@@ -101,41 +101,46 @@ def split_PRN(t, TEC):
     for i, dt in enumerate(gradient_t):
         if dt > 0.01: # 0.01 is like 10 times the regular GPS frequency
             index_discontinuity.append(i) # collect the indices where time gradient is big enough
-    split_t = np.split(t, index_discontinuity)
-    split_TEC = np.split(TEC, index_discontinuity)
-    output_t = []
-    output_TEC =[]
-    for s, tec in zip(split_t, split_TEC):
-        if len(s) > 20: #if the subarray contain too few elements will be discarded
-            output_t.append(s)
-            output_TEC.append(tec)
-    return output_t, output_TEC
+        split_t = np.split(t, index_discontinuity)
+        split_TEC = np.split(TEC, index_discontinuity)
+        output_t = []
+        output_TEC =[]
+        for s, tec in zip(split_t, split_TEC):
+            if len(s) > 20: #if the subarray contain too few elements will be discarded
[…]

### 2022-12-03 TEC_series.py

@@ -5,58 +5,98 @@ import matplotlib.pyplot as plt
 import glob
 from statistics import mode
 import seaborn as sns
-parser = argparse.ArgumentParser(
-	   description=""" Choose a file to work""")
+parser = argparse.ArgumentParser(description=""" Choose a file to work""")
 
 
 parser.add_argument('--date', type=str, default='2000-01-01',
 				      help='Choose date. Format: yyyy-mm-dd')
 
-
-#parser.add_argument("--filterhigh", type=float, default=30, 
-#			    help="Filter the upper time interval of the TEC curve (in minutes)")
-#parser.add_argument("--filterlow", type=float, default=10, 
-#			    help="Filter the lower time interval of the TEC curve (in minutes)")
+parser.add_argument("--station", type=str, default="cn05", help="Choose station")
+parser.add_argument("--PRNs", type=str, default="1", help="Choose PRNs to graph (separate with commas)")
 parser.add_argument("--previous", action="store_true", help="Choose previous day data")
-parser.add_argument("--sets", type=str, help="Choose between sets of stations")
+parser.add_argument("--Next", action="store_true", help="Choose next day data")
+parser.add_argument("--sets", type=str, default="1", help="Choose between sets of stations")
+parser.add_argument("--allp", action="store_true", help="Use all PRNs in graph")
+parser.add_argument("--sTEC", action="store_true", help="Use sTEC data")
 cmd_args = parser.parse_args()
 date = cmd_args.date
-#filter_high = cmd_args.filterhigh
-#filter_low = cmd_args.filterlow
 previous = cmd_args.previous
+Next = cmd_args.Next
 stations_set = cmd_args.sets
 set_folder = "/set"+stations_set
 directory = "./data/"+date+set_folder
 outdir = "./TEC_series/"+date+set_folder
-infile = glob.glob(directory+"/*.csv")[0]
-Date, time, residual = infile.split("_")
+prn_str = cmd_args.PRNs
+s = cmd_args.station.lower()
+allp = cmd_args.allp
+sTEC = cmd_args.sTEC
+outlabel = ""
 if previous:
-    infile = glob.glob(directory+"/previous/*.csv")[0]
[…]

### 2022-12-03 TEC_series_iplots.py

@@ -1,0 +1,87 @@
+#In this program we will recover the former TEC_series.py script, since that scipt now
+#plots the TEC series for several PRNs in a single graph, and I still need to see the individual graphs.
+
+import pandas as pd
+import argparse 
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+from statistics import mode
+import seaborn as sns
+parser = argparse.ArgumentParser(
+	     description=""" Choose a file to work""")
+
+
+parser.add_argument('--date', type=str, default='2000-01-01',
+					help='Choose date. Format: yyyy-mm-dd')
+
+
+parser.add_argument("--previous", action="store_true", help="Plot previous day data")
+parser.add_argument("--Next", action="store_true", help="Plot next day data")
+parser.add_argument("--sets", type=str, help="Choose between sets of stations")
+parser.add_argument("--sTEC", action="store_true", help="Use sTEC data")
+cmd_args = parser.parse_args()
+date = cmd_args.date
+previous = cmd_args.previous
+Next = cmd_args.Next
+stations_set = cmd_args.sets
+sTEC = cmd_args.sTEC
+set_folder = "/set"+stations_set
+directory = "./data/"+date+set_folder
+outdir = "./TEC_series/"+date+set_folder
+outlabel = ""
+if previous:
+    directory = "./data/{}{}/previous".format(date, set_folder)
+    outlabel = "-previous"
+elif Next:
+    directory = "./data/{}{}/next".format(date, set_folder)
+    outlabel = "-next"
+if sTEC:
+    infile = glob.glob(directory+"/*sTEC.csv")[0]
+else:
+    infile = glob.glob(directory+"/*-TEC.csv")[0]
+Date, time, residual = infile.split("_")
+#if previous:
+#    infile = glob.glob(directory+"/previous/*.csv")[0]
+#    outdir = "./TEC_series/"+date+set_folder+"/previous"
+# ****************************** Read data file ************************************************
+
+csv_file = pd.read_csv(infile)
+
+station_array = np.unique(csv_file["Station"])
+time_hours = float(time)
+# fh = 130
+# fl = -60
+# ws = fh-fl
+sns.set_style("whitegrid")
+
+#if Next:
+#    outlabel = "next"
+#elif previous:
+#    outlabel = "previous"
+#else:
+#    outlabel = ""
[…]

### 2022-12-03 az-elevation.py

@@ -1,0 +1,209 @@
+# The purpose of this program is to evaluate the azimuth-elevation plots for all satellites which could make contact with
+#our GPS stations and took data of TEC. Also we now seek to constrain the TIDs velocities in order to find a a possible range
+
+import argparse
+import numpy as np
+from astropy.table import Table
+import matplotlib.pyplot as plt
+import glob
+import pandas as pd
+import seaborn as sns
+
+def Change_coords(slon, slat, lon, lat):
+    """
+    Change coordinate from Latitude-Longitude reference system to local Azimuth-Elevation system
+    Inputs:
+      slon, slat: Coordinates of station (in degrees)
+      lon, lat: Coordinates of object (can be an scalar or array, in degrees)
+    Output: AZ, ELE, Coordinates of object in local reference system (in degrees)
+    """
+    HA = slon - lon
+    sin_ELE = np.sin(np.radians(lat))*np.sin(np.radians(slat))+np.cos(np.radians(lat))*np.cos(np.radians(slat))*np.cos(np.radians(HA))
+    cos_ELE = np.sqrt(1.-sin_ELE**2)
+    cosA = (np.sin(np.radians(lat))-sin_ELE*np.sin(np.radians(slat)))/(cos_ELE*np.cos(np.radians(slat)))
+    ELE = np.degrees(np.arcsin(sin_ELE))
+    A = np.degrees(np.arccos(cosA))
+    AZ = []
+    for a, ha in zip(A, HA):
+        pi_mask = np.sin(np.radians(ha)) <0
+        if pi_mask:
+            az = a
+        else:
+            az = 360. - a
+        AZ.append(az)
+    return np.array(AZ), ELE
+
+def change_coords2(slon, slat, lon, lat, h):
+    """
+    Change coordinate from Latitude-Longitude reference system to local Azimuth-Elevation system
+    Inputs:
+      slon, slat: Coordinates of station (in degrees)
+      lon, lat: Coordinates of object (can be an scalar or array, in degrees)
+      h: bolide height (in kilometers)
[…]

### 2022-12-03 az-elevation2.py

@@ -1,0 +1,199 @@
+# This program is a copy of az-elevation.py with the difference that in this case we highlight the satellite positions where TIDs
+# were detected in hope of tracing the TIDs origin and propagation
+
+import argparse
+import numpy as np
+from astropy.table import Table
+import matplotlib.pyplot as plt
+import glob
+import pandas as pd
+import seaborn as sns
+
+def Change_coords(slon, slat, lon, lat):
+    """
+    Change coordinate from Latitude-Longitude reference system to local Azimuth-Elevation system
+    Inputs:
+      slon, slat: Coordinates of station (in degrees)
+      lon, lat: Coordinates of object (can be an scalar or array, in degrees)
+    Output: AZ, ELE, Coordinates of object in local reference system (in degrees)
+    """
+    HA = slon - lon
+    sin_ELE = np.sin(np.radians(lat))*np.sin(np.radians(slat))+np.cos(np.radians(lat))*np.cos(np.radians(slat))*np.cos(np.radians(HA))
+    cos_ELE = np.sqrt(1.-sin_ELE**2)
+    cosA = (np.sin(np.radians(lat))-sin_ELE*np.sin(np.radians(slat)))/(cos_ELE*np.cos(np.radians(slat)))
+    ELE = np.degrees(np.arcsin(sin_ELE))
+    A = np.degrees(np.arccos(cosA))
+    AZ = []
+    for a, ha in zip(A, HA):
+        pi_mask = np.sin(np.radians(ha)) <0
+        if pi_mask:
+            az = a
+        else:
+            az = 360. - a
+        AZ.append(az)
+    return np.array(AZ), ELE
+
+def change_coords2(slon, slat, lon, lat, h):
+    """
+    Change coordinate from Latitude-Longitude reference system to local Azimuth-Elevation system
+    Inputs:
+      slon, slat: Coordinates of station (in degrees)
+      lon, lat: Coordinates of object (can be an scalar or array, in degrees)
+      h: bolide height (in kilometers)
+    Output: AZ, ELE, Coordinates of object in local reference system (in degrees)
[…]

### 2022-12-03 background-average.py

@@ -1,59 +1,56 @@
 import numpy as np
 from astropy.table import Table
 import glob
-import statistics as stats
 import argparse
 
-# objetivo del programa: Obtener la curva TEC vs tiempo en diferentes fechas previas al evento
-# para una misma estaci髇 y obtener ~~un promedio~~ la mediana del comportamiento del TEC y restarlo a los datos
-# Observar si hay alguna fluctuci髇 inusual que ser韆 nuestra detecci髇.
+# objetivo del programa: Obtener la curva TEC vs tiempo para 27 d铆as previos al evento
+# para una misma estaci贸n y recopilar los datos de todas las curvas TEC en un mismo archivo
 
+# Obtenci贸n de par谩metros de l铆nea de comandos.
+# - Station: Estaci贸n de GPS de la cual recopilaremos las curvas TEC
+# - date: Fecha en la cual se detect贸 el meteoro
+# - sets: set de estaciones donde se encuentra la estaci贸n que deseamos
 
 parser = argparse.ArgumentParser(
-    description=""" Choose a file to work""")
+	description=""" Choose a file to work""")
 
 parser.add_argument("--station", type=str,
-                    default="kvtx",
-                    help=" Choose station")
+			default="kvtx",
+			help=" Choose station")
 
 parser.add_argument('--date', type=str, default='2000-01-01',
-                    help='Choose date. Format: yyyy-mm-dd')
+			help='Choose date. Format: yyyy-mm-dd')
 
-
+parser.add_argument("--sets", type=str, default="1", help="Choose a set of stations")
 
 
 cmd_args = parser.parse_args()
 date = cmd_args.date
 station = cmd_args.station
+set_folder = cmd_args.sets
 
-directory = "./data/"+date
-b_data = glob.glob(directory+"/background/"+station+"*.Std")
-
-
-
-Tec_Matrix = []
-
+directory = "./data/{}/set{}/previous/".format(date, set_folder) # Directorio del cual extraemos las curvas TEC de
+                                                                 # los d铆as previos
+b_data = glob.glob(directory+"{}*.Std".format(station))
+outtab = Table(names=("FileID", "time", "TEC", "sigma_TEC")) # Iniciamos tabla de salida, donde recopilaremos todas 
+                                                             #las curvas TEC
+outdir = "./data/{}/set{}/".format(date, set_folder)         # Directorio de la tabla de salida
[…]

### 2022-12-03 background_average2.py

@@ -1,0 +1,160 @@
+# Este programa lee el archivo creado por background_average.py, calcula la mediana del TEC, el dTEC y crea tres gráficas:
+# 1. Grafica las curvas TEC de los 27 días y la mediana.
+# 2. Compara la mediana con la curva TEC del día del evento
+# 3. Curva de dTEC vs tiempo y en fondo de colores los correspondientes valores del indice W.
+
+import argparse
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+from astropy.table import Table
+from statistics import median
+import pandas as pd
+
+def julian_day(Date):
+    """
+    Finds the julian day of event, needed to find correctly the file name
+    of the *.Std TEC data
+    """
+    year, month, sday = Date.split("-")
+    day = float(sday)
+    month_dict = {"01":[0, 0], "02":[31, 31], "03":[31+28, 31+29], "04":[31+28+31, 31+29+31], 
+                  "05":[31+28+31+30, 31+29+31+30], "06":[31+28+31+30+31, 31+29+31+30+31], 
+                  "07":[31+28+31+30+31+30, 31+29+31+30+31+30], "08":[31+28+31+30+31+30+31, 31+29+31+30+31+30+31], 
+                  "09":[31+28+31+30+31+30+31+31, 31+29+31+30+31+30+31+31], 
+                  "10":[31+28+31+30+31+30+31+31+30, 31+29+31+30+31+30+31+31+30], 
+                  "11":[31+28+31+30+31+30+31+31+30+31, 31+29+31+30+31+30+31+31+30+31], 
+                  "12":[31+28+31+30+31+30+31+31+30+31+30, 31+29+31+30+31+30+31+31+30+31+30]}
+    bisiesto = {"2000":True, "2001":False, "2002":False, "2003":False, "2004":True, "2005":False, 
+                "2006":False, "2007":False, "2008":True, "2009":False, "2010":False, "2011":False,
+                "2012":True, "2013":False, "2014":False, "2015":False, "2016":True, "2017":False, 
+                "2018":False, "2019":False, "2020":True, "2021":False}
+    
+    if bisiesto[year]:
+        julian = day + month_dict[month][1]
+    else:
+        julian = day + month_dict[month][0]
+
[…]

### 2022-12-03 join_time_series.py

@@ -1,0 +1,132 @@
+# This program has the purpose to attach two time series from adjacent dates from an
+# specific station and an specific PRN and make a single time series.
+# Starts as a clone of the time series grapher but I will start making changes
+
+import pandas as pd
+import argparse 
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+from statistics import mode
+import seaborn as sns
+parser = argparse.ArgumentParser(
+	       description=""" Choose a file to work""")
+
+
+parser.add_argument('--date', type=str, default='2000-01-01',
+					  help='Choose date. Format: yyyy-mm-dd')
+
+
+parser.add_argument("--previous", action="store_true", help="Join with previous day data")
+parser.add_argument("--Next", action="store_true", help="Join with next day data")
+parser.add_argument("--sets", type=str, help="Choose between sets of stations")
+parser.add_argument("--sTEC", action="store_true", help="Use sTEC data")
+parser.add_argument("--PRNs", type=str, default="1", help="Select PRNs which we need to join with another day")
+parser.add_argument("--station", type=str, default="bara", help="Select station")
+
+cmd_args = parser.parse_args()
+date = cmd_args.date
+previous = cmd_args.previous
+Next = cmd_args.Next
+stations_set = cmd_args.sets
+sTEC = cmd_args.sTEC
+set_folder = "/set"+stations_set
+directory = "./data/"+date+set_folder
+outdir = "./TEC_series/"+date+set_folder
+PRNs = cmd_args.PRNs
+station = cmd_args.station
+if sTEC:
+    infile = glob.glob(directory+"/*sTEC.csv")[0]
+    title_label = "Detrended slant TEC series for individual satellites. Station {}".format(station.upper())
+    g_extention = "/{}-joint-sTEC_series.pdf".format(station)
+else:
+    infile = glob.glob(directory+"/*-TEC.csv")[0]
+    title_label = "Detrended vTEC series for individual satellites. Station {}".format(station.upper())
+    g_extention = "/{}-joint-TEC_series.pdf".format(station)
+
+
+
[…]

### 2022-12-03 solar_wind.py

@@ -1,0 +1,131 @@
+# In this program we will plot some solar wind properties
+# in netCDF format. 
+
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+import netCDF4 as nc
+import argparse
+import glob
+
+parser = argparse.ArgumentParser(description = "Choose a file to work")
+parser.add_argument("--edate", type=str, default="2019-06-22", help="Choose event date")
+parser.add_argument("--date", type=str, default="2019-06-22", help="Choose data date")
+
+cmd_args = parser.parse_args()
+edate = cmd_args.edate
+date = cmd_args.date
+year, month, day = date.split("-")
+
+#Load netCDF files
+
+directory = "./solar_data/{}/".format(edate)
+format_dir = {"fn1":"f1m", "fn2":"m1m"}
+fn1 = directory+"oe_{}_dscovr_s{}{}{}*.nc".format(format_dir["fn1"], year, month, day)
+fn2 = directory+"oe_{}_dscovr_s{}{}{}*.nc".format(format_dir["fn2"], year, month, day)
+f1 = glob.glob(fn1)[0]
+f2 = glob.glob(fn2)[0]
+ds1 = nc.Dataset(f1)
+ds2 = nc.Dataset(f2)
+
+#Extract relevant data
+
+  # Time column is measured since 1970-01-01 and is measured in miliseconds, so we need to 
+  # convert to hours and make sure we first element in our arrays is 0:00:00 
+t_raw1 = ds1["time"][:]
+t_raw2 = ds2["time"][:]
+time1 = 1e-3*(t_raw1 - t_raw1[0])/3600.
+time2 = 1e-3*(t_raw2 - t_raw2[0])/3600.
+p_speed = ds1["proton_speed"][:]
+p_density = ds1["proton_density"][:]
+p_temperature = ds1["proton_temperature"][:]
+proton_mass = 1.67
+units_conversion = 1e-6 # includes ten power of proton mass and conversion factors so the pressure is measured 
+                        # in nano pascals
+p_dyn_pressure = 0.5*proton_mass*p_density*p_speed**2*units_conversion # dynamic pressure is not included with
+                                                                       # date: must be estimated
+
[…]

### 2022-12-03 wavelet_power.py

@@ -1,5 +1,7 @@
 #We used a github repository to analyze the wavelets spectrum base on Torrence & Compo 1998
 # Available at https://github.com/chris-torrence/wavelets
+#This program is intended to calculate coherence spectrums between two time series, we must select them by
+# giving the program the corresponding station and satellite which collected the data
 import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
@@ -23,99 +25,130 @@ parser.add_argument('--date', type=str, default='2000-01-01',
 parser.add_argument("--frequency", type=float, default=15,
 			    help="Sampling time (in seconds)")
 
-parser.add_argument("--sets", type=str, help="Choose between sets of stations")
+parser.add_argument("--sets1", type=str, default="1", help="Choose between sets of stations (first data set)")
+parser.add_argument("--sets2", type=str, default="1", help="Choose between sets of stations (second data set)")
+parser.add_argument("--station1", type=str, default="bara", help="Choose first station")
+parser.add_argument("--station2", type=str, default="bara", help="Choose second station")
+parser.add_argument("--PRN1", type=int, default=1, help="Select the first satellite PRN")
+parser.add_argument("--PRN2", type=int, default=1, help="Select the second satellite PRN")
+parser.add_argument("--previous", action="store_true", help="Use previous day data")
+parser.add_argument("--Next", action="store_true", help="Use next day data")
+parser.add_argument("--sTEC", action="store_true", help="Use sTEC data")
 cmd_args = parser.parse_args()
 date = cmd_args.date
 dt = cmd_args.frequency/3600.
-stations_set = cmd_args.sets
-set_folder = "/set"+stations_set
-directory ="./data/"+date+set_folder
-outdir = "./TEC_power_spectrum/"+date+set_folder
-pdirectory = "./data/"+date+set_folder+"/previous"
-infile = glob.glob(directory+"/*.csv")[0]
-pinfile = glob.glob(pdirectory+"/*.csv")[0]
-df = pd.read_csv(infile)
[…]

### 2022-12-03 wavelet_power2.py

@@ -28,67 +28,98 @@ parser.add_argument("--frequency", type=float, default=15,
 parser.add_argument("--sets", type=str, help="Choose between sets of stations")
 parser.add_argument("--station", type=str, help="Choose station")
 parser.add_argument("--PRN", type=int, help="Choose PRN")
+parser.add_argument("--sTEC", action="store_true", help="Choose sTEC data")
+parser.add_argument("--previous", action="store_true", help="Use previous day data")
+parser.add_argument("--Next", action="store_true", help="Use next day data")
 cmd_args = parser.parse_args()
 date = cmd_args.date
 dt = cmd_args.frequency/3600.
 stations_set = cmd_args.sets
 set_folder = "/set"+stations_set
-station = cmd_args.station
+station = cmd_args.station.lower()
 PRN = cmd_args.PRN
+previous = cmd_args.previous
+Next = cmd_args.Next
 directory ="./data/"+date+set_folder
-outdir = "./paper/figures"
-pdirectory = "./data/"+date+set_folder+"/previous"
+outlabel=""
+if previous:
+    directory = directory +"/previous"
+    outlabel = "-previous"
+elif Next:
+    directory = directory + "/Next"
+    outlabel = "-next"
+outdir = "./power_spec/{}/set{}/".format(date,stations_set)
+#pdirectory = "./data/"+date+set_folder+"/previous"
 infile = glob.glob(directory+"/*.csv")[0]
-pinfile = glob.glob(pdirectory+"/*.csv")[0]
+#pinfile = glob.glob(pdirectory+"/*.csv")[0]
 df = pd.read_csv(infile)
-pdf = pd.read_csv(pinfile)
+#pdf = pd.read_csv(pinfile)
 Date, time, residuals = infile.split("_") 
-start_time = float(time)
+#start_time = float(time)
 levels = 20
 norm = MidpointNormalize(midpoint=0)
-
+sTEC = cmd_args.sTEC
 fh = 130
 fl = -60
 ws = fh-fl
 
 prn_mask = df["PRN"] == PRN
-p_prn_mask = pdf["PRN"] == PRN
+#p_prn_mask = df["PRN"] == PRN
[…]

### 2022-12-03 paper/sTEC-time_series.tex
Synchronize MDPI paper with overleaf

@@
     \centering
+    \begin{adjustwidth}{-\extralength}{0cm}
     \includegraphics[width=\linewidth]{../figures/caribbean-Dst-index.pdf}
+    \end{adjustwidth}
     \caption{Dst index for 2019 June 22th. Data obtained from WDC for Geomagnetism, Kyoto DST index service.}
@@
     \centering
+    \begin{adjustwidth}{-\extralength}{0cm}
     \includegraphics[width=\linewidth]{../figures/solar_speed_all_wcs.pdf}
+    \end{adjustwidth}
     \caption{Relative speed of solar wind at the event day and previous week respect the previous day, normalized with speed of sound. Each curve represents one day data.}
@@
 Seasonal variations may be important too, since solar flux varies as the Earth revolves around the Sun.
-To measure these effects, we computed dTEC, defined as:
+To measure these effects, we computed dTEC, defined as \citep{Gulyaeva:2008}:
 
@@
     \centering
-    \caption{W index values with their corresponding dTEC values and a brief description of the ionospheric state when thos index is obtained.}
+    \caption{W index values with their corresponding dTEC values and a brief description of the ionospheric state when those index is obtained \citep{Gulyaeva:2008}.}
     \begin{tabular}{lcr}\toprule
@@
     \centering
+    \begin{adjustwidth}{-\extralength}{0cm}
     \includegraphics[width=\linewidth]{../figures/dTEC_Windex_boav.pdf}
+    \end{adjustwidth}
     \caption{dTEC and W index for station BOAV.
@@
     \centering
-    \includegraphics[width=\linewidth]{../figures/BOAV-KOUG-KOUR-sunset.pdf}
+    \begin{adjustwidth}{-\extralength}{0cm}
+    \includegraphics[width=\linewidth]{../figures/BOAV-KOUG-KOUR-sunset.png}
+    \end{adjustwidth}
     \caption{Solar terminator position for the most southern stations: BOAV (yellow shadow), KOUG and KOUR (gray shadow).
@@
     \centering
+    \begin{adjustwidth}{-\extralength}{0cm}
     \begin{tabular}{ccc}
-    \includegraphics[width=0.3\linewidth]{../figures/KOUG_2019-06-19_PRN2.pdf} & \includegraphics[width=0.3\linewidth]{../figures/KOUG_2019-06-20_PRN2.pdf}& \includegraphics[width=0.3\linewidth]{../figures/koug-sTEC_series_PRN_2.pdf} \\
-\includegraphics[width=0.3\linewidth]{../figures/KOUG_2019-06-19_PRN12.pdf} & \includegraphics[width=0.3\linewidth]{../figures/KOUG_2019-06-20_PRN12.pdf} & \includegraphics[width=0.3 \linewidth]{../figures/koug-sTEC_series_PRN_12.pdf}
+    \includegraphics[width=0.33\linewidth]{../figures/KOUG_2019-06-19_PRN2.pdf} & \includegraphics[width=0.33\linewidth]{../figures/KOUG_2019-06-20_PRN2.pdf}& \includegraphics[width=0.33\linewidth]{../figures/koug-sTEC_series_PRN_2.pdf} \\
+    \includegraphics[width=0.33\linewidth]{../figures/KOUG_2019-06-19_PRN12.pdf} & \includegraphics[width=0.33\linewidth]{../figures/KOUG_2019-06-20_PRN12.pdf} & \includegraphics[width=0.33\linewidth]{../figures/koug-sTEC_series_PRN_12.pdf}
     \end{tabular}
+    \end{adjustwidth}
     \caption{Detrended sTEC time series for station KOUG for the days 2019-06-19, 2019-06-20 and 2019-06-22 (three days before meteor fall, two days and the meteor fall date, from left to right).
@@
     \centering
+    \begin{adjustwidth}{-\extralength}{0cm}
     \begin{tabular}{cc}
@@
     \end{tabular}
+    \end{adjustwidth}
     \caption{sTEC time series for stations where TIDs are likely to be detected.
@@
     \end{tabular}
+    \end{adjustwidth}
     \caption{Continuation of figure \ref{fig:sTEC-series}}
@@
     \end{tabular}
+    \end{adjustwidth}
     \caption{Continuation of figures \ref{fig:sTEC-series} and \ref{fig:sTEC-series2}.}
@@
 \begin{figure*}
+\begin{adjustwidth}{-\extralength}{0cm}
     \begin{tabular}{cc}
-      \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-boav-polar-hlght.pdf}   & \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-cn04-polar-hlght.pdf} \\
-            \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-cn40-polar-hlght.pdf}   & \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-gre1-polar-hlght.pdf} \\
-     \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-koug-polar-hlght.pdf}   & \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-ttsf-polar-hlght.pdf} \\
+      \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-boav-polar-hlght.png}   & \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-cn04-polar-hlght.png} \\
+            \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-cn40-polar-hlght.png}   & \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-gre1-polar-hlght.png} \\
+     \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-koug-polar-hlght.png}   & \includegraphics[width=0.45\linewidth]{../figures/azimuth-elevation-map-ttsf-polar-hlght.png} \\
     \end{tabular}
+    \end{adjustwidth}
+    \caption{Azimuth-Elevation maps for GPS stations which presumably detected TIDs.
+In colored curves we show the satellites trajectories with their respective label, the trajectory starts at the big colored dot.
+The black dots are the meteor trajectory using the GLM data and the magenta dashed curve represent the meteor trajectory using the velocity parameters from table \ref{tab:Meteor-parameters}.}
     \label{fig:azimuth-elevations-maps-1}
-    \caption{Azimuth-Elevation maps for GPS stations which presumably detected TIDs.
-In colored curves we show the satellites trajectories with their respective label.
-The black dots are the meteor trajectory using the GLM data and the magenta dashed curve represent the meteor trajectory using the velocity parameters from table \ref{tab:Meteor-parameters}.}
 \end{figure*}
@@
 \begin{figure*}
+\begin{adjustwidth}{-\extralength}{0cm}
     \centering
     \begin{tabular}{cc}
-    \includegraphics[width=0.45\linewidth]{../figures/boav_satellites_positions_terminator_21-25-48.pdf} & \includegraphics[width=0.45\linewidth]{../figures/cn04_satellites_positions_terminator_21-25-48.pdf}\\
-    \includegraphics[width=0.45\linewidth]{../figures/cn40_satellites_positions_terminator_21-25-48.pdf} & \includegraphics[width=0.45\linewidth]{../figures/gre1_satellites_positions_terminator_21-25-48.pdf} \\
-    \includegraphics[width=0.45\linewidth]{../figures/koug_satellites_positions_terminator_21-25-48.pdf} & \includegraphics[width=0.45\linewidth]{../figures/ttsf_satellites_positions_terminator_21-25-48.pdf}
+    \includegraphics[width=0.5\linewidth]{../figures/boav_satellites_positions_terminator_21-25-48.png} & \includegraphics[width=0.5\linewidth]{../figures/cn04_satellites_positions_terminator_21-25-48.png}\\
+    \includegraphics[width=0.5\linewidth]{../figures/cn40_satellites_positions_terminator_21-25-48.png} & \includegraphics[width=0.5\linewidth]{../figures/gre1_satellites_positions_terminator_21-25-48.png} %\\
+   % \includegraphics[width=0.5\linewidth]{figures/koug_satellites_positions_terminator_21-25-48.png} & \includegraphics[width=0.5\linewidth]{figures/ttsf_satellites_positions_terminator_21-25-48.png}
     \end{tabular}
+    \end{adjustwidth}
     \caption{Position of IPP in the satellite-receiver LoS for the same GPS stations as figure \ref{fig:azimuth-elevations-maps-1}.
@@
 \end{figure*}
-
-% The mathematical proccedure to change the GLM data and the estimated trajectory, using the parameters from table \ref{tab:Meteor-parameters}. 
+%The mathematical proccedure to change the GLM data and the estimated trajectory, using the parameters from table \ref{tab:Meteor-parameters}. 
 %\subsection{Wavelet power spectrum}
